### 2017-11-14 method.rmd
adding experiment materials

---
title: "Design, Procedure, and Randomization"
author: "Masoud Jasbi"
date: ""
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

# Design

## Card Types

There are three animals in the card-game: cat, dog, and elephant. Each card may have one or two of them. I represent the card types in the following way:

| Representation | Description | Cards |
|---------|-----------|---------------------------|
|**X**| Only one animal on the card |  <img src="stimuli/oneanimal_card.jpg" width="300" height="300" /> |
|**XY**| Two animals on the card | <img src="stimuli/twoanimal_card.jpg" width="300" height="300" /> |

## Guess Types

| Representation | Description | 
|---|------------------------------------------------------------|
| **Z** | The puppet mentions an animal not on the card | 
| **X** | The puppet mentions one of the animals (perhaps the only animal) on the card |
| **XorY** | The puppet mentions both animals on the card and uses the connective "or" |
| **XandY** | The puppet mentions both animals on the card and uses the connective "and"|

## Trial Types

The combination of card types and guess types creats 12 possible trial types and 36 possible trials. We choose 8 trial types out of 12 to balance for the type of card (X vs. XY), the type of guess (with vs. without connective), and types of responses (wrong, right). We represent each trial type using the pattern "CARD-GUESS" with X, Y and Z abstracting over the specific animals:

| Representation | Example Card | Example Guess |
|---|---|------------------------|
|  **XY-XorY** | <img src="stimuli/catdog_card.jpg" width="70" height="70" /> | There is a cat **or** a dog |
| **XY-XandY** | <img src="stimuli/catdog_card.jpg" width="70" height="70" />| There is a cat **and** a dog |
| **XY-X** | <img src="stimuli/catdog_card.jpg" width="70" height="70" />| There is a cat! |
| **XY-Z** | <img src="stimuli/catdog_card.jpg" width="70" height="70" />| There is an elephantl! |
| **X-XorY** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a cat or a dog! |
| **X-XandY** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a cat and a dog! |
|  **X-X** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a cat! |
| **X-Z** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a dog! |

The table below shows all the 36 possible trials and trial types:

```{r all_trials, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(lubridate)

all_trials <-
  data.frame(
    trial_type = c(rep("XY.XorY", 3), 
                   rep("XY.XandY", 3),
                   rep("XY.X", 6),
                   rep("XY.Z",3),
                   rep("X.XorY", 6),
                   rep("X.XandY", 6),
                   rep("X.X", 3),
                   rep("X.Z", 6)
                   ),
    card = c("CAT-DOG", "CAT-ELE", "DOG-ELE", 
              "CAT-DOG", "CAT-ELE", "DOG-ELE",
              "CAT-DOG", "CAT-DOG", "CAT-ELE", "CAT-ELE", "DOG-ELE", "DOG-ELE",
              "CAT-DOG", "CAT-ELE", "DOG-ELE",
              "CAT", "DOG", "CAT", "ELE", "DOG", "ELE",
              "CAT", "DOG", "CAT", "ELE", "DOG", "ELE",
              "CAT", "DOG", "ELE",
              "CAT", "CAT", "DOG", "DOG", "ELE", "ELE"),
    guess = c("cat or dog", "cat or elephant", "dog or elephant",
              "cat and dog", "cat and elephant", "dog and elephant",
              "cat", "dog", "cat", "elephant", "dog", "elephant",
              "elephant", "dog", "cat",
              "cat or dog", "cat or dog", "cat or elephant", "cat or elephant", "dog or elephant", "dog or elephant",
              "cat and dog", "cat and dog", "cat and elephant", "cat and elephant", "dog and elephant", "dog and elephant",
              "cat", "dog", "elephant",
              "dog", "elephant", "cat", "elephant", "cat", "dog")

  )

knitr::kable(all_trials)
```

# Procedure

Three decks of cards  are prepared: 1. introduction, 2. instruction, and 3. warm-up+test.

## Introduction

The introduction deck includes six cards; one of each card type. The experimenter puts the introduction cards on the table and shows them to the child. He asks the child to name the three animals in the game using the question "what is this one?" When it is clear that the child knows the names of the animals (cat, dog, and, elephant), the experimenter proceeds to the instruction deck.

## Instruction

The experimenter puts the instruction deck on the table and explains the game to the child:

> *Jazzy likes to guess the animal on the card! But she doesn't wanna see the cards. So she is going to put this sleeping mask on her eyes [puts the sleeping mask on the puppet]. Jazzy! Do you see anythig? [puppet says no.] You can pick a card [gives a card to the child] and Jazzy is going to guess what's on it. If Jazzy is right, say "Yes!". If Jazzy is not right, say "No!" and tell Jazzy how to say it better. OK? Jazzy, can you guess what animal is on this one? [puppet guesses]*

The table below shows the order of the cards in the instruction deck, the puppet's guesses for each card, and the experimenter's responses.

| Card | Puppet's Guess |
|------|----------------|
<img src="stimuli/cat_card.jpg" width="100" height="100" /> | There is a dog |
<img src="stimuli/elephant_card.jpg" width="100" height="100" />| There is an elephant |
<img src="stimuli/dogelephant_card.jpg" width="100" height="100" />| There is a cat! |
<img src="stimuli/dog_card.jpg" width="100" height="100" />| There is a dog! |

## Warm-up + Test

When the instruction deck is done, the experimenter moves to the warm-up+test deck.

> *Here are some more cards [uses the warm-up+test deck]. Remember, if Jazzy is right, say "Yes!". If he is not right, say "No" and tell him how to say it better.*

The warm-up+test deck is arranged using the randomization procedure explained in the next section. The first two trials of this deck are arranged as warm-up. They do not contain cennectives. The next 14 trials are test trials. They include all the conjunction and disjunction trials.

# Randomization

With 8 trial types, it is reasonable to assume that children can sit through two trials per trial type: 16 trials total. Therefore we need to randomly sample 2 trials from the trial types for each participant. The code below does exactly that.

```{r randomization}
#shuffle the row orders
randomized_trials <- all_trials[sample(1:nrow(all_trials)), ]

# assign numbers to the trials, pick 2 per trial type
participant_trials <- 
  randomized_trials %>%
  group_by(trial_type) %>%
  mutate(n=row_number()) %>%
  filter(n==1 | n==2)

# Take the warmup trials and put them at the front
warmup_trials <- 
  participant_trials %>%
  filter(trial_type=="X.X" & n==1 | trial_type=="X.Z" & n==1)

# put the rest of the trials as test trials
test_trials <- 
  participant_trials %>%
  filter(trial_type!="X.X" | n!=1, trial_type!="X.Z" | n!=1)

# bind the warmup and test trials
trials <- rbind (warmup_trials, test_trials)

# add the subject id
subid <- paste(date(now()), hour(now()), minute(now()), sep="-")
trials[,"id"] <- subid

# remove column n
trials <- select(trials, -n)

write.csv(trials, paste(subid,".csv", sep=""))
knitr::kable(trials)
```

### 2018-01-18 experiments/1_methods/connective_game.js
resluts as json

@@ -304,6 +304,7 @@ var experiment = {
 
     // submitcomments function
     submit_comments: function() {
+//        console.log("done");
         experiment.data.age.push(document.getElementById("age").value);
         experiment.data.gender.push(document.getElementById("gender").value);
         experiment.data.education.push(document.getElementById("education").value);
@@ -311,7 +312,6 @@ var experiment = {
         experiment.data.expt_gen.push(document.getElementById("expcomments").value);
         experiment.data.language.push(document.getElementById("explanguage").value);
         experiment.data.user_agent.push(window.navigator.userAgent);
-        experiment.data.version.push(trial_order);
         experiment.end();
     }
 }

### 2018-01-18 experiments/3_processed_data/mturk_data_processing.Rmd
added the json to csv processing rmd

---
title: "mturk_data_processing"
author: "Masoud Jasbi"
date: "3/7/2017"
output: html_document
---

```{r cars}
library(rjson)
library(tidyverse)
```

```{r}
# read the json file names to be loaded in the json directory
files <- dir("../1_raw_data/", pattern =".json") 
# make an empty data frame to append the json data participant by participant
adult_data <- data.frame()

#loop through json files
for (file in files) {
  #read the json file into jd
  jd <- fromJSON(paste(readLines(paste("../1_raw_data/", file, sep="")), collapse=""))
  #create a data frame with the column names on the left
  id <- data_frame(participant = jd$WorkerId,
                  gender = jd$answers$data$gen,
                  age = jd$answers$data$age,
                  Lang = jd$answers$data$language,
                  version = jd$answers$data$version,
                  logical_training = jd$answers$data$education,
                  trials = jd$answers$data$trial,
                  response = jd$answers$data$response,
                  duration = jd$answers$data$elapsed_ms,
                  AgeGroup = "adult",
                  aim = jd$answers$data$expt_aim,
                  comments = jd$answers$data$expt_gen
                  )
  # append the dataframe for that json file to the big data frame 
  adult_data <- bind_rows(adult_data, id)
}

write.csv(adult_data, "../2_processed_data/adult_data.csv")
```

### 2018-01-21 experiments/3_processed_data/mturk_data_processing.Rmd
added the csv file. some participants had 25 responses

@@
 # read the json file names to be loaded in the json directory
-files <- dir("../1_raw_data/", pattern =".json") 
+files <- dir("../2_raw_data/", pattern =".json") 
 # make an empty data frame to append the json data participant by participant
@@
   #read the json file into jd
-  jd <- fromJSON(paste(readLines(paste("../1_raw_data/", file, sep="")), collapse=""))
+  jd <- fromJSON(paste(readLines(paste("../2_raw_data/", file, sep="")), collapse=""))
   #create a data frame with the column names on the left
@@
                   age = jd$answers$data$age,
-                  Lang = jd$answers$data$language,
-                  version = jd$answers$data$version,
+                  language = jd$answers$data$language,
+#                  version = jd$answers$data$version,
                   logical_training = jd$answers$data$education,
@@
                   response = jd$answers$data$response,
-                  duration = jd$answers$data$elapsed_ms,
-                  AgeGroup = "adult",
+#                  duration = jd$answers$data$elapsed_ms,
+#                  AgeGroup = "adult",
                   aim = jd$answers$data$expt_aim,
@@
 
-write.csv(adult_data, "../2_processed_data/adult_data.csv")
+write.csv(adult_data, "../3_processed_data/adult_data.csv")
 ```

### 2018-01-30 experiments/bayesian data analysis/modelcomparison_1.js
added a couple toy BDA scripts
- modelcomparison_1.js:

in the "binary choice", "animals A + B on card", "speaker says 'AorB" condition, we had 114 observations, 100 of which were "Right". Given this, what is the likelihood of our literal listener model, compared against an alternative model (in this case, the speaker model)?

In this case, P is close to 1: the speaker model does a really bad job reative to the null model of predicting the data we saw.

- parameterestimation_1.js:

estimate our rationality parameter given our speaker model and the observed data (same as above).

@@ -1,0 +1,71 @@
+var statePrior = function() {
+  return uniformDraw([["A"], ["B"], ["A","B"], ["C"], ["A","C"], ["B","C"]])
+};
+
+var utterancePrior = function() {
+  return uniformDraw(['A', 'B', 'AorB', 'AandB']);
+};
+
+var literalMeanings = {
+  A: function(state) { return state.includes("A"); },
+  B: function(state) { return state.includes("B"); },
+  AorB: function(state) { return state.includes("A") || state.includes("B"); },
+  AandB: function(state) { return state.includes("A") && state.includes("B"); },
+};
+
+var literalListener = cache(function(utt) {
+  return Infer({model: function(){
+    var state = statePrior()
+    var meaning = literalMeanings[utt]
+    condition(meaning(state))
+    return state
+  }})
+});
+
+// set speaker optimality
+var alpha = 1
+
+// pragmatic speaker
+var speaker = cache(function(state) {
+  return Infer({model: function(){
+    var utt = utterancePrior()
+    factor(alpha * literalListener(utt).score(state))
+    return utt
+  }})
+});
+
+// pragmatic listener
+var pragmaticListener = cache(function(utt) {
+  return Infer({model: function(){
+    var state = statePrior()
+    observe(speaker(state),utt)
+    return state
+  }})
+});
+
+print("speaker distribution given state where A & B true:")
+viz.hist(speaker(["A","B"]));
+
+//Bayesian data analysis. Calculate P(M^0 | D), where D = the results for how people
+//responded in the "binary" condition where they saw two animals "A" and "B" on the card
+//but the utterance under evaluation was of the form "A or B". M^0 is the literal 
+//listener model. We compare M^0 against M^1, the pragmatic speaker model described above.
+// A "success" is an answer of "Right" in this condition. 
+
+var total_observations = 114
+var observed_successes = 100
+var speaker_prob = Math.exp(speaker(["A","B"]).score('AorB'))
+
+print("probability of 'AorB' given state where A & B true: ")
+display(speaker_prob)
+
+var LH_literalLister = Math.exp(Binomial({n: total_observations, p: 0.5}).score(observed_successes))
+                                
+var LH_speaker = Math.exp(Binomial({n: total_observations, p: speaker_prob}).score(observed_successes))
+
+var posterior_literalLister = LH_literalLister / (LH_literalLister + LH_speaker)
+
+print("P(M^0 | D) (assuming uniform prior beliefs about M^0 and M^1): ")
+display(posterior_literalLister)
+
+

### 2018-01-30 experiments/1_methods/online_experiment/connective_game.js
Fixed Log Error bug
Fixed the log bug

@@ -234,14 +234,17 @@ var experiment = {
           radios[i].checked = false
         }
       } else {
-        // Slider Data Collection
-        var sliders = document.getElementsByName('slider' + choice)[0];
-        console.log(sliders)
-        experiment.data.response.push(sliders.value);
-        experiment.data.elapsed_ms.push(elapsed);
-        experiment.data.num_errors.push(experiment.num_errors);
+        if (response_logged) {
+          console.log('here')
+          // Slider Data Collection
+          var sliders = document.getElementsByName('slider' + choice)[0];
+          console.log(sliders)
+          experiment.data.response.push(sliders.value);
+          experiment.data.elapsed_ms.push(elapsed);
+          experiment.data.num_errors.push(experiment.num_errors);
 
-        sliders.value = "50";
+          sliders.value = "50";
+        }
       }
 
       // If response logged, prepare next slide, else throw error

### 2018-01-30 experiments/3_processed_data/mturk_data_processing.Rmd
added the methods explanations

@@
   id <- data_frame(participant = jd$WorkerId,
+                   order=seq(1:24),
                   gender = jd$answers$data$gen,
@@
 }
-
 write.csv(adult_data, "../3_processed_data/adult_data.csv")
 ```
+
+```{r}
+processed_data <- read.csv("../3_processed_data/adult_data_withConditions.csv")
+
+processed_data2 <-
+  processed_data %>%
+  separate(trials, c("card_type", "guess_type", "card", "guess"), sep = "_", extra = "drop")
+
+write.csv(processed_data2, "../3_processed_data/processed_data2.csv")
+
+processed_data2 %>%
+  group_by(type, card_type, guess_type) %>%
+  summarize(count=n())
+```

### 2018-01-30 experiments/1_methods/online_experiment/connective_game.js

@@ -121,49 +121,49 @@ $.urlParam = function(name){
 
 var trials = {
     // training: ["training_dog_animal","dog.jpg", "There is an animal!", "X.A"],    
-    X_X: {X_X_dog: ["X.X_dog","dog.jpg", "Bob: There is a dog!"],
-          X_X_cat: ["X.X_cat","cat.jpg", "Bob: There is a cat!"],
-          X_X_ele: ["X.X_ele","ele.jpg", "Bob: There is an elephant!"]},
+    X_X: {X_X_dog: ["X_X_DOG_dog","dog.jpg", "Bob: There is a dog!"],
+          X_X_cat: ["X_X_CAT_cat","cat.jpg", "Bob: There is a cat!"],
+          X_X_ele: ["X_X_ELE_ele","ele.jpg", "Bob: There is an elephant!"]},
     X_Z:{
-        X_Z_dog_cat: ["X_Z_dog_cat","dog.jpg", "Bob: There is a cat!"],
-        X_Z_cat_dog: ["X_Z_cat_dog","cat.jpg", "Bob: There is a dog!"],
-        X_Z_ele_cat: ["X_Z_ele_cat","ele.jpg", "Bob: There is a cat!"],
-        X_Z_dog_ele: ["X_Z_dog_ele","dog.jpg", "Bob: There is an elephant!"],
-        X_Z_cat_ele: ["X_Z_cat_ele","cat.jpg", "Bob: There is an elephant!"],
-        X_Z_ele_dog: ["X_Z_ele_dog","ele.jpg", "Bob: There is a dog!"]},
+        X_Z_dog_cat: ["X_Z_DOG_cat","dog.jpg", "Bob: There is a cat!"],
+        X_Z_cat_dog: ["X_Z_CAT_dog","cat.jpg", "Bob: There is a dog!"],
+        X_Z_ele_cat: ["X_Z_ELE_cat","ele.jpg", "Bob: There is a cat!"],
+        X_Z_dog_ele: ["X_Z_DOG_ele","dog.jpg", "Bob: There is an elephant!"],
+        X_Z_cat_ele: ["X_Z_CAT_ele","cat.jpg", "Bob: There is an elephant!"],
+        X_Z_ele_dog: ["X_Z_ELE_dog","ele.jpg", "Bob: There is a dog!"]},
     XY_XorY:{
-        XY_XorY_catdog: ["XY.XorY_catdog","catdog.jpg", "Bob: There is a cat or a dog!"],
[…]

### 2018-02-13 linkinghypotheses.Rmd
added notes on linking hypotheses
Tries to explain the intuition for taking logistic regression as the basis of a linking hypothesis. Talks briefly about the other hypotheses we've come up with thus far.

---
title: "Linking Hypotheses and SI_Paradigms"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Some preliminaries:
```{r echo=TRUE, message=FALSE}
require("rwebppl")
require("tidyverse")
require("ordinal")
```

## The problem

The RSA model of a pragmatically competent speaker is a probability distribution of possible utterances given some world state the speaker intends to communicate to a listener. We'd like to be able to link this model to the categorical responses we observe in the SI_Paradigms experiment. For the purposes of this document, I'll focus on the version of the experiment where speakers rated an utterance on a two-point scale of Right / Wrong.

##Setting up the RSA model

In the RSA model, the function S1 returns the probability of an utterance given the world state the speaker intends to communicate.

Let's imagine that a speaker is in a scenario where there are exactly three animals - X, Y, and Z - that each might be on some card. We represent all of the possible world states as an nested array, where the array ['X'] corresponds to the world state where an animal X is on the card (and no other animal is). We define a set of possible sentences a speaker might utter, assuming the speaker intends to communicate which animals are on the card. Next, we attribute meanings to those utterances. Lastly, we define the pragmatic speaker function.

```{r}
model = "
var states = [['X'], ['Y'], ['Z'], ['X','Y'], ['X','Z'], ['Y','Z'], ['X','Y','Z']];
var utterances = ['X', 'Y', 'XorY', 'XandY', 'Z','XorZ','XandZ','YorZ','YandZ','XandYandZ','XorYorZ'];

var statePrior = function() {
  return uniformDraw(states)
};

var utterancePrior = function() {
  return uniformDraw(utterances);
};

var literalMeanings = {
  X: function(state) { return state.includes('X'); },
  Y: function(state) { return state.includes('Y'); },
  Z: function(state) { return state.includes('Z'); },
  XorY: function(state) { return state.includes('X') || state.includes('Y'); },
  XandY: function(state) { return state.includes('X') && state.includes('Y'); },
  XorZ: function(state) { return state.includes('X') || state.includes('Z'); },
  XandZ: function(state) { return state.includes('X') && state.includes('Z'); },
  YorZ: function(state) { return state.includes('Y') || state.includes('Z'); },
  YandZ: function(state) { return state.includes('Y') && state.includes('Z'); },
  XorYorZ: function(state) { return state.includes('X') || state.includes('Y') || state.includes('Z'); },
  XandYandZ: function(state) { return state.includes('X') && state.includes('Y') && state.includes('Z'); },
};

var literalListener = cache(function(utt) {
  return Infer({model: function(){
    var state = statePrior()
    var meaning = literalMeanings[utt]
    condition(meaning(state))
    return state
  }})
});

// set speaker optimality
var alpha = 1;

// pragmatic speaker
var speaker = cache(function(state) {
  return Infer({model: function(){
    var utt = utterancePrior()
    factor(alpha * literalListener(utt).score(state))
    return utt
  }})
});
"
```

Sanity check: what is the probability distribution over possible utterances given world state ['X','Y']?

```{r}
code <- paste(model,"speaker(['X','Y'])",sep="\n")
webppl(code)
```

## The empirical picture

As we expect, the utterance 'XorY' (i.e. "there is an X or a Y on the card") is of substantially lower probability than utterance 'XandY'. We interpret this to mean that in our model, 'XorY' is not the optimal utterance given that a speaker is trying to communicate the world state denoted by ['X','Y'] (i.e. both X and Y are on the card).

Consider this output of the model in the context of the following empirical result of the SI_Paradigms pilot: in the condition where a participant is shown a card with two animals X and Y, people overwhelmingly find a guess of "there is an X or a Y on the card" to be Right rather than Wrong.

```{r echo=FALSE}
d <- read.csv("processed_data2.csv")
d$response <- as.factor(d$response)

agr = d %>%
  group_by(type,card_type,guess_type,response) %>%
  summarise(n = n())
ggplot(filter(agr, card_type == "XY" & guess_type == "XorY" & type == "binary"),aes(x=response,y=n))+
  geom_bar(stat = "identity", position="dodge") +
  scale_fill_grey(guide=FALSE) +
  scale_x_discrete(labels=c("0"="Wrong", "1"="Right")) +
  theme(axis.title.x = element_blank()) +
  ggtitle("Right vs. wrong responses (two animals on card, guess of 'or'):")
```

## Straw-man linking hypothesis: participants sample 'directly' from S:

Our linking hypothesis should say something about why an overwhelming majority of individuals would rate an 'XorY' guess to be Right in an ['X','Y'] world state, despite 'XorY' being a suboptimal utterance choice in this world state according to our pragmatic speaker model.

Let's first explore a linking hypothesis that makes the wrong predictions in this regard. We might hypothesize that speakers, when confronted with a world state w (i.e. the configuration of animals on the card in a given SI_Paradigms trial) and an utterance u (the guess in that trial), have access to the density that the S1 distribution assigns to the value u|w.

```{r}
commands <- "
var prob = Math.exp(speaker(['X','Y']).score('XorY'));
prob;"
code <- paste(model,commands,sep="\n")
webppl(code)
```

On this simplistic straw-man story, we might say that all that happens next is that speakers sample from a Bernoulli distribution where the probability of success is equal to S1(u|w). If that sample is a success, the utterance is rated as Right; if failure, the utterance is rated as Wrong.

```{r}
commands <- "
var prob = Math.exp(speaker(['X','Y']).score('XorY'));
sample(Bernoulli({p: prob}));
"
code <- paste(model,commands,sep = "\n")
webppl(code)
```

Obviously, this model is going to be a very poor fit for the observed data (we could confirm this easily with a binomial test). It will predict that in the vast majority of cases, participants should actually reject 'XorY' in the ['X','Y'] condition. Moreover, it's unclear how to extend this linking hypothesis to the experimental conditions in which there are more than two possible responses. Lastly, it doesn't even get the qualitative pattern of responses right for the binary-choice experiment. For example, in the conditions where there were two animals X and Y on the card, it was possible that speakers had to rate a guess of 'X or Y' or a guess of just 'X'. However, across both of these guess types, the proportion of Right responses among pilot participants is nearly identical -- despite the RSA model prediction that 'X' should be a substantially more optimal utterance than 'X or Y' in this world state. On the naive story built up so far, it is unclear as to why this would be the case.

```{r echo=FALSE}
ggplot(filter(agr, card_type == "XY" & response == "1" & type == "binary"),aes(x=guess_type,y=n))+
  geom_bar(stat = "identity", position="dodge") +
  #scale_x_discrete(labels=c("0"="Wrong", "1"="Right")) +
  theme(axis.title.x = element_blank()) +
  ggtitle("Number of participants answering 'Right' when two animals on card,\nbroken down by guess type:")
```

## A better hypothesis? The logistic function

The straw-man linking hypothesis described above was clearly inadequate. But it is a linking hypothesis: it generates predictions about categorical behavior (e.g. responses in the SI_Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5). The above hypothesis achieves this by positing that the categorical behavior of interest (answering Right/Wrong) can be understood as a probabilistic process, namely the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker proabibility of u in w as computed by the RSA model:

P("Right"|u,w) = S1(u|w)

Perhaps the straw-man hypothesis is basically correct in conceptualizing the categorical response as a probabilistic process. If we accept the basic story that the categorical response can be represented as P("Right"|u,w), then we need a way to link P("Right"|u,w) to our RSA speaker distribution S1(u|w) - with better empirical coverage than the straw-man hypothesis explored above.

One alternative would be to say that P("Right"|u,w) is a function of, but not identical to, the probability of utterance u given world state w in the S1 model. The challenge then becomes to specify this function. Logistic regression provides one possible solution. This type of regression returns a model of the log odds of some binary categorical response (e.g. "Right"/"Wrong") as a function of an independent variable (e.g. speaker probability of utterance given a world state).

Exploring this given our results file requires some data transformation. We continue to look at the subset of the SI_paradigms pilot data where response was binary "Right"/"Wrong". Now, for every row in the data (each row corresponds to one response), we add a value S1(u|w) in a new column (speaker_probability) of the data frame, where S1(u|w) is the speaker probability of u (the 'guess' presented on the screen) given w (the configuration of animals on the card).

```{r}
binary <- filter(d, type == "binary")
binary <- add_column(binary, speaker_probability = 0)

code <- paste(model,"speaker(['X','Y'])",sep="\n")
speaker_probs_xy <- webppl(code)

code <- paste(model,"speaker(['X'])",sep="\n")
speaker_probs_x <- webppl(code)

for(i in 1:nrow(binary)){
  for(j in 1:nrow(speaker_probs_xy)){
    if((as.character(speaker_probs_xy[j,]$support) == as.character(binary[i,]$guess_type)) & binary[i,]$card_type == "XY"){
      binary[i,]$speaker_probability <- speaker_probs_xy[j,]$prob
    }
  }
}

for(i in 1:nrow(binary)){
  for(j in 1:nrow(speaker_probs_x)){
    if((as.character(speaker_probs_x[j,]$support) == as.character(binary[i,]$guess_type))& binary[i,]$card_type == "X"){
      binary[i,]$speaker_probability <- speaker_probs_x[j,]$prob
    }
  }
}

```

Now, specify a logistic regression model whereby categorical response (coded as "1" or "0" in the data set) is predicted by speaker_probability.

```{r}
l <- glm(as.factor(response) ~ speaker_probability, data = binary, family = "binomial")
summary(l)
#confint(l)
```

The above model provides the log odds of responding "Right" vs. "Wrong" as a function of the speaker probability of the utterance being assessed by the participant (in a particular utterance context). It is a better model than the simple straw-man model which assumed a one-to-one correspondance between a) the probability a participant judges some utterance u to be "Right" in w and b) the probability of that utterance u in a world state w, as according to our pragmatic speaker distribution [say more? model comparison?].

### Extending the logistic regression model to other SI_Paradigms conditions, e.g. quatenary response

```{r}

quatenary <- filter(d, type == "quatenary")
quatenary <- add_column(quatenary, speaker_probability = 0)

for(i in 1:nrow(quatenary)){
  for(j in 1:nrow(speaker_probs_xy)){
    if((as.character(speaker_probs_xy[j,]$support) == as.character(quatenary[i,]$guess_type)) & quatenary[i,]$card_type == "XY"){
      quatenary[i,]$speaker_probability <- speaker_probs_xy[j,]$prob
    }
  }
}

for(i in 1:nrow(quatenary)){
  for(j in 1:nrow(speaker_probs_x)){
    if((as.character(speaker_probs_x[j,]$support) == as.character(quatenary[i,]$guess_type))& quatenary[i,]$card_type == "X"){
      quatenary[i,]$speaker_probability <- speaker_probs_x[j,]$prob
    }
  }
}

lq <- clmm2(ordered(response) ~ speaker_probability, data = quatenary,link = "logistic")
summary(lq)
#confint(lq)
```

## Another hypothesis: thresholds

Another conceivable hypothesis is that for some utterance u in world state w, u is "Right" so long as S1(u|w) exceeds some probability threshold $\theta$.

## Another hypothesis: mixing log odds + the threshold parameter

Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of S1'(u|w), where S1' is a transformation of the pragmatic speaker distribution. More specifically, S1' is a renormalized version of S1 after low-probability utterances are removed from S1 (according to some threshold of 'low' probability).

### 2018-02-13 linkinghypotheses.Rmd
edits to linking hypotheses notes

@@
 We'd like to be able to link this model to the categorical responses we observe in the SI_Paradigms experiment.
-For the purposes of this document, I'll focus on the version of the experiment where speakers rated an utterance on a two-point scale of Right / Wrong.
+For the purposes of this document, I'll focus on the version of the experiment where speakers rated an utterance on a two-point scale of "Right"/"Wrong".
 
@@
 
-Consider this output of the model in the context of the following empirical result of the SI_Paradigms pilot: in the condition where a participant is shown a card with two animals X and Y, people overwhelmingly find a guess of "there is an X or a Y on the card" to be Right rather than Wrong.
+Consider this output of the model in the context of the following empirical result of the SI_Paradigms pilot: in the condition where a participant is shown a card with two animals X and Y, people overwhelmingly find a guess of "there is an X or a Y on the card" to be "Right"" rather than "Wrong".
 
@@
 We might hypothesize that speakers, when confronted with a world state w (i.e.
-the configuration of animals on the card in a given SI_Paradigms trial) and an utterance u (the guess in that trial), have access to the density that the S1 distribution assigns to the value u|w.
+the configuration of animals on the card in a given SI_Paradigms trial) and an utterance u (the guess in that trial), have access to the probability that the S1 distribution assigns to u in w.
 
@@
 For example, in the conditions where there were two animals X and Y on the card, it was possible that speakers had to rate a guess of 'X or Y' or a guess of just 'X'.
-However, across both of these guess types, the proportion of Right responses among pilot participants is nearly identical -- despite the RSA model prediction that 'X' should be a substantially more optimal utterance than 'X or Y' in this world state.
+However, across both of these guess types, the proportion of "Right" responses among pilot participants is nearly identical -- despite the RSA model prediction that 'X' should be a substantially more optimal utterance than 'X or Y' in this world state.
 On the naive story built up so far, it is unclear as to why this would be the case.
@@
 responses in the SI_Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5).
-The above hypothesis achieves this by positing that the categorical behavior of interest (answering Right/Wrong) can be understood as a probabilistic process, namely the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker proabibility of u in w as computed by the RSA model:
+The above hypothesis achieves this by positing that the categorical behavior of interest (answering "Right"/"Wrong"") can be understood as a probabilistic process, whereby the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker proabibility of u in w as computed by the RSA model:
 
-P("Right"|u,w) = S1(u|w)
+P(Participant answers "Right"|u,w) = S1(u|w)
 
 Perhaps the straw-man hypothesis is basically correct in conceptualizing the categorical response as a probabilistic process.
-If we accept the basic story that the categorical response can be represented as P("Right"|u,w), then we need a way to link P("Right"|u,w) to our RSA speaker distribution S1(u|w) - with better empirical coverage than the straw-man hypothesis explored above.
+If we accept the basic story that the categorical response can be represented as P("Right"|u,w), then we need a way to link P("Right"|u,w) to our RSA speaker distribution S1(u|w) - in a way that gets better empirical coverage than the straw-man hypothesis explored above.
 
@@
 
-Exploring this given our results file requires some data transformation.
+Exploring this requires some transformation to our results.
 We continue to look at the subset of the SI_paradigms pilot data where response was binary "Right"/"Wrong".

### 2018-02-13 experiments/1_methods/online_experiment/connective_game.js
Masoud's Recommended Changes
- Change the bullet point labels
- Add a true-false scale
- add 5-point scale: neither right nor wrong
- remove sliders

@@ -34,9 +34,9 @@ function options() {
 function createRadioButtons() {
   choice = random(5);
   var radio = Array.from(document.getElementsByName(String(choice)))
-  if (choice == 3 || choice == 4) {
-    radio.push(document.getElementsByName('slider' + choice)[0])
-  }
+  // if (choice == 3 || choice == 4) {
+  //   radio.push(document.getElementsByName('slider' + choice)[0])
+  // }
   for (i = 0; i < radio.length; i++) {
     radio[i].style.visibility = 'visible'
   }
@@ -90,22 +90,22 @@ function randomTrials(trials){
     var vals = Object.values(trials[shuf[i]])
     var shuf2 = shuffle(vals)
     output.push(shuf2[0])
-    output.push(shuf2[1])
-    output.push(shuf2[2])
+    // output.push(shuf2[1])
+    // output.push(shuf2[2])
   }
   return shuffle(output)
 }
 
-//Track Slider! 
-document.addEventListener('DOMContentLoaded',function() {
-    document.getElementsByName('slider3')[0].onchange=changeEventHandler;
-    document.getElementsByName('slider4')[0].onchange=changeEventHandler;
-},false);
+// //Track Slider! 
+// document.addEventListener('DOMContentLoaded',function() {
+//     document.getElementsByName('slider3')[0].onchange=changeEventHandler;
+//     document.getElementsByName('slider4')[0].onchange=changeEventHandler;
+// },false);
 
 response_logged = false;
-function changeEventHandler(event) {
-    response_logged = true;
-}
+// function changeEventHandler(event) {
+//     response_logged = true;
+// }
 
 // from: http://www.sitepoint.com/url-parameters-jquery/
 $.urlParam = function(name){
@@ -213,7 +213,7 @@ var experiment = {
 // LOG FUNCTION: the function that records the responses
     log_response: function() {
       var elapsed = Date.now() - experiment.start_ms;
-      if (choice < 3) {
+      if (choice < 5) {
         // Radio Button Collection  
         var radios = [];
         var initial = document.getElementsByName(String(choice));
@@ -235,10 +235,8 @@ var experiment = {
         }
       } else {
         if (response_logged) {
-          console.log('here')
           // Slider Data Collection
           var sliders = document.getElementsByName('slider' + choice)[0];
-          console.log(sliders)
           experiment.data.response.push(sliders.value);
           experiment.data.elapsed_ms.push(elapsed);
           experiment.data.num_errors.push(experiment.num_errors);
[…]

### 2018-02-13 experiments/1_methods/online_experiment/connective_game.js
Masoud Follow Up
- Widened card
- Removed extra trials

@@ -32,7 +32,7 @@ function options() {
 
 // Randomize Radio Buttons 
 function createRadioButtons() {
-  choice = random(5);
+  choice = random(3,4);
   var radio = Array.from(document.getElementsByName(String(choice)))
   // if (choice == 3 || choice == 4) {
   //   radio.push(document.getElementsByName('slider' + choice)[0])
@@ -90,8 +90,8 @@ function randomTrials(trials){
     var vals = Object.values(trials[shuf[i]])
     var shuf2 = shuffle(vals)
     output.push(shuf2[0])
-    // output.push(shuf2[1])
-    // output.push(shuf2[2])
+    output.push(shuf2[1])
+    output.push(shuf2[2])
   }
   return shuffle(output)
 }

### 2018-02-14 experiments/pilot/1_methods/methods.rmd
reorder the folders

---
title: "Card Game Methods"
author: "Masoud Jasbi"
output: 
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

### Card Types:

There are three animals in the card-game: cat, dog, and elephant. Each card may have one or two of them. I represent the card types in the following way:

| Representation | Description | Cards |
|---------|-----------|---------------------------|
|**X**| Only one animal on the card |  <img src="stimuli/oneanimal_card.jpg" width="300" height="300" /> |
|**XY**| Two animals on the card | <img src="stimuli/twoanimal_card.jpg" width="300" height="300" /> |

## Guess Types

| Representation | Description | 
|---|------------------------------------------------------------|
| **Z** | The puppet mentions an animal not on the card | 
| **X** | The puppet mentions one of the animals (perhaps the only animal) on the card |
| **XorY** | The puppet mentions both animals on the card and uses the connective "or" |
| **XandY** | The puppet mentions both animals on the card and uses the connective "and"|

## Trial Types

The combination of card types and guess types creats 12 possible trial types and 36 possible trials. We choose 8 trial types out of 12 to balance for the type of card (X vs. XY), the type of guess (with vs. without connective), and types of responses (wrong, right). We represent each trial type using the pattern "CARD-GUESS" with X, Y and Z abstracting over the specific animals:

| Representation | Example Card | Example Guess |
|---|---|------------------------|
|  **XY-XorY** | <img src="stimuli/catdog_card.jpg" width="70" height="70" /> | There is a cat **or** a dog |
| **XY-XandY** | <img src="stimuli/catdog_card.jpg" width="70" height="70" />| There is a cat **and** a dog |
| **XY-X** | <img src="stimuli/catdog_card.jpg" width="70" height="70" />| There is a cat! |
| **XY-Z** | <img src="stimuli/catdog_card.jpg" width="70" height="70" />| There is an elephantl! |
| **X-XorY** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a cat or a dog! |
| **X-XandY** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a cat and a dog! |
|  **X-X** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a cat! |
| **X-Z** | <img src="stimuli/cat_card.jpg" width="70" height="70" />| There is a dog! |

Below, I create trial type variables that hold lists of the trials in each trial type:
```{r}
### Two animals, two correct lables with or:
XY.XorY <- list(c("CAT-DOG", "cat or dog"), c("CAT-ELE", "cat or elephant"), c("DOG-ELE", "dog or elephant"))

### Two animals, two correct lables with or: 
XY.XandY <- list(c("CAT-DOG", "cat and dog"), c("CAT-ELE", "cat and elephant"), c("DOG-ELE", "dog and elephant"))

### Two animals, one correct lable:
XY.X <- list(c("CAT-DOG", "cat"), c("CAT-DOG", "dog"), c("CAT-ELE", "cat"), c("CAT-ELE", "elephant"), c("DOG-ELE", "dog"), c("DOG-ELE", "elephant"))

### Two animals, one incorrect lable:
XY.Z <- list(c("CAT-DOG", "elephant"), c("CAT-ELE", "dog"), c("DOG-ELE", "cat"))

### One animal, two lables with or, one label correct
X.XorY <- list(c("CAT", "cat or dog"), c("DOG", "cat or dog"), c("CAT", "cat or elephant"), c("ELE", "cat or elephant"), c("DOG", "dog or elephant"), c("ELE", "dog or elephant"))

### One animal, two lables with and, one label correct
X.XandY <- list(c("CAT", "cat and dog"), c("DOG", "cat and dog"), c("CAT", "cat and elephant"), c("ELE", "cat and elephant"), c("DOG", "dog and elephant"), c("ELE", "dog and elephant"))

### one animal, one correct label:
X.X <- list(c("CAT", "cat"), c("DOG", "dog"), c("ELE", "elephant"))

### one animal, one incorrect label:
X.Z <- list(c("CAT", "dog"), c("CAT", "elephant"), c("DOG", "cat"), c("DOG", "elephant"), c("ELE", "cat"), c("ELE", "dog"))
```

### Randomization:

With 8 trial types, it is reasonable to assume that children can sit through two trials per trial type: 16 trials total. Therefore we need to randomly sample 2 trials from the trial types for each participant. Some trial types have 6 trials and some 3. For those with 6 trials I only randomize them. For those with 3, I randomize them twice and bind them to create a list of six trials. This way, each trial type has 6 randomized trials.

```{r}
XY.XorY.s <- c(sample(XY.XorY), sample(XY.XorY))
XY.XandY.s <- c(sample(XY.XandY), sample(XY.XandY))
XY.X.s <- sample(XY.X)
XY.Z.s <- c(sample(XY.Z), sample(XY.Z))
X.XorY.s <- sample(X.XorY)
X.XandY.s <- sample(X.XandY)
X.X.s <- c(sample(X.X), sample(X.X)) 
X.Z.s <- sample(X.Z)
```

Now for each trial type, I pick the first two trials for the first participant, the second two for the second, and the third two for the third.

Now there are two main bocks. Each block has

```{r}
# Taking the first and the second trial of each trial type for participant 1:
part1 <- c(
  sample(c(X.Z.s[1], X.X.s[1], XY.X.s[1])), 
  sample(c(XY.XorY.s[1], XY.XandY.s[1], XY.Z.s[1], X.XorY.s[1], X.XandY.s[1])),
  sample(c(XY.XorY.s[2], XY.XandY.s[2], XY.X.s[2], XY.Z.s[2], X.XorY.s[2], X.XandY.s[2], X.X.s[2], X.Z.s[2]))
          )
# Taking the third and the fourth trial of each trial type for participant 2:
part2 <- c(
  sample(c(X.Z.s[3], X.X.s[3], XY.X.s[3])), 
  sample(c(XY.XorY.s[3], XY.XandY.s[3], XY.Z.s[3], X.XorY.s[3], X.XandY.s[3])),
  sample(c(XY.X.s[4], XY.XorY.s[4], XY.XandY.s[4], XY.Z.s[4], X.XorY.s[4], X.XandY.s[4], X.X.s[4], X.Z.s[4]))
        )

# Taking the fifth and the sixth trial of each trial type for participant 1:
part3 <- c(
  sample(c(X.Z.s[5], X.X.s[5], XY.X.s[5])), 
  sample(c(XY.XorY.s[5], XY.XandY.s[5], XY.Z.s[5], X.XorY.s[5], X.XandY.s[5])),
  sample(c(XY.XorY.s[6], XY.XandY.s[6], XY.X.s[6], XY.Z.s[6], X.XorY.s[6], X.XandY.s[6], X.Z.s[6], X.X.s[6]))
  )
```

The code below saves randomized trials for 3 participants in the expeirment in three separate CSV files.

```{r eval=FALSE}
######### Creating the CSV files:

## File 1:
file1 <- c()
for (i in 1:16) {
   file1 <- rbind(file1, part1[[i]])
}
colnames(file1) <- c("Card", "Guess")
write.csv(file1, file="file1.csv", row.names=FALSE)

## File 2:
file2 <- c()
for (i in 1:16) {
   file2 <- rbind(file2, part2[[i]])
}

colnames(file2) <- c("Card", "Guess")
write.csv(file2, file="file2.csv", row.names=FALSE)

## File 3:
file3 <- c()
for (i in 1:16) {
   file3 <- rbind(file3, part3[[i]])
}

colnames(file3) <- c("Card", "Guess")
write.csv(file3, file="file3.csv", row.names=FALSE)
```

### Procedure:

Three decks of cards  are prepared: introduction, instruction, and warm-up+test. The introduction deck includes six cards; one of each card type.

**Introduction**

The experimenter puts the introduction cards on the table and shows them to the puppet and the child. The puppet asks about the name of the animals on the cards. The experimenter waits to see if the child can answer the puppet's questions. The experimenter can also encourage the child to answer the puppet's questions.

*Experimenter: Look! My game has a lot of cards!*
*Puppet: Ooh look at all these animals! [points to a card] what is this one? [waits for answer, points to another card] What is on this one? etc.*

When it is clear that the child knows the animals well the experimeter proceeds to the instruction deck.

**Instruction**

Then the experimenter explains the game to the puppet. Picks up the instruction deck. The instruction deck is always arranged as: CAT > ELEPHANT > CAT-DOG. The puppet guesses are: dog > elephant > cat. The experimenter responds to geusses with: "Sorry. That's not right" > "Yes! That's right" > "That's a little bit right!". After each feedback, he also explains to the child how to give feedback to the puppet.

*Now! I'm going to put the cards like this [puts the warm-up deck on the table face down]. I'm going to pick this card on the top. Can you guess what animal is on this one? What is on this card? [puppet guesses] Yes! That's right! When [puppet name] is right, you can tell her: Yes! you are right.*

**Warm-up + Test**

The warm-up+test deck is arranged according to the order of the trials in the participant csv file. When the instruction deck is done, the puppet asks to play with the child. The experimenter explains to the child:

*Here are some more cards [uses the warm-up+test deck]. Now you pick a card and Jazzy is going to guess what is on the card. If Jazzy is right, tell her "you are right"! If she is a little bit right, tell her "you are a little bit right", if she is wrong, tell her "sorry. that's not right"*

The first three trials of this deck are arranged as warm-up. They have the trial types in the instruction set but the order and animals are randomized. The warm up trials let us know how comfortable the child is with giving feedback. The next 13 trials are test trials. They include all the conjunction and disjunction trials.

### 2018-02-14 models/linking hypotheses/linkinghypotheses.rmd
reorder the folders

--- 2018-02-13 linkinghypotheses.Rmd
@@
 ---
-title: "Linking Hypotheses and SI_Paradigms"
-output: html_document
+title: "Linking Hypotheses and SI-Paradigms"
+author: "Brandon Waldon"
+output: github_document
 ---
@@
 The RSA model of a pragmatically competent speaker is a probability distribution of possible utterances given some world state the speaker intends to communicate to a listener.
-We'd like to be able to link this model to the categorical responses we observe in the SI_Paradigms experiment.
+We'd like to be able to link this model to the categorical responses we observe in the SI-Paradigms experiment.
 For the purposes of this document, I'll focus on the version of the experiment where speakers rated an utterance on a two-point scale of "Right"/"Wrong".
@@
 
-Consider this output of the model in the context of the following empirical result of the SI_Paradigms pilot: in the condition where a participant is shown a card with two animals X and Y, people overwhelmingly find a guess of "there is an X or a Y on the card" to be "Right"" rather than "Wrong".
+Consider this output of the model in the context of the following empirical result of the SI-Paradigms pilot: in the condition where a participant is shown a card with two animals X and Y, people overwhelmingly find a guess of "there is an X or a Y on the card" to be "Right"" rather than "Wrong".
 
@@
 We might hypothesize that speakers, when confronted with a world state w (i.e.
-the configuration of animals on the card in a given SI_Paradigms trial) and an utterance u (the guess in that trial), have access to the probability that the S1 distribution assigns to u in w.
+the configuration of animals on the card in a given SI-Paradigms trial) and an utterance u (the guess in that trial), have access to the probability that the S1 distribution assigns to u in w.
 
@@
 But it is a linking hypothesis: it generates predictions about categorical behavior (e.g.
-responses in the SI_Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5).
+responses in the SI-Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5).
 The above hypothesis achieves this by positing that the categorical behavior of interest (answering "Right"/"Wrong"") can be understood as a probabilistic process, whereby the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker proabibility of u in w as computed by the RSA model:
@@
 Exploring this requires some transformation to our results.
-We continue to look at the subset of the SI_paradigms pilot data where response was binary "Right"/"Wrong".
+We continue to look at the subset of the SI-paradigms pilot data where response was binary "Right"/"Wrong".
 Now, for every row in the data (each row corresponds to one response), we add a value S1(u|w) in a new column (speaker_probability) of the data frame, where S1(u|w) is the speaker probability of u (the 'guess' presented on the screen) given w (the configuration of animals on the card).
@@
 
-### Extending the logistic regression model to other SI_Paradigms conditions, e.g. quatenary response
+### Extending the logistic regression model to other SI-Paradigms conditions, e.g. quatenary response
 
@@
 
+We can enrich the pragmatic speaker model provided above to model such a function.
+First, we specify a threshold function which takes as its input a world state w and a probability threshold $\theta$ and returns only those utterances for which S1(u|w) > $\theta$ is true.
+The following model also specifies a cost function - for now, we'll keep the cost uniform on utterances.
+
+```{r}
+model_threshold = "
+var states = [['X'], ['Y'], ['Z'], ['X','Y'], ['X','Z'], ['Y','Z'], ['X','Y','Z']];
+var utterances = ['X', 'Y', 'XorY', 'XandY', 'Z','XorZ','XandZ','YorZ','YandZ','XandYandZ','XorYorZ'];
+
+var statePrior = function() {
+  return uniformDraw(states)
+};
+
+var cost = function(u) {
+  return 1
+};
+
+var utterancePrior = function() {
+  return uniformDraw(utterances);
+};
+
+var literalMeanings = {
+  X: function(state) { return state.includes('X'); },
+  Y: function(state) { return state.includes('Y'); },
+  Z: function(state) { return state.includes('Z'); },
+  XorY: function(state) { return state.includes('X') || state.includes('Y'); },
+  XandY: function(state) { return state.includes('X') && state.includes('Y'); },
+  XorZ: function(state) { return state.includes('X') || state.includes('Z'); },
+  XandZ: function(state) { return state.includes('X') && state.includes('Z'); },
+  YorZ: function(state) { return state.includes('Y') || state.includes('Z'); },
+  YandZ: function(state) { return state.includes('Y') && state.includes('Z'); },
+  XorYorZ: function(state) { return state.includes('X') || state.includes('Y') || state.includes('Z'); },
+  XandYandZ: function(state) { return state.includes('X') && state.includes('Y') && state.includes('Z'); },
+};
+
+var literalListener = cache(function(utt) {
+  return Infer({model: function(){
+    var state = statePrior()
+    var meaning = literalMeanings[utt]
+    condition(meaning(state))
+    return state
+  }})
+});
+
+// set speaker optimality
+var alpha = 1
+
+// pragmatic speaker
+var speaker = cache(function(state) {
+  return Infer({model: function(){
+    var utt = utterancePrior()
+    factor(alpha * literalListener(utt).score(state))
+    return utt
+  }})
+});
+
+// threshold function
+
+var threshold = function(state,threshold) {
+  var supported_utts_string = speaker(state).support().toString();
+  var supported_utts = supported_utts_string.split(',');
+  return filter(function(x) { return Math.exp(speaker(state).score(x)) > threshold; }, supported_utts)
+}
+"
+```
+
+Now it is possible to model the linking function of interest: we say that for any utterance u given world state w and probability threshold $\theta$, u is "Right" so long as S(u|w) exceeds $\theta$ and is "Wrong" otherwise (more precisely, the model returns "Right" so long as u is in the set of utterances returned by threshold(w,$\theta$), and "Wrong" otherwise).
+
+```{r}
+right_or_wrong <- "
+var right_or_wrong = function(utt,state,theta) {
+  if (threshold(state,theta).includes(utt)) { return 'Right'; } else { return 'Wrong'; }
+}
+"
+```
+
+Suppose the utterance of interest is 'X or Y' in the world state ['X','Y'] given a probability threshold of 0.2. Which categorical response does our model predict?
+
+```{r}
+commands <- "right_or_wrong('XorY',['X','Y'],0.2)"
+code <- paste(model_threshold,right_or_wrong,commands,sep = "\n")
+webppl(code)
+```
+
+For the experimental conditions in which more than two choices were provided, we need to specify an enriched linking function.
+For the ternary choice condition, we need a function that takes as its input an utterance, a world state, and two thresholds $\theta_1$ and $\theta_2$.
+An utterance is "Wrong" in world state w just in case S1(u|w) is less than $\theta_1$.
+It is "Right" just in case S1(u|w) > $\theta_2$.
+It is "Neither" just in case  $\theta_1$ < S1(u|w) < $\theta_2$.
+
+What if our $\theta_1$ is 0.1, and our $\theta_2$ is 0.2? What does this linking model predict a respondent will say about 'X or Y' in world state ['X','Y']?
+
+```{r}
+right_neither_wrong <- "
+var right_neither_wrong = function(utt,state,thetaone,thetatwo) {
+if (threshold(state,thetatwo).includes(utt)) { return 'Right'; }
+if (threshold(state,thetaone).includes(utt)) { return 'Neither'; } 
+else { return 'Wrong'; }
+}
+"
+
+commands <- "right_neither_wrong('XorY',['X','Y'],0.1,0.2)"
+code <- paste(model_threshold,right_neither_wrong,commands,sep = "\n")
+webppl(code)
+```
+
 ## Another hypothesis: mixing log odds + the threshold parameter
@@
 Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of S1'(u|w), where S1' is a transformation of the pragmatic speaker distribution.
-More specifically, S1' is a renormalized version of S1 after low-probability utterances are removed from S1 (according to some threshold of 'low' probability).
+More specifically, S1' is a renormalized version of S1 after low-probability utterances are filtered from S1 (according to some threshold of probability).
+
+In order to explore this hypothesis, we first need to model S1' (specified below as speaker_filtered).
+Speaker_filtered is a function of utterancePrior_filtered - an utterance prior function which takes as its input only high-probability utterances; that is, utterances for which S1(u|w) > $\theta$ is true.
+
+```{r}
+
+filter_utterances <- "
+var utterancePrior_filtered = function(state,theta) {
+  return uniformDraw(threshold(state,theta).toString().split(','));
+};
+
+var speaker_filtered = cache(function(state,theta) {
+  return Infer({model: function(){
+    var utt = utterancePrior_filtered(state,theta)
+    factor(alpha * literalListener(utt).score(state))
+    return utt
+  }})
+});
+"
+
+model_threshold_2 <- paste(model_threshold,filter_utterances,sep = "\n")
+
+```
+
+Let's explore this new S1' distribution over utterances, given a world state ['X','Y'] and that we are only interested in those utterances for which it is true that S1(u|w) > 0.12.
+
+```{r}
+commands <- "speaker_filtered(['X','Y'],0.12)"
+code <- paste(model_threshold_2, commands, sep = "\n")
+webppl(code)
+```
+
+With this model, we could revisit the logistic regression linking function explored above: the log odds of categorical response is a function of the (filtered) speaker probability of that utterance in a particular world state w and given a probability threshold $\theta$.

### 2018-02-14 models/linking hypotheses/linkinghypotheses.rmd

@@
 
-Our linking hypothesis should say something about why an overwhelming majority of individuals would rate an 'XorY' guess to be Right in an ['X','Y'] world state, despite 'XorY' being a suboptimal utterance choice in this world state according to our pragmatic speaker model.
+Our linking hypothesis should say something about why an overwhelming majority of individuals would rate an 'XorY' guess to be Right in an ['X','Y'] world state, despite 'XorY' being a sub-optimal utterance choice in this world state according to our pragmatic speaker model.
 
@@
 responses in the SI-Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5).
-The above hypothesis achieves this by positing that the categorical behavior of interest (answering "Right"/"Wrong"") can be understood as a probabilistic process, whereby the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker proabibility of u in w as computed by the RSA model:
+The above hypothesis achieves this by positing that the categorical behavior of interest (answering "Right"/"Wrong"") can be understood as a probabilistic process, whereby the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker probability of u in w as computed by the RSA model:
 
@@
 "Wrong" as a function of the speaker probability of the utterance being assessed by the participant (in a particular utterance context).
-It is a better model than the simple straw-man model which assumed a one-to-one correspondance between a) the probability a participant judges some utterance u to be "Right" in w and b) the probability of that utterance u in a world state w, as according to our pragmatic speaker distribution [say more?
+It is a better model than the simple straw-man model which assumed a one-to-one correspondence between a) the probability a participant judges some utterance u to be "Right" in w and b) the probability of that utterance u in a world state w, as according to our pragmatic speaker distribution [say more?
 model comparison?].
@@
 Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of S1'(u|w), where S1' is a transformation of the pragmatic speaker distribution.
-More specifically, S1' is a renormalized version of S1 after low-probability utterances are filtered from S1 (according to some threshold of probability).
+More specifically, S1' is a re-normalized version of S1 after low-probability utterances are filtered from S1 (according to some threshold of probability).
 
@@
 With this model, we could revisit the logistic regression linking function explored above: the log odds of categorical response is a function of the (filtered) speaker probability of that utterance in a particular world state w and given a probability threshold $\theta$.
+
+```{r}
+binary <- add_column(binary, speaker_renorm_probability = 0)
+
+commands <- "speaker_filtered(['X','Y'],0.12)"
+code <- paste(model_threshold_2,commands,sep="\n")
+speaker_renormprobs_xy <- webppl(code)
+
+commands <- "speaker_filtered(['X'],0.12)"
+code <- paste(model_threshold_2,commands,sep="\n")
+speaker_renormprobs_x <- webppl(code)
+
+for(i in 1:nrow(binary)){
+  for(j in 1:nrow(speaker_renormprobs_xy)){
+    if((as.character(speaker_renormprobs_xy[j,]$support) == as.character(binary[i,]$guess_type)) & binary[i,]$card_type == "XY"){
+      binary[i,]$speaker_renorm_probability <- speaker_renormprobs_xy[j,]$prob
+    }
+  }
+}
+
+for(i in 1:nrow(binary)){
+  for(j in 1:nrow(speaker_renormprobs_x)){
+    if((as.character(speaker_renormprobs_x[j,]$support) == as.character(binary[i,]$guess_type)) & binary[i,]$card_type == "X"){
+      binary[i,]$speaker_renorm_probability <- speaker_renormprobs_x[j,]$prob
+    }
+  }
+}
+
+l <- glm(as.factor(response) ~ speaker_renorm_probability, data = binary, family = "binomial")
+summary(l)
+
+```

### 2018-02-14 models/linking hypotheses/linkinghypotheses.rmd
made edits to linkinghypotheses file

@@
 ---
-title: "Linking Hypotheses and SI-Paradigms"
+title: "Understanding Experimental Data in the Rational Speech Act Framework"
 author: "Brandon Waldon"
@@
 
+## Background
+
+Two contributions: one empirical, one theoretical
+
+**'Sentence verification' paradigms and scalar implicature**
+
+- Lots of things can affect speakers' judgments about scalar implicature.
+
+- Pragmatic judgments change according to ``dependent measure used to probe linguistic intuitions" - e.g.
+'sentence verification' tasks, 'word probability rating' tasks, and 'sentence interpretation' tasks (Degen and Goodman 2014: 1).
+Moreover, Degen and Goodman (2014) show that some experimental paradigms are more sensitive to contextual manipulations than others.
+
+- Building off that work, we provide evidence that judgments in 'sentence verification' tasks are furthermore sensitive to the number of response options participants have when completing the task.
+
+**Understanding what is measured in 'sentence verification' paradigms**
+
+- The typical neo-Gricean way of understanding participant behavior on truth value judgment task experiments (to the extent linking hypotheses are discussed in that literature): a participant either does or does not `calculate' an implicature when presented some sentence S.
+The evaluation of the sentence S as "Right"/"Wrong", "True"/"False", "Correct"/"Incorrect" depends on whether an implicature was derived and whether or not that pragmatically enriched interpretation is actually used to verify S.
+
+- Another proposal: building off Degen and Goodman (2014), participants' behavior on these tasks can be modeled directly as a function of a Rational Speech Act model of a pragmatic speaker.
+
 ## The problem
@@
 
-##Setting up the RSA model
+## Setting up the RSA model
 
-In the RSA model, the function S1 returns the probability of an utterance given the world state the speaker intends to communicate.
+In the RSA model, the function $S_1$ returns the probability of an utterance given the world state the speaker intends to communicate.
 
@@
 We might hypothesize that speakers, when confronted with a world state w (i.e.
-the configuration of animals on the card in a given SI-Paradigms trial) and an utterance u (the guess in that trial), have access to the probability that the S1 distribution assigns to u in w.
+the configuration of animals on the card in a given SI-Paradigms trial) and an utterance u (the guess in that trial), have access to the probability that the $S_1$ distribution assigns to u in w.
 
@@
 
-On this simplistic straw-man story, we might say that all that happens next is that speakers sample from a Bernoulli distribution where the probability of success is equal to S1(u|w).
+On this simplistic straw-man story, we might say that all that happens next is that speakers sample from a Bernoulli distribution where the probability of success is equal to $S_1$(u|w).
 If that sample is a success, the utterance is rated as Right; if failure, the utterance is rated as Wrong.
@@
 
-P(Participant answers "Right"|u,w) = S1(u|w)
+P(Participant answers "Right"|u,w) = $S_1$(u|w)
 
 Perhaps the straw-man hypothesis is basically correct in conceptualizing the categorical response as a probabilistic process.
-If we accept the basic story that the categorical response can be represented as P("Right"|u,w), then we need a way to link P("Right"|u,w) to our RSA speaker distribution S1(u|w) - in a way that gets better empirical coverage than the straw-man hypothesis explored above.
+If we accept the basic story that the categorical response can be represented as P("Right"|u,w), then we need a way to link P("Right"|u,w) to our RSA speaker distribution $S_1$(u|w) - in a way that gets better empirical coverage than the straw-man hypothesis explored above.
 
-One alternative would be to say that P("Right"|u,w) is a function of, but not identical to, the probability of utterance u given world state w in the S1 model.
+One alternative would be to say that P("Right"|u,w) is a function of, but not identical to, the probability of utterance u given world state w in the $S_1$ model.
 The challenge then becomes to specify this function.
@@
 We continue to look at the subset of the SI-paradigms pilot data where response was binary "Right"/"Wrong".
-Now, for every row in the data (each row corresponds to one response), we add a value S1(u|w) in a new column (speaker_probability) of the data frame, where S1(u|w) is the speaker probability of u (the 'guess' presented on the screen) given w (the configuration of animals on the card).
+Now, for every row in the data (each row corresponds to one response), we add a value $S_1$(u|w) in a new column (speaker_probability) of the data frame, where $S_1$(u|w) is the speaker probability of u (the 'guess' presented on the screen) given w (the configuration of animals on the card).
 
@@
 
-Another conceivable hypothesis is that for some utterance u in world state w, u is "Right" so long as S1(u|w) exceeds some probability threshold $\theta$.
+Another conceivable hypothesis is that for some utterance u in world state w, u is "Right" so long as $S_1$(u|w) exceeds some probability threshold $\theta$.
 
 We can enrich the pragmatic speaker model provided above to model such a function.
-First, we specify a threshold function which takes as its input a world state w and a probability threshold $\theta$ and returns only those utterances for which S1(u|w) > $\theta$ is true.
+First, we specify a threshold function which takes as its input a world state w and a probability threshold $\theta$ and returns only those utterances for which $S_1$(u|w) > $\theta$ is true.
 The following model also specifies a cost function - for now, we'll keep the cost uniform on utterances.
@@
 For the ternary choice condition, we need a function that takes as its input an utterance, a world state, and two thresholds $\theta_1$ and $\theta_2$.
-An utterance is "Wrong" in world state w just in case S1(u|w) is less than $\theta_1$.
-It is "Right" just in case S1(u|w) > $\theta_2$.
-It is "Neither" just in case  $\theta_1$ < S1(u|w) < $\theta_2$.
+An utterance is "Wrong" in world state w just in case $S_1$(u|w) is less than $\theta_1$.
+It is "Right" just in case $S_1$(u|w) > $\theta_2$.
+It is "Neither" just in case  $\theta_1$ < $S_1$(u|w) < $\theta_2$.
 
@@
 
-Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of S1'(u|w), where S1' is a transformation of the pragmatic speaker distribution.
-More specifically, S1' is a re-normalized version of S1 after low-probability utterances are filtered from S1 (according to some threshold of probability).
+Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of $S_1$'(u|w), where $S_1$' is a transformation of the pragmatic speaker distribution.
+More specifically, $S_1$' is a re-normalized version of $S_1$ after low-probability utterances are filtered from $S_1$ (according to some threshold of probability).
 
-In order to explore this hypothesis, we first need to model S1' (specified below as speaker_filtered).
-Speaker_filtered is a function of utterancePrior_filtered - an utterance prior function which takes as its input only high-probability utterances; that is, utterances for which S1(u|w) > $\theta$ is true.
+In order to explore this hypothesis, we first need to model $S_1$' (specified below as speaker_filtered).
+Speaker_filtered is a function of utterancePrior_filtered - an utterance prior function which takes as its input only high-probability utterances; that is, utterances for which $S_1$(u|w) > $\theta$ is true.
 
@@
 
-Let's explore this new S1' distribution over utterances, given a world state ['X','Y'] and that we are only interested in those utterances for which it is true that S1(u|w) > 0.12.
+Let's explore this new $S_1$' distribution over utterances, given a world state ['X','Y'] and that we are only interested in those utterances for which it is true that $S_1$(u|w) > 0.12.
 
@@
 
-With this model, we could revisit the logistic regression linking function explored above: the log odds of categorical response is a function of the (filtered) speaker probability of that utterance in a particular world state w and given a probability threshold $\theta$.
+With this model, we could revisit the logistic regression linking function explored above: the log odds of categorical response is a function of the (filtered) speaker probability of that utterance in a particular world state w and given a probability threshold $\theta$ (in the example below, $\theta$ is 0.12 - a totally arbitrary value).
 

### 2018-02-22 experiments/pilot/1_methods/online_experiment/connective_game.js
Tracking Question Type
Added functionality for better tracking of question type.
Writes to new response element called “type”

@@ -32,7 +32,7 @@ function options() {
 
 // Randomize Radio Buttons 
 function createRadioButtons() {
-  choice = random(3,4);
+  choice = [1,5].random();
   var radio = Array.from(document.getElementsByName(String(choice)))
   // if (choice == 3 || choice == 4) {
   //   radio.push(document.getElementsByName('slider' + choice)[0])
@@ -90,8 +90,8 @@ function randomTrials(trials){
     var vals = Object.values(trials[shuf[i]])
     var shuf2 = shuffle(vals)
     output.push(shuf2[0])
-    output.push(shuf2[1])
-    output.push(shuf2[2])
+    // output.push(shuf2[1])
+    // output.push(shuf2[2])
   }
   return shuffle(output)
 }
@@ -185,6 +185,7 @@ var experiment = {
         gender: [],
         education: [],
         version: [],
+        type: [], 
         trial: [], // what trial/video was presented to the participant
         response: [], // response
         feedback: [], // their linguistic feedback
@@ -213,7 +214,7 @@ var experiment = {
 // LOG FUNCTION: the function that records the responses
     log_response: function() {
       var elapsed = Date.now() - experiment.start_ms;
-      if (choice < 5) {
+      if (choice < 6) {
         // Radio Button Collection  
         var radios = [];
         var initial = document.getElementsByName(String(choice));
@@ -223,6 +224,7 @@ var experiment = {
         // Loop through Radio Buttons and collect data
         for (i = 0; i < radios.length; i++) {
           if (radios[i].checked) {
+            experiment.data.type.push(choice);
             experiment.data.response.push(radios[i].value);
             experiment.data.elapsed_ms.push(elapsed);
             experiment.data.num_errors.push(experiment.num_errors);
@@ -237,6 +239,7 @@ var experiment = {
         if (response_logged) {
           // Slider Data Collection
           var sliders = document.getElementsByName('slider' + choice)[0];
+          experiment.data.type.push(choice);
           experiment.data.response.push(sliders.value);
           experiment.data.elapsed_ms.push(elapsed);
           experiment.data.num_errors.push(experiment.num_errors);

### 2018-02-23 experiments/pilot/1_methods/online_experiment/connective_game.js
Restructure Output
Restructured output

@@ -181,19 +181,24 @@ var experiment = {
 
 // DATA: The data structure that records the responses to be sent to mTurk
     data: {
-        age: [],
-        gender: [],
-        education: [],
-        version: [],
-        type: [], 
-        trial: [], // what trial/video was presented to the participant
-        response: [], // response
-        feedback: [], // their linguistic feedback
-        elapsed_ms: [], // time taken to provide an answer
-        num_errors: [], // number of times participant attempted to go to the next slide without providing an answer
-        expt_aim: [], // participant's comments on the aim of the study
-        expt_gen: [], // participant's general comments
-        language: [], // what is the native language of the participant
+        // Participant Worker ID
+        gender: [],           // gender of participant
+        age: [],              // age
+        language: [],         // what is the native language of the participant
+        logical_training: [], // what is the participant's experience with formal logic
+        trial_type: [],       // X_XorY
+        card_type: [],        // X
+        guess_type: [],       // XorY
+        card: [],             // Actual card
+        guess: [],            // Actual Guess
+        response: [],         // Response
+        response_type: [],    // Response Type
+        aim: [],              // participant's comments on the aim of the study
+        comments: [],          // participant's general comments
+
+        elapsed_ms: [],       // time taken to provide an answer
+        num_errors: [],       // number of times participant attempted to go to the next slide without providing an answer     
+        
         user_agent: [],
         window_width: [],
         window_height: [],
@@ -214,6 +219,7 @@ var experiment = {
 // LOG FUNCTION: the function that records the responses
     log_response: function() {
       var elapsed = Date.now() - experiment.start_ms;
+      var response_types = ['','true-false','binary','tertiary','quatenary','quinary']
       if (choice < 6) {
         // Radio Button Collection  
         var radios = [];
@@ -224,7 +230,7 @@ var experiment = {
         // Loop through Radio Buttons and collect data
         for (i = 0; i < radios.length; i++) {
           if (radios[i].checked) {
-            experiment.data.type.push(choice);
+            experiment.data.response_type.push(response_types[choice]);
             experiment.data.response.push(radios[i].value);
             experiment.data.elapsed_ms.push(elapsed);
             experiment.data.num_errors.push(experiment.num_errors);
@@ -293,8 +299,12 @@ var experiment = {
           $("#guess").text(current_trial[2]);
 
           // push all relevant variables into data object
-          experiment.data.trial.push(current_trial[0]);
[…]

### 2018-02-23 experiments/pilot/3_processed_data/processed_data_processing.Rmd
before pulling the final website changes

---
title: "mturk_data_processing"
author: "Masoud Jasbi"
date: "3/7/2017"
output: html_document
---

```{r cars}
library(tidyverse)
```

```{r}
data <- read.csv("adult_data_withConditions.csv")

data[data$type=="binary" & data$response==0,]$response <- "wrong"
data[data$type=="binary" & data$response==1,]$response <- "right"

data[data$type=="ternary" & data$response==0,]$response <- "wrong"
data[data$type=="ternary" & data$response==1,]$response <- "right"
data[data$type=="ternary" & data$response==2,]$response <- "neiter"

data[data$type=="quatenary" & data$response==0,]$response <- "wrong"
data[data$type=="quatenary" & data$response==1,]$response <- "kinda wrong"
data[data$type=="quatenary" & data$response==2,]$response <- "kinda right"
data[data$type=="quatenary" & data$response==3,]$response <- "right"

final_data <- 
  data %>% 
  filter(type!="slider") %>% 
  separate(trials, into = c("card_type", "guess_type", "card", "guess"), sep = "_") %>%
  unite(trial_type, card_type, guess_type, remove = FALSE) %>%
  rename(response_type = "type")

write.csv(final_data, "guessingGame_data.csv", row.names = FALSE)
```

### 2018-02-23 writeup.Rmd
before pulling the final website changes

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Second Author"
    affiliation   : "1"
  - name          : "Third Author"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Stanford University"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(lme4)
library(ggthemes)
library(forcats)
library(brms)
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

# Introduction

# Background

* discussing the ways people in tha past have measured the "implicature rate".

# Methods

```{r importData, warning=FALSE, echo=FALSE}
data <- read_csv("experiments/pilot/3_processed_data/guessingGame_data.csv")

# define an implicature column for the ad-hoc and implicature trials
pragmatic_trials <- 
  data %>%
  filter(trial_type == "XY_XorY" | trial_type=="XY_X")

# adding a column that defines pragmatic vs. literal
pragmatic_trials$implicature<-1
pragmatic_trials[pragmatic_trials$response=="right",]$implicature <-0

# chaing trial type names to adhoc vs. scalar
pragmatic_trials$trial_type <-fct_recode(pragmatic_trials$trial_type, 
                                         adhoc = "XY_X", scalar = "XY_XorY")
```

* data exclusion? we don't expect any.

## Participants

* how are we choosing the sample size?

## Materials and Design

```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3, fig.height=1.5, set.cap.width=T, num.cols.cap=1, fig.width=1.5,fig.cap = "Cards used in the connective guessing game."}
cards_img <- jpeg::readJPEG("experiments/figs/cards.jpg")
grid::grid.raster(cards_img)
```

* Manipulations: type of card and the type of guess.

The study included six cards with cartoon images of a cat, a dog, and an elephant (Figure \@ref(fig:stimuli)). The study was designed based on the type of cards participants saw and the type of guesses they heard. There were two types of cards: cards with only one animal on them and the ones with two animals. There were three types of guesses: simple (e.g. *There is a cat*), conjunctive (e.g. *There is a cat and a dog*), and disjunctive (e.g. *There is a cat or a dog*). In each guess, the animal labels used in the guess and the animal images on the card may have no overlap (e.g. Image: dog, Guess: *There is a cat or an elephant*), a partial overlap (e.g. Image: Cat, Guess: *There is a cat or an elephant*), or a total overlap (e.g. Image: cat and elephant, Guess: *There is a cat or an elephant*). Crossing the number of animals on the card, the type of guess, and the overlap between the guess and the card results in 12 different possible trial types. We chose 8 trial types (Figure \@ref(fig:trials)), balancing the number of one-animal vs. two-animal cards, simple vs. connective guesses, and expected true vs. false trials.

* The study used five different types of measurements. 1. two-options (true vs. false) 2. two-options (wrong vs. right) 3. three-options (wrong, neither, right) 4. four-options (wrong, kinda wrong, kinda right, right) 5. five-options (wrong, kinda wrong, neither, kinda right).

```{r trials, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.width=1.5, fig.cap = "Trial types represented by example cards and guesses."}
trials_img <- jpeg::readJPEG("experiments/figs/trialTypes.jpg")
grid::grid.raster(trials_img)
```

## Procedure

You can access and view the online study using [the following link]().

## Pre-registered Analysis

<!-- changes in the experiment
 - record the response type as response_type
 - record trial type, separate from the card itself and what was said: trial_type, card_type, guess_type, card, guess

-->

<!--We used `r cite_r("r-references.bib")` for all our analyses.-->

* Define implicature rate:

This study set out to test two hypotheses. First, that the proportion of pragmatic vs. literal responses in a truth values judgement task changes based on the number of response options available to the participants. We test this hypothesis formally using a binomial mixed effects model with the fixed effect of response type and the random intercept for participants as well as random intercept and slope for

Second, ...

# Results

```{r}
results<-
  data %>%
  group_by(response_type, trial_type, response) %>%
  summarize(counts = n()) %>%
  group_by(trial_type, response_type) %>%
  mutate(total = sum(counts), proportion = counts/total)
```

```{r}
ggplot(results, aes(x=response,y=proportion)) +
  geom_bar(stat="identity") +
  facet_grid(response_type~trial_type, drop = TRUE) +
  theme_few()
```

# Analysis

```{r}

implicature_analysis <- glmer(implicature ~ response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=pragmatic_trials)

implicature_analysis <- brm(implicature ~ response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=pragmatic_trials)

```

# Modeling

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2018-02-23 writeup.tex
before pulling the final website changes

\documentclass[man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%

% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={The title},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

 % Line numbering
  \usepackage{lineno}
  \linenumbers

\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{The title}

  \shorttitle{Title}

  \author{First Author\textsuperscript{1}, Second Author\textsuperscript{1}, \& Third Author\textsuperscript{1}}

  % \def\affdep{{"", "", ""}}%
  % \def\affcity{{"", "", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Stanford University  }

  \authornote{
    Add complete departmental affiliations for each author here. Each new
    line herein must be indented, like this line.

    Enter author note here.

    Correspondence concerning this article should be addressed to First
    Author, Postal address. E-mail:
    \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
  }

  \abstract{Enter abstract here. Each new line herein must be indented, like this
line.}
  \keywords{keywords \\

    \indent Word count: X
  }

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}

\section{Introduction}\label{introduction}

\section{Background}\label{background}

\begin{itemize}
\tightlist
\item
  discussing the ways people in tha past have measured the
  \enquote{implicature rate}.
\end{itemize}

\section{Methods}\label{methods}

\begin{itemize}
\tightlist
\item
  data exclusion? we don't expect any.
\end{itemize}

\subsection{Participants}\label{participants}

\begin{itemize}
\tightlist
\item
  how are we choosing the sample size?
\end{itemize}

\subsection{Materials and Design}\label{materials-and-design}

\begin{figure}[t]

{\centering \includegraphics{writeup_files/figure-latex/stimuli-1}

}

\caption{Cards used in the connective guessing game.}\label{fig:stimuli}
\end{figure}

\begin{itemize}
\tightlist
\item
  Manipulations: type of card and the type ofgue
\end{itemize}

The study included six cards with cartoon images of a cat, a dog, and an
elephant (Figure \ref{fig:stimuli}). The study was designed based on the
type of cards participants saw and the type of guesses they heard. There
were two types of cards: cards with only one animal on them and the ones
with two animals. There were three types of guesses: simple (e.g.
\emph{There is a cat}), conjunctive (e.g. \emph{There is a cat and a
dog}), and disjunctive (e.g. \emph{There is a cat or a dog}). In each
guess, the animal labels used in the guess and the animal images on the
card may have no overlap (e.g.~Image: dog, Guess: \emph{There is a cat
or an elephant}), a partial overlap (e.g.~Image: Cat, Guess: \emph{There
is a cat or an elephant}), or a total overlap (e.g.~Image: cat and
elephant, Guess: \emph{There is a cat or an elephant}). Crossing the
number of animals on the card, the type of guess, and the overlap
between the guess and the card results in 12 different possible trial
types. We chose 8 trial types (Figure \ref{fig:trials}), balancing the
number of one-animal vs.~two-animal cards, simple vs.~connective
guesses, and expected true vs.~false trials.

\begin{itemize}
\tightlist
\item
  The study used five different types of measurements. 1. two-options
  (true vs.~false) 2. two-options (wrong vs.~right) 3. three-options
  (wrong, neither, right) 4. four-options (wrong, kinda wrong, kinda
  right, right) 5. five-options (wrong, kinda wrong, neither, kinda
  right).
\end{itemize}

\begin{figure}[t]

{\centering \includegraphics{writeup_files/figure-latex/trials-1}

}

\caption{Trial types represented by example cards and guesses.}\label{fig:trials}
\end{figure}

\subsection{Procedure}\label{procedure}

\subsection{Pre-registered Analysis}\label{pre-registered-analysis}

This study set out to test the hypothesis that the proportion of
pragmatic vs.~literal responses in a truth values judgement task changes
based on the number of response options available to the participants.
We test this hypothesis formally using a binomial mixed effects model
with the fixed effect of blah and the random effects of blah.

\begin{verbatim}
## implicature_rate ~ response_type + (1 + response_type | tiral_type) + 
##     (1 | participant)
\end{verbatim}

\section{Results}\label{results}

\section{Analysis}\label{analysis}

\section{Modeling}\label{modeling}

\section{Discussion}\label{discussion}

\newpage

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\end{document}

### 2018-02-23 writeup.Rmd
initial writup

@@
 
+* In a truth-value judgment task, how do we know whether an interpretation is literal or the result of an implicature computation?
+
+Traditional Linking Hypotheses:
+* If an implicature is calculated, the participant chooses a Non-True/Right response
+* If an implicature is calculated, the participant chooses the Wrong/False response
+* If an implicature is calculated, the participant chooses the lower end of the scale (2: wrong/False, 3: wrong, 4: wrong/kinda-wrong, 5: wrong/kinda-wrong)
+
+Questions:
+* Do these linking hypotheses give us different measures of implicature computation?
+* If they do differ, which one is most stable?
+
+Alternative Linking Hypothesis:
+* RSA: Response behavior across conditions (utterance-card combinations) and dependent measures can be predicted by a linking hypothesis that assumes that participants are behaving like soft-optimal RSA speakers and provide a particular response (eg TRUE) to an utterance u if the RSA speaker probability of u (given the card) is within a particular probability interval (eg, within the interval [theta, 1]).
+
+* Differences between traditional approaches and RSA: 1.
+The traditional linking hypotheses are based on a binary implicature/literal theory of pragmatic reasoning but RSA gives a continuous measure of pragmatic reasoning and allows for better predicting response behavior with multiple options.
+
 # Background
@@
 * discussing the ways people in tha past have measured the "implicature rate".
+* it seems like the literature takes the n(not-True)/n(Total) as the proporition of responses caused by implicature calculation
+* BUT, I remember that Jesse Snedeker said it's NOT n(not-True)/n(Total) but it is n(False)/n(Total)
+* However, this is probably not a consensus in the field because Katsos & Bishop consider the mid-point response "big" on the scale small-big-huge (strawberry) to be the result of implicture caculation
+
+* what is the most common measure of "implicature rate" in the literature?
+Binary True/False: Noveck 2001, 
+Ternary: Katsos & Bishop 2011
 
@@
 
-* data exclusion? we don't expect any.
+* No data will be excluded.
 
@@
 
-* how are we choosing the sample size?
+* how are we choosing the sample size? We went for a 20 per cell number. based on?
 

### 2018-02-24 experiments/pilot/1_methods/methods.rmd
pilot 2 data

@@
 ```
-
-### Procedure:
-
-Three decks of cards  are prepared: introduction, instruction, and warm-up+test. The introduction deck includes six cards; one of each card type.
-
-**Introduction**
-
-The experimenter puts the introduction cards on the table and shows them to the puppet and the child.
-The puppet asks about the name of the animals on the cards.
-The experimenter waits to see if the child can answer the puppet's questions.
-The experimenter can also encourage the child to answer the puppet's questions.
-
-*Experimenter: Look! My game has a lot of cards!*
-*Puppet: Ooh look at all these animals! [points to a card] what is this one? [waits for answer, points to another card] What is on this one? etc.*
-
-When it is clear that the child knows the animals well the experimeter proceeds to the instruction deck.
-
-**Instruction**
-
-Then the experimenter explains the game to the puppet.
-Picks up the instruction deck.
-The instruction deck is always arranged as: CAT > ELEPHANT > CAT-DOG.
-The puppet guesses are: dog > elephant > cat.
-The experimenter responds to geusses with: "Sorry.
-That's not right" > "Yes!
-That's right" > "That's a little bit right!".
-After each feedback, he also explains to the child how to give feedback to the puppet.
-
-*Now!
-I'm going to put the cards like this [puts the warm-up deck on the table face down].
-I'm going to pick this card on the top.
-Can you guess what animal is on this one?
-What is on this card?
-[puppet guesses] Yes!
-That's right!
-When [puppet name] is right, you can tell her: Yes!
-you are right.*
-
-**Warm-up + Test**
-
-The warm-up+test deck is arranged according to the order of the trials in the participant csv file.
-When the instruction deck is done, the puppet asks to play with the child.
-The experimenter explains to the child:
-
-*Here are some more cards [uses the warm-up+test deck].
-Now you pick a card and Jazzy is going to guess what is on the card.
-If Jazzy is right, tell her "you are right"!
-If she is a little bit right, tell her "you are a little bit right", if she is wrong, tell her "sorry.
-that's not right"*
-
-The first three trials of this deck are arranged as warm-up.
-They have the trial types in the instruction set but the order and animals are randomized.
-The warm up trials let us know how comfortable the child is with giving feedback.
-The next 13 trials are test trials.
-They include all the conjunction and disjunction trials.

### 2018-02-24 experiments/pilot/3_processed_data/mturk_data_processing.Rmd
pilot 2 data

---
title: "mturk_data_processing"
author: "Masoud Jasbi"
date: "3/7/2017"
output: html_document
---

```{r cars}
library(rjson)
library(tidyverse)
```

```{r}
# read the json file names to be loaded in the json directory
files <- dir("../2_raw_data/round2/", pattern =".json") 
# make an empty data frame to append the json data participant by participant
adult_data <- data.frame()

#loop through json files
for (file in files) {
  #read the json file into jd
  jd <- fromJSON(paste(readLines(paste("../2_raw_data/round2/", file, sep="")), collapse=""))
  #create a data frame with the column names on the left
  id <- data_frame(participant = jd$WorkerId,
                   order=seq(1:24),
                  gender = jd$answers$data$gen,
                  age = jd$answers$data$age,
                  language = jd$answers$data$language,
                  trial_type = jd$answers$data$trial_type,
                  response_type = jd$answers$data$response_type,
                  guess_type = jd$answers$data$guess_type,
                  guess = jd$answers$data$guess,
                  card_type = jd$answers$data$card_type,
                  card = jd$answers$data$card,
                  logical_training = jd$answers$data$logical_training,
                  response = jd$answers$data$response,
                  duration = jd$answers$data$elapsed_ms,
                  aim = jd$answers$data$aim,
                  comments = jd$answers$data$comments
                  )
  # append the dataframe for that json file to the big data frame 
  adult_data <- bind_rows(adult_data, id)
}
write.csv(adult_data, "../3_processed_data/pilot2_data.csv")
```

```{r}
#processed_data <- read.csv("../3_processed_data/adult_data_withConditions.csv")

#processed_data2 <-
#  processed_data %>%
#  separate(trials, c("card_type", "guess_type", "card", "guess"), sep = "_", extra = "drop")

#write.csv(processed_data2, "../3_processed_data/processed_data2.csv")

#processed_data2 %>%
#  group_by(type, card_type, guess_type) %>%
#  summarize(count=n())
```

### 2018-02-24 experiments/pilot/1_methods/online_experiment/connective_game.js

@@ -90,8 +90,8 @@ function randomTrials(trials){
     var vals = Object.values(trials[shuf[i]])
     var shuf2 = shuffle(vals)
     output.push(shuf2[0])
-    // output.push(shuf2[1])
-    // output.push(shuf2[2])
+    output.push(shuf2[1])
+    output.push(shuf2[2])
   }
   return shuffle(output)
 }

### 2018-04-07 writeup.Rmd
pilot 2 data
pilot data and prereg

@@
 
+Explain the setup
+* the speaker produces weaker alternative from the scale
+* the facts are such that the stronger alternative is true
+
 Traditional Linking Hypotheses:
-* If an implicature is calculated, the participant chooses a Non-True/Right response
+* If an implicature is calculated, the participant chooses a Non-True/Non-Right response
 * If an implicature is calculated, the participant chooses the Wrong/False response
@@
 * what is the most common measure of "implicature rate" in the literature?
-Binary True/False: Noveck 2001, 
+Binary True/False: Noveck 2001, Chemla & Spector 2011, 
 Ternary: Katsos & Bishop 2011
@@
 ```{r importData, warning=FALSE, echo=FALSE}
-data <- read_csv("experiments/pilot/3_processed_data/guessingGame_data.csv")
+data <- read_csv("experiments/pilot/3_processed_data/pilot_data.csv")
+data$response <- pilot_data$response %>% tolower()
 
@@
 # adding a column that defines pragmatic vs. literal
-pragmatic_trials$implicature<-1
-pragmatic_trials[pragmatic_trials$response=="right",]$implicature <-0
 
-# chaing trial type names to adhoc vs. scalar
-pragmatic_trials$trial_type <-fct_recode(pragmatic_trials$trial_type, 
+# high definition only considers the highest point on the scale as "literal"
+pragmatic_trials$high<-1
+pragmatic_trials[pragmatic_trials$response=="right" | pragmatic_trials$response=="true",]$high <-0
+
+# low definition only considers the lowers point on the scale as implicature 
+pragmatic_trials$low<-0
+pragmatic_trials[pragmatic_trials$response=="wrong" | pragmatic_trials$response=="false",]$low <-1
+
+implicature_rate <- 
+  pragmatic_trials %>% gather("definition","implicature", high:low)
+
+# changing trial type names to adhoc vs. scalar
+implicature_rate$trial_type <-fct_recode(pragmatic_trials$trial_type, 
                                          adhoc = "XY_X", scalar = "XY_XorY")
@@
 
-* how are we choosing the sample size? We went for a 20 per cell number. based on?
+100 participants (20 per condition) were recruited using Amazon Mechanical Turk.
 
-## Materials and Design
+## Procedure
+
+The study was administered online and through Amazon Mechanical Turk.
+Participants were introduced to a set of cards with pictures of one or two animals (Figure \@ref(fig:stimuli)).
+They were told that a blindfolded fictional character called Bob is going to guess what animals are on the card.
+In each trial, participants saw a card as well as a sentence representing Bob's guess.
+For example they saw a card with a cat on it and read the sentence "there is a cat on the card." The study ended after 24 trials.
+At the end participants were asked about their
+You can access and view [the online study here]().
+
+## Design and Materials
 
@@
 
-* Manipulations: type of card and the type of guess.
-
-The study included six cards with cartoon images of a cat, a dog, and an elephant (Figure \@ref(fig:stimuli)).
-The study was designed based on the type of cards participants saw and the type of guesses they heard.
-There were two types of cards: cards with only one animal on them and the ones with two animals.
-There were three types of guesses: simple (e.g.
+The design had two main manipulaitons: the type of card and the type of guess.
+There were two types of cards.
+Cards with only one animal on them and cards with two animals.
+Animals were chosen from the following set: cat, dog, and elephant  There were three types of guesses: simple (e.g.
 *There is a cat*), conjunctive (e.g.
@@
 *There is a cat or a dog*).
-In each guess, the animal labels used in the guess and the animal images on the card may have no overlap (e.g.
+
+In each trial, the animal labels used in the guess and the animal images on the card may have no overlap (e.g.
 Image: dog, Guess: *There is a cat or an elephant*), a partial overlap (e.g.
@@
 four-options (wrong, kinda wrong, kinda right, right) 5.
-five-options (wrong, kinda wrong, neither, kinda right).
+five-options (wrong, kinda wrong, neither, kinda right, right).
 
@@
 
-## Procedure
-
-You can access and view the online study using [the following link]().
-
 ## Pre-registered Analysis
-
-<!-- changes in the experiment
- - record the response type as response_type
- - record trial type, separate from the card itself and what was said: trial_type, card_type, guess_type, card, guess
-
--->
 
@@
 
-* Define implicature rate:
+We are primarily concerned with the rate of implicatures in an experimental study.
+Two trial types are predicted to include pragmatic implicatures.
+First, trials where there are two animals on the card but the fictional character guesses using the connective *or*; for example "cat or dog" when the card has both a cat and a dog on it.
+We call such trials "scalar" trials.
+Second, trials where there are two animals on the card but the character guesses only one; for example "cat" when the card has a cat and a dog on it.
+We call such trials "exhaustive".
+In our assessment of implicature rate we focus on these two types of trials.
+
+We define "implicature rate" in two ways:
 
@@
 
+```{r implicatureResultss}
+implicature_results<-
+  implicature_rate %>%
+  group_by(response_type, trial_type, implicature, definition) %>%
+  summarize(counts = n()) %>%
+  group_by(response_type, trial_type, definition) %>%
+  mutate(total = sum(counts), proportion = counts/total)
+```
+
 ```{r}
+ggplot(implicature_results, aes(x=as.factor(implicature),y=proportion)) +
+  geom_bar(stat="identity", position = "dodge") +
+  facet_grid(response_type~definition + trial_type, drop = TRUE) +
+  theme_few() + 
+  labs(x="Implicature")
+```
 
-implicature_analysis <- glmer(implicature ~ response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=pragmatic_trials)
+```{r}
+implicature_analysis_a <- glmer(implicature ~ definition * response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
 
-implicature_analysis <- brm(implicature ~ response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=pragmatic_trials)
+summary(implicature_analysis)
 
+implicature_analysis_b <- brm(implicature ~ definition * response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
 ```

### 2018-04-08 writeup.Rmd
binary plot

@@
 shorttitle        : "Title"
+author:
 
-author: 
   - name          : "First Author"
@@
     affiliation   : "1"
-
 affiliation:
@@
     institution   : "Stanford University"
-
 author_note: |
   Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
   Enter author note here.
-
 abstract: |
@@
 wordcount         : "X"
-
 bibliography      : ["r-references.bib"]
-
 figsintext        : no
@@
 mask              : no
-
 class             : "man"
 output            : papaja::apa6_pdf
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```{r load_packages, include = FALSE}
+library(grid)
+library(gtable)
 library(papaja)
@@
 library(png)
+library(jpeg)
 library(lme4)
@@
 
-# changing trial type names to adhoc vs. scalar
+# changing trial type names to exhaustive vs. scalar
 implicature_rate$trial_type <-fct_recode(pragmatic_trials$trial_type, 
-                                         adhoc = "XY_X", scalar = "XY_XorY")
+                                         exhaustive = "XY_X", scalar = "XY_XorY")
 ```
-
-* No data will be excluded.
 
@@
 
-100 participants (20 per condition) were recruited using Amazon Mechanical Turk.
+100 participants (20 per condition) were recruited using Amazon Mechanical Turk. No participant was excluded from the final analysis.
 
@@
 
-* The study used five different types of measurements.
+The study used five different types of measurements.
 1.
@@
 
-We are primarily concerned with the rate of implicatures in an experimental study.
+We are primarily concerned with the "rate of implicatures" in an experimental study.
 Two trial types are predicted to include pragmatic implicatures.
@@
 
-Second, ...
+A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.
 
 # Results
+
+```{r binaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' two-alternative forced choice judgments in the connective guessing game."}
+
+binary_summary<-
+  data %>%
+  filter(response_type=="binary") %>%
+  group_by(card_type, guess_type, response) %>%
+  summarize(count=n()) %>%
+  group_by(card_type, guess_type) %>%
+  mutate(total = sum(count), proportion=count/total)
+
+binary_summary$response <- factor(binary_summary$response, levels = c("wrong","right"))
+binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
+binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+
+binary_plot<-
+  binary_summary %>%
+  ggplot(aes(x=response, y=proportion, fill=response)) +
+  geom_bar(stat = "identity", position="dodge", width = 0.6) +
+#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
+  facet_grid(card_type~guess_type) +
+  labs(x="", y="")+
+  theme_few() +
+  theme(text = element_text(size=17)) +
+  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)
+
+cat <- 
+  readJPEG("experiments/figs/cat_card.jpg") %>%
+  rasterGrob(width=0.9)
+
+cat_dog <- 
+  readJPEG("experiments/figs/catdog_card.jpg")%>%
+  rasterGrob(width=0.9)
+
+binary_plot_g <- ggplot_gtable(ggplot_build(binary_plot))
+
+strips <- grep("strip-r", binary_plot_g$layout$name)
+
+new_grobs <- list(cat, cat_dog)
+
+binary_plot_g <- with(binary_plot_g$layout[strips,],
+          gtable_add_grob(binary_plot_g, new_grobs,
+                          t=t, l=l, b=b, r=r, name="cards"))        
+binary_plot_g$widths[[11]] <- unit(2.5,"cm")
+
+grid.draw(binary_plot_g)
+```
 
@@
 ```{r}
-implicature_analysis_a <- glmer(implicature ~ definition * response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
+implicature_rate$card <- implicature_rate$card %>% tolower()
+
+implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)
 
@@
 
-implicature_analysis_b <- brm(implicature ~ definition * response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
+implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
 ```

### 2018-04-08 experiments/main/1_methods/online_experiment/connective_game.js
Changed File System
Created main experiment folder and removed redundant folders

@@ -1,0 +1,347 @@
+// ############################## Helper functions ##############################
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+  // Hide all slides
+  $(".slide").hide();
+  // Show just the slide we want to show
+  $("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+  if (typeof b == "undefined") {
+    a = a || 2;
+    return Math.floor(Math.random()*a);
+  } else {
+    return Math.floor(Math.random()*(b-a+1)) + a;
+  }
+}
+
+// Remove Option Redundancy 
+function options() {
+  var ages = document.getElementById("age");
+  var max  = 90;
+  for (i = 18; i < max; i++) {
+    var option = new Option(String(i), i);
+    ages.options.add(option);
+  }
+}
+
+
+// Randomize Radio Buttons 
+function createRadioButtons() {
+  choice = [1,5].random();
+  var radio = Array.from(document.getElementsByName(String(choice)))
+  // if (choice == 3 || choice == 4) {
+  //   radio.push(document.getElementsByName('slider' + choice)[0])
+  // }
+  for (i = 0; i < radio.length; i++) {
+    radio[i].style.visibility = 'visible'
+  }
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle ordering of argument array -- are we missing a parenthesis?
+//function shuffle (a)
+//{
+//    var o = [];
+//
+//    for (var i=0; i < a.length; i++) {
+//      o[i] = a[i];
+//    }
+//
+//    for (var j, x, i = o.length;
+//         i;
+//         j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);
+//    return o;
+//}
+
+function shuffle(array) {
+  var currentIndex = array.length, temporaryValue, randomIndex;
+
[…]

### 2018-04-08 experiments/main/1_methods/online_experiment/connective_game.js
Added Trial Randomization Management
Copied code from Mike Frank’s website:
https://babieslearninglanguage.blogspot.com/search?q=getter

@@ -1,4 +1,17 @@
 // ############################## Helper functions ##############################
+// Condition - call the maker getter to get the cond variable 
+try {
+    var filename = "myexpt_v1"
+    var condCounts = "1,20;2,20;3,20;4,20;5,20"
+    var xmlHttp = null;
+    xmlHttp = new XMLHttpRequest();
+    xmlHttp.open( "GET", "http://website.com/cgi-bin/maker_getter.php?conds=" + 
+    condCounts +"&filename=" + filename);
+    xmlHttp.send( null );
+    choice = Number(xmlHttp.responseText) - 1;
+} catch (e) {
+    var choice = 0;
+}
 
 // Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
 function showSlide(id) {
@@ -32,7 +45,6 @@ function options() {
 
 // Randomize Radio Buttons 
 function createRadioButtons() {
-  choice = [1,5].random();
   var radio = Array.from(document.getElementsByName(String(choice)))
   // if (choice == 3 || choice == 4) {
   //   radio.push(document.getElementsByName('slider' + choice)[0])
@@ -211,6 +223,16 @@ var experiment = {
 // END FUNCTION: The function to call when the experiment has ended
     end: function() {
       showSlide("finished");
+      // Decrement only if this is an actual turk worker!  
+      if (turk.workerId.length > 0){
+       var xmlHttp = null;
+       xmlHttp = new XMLHttpRequest();
+       xmlHttp.open('GET',    
+        'http://website.com/cgi-bin/' + 
+        'decrementer.php?filename=' + 
+        filename + "&to_decrement=" + choice);
+        xmlHttp.send(null);
+      }
       setTimeout(function() {
         turk.submit(experiment.data)
       }, 1500);

### 2018-04-10 experiments/main/1_methods/online_experiment/connective_game.js
more changes to the writeup

@@ -5,7 +5,7 @@ try {
     var condCounts = "1,20;2,20;3,20;4,20;5,20"
     var xmlHttp = null;
     xmlHttp = new XMLHttpRequest();
-    xmlHttp.open( "GET", "http://website.com/cgi-bin/maker_getter.php?conds=" + 
+    xmlHttp.open( "GET", "https://website.com/cgi-bin/maker_getter.php?conds=" + 
     condCounts +"&filename=" + filename);
     xmlHttp.send( null );
     choice = Number(xmlHttp.responseText) - 1;
@@ -228,7 +228,7 @@ var experiment = {
        var xmlHttp = null;
        xmlHttp = new XMLHttpRequest();
        xmlHttp.open('GET',    
-        'http://website.com/cgi-bin/' + 
+        'https://website.com/cgi-bin/' + 
         'decrementer.php?filename=' + 
         filename + "&to_decrement=" + choice);
         xmlHttp.send(null);

### 2018-04-10 experiments/main/1_methods/online_experiment/connective_game.js
Cleaned Up Code
Removed Binary options and attempts at standardizing number of trials

@@ -1,18 +1,4 @@
 // ############################## Helper functions ##############################
-// Condition - call the maker getter to get the cond variable 
-try {
-    var filename = "myexpt_v1"
-    var condCounts = "1,20;2,20;3,20;4,20;5,20"
-    var xmlHttp = null;
-    xmlHttp = new XMLHttpRequest();
-    xmlHttp.open( "GET", "http://website.com/cgi-bin/maker_getter.php?conds=" + 
-    condCounts +"&filename=" + filename);
-    xmlHttp.send( null );
-    choice = Number(xmlHttp.responseText) - 1;
-} catch (e) {
-    var choice = 0;
-}
-
 // Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
 function showSlide(id) {
   // Hide all slides
@@ -45,6 +31,7 @@ function options() {
 
 // Randomize Radio Buttons 
 function createRadioButtons() {
+  choice = random(2,5)
   var radio = Array.from(document.getElementsByName(String(choice)))
   // if (choice == 3 || choice == 4) {
   //   radio.push(document.getElementsByName('slider' + choice)[0])
@@ -223,16 +210,6 @@ var experiment = {
 // END FUNCTION: The function to call when the experiment has ended
     end: function() {
       showSlide("finished");
-      // Decrement only if this is an actual turk worker!  
-      if (turk.workerId.length > 0){
-       var xmlHttp = null;
-       xmlHttp = new XMLHttpRequest();
-       xmlHttp.open('GET',    
-        'http://website.com/cgi-bin/' + 
-        'decrementer.php?filename=' + 
-        filename + "&to_decrement=" + choice);
-        xmlHttp.send(null);
-      }
       setTimeout(function() {
         turk.submit(experiment.data)
       }, 1500);

### 2018-04-12 experiments/main/3_processed_data/mturk_processing.Rmd
data collection and plotting

---
title: "mturk_data_processing"
author: "Masoud Jasbi"
date: "3/7/2017"
output: html_document
---

```{r cars}
library(rjson)
library(tidyverse)
```

```{r}
# read the json file names to be loaded in the json directory
files <- dir("../2_raw_data/", pattern =".json") 
# make an empty data frame to append the json data participant by participant
adult_data <- data.frame()

#loop through json files
for (file in files) {
  #read the json file into jd
  jd <- fromJSON(paste(readLines(paste("../2_raw_data/", file, sep="")), collapse=""))
  #create a data frame with the column names on the left
  id <- data_frame(participant = jd$WorkerId,
                   order=seq(1:24),
                  gender = jd$answers$data$gen,
                  age = jd$answers$data$age,
                  language = jd$answers$data$language,
                  response_type = jd$answers$data$response_type,
                  trial_type = jd$answers$data$trial_type,
                  guess_type = jd$answers$data$guess_type,
                  guess = jd$answers$data$guess,
                  card_type = jd$answers$data$card_type,
                  card = jd$answers$data$card,
                  response = jd$answers$data$response,
                  logical_training = jd$answers$data$logical_training,
                  duration = jd$answers$data$elapsed_ms,
                  aim = jd$answers$data$aim,
                  comments = jd$answers$data$comments
                  )
  # append the dataframe for that json file to the big data frame 
  adult_data <- bind_rows(adult_data, id)
}
write_csv(adult_data, "../3_processed_data/data_main.csv")
```

### 2018-04-12 writeup.Rmd
data collection and plotting

@@
 ```{r importData, warning=FALSE, echo=FALSE}
-data <- read_csv("experiments/pilot/3_processed_data/pilot_data.csv")
-data$response <- pilot_data$response %>% tolower()
+data <- read_csv("experiments/main/3_processed_data/data_main.csv")
+
+data$response_type <- recode(data$response_type, quatenary = "quaternary", tertiary = "ternary")
 
@@
 pragmatic_trials$high<-1
-pragmatic_trials[pragmatic_trials$response=="right" | pragmatic_trials$response=="true",]$high <-0
+pragmatic_trials[pragmatic_trials$response=="Right"]$high <-0
 
@@
 pragmatic_trials$low<-0
-pragmatic_trials[pragmatic_trials$response=="wrong" | pragmatic_trials$response=="false",]$low <-1
+pragmatic_trials[pragmatic_trials$response=="Wrong"]$low <-1
 
@@
 
-100 participants (20 per condition) were recruited using Amazon Mechanical Turk. No participant was excluded from the final analysis.
+```{r participants}
+participants_info <-
+  data %>%
+  group_by(response_type) %>%
+  summarise(count = n()/24)
+```
+
+200 participants were recruited using Amazon Mechanical Turk (binary=`r participants_info$count[1]`, ternary`r participants_info$count[4]`, quaternary=`r participants_info$count[2]`, quinary=`r participants_info$count[3]`).
+No participant was excluded from the final analysis.
 
@@
 
-binary_summary$response <- factor(binary_summary$response, levels = c("wrong","right"))
+binary_summary$response <- factor(binary_summary$response, levels = c("Wrong","Right"))
 binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
@@
   theme_few() +
-  theme(text = element_text(size=17)) +
+  theme(text = element_text(size=15)) +
   scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)
@@
 
+```{r ternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
+
+ternary_summary<-
+  data %>%
+  filter(response_type=="ternary") %>%
+  group_by(card_type, guess_type, response) %>%
+  summarize(count=n()) %>%
+  group_by(card_type, guess_type) %>%
+  mutate(total = sum(count), proportion=count/total)
+
+ternary_summary$response <- factor(ternary_summary$response, levels = c("Wrong","Neither", "Right"))
+ternary_summary$guess_type <- factor(ternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
+ternary_summary$guess_type <- recode(ternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+
+ternary_plot<-
+  ternary_summary %>%
+  ggplot(aes(x=response, y=proportion, fill=response)) +
+  geom_bar(stat = "identity", position="dodge", width = 0.6) +
+#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
+  facet_grid(card_type~guess_type) +
+  labs(x="", y="")+
+  theme_few() +
+  theme(text = element_text(size=15)) +
+  scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE)
+
+cat <- 
+  readJPEG("experiments/figs/cat_card.jpg") %>%
+  rasterGrob(width=0.9)
+
+cat_dog <- 
+  readJPEG("experiments/figs/catdog_card.jpg")%>%
+  rasterGrob(width=0.9)
+
+ternary_plot_g <- ggplot_gtable(ggplot_build(ternary_plot))
+
+strips <- grep("strip-r", ternary_plot_g$layout$name)
+
+new_grobs <- list(cat, cat_dog)
+
+ternary_plot_g <- with(ternary_plot_g$layout[strips,],
+          gtable_add_grob(ternary_plot_g, new_grobs,
+                          t=t, l=l, b=b, r=r, name="cards"))        
+ternary_plot_g$widths[[11]] <- unit(2.5,"cm")
+
+grid.draw(ternary_plot_g)
+```
+
+```{r quaternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
+
+quaternary_summary<-
+  data %>%
+  filter(response_type=="quaternary") %>%
+  group_by(card_type, guess_type, response) %>%
+  summarize(count=n()) %>%
+  group_by(card_type, guess_type) %>%
+  mutate(total = sum(count), proportion=count/total)
+
+quaternary_summary$response <- factor(quaternary_summary$response, levels = c("Wrong","Kinda Wrong", "Kinda Right", "Right"))
+quaternary_summary$guess_type <- factor(quaternary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
+quaternary_summary$guess_type <- recode(quaternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+
+quaternary_plot<-
+  quaternary_summary %>%
+  ggplot(aes(x=response, y=proportion, fill=response)) +
+  geom_bar(stat = "identity", position="dodge", width = 0.6) +
+#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
+  facet_grid(card_type~guess_type) +
+  labs(x="", y="")+
+  theme_few() +
+  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)
+
+cat <- 
+  readJPEG("experiments/figs/cat_card.jpg") %>%
+  rasterGrob(width=0.9)
+
+cat_dog <- 
+  readJPEG("experiments/figs/catdog_card.jpg")%>%
+  rasterGrob(width=0.9)
+
+quaternary_plot_g <- ggplot_gtable(ggplot_build(quaternary_plot))
+
+strips <- grep("strip-r", quaternary_plot_g$layout$name)
+
+new_grobs <- list(cat, cat_dog)
+
+quaternary_plot_g <- with(quaternary_plot_g$layout[strips,],
+          gtable_add_grob(quaternary_plot_g, new_grobs,
+                          t=t, l=l, b=b, r=r, name="cards"))        
+quaternary_plot_g$widths[[11]] <- unit(2.5,"cm")
+
+grid.draw(quaternary_plot_g)
+```
+
+```{r quinaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
+
+quinary_summary<-
+  data %>%
+  filter(response_type=="quinary") %>%
+  group_by(card_type, guess_type, response) %>%
+  summarize(count=n()) %>%
+  group_by(card_type, guess_type) %>%
+  mutate(total = sum(count), proportion=count/total)
+
+quinary_summary$response <- factor(quinary_summary$response, levels = c("Wrong","Kinda Wrong", "Neither", "Kinda Right", "Right"))
+quinary_summary$guess_type <- factor(quinary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
+quinary_summary$guess_type <- recode(quinary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+
+quinary_plot<-
+  quinary_summary %>%
+  ggplot(aes(x=response, y=proportion, fill=response)) +
+  geom_bar(stat = "identity", position="dodge", width = 0.6) +
+#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
+  facet_grid(card_type~guess_type) +
+  labs(x="", y="")+
+  theme_few() +
+  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)
+
+cat <- 
+  readJPEG("experiments/figs/cat_card.jpg") %>%
+  rasterGrob(width=0.9)
+
+cat_dog <- 
+  readJPEG("experiments/figs/catdog_card.jpg")%>%
+  rasterGrob(width=0.9)
+
+quinary_plot_g <- ggplot_gtable(ggplot_build(quinary_plot))
+
+strips <- grep("strip-r", quinary_plot_g$layout$name)
+
+new_grobs <- list(cat, cat_dog)
+
+quinary_plot_g <- with(quinary_plot_g$layout[strips,],
+          gtable_add_grob(quinary_plot_g, new_grobs,
+                          t=t, l=l, b=b, r=r, name="cards"))        
+quinary_plot_g$widths[[11]] <- unit(2.5,"cm")
+
+grid.draw(quinary_plot_g)
+```
+
 ```{r}
@@
 ```
+
+* make sure to break down based on whether participants had logical training or not.
 

### 2018-04-25 writeup.Rmd
added link visualization

@@
 # Introduction
+
+```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3, fig.height=1, set.cap.width=T, num.cols.cap=1,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
+cards_img <- jpeg::readJPEG("writeup_files/link-visualization.jpg")
+grid::grid.raster(cards_img)
+```
 

### 2018-04-26 writeup.Rmd
more intro

--- 2018-04-12 writeup.Rmd
@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "The effect of linking assumptions and number of response options on inferred scalar implicature rate"
+shorttitle        : "Linking assumptions and implicature rate"
 author:
 
-  - name          : "First Author"
+  - name          : "Masoud Jasbi"
     affiliation   : "1"
@@
     email         : "my@email.com"
-  - name          : "Second Author"
+  - name          : "Brandon Waldon"
     affiliation   : "1"
-  - name          : "Third Author"
+  - name          : "Judith Degen"
     affiliation   : "1"
@@
 
-keywords          : "keywords"
+keywords          : "scalar implicature; methodology; linking assumption; experimental pragmatics; truth-value judgment task"
 wordcount         : "X"
 bibliography      : ["r-references.bib"]
-figsintext        : no
+figsintext        : yes
 figurelist        : no
@@
 library(forcats)
-library(brms)
+# library(brms)
+theme_set(theme_bw(18))
 ```
@@
 # Introduction
+
+The past 15 years have seen the rise and development of a bustling and exciting new field at the intersection of linguistics, psychology, and philosophy: *experimental pragmatics* [@bott2004;@Breheny2006;@DegenTanenhaus2015;@Grodner2010;@huang2009;@Geurts2009;@noveck2008] **XXX ADD MORE**.
+Experimental pragmatics is devoted to experimentally testing theories of how language is used in context.
+How do listeners draw inferences about the -- often underspecified -- linguistic signal they receive from speakers?
+How do speakers choose between the many utterance alternatives they have at their disposal?
+
+The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*.
+Scalar implicatures arise in virtue of a speaker producing the weaker of two ordered scalemates [@grice1975; hornXXX; @hirschberg1985; @Geurts2010].
+Examples are provided in (1) and (2).
+
+1. 
+  a. *Utterance:* Some of her pets are cats.
+  b. *Implicature:* Some, but not all, of her pets are cats.
+  c. *Scale:* <all, some>
+
+2. 
+  a. *Utterance:* She owns a cat or a dog.
+  b. *Implicature:* She owns a cat or a dog, but not both.
+  c. *Scale:* <and, or>
+
+A listener, upon observing the utterances in (1a) and (2a), typically infers that the speaker intended to convey the meanings in (1b) and (2b), respectively.
+Since @grice1975, the agreed-upon abstract rationalization the listener could give for their inference goes something like this: if the speaker knows whether the stronger alternative (e.g., *All of her pets are cats.*) is true, then if it is, they should have produced it.
+They chose not to.
+I believe the speaker knows whether the stronger alternative is true.
+Hence, it must not be true.
+
+CONTINUE HERE: motivation for examining implicature rate assumptions:
+
+* surging interest in differences in implicature rates (eg van tiel, dgen tanenhaus)
+* implicature rates serve as basis for claims about online processing (bott & noveck, degen tanenhaus)
+* implicature rates serve as basis for claims about children (bishop katsos, barner, frank)
+
+* add @deneys2007
+* @demarneffetonhauser for investigations of scalar adjectives, and @vantiel
+
+```{r linkvisualization, fig.env = "figure", fig.align='center', fig.width=5, set.cap.width=T, num.cols.cap=1,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
+link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
+grid::grid.raster(link_img)
+```
 
@@
 pragmatic_trials$high<-1
-pragmatic_trials[pragmatic_trials$response=="Right"]$high <-0
+pragmatic_trials[pragmatic_trials$response=="Right",]$high <-0
 
@@
 pragmatic_trials$low<-0
-pragmatic_trials[pragmatic_trials$response=="Wrong"]$low <-1
+pragmatic_trials[pragmatic_trials$response=="Wrong",]$low <-1
 
@@
 
-summary(implicature_analysis)
+summary(implicature_analysis_a)
 
-implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
+# implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
 ```

### 2018-04-26 writeup.Rmd
more intro

@@
 1. 
-  a. *Utterance:* Some of her pets are cats.
-  b. *Implicature:* Some, but not all, of her pets are cats.
-  c. *Scale:* <all, some>
+  + *Utterance:* Some of her pets are cats.
+  + *Implicature:* Some, but not all, of her pets are cats.
+  + *Scale:* <all, some>
 
 2. 
-  a. *Utterance:* She owns a cat or a dog.
-  b. *Implicature:* She owns a cat or a dog, but not both.
-  c. *Scale:* <and, or>
+  + *Utterance:* She owns a cat or a dog.
+  + *Implicature:* She owns a cat or a dog, but not both.
+  + *Scale:* <and, or>
 

### 2018-04-29 writeup.Rmd
added to intro

@@
 A listener, upon observing the utterances in (1a) and (2a), typically infers that the speaker intended to convey the meanings in (1b) and (2b), respectively.
-Since @grice1975, the agreed-upon abstract rationalization the listener could give for their inference goes something like this: if the speaker knows whether the stronger alternative (e.g., *All of her pets are cats.*) is true, then if it is, they should have produced it.
+Since @grice1975, the agreed-upon abstract rationalization the listener could give for their inference goes something like this: the speaker could have made a more informative statement by producing the stronger alternative (e.g., *All of her pets are cats.*).
+If the stronger alternative is true, they should have produced it to comply with the Cooperative Principle.
 They chose not to.
@@
 Hence, it must not be true.
+
+Because the basic reconstruction of the inference is much more easily characterized for  scalar implicatures than for other implicatures, scalar implicatures have served as a test bed for many questions in experimental pragmatics, including, but not limited to:
+1. Are scalar inferences default inferences, in the sense that they arise unless blocked by (marked) contexts [@horn1984; @levinson2000; @Degen2015]?
+2.
+Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009]?
+3.
+What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @DegenGoodman2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffeTonhauser;@DeNeys2007;@Bonnefon2009]?
+4. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; Frank; @Musolino2004]? 
+5. How much diversity is there across implicature types, and within scalar implicatures across scale types, in whether or not an implicature is computed [@Doran2012;@VanTiel2014]?
 

### 2018-04-29 writeup.tex
added to intro

@@
-\documentclass[man]{apa6}
+\documentclass[floatsintext,man]{apa6}
 
@@
 
-  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
-  \ifthenelse{\equal{\string man}{\string man}}{%
-   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
-   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
-   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
-  }{}%
-
 % The following enables adjusting longtable caption width to table width
@@
 
+  \usepackage{graphicx}
+  \makeatletter
+  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+  \makeatother
+  % Scale images if necessary, so that they will not overflow the page
+  % margins by default, and it is still possible to overwrite the defaults
+  % using explicit options in \includegraphics[width, height, ...]{}
+  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \ifxetex
@@
             pdfauthor={},
-            pdftitle={The title},
+            pdftitle={The effect of linking assumptions and number of response options on inferred scalar implicature rate},
             colorlinks=true,
@@
 % Essential manuscript parts
-  \title{The title}
+  \title{The effect of linking assumptions and number of response options on
+inferred scalar implicature rate}
 
-  \shorttitle{Title}
+  \shorttitle{Linking assumptions and implicature rate}
 
-  \author{First Author\textsuperscript{1}, Second Author\textsuperscript{1}, \& Third Author\textsuperscript{1}}
+  \author{Masoud Jasbi\textsuperscript{1}, Brandon Waldon\textsuperscript{1}, \& Judith Degen\textsuperscript{1}}
 
@@
     Add complete departmental affiliations for each author here. Each new
-    line herein must be indented, like this line.
+    line herein must be indented, like this line. Enter author note here.
 
-    Enter author note here.
-
-    Correspondence concerning this article should be addressed to First
-    Author, Postal address. E-mail:
+    Correspondence concerning this article should be addressed to Masoud
+    Jasbi, Postal address. E-mail:
     \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
@@
 line.}
-  \keywords{keywords \\
+  \keywords{scalar implicature; methodology; linking assumption; experimental
+pragmatics; truth-value judgment task \\
 
@@
 \usepackage{amsthm}
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{proposition}{Proposition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
 \theoremstyle{definition}
-\newtheorem{example}{Example}
+\newtheorem{example}{Example}[section]
 \theoremstyle{definition}
-\newtheorem{exercise}{Exercise}
+\newtheorem{exercise}{Exercise}[section]
 \theoremstyle{remark}
@@
 
-\section{Background}\label{background}
+The past 15 years have seen the rise and development of a bustling and
+exciting new field at the intersection of linguistics, psychology, and
+philosophy: \emph{experimental pragmatics} (Bott \& Noveck, 2004;
+Breheny, Katsos, \& Williams, 2006; Degen \& Tanenhaus, 2015; Geurts \&
+Pouscoulous, 2009; Grodner, Klein, Carbary, \& Tanenhaus, 2010; Huang \&
+Snedeker, 2009; I. A. Noveck \& Reboul, 2008) \textbf{XXX ADD MORE}.
+Experimental pragmatics is devoted to experimentally testing theories of
+how language is used in context. How do listeners draw inferences about
+the -- often underspecified -- linguistic signal they receive from
+speakers? How do speakers choose between the many utterance alternatives
+they have at their disposal?
+
+The most prominently studied phenomenon in experimental pragmatics is
+undoubtedly \emph{scalar implicature}. Scalar implicatures arise in
+virtue of a speaker producing the weaker of two ordered scalemates
+(hornXXX; {\textbf{???}}, {\textbf{???}}; Grice, 1975). Examples are
+provided in (1) and (2).
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+\end{enumerate}
 
@@
 \item
+  \emph{Utterance:} Some of her pets are cats.
+\item
+  \emph{Implicature:} Some, but not all, of her pets are cats.
+\item
+  \emph{Scale:} 
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\item
+\end{enumerate}
+
+\begin{itemize}
+\tightlist
+\item
+  \emph{Utterance:} She owns a cat or a dog.
+\item
+  \emph{Implicature:} She owns a cat or a dog, but not both.
+\item
+  \emph{Scale:} 
+\end{itemize}
+
+A listener, upon observing the utterances in (1a) and (2a), typically
+infers that the speaker intended to convey the meanings in (1b) and
+(2b), respectively. Since Grice (1975), the agreed-upon abstract
+rationalization the listener could give for their inference goes
+something like this: the speaker could have made a more informative
+statement by producing the stronger alternative (e.g., \emph{All of her
+pets are cats.}). If the stronger alternative is true, they should have
+produced it to comply with the Cooperative Principle. They chose not to.
+I believe the speaker knows whether the stronger alternative is true.
+Hence, it must not be true.
+
+Because the basic reconstruction of the inference is much more easily
+characterized for scalar implicatures than for other implicatures,
+scalar implicatures have served as a test bed for many questions in
+experimental pragmatics, including, but not limited to: 1. Are scalar
+inferences default inferences (in the sense of default as arising unless
+blocked by marked contexts \textbf{XXX horn, levinson, degen2015)}? 2.
+Are scalar inferences default inferences (in the sense that they are
+computed automatically in online processing and only cancelled by
+context in a second effortful step if required by context)
+({\textbf{???}}; Bott \& Noveck, 2004; Breheny et al., 2006; Grodner et
+al., 2010; Huang \& Snedeker, 2009)? 3. What are the (linguistic and
+extra-linguistic) factors that affect whether a scalar implicature is
+derived {[}({\textbf{???}});DegenTanenhaus2015; DegenTanenhaus2016;
+Degen2015; DegenGoodman2014; BergenGrodner2012; Breheny2006;
+FergusonBreheny2013;DeMarneffeTonhauser;DeNeys2007;Bonnefon{]}? 4. At
+what age do children acquire the ability to compute implicatures
+{[}Noveck2001; Reboul; Papafragou; Barner; Frank; Musolino{]}?
+\textbf{XXX fill in refs}
+
+CONTINUE HERE: motivation for examining implicature rate assumptions:
+
+\begin{itemize}
+\item
+  surging interest in differences in implicature rates (eg van tiel,
+  dgen tanenhaus)
+\item
+  implicature rates serve as basis for claims about online processing
+  (bott \& noveck, degen tanenhaus)
+\item
+  implicature rates serve as basis for claims about children (bishop
+  katsos, barner, frank)
+\item
+  add ({\textbf{???}})
+\item
+  ({\textbf{???}}) for investigations of scalar adjectives, and
+  ({\textbf{???}})
+\end{itemize}
+
+\begin{figure}
+
+{\centering \includegraphics{writeup_files/figure-latex/linkvisualization-1}
+
+}
+
+\caption{Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true.}\label{fig:linkvisualization}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  In a truth-value judgment task, how do we know whether an
+  interpretation is literal or the result of an implicature computation?
+\end{itemize}
+
+Explain the setup * the speaker produces weaker alternative from the
+scale * the facts are such that the stronger alternative is true
+
+Traditional Linking Hypotheses: * If an implicature is calculated, the
+participant chooses a Non-True/Non-Right response * If an implicature is
+calculated, the participant chooses the Wrong/False response * If an
+implicature is calculated, the participant chooses the lower end of the
+scale (2: wrong/False, 3: wrong, 4: wrong/kinda-wrong, 5:
+wrong/kinda-wrong)
+
+Questions: * Do these linking hypotheses give us different measures of
+implicature computation? * If they do differ, which one is most stable?
+
+Alternative Linking Hypothesis: * RSA: Response behavior across
+conditions (utterance-card combinations) and dependent measures can be
+predicted by a linking hypothesis that assumes that participants are
+behaving like soft-optimal RSA speakers and provide a particular
+response (eg TRUE) to an utterance u if the RSA speaker probability of u
+(given the card) is within a particular probability interval (eg, within
+the interval {[}theta, 1{]}).
+
+\begin{itemize}
+\tightlist
+\item
+  Differences between traditional approaches and RSA: 1. The traditional
+  linking hypotheses are based on a binary implicature/literal theory of
+  pragmatic reasoning but RSA gives a continuous measure of pragmatic
+  reasoning and allows for better predicting response behavior with
+  multiple options.
+\end{itemize}
+
+\section{Background}\label{background}
+
+\begin{itemize}
+\item
   discussing the ways people in tha past have measured the
   \enquote{implicature rate}.
+\item
+  it seems like the literature takes the n(not-True)/n(Total) as the
+  proporition of responses caused by implicature calculation
+\item
+  BUT, I remember that Jesse Snedeker said it's NOT n(not-True)/n(Total)
+  but it is n(False)/n(Total)
+\item
+  However, this is probably not a consensus in the field because Katsos
+  \& Bishop consider the mid-point response \enquote{big} on the scale
+  small-big-huge (strawberry) to be the result of implicture caculation
+\item
+  what is the most common measure of \enquote{implicature rate} in the
+  literature? Binary True/False: Noveck 2001, Chemla \& Spector 2011,
+  Ternary: Katsos \& Bishop 2011
 \end{itemize}
@@
 
-\begin{itemize}
-\tightlist
-\item
-  data exclusion? we don't expect any.
-\end{itemize}
-
 \subsection{Participants}\label{participants}
 
-\begin{itemize}
-\tightlist
-\item
-  how are we choosing the sample size?
-\end{itemize}
+200 participants were recruited using Amazon Mechanical Turk (binary=50,
+ternary53, quaternary=43, quinary=54). No participant was excluded from
+the final analysis.
 
-\subsection{Materials and Design}\label{materials-and-design}
+\subsection{Procedure}\label{procedure}
+
+The study was administered online and through Amazon Mechanical Turk.
+Participants were introduced to a set of cards with pictures of one or
+two animals (Figure \ref{fig:stimuli}). They were told that a
+blindfolded fictional character called Bob is going to guess what
+animals are on the card. In each trial, participants saw a card as well
+as a sentence representing Bob's guess. For example they saw a card with
+a cat on it and read the sentence \enquote{there is a cat on the card.}
+The study ended after 24 trials. At the end participants were asked
+about their\\
+You can access and view \href{}{the online study here}.
+
+\subsection{Design and Materials}\label{design-and-materials}
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  Manipulations: type of card and the type ofgue
-\end{itemize}
+The design had two main manipulaitons: the type of card and the type of
+guess. There were two types of cards. Cards with only one animal on them
+and cards with two animals. Animals were chosen from the following set:
+cat, dog, and elephant There were three types of guesses: simple (e.g.
+\emph{There is a cat}), conjunctive (e.g. \emph{There is a cat and a
+dog}), and disjunctive (e.g. \emph{There is a cat or a dog}).
 
-The study included six cards with cartoon images of a cat, a dog, and an
-elephant (Figure \ref{fig:stimuli}). The study was designed based on the
-type of cards participants saw and the type of guesses they heard. There
-were two types of cards: cards with only one animal on them and the ones
-with two animals. There were three types of guesses: simple (e.g.
-\emph{There is a cat}), conjunctive (e.g. \emph{There is a cat and a
-dog}), and disjunctive (e.g. \emph{There is a cat or a dog}). In each
-guess, the animal labels used in the guess and the animal images on the
-card may have no overlap (e.g.~Image: dog, Guess: \emph{There is a cat
-or an elephant}), a partial overlap (e.g.~Image: Cat, Guess: \emph{There
-is a cat or an elephant}), or a total overlap (e.g.~Image: cat and
-elephant, Guess: \emph{There is a cat or an elephant}). Crossing the
-number of animals on the card, the type of guess, and the overlap
+In each trial, the animal labels used in the guess and the animal images
+on the card may have no overlap (e.g.~Image: dog, Guess: \emph{There is
+a cat or an elephant}), a partial overlap (e.g.~Image: Cat, Guess:
+\emph{There is a cat or an elephant}), or a total overlap (e.g.~Image:
+cat and elephant, Guess: \emph{There is a cat or an elephant}). Crossing
+the number of animals on the card, the type of guess, and the overlap
 between the guess and the card results in 12 different possible trial
@@
 
-\begin{itemize}
-\tightlist
-\item
 The study used five different types of measurements. 1. two-options
@@
 (wrong, neither, right) 4. four-options (wrong, kinda wrong, kinda
-  right, right) 5. five-options (wrong, kinda wrong, neither, kinda
+right, right) 5. five-options (wrong, kinda wrong, neither, kinda right,
 right).
-\end{itemize}
 
@@
 
-\subsection{Procedure}\label{procedure}
-
 \subsection{Pre-registered Analysis}\label{pre-registered-analysis}
 
-This study set out to test the hypothesis that the proportion of
+We are primarily concerned with the \enquote{rate of implicatures} in an
+experimental study. Two trial types are predicted to include pragmatic
+implicatures. First, trials where there are two animals on the card but
+the fictional character guesses using the connective \emph{or}; for
+example \enquote{cat or dog} when the card has both a cat and a dog on
+it. We call such trials \enquote{scalar} trials. Second, trials where
+there are two animals on the card but the character guesses only one;
+for example \enquote{cat} when the card has a cat and a dog on it. We
+call such trials \enquote{exhaustive}. In our assessment of implicature
+rate we focus on these two types of trials.
+
+We define \enquote{implicature rate} in two ways:
+
+This study set out to test two hypotheses. First, that the proportion of
 pragmatic vs.~literal responses in a truth values judgement task changes
@@
 We test this hypothesis formally using a binomial mixed effects model
-with the fixed effect of blah and the random effects of blah.
+with the fixed effect of response type and the random intercept for
+participants as well as random intercept and slope for
 
-\begin{verbatim}
-## implicature_rate ~ response_type + (1 + response_type | tiral_type) + 
-##     (1 | participant)
-\end{verbatim}
+A second hypothesis was that the definition of what responses count as
+participants computing an implicature may affect the estimated rate of
+implicature in the experimental task.
 
@@
 
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/binaryPlot-1}
+
+}
+
+\caption{Adults' two-alternative forced choice judgments in the connective guessing game.}\label{fig:binaryPlot}
+\end{figure}
+
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/ternaryPlot-1}
+
+}
+
+\caption{Adults' three-alternative forced choice judgments in the connective guessing game.}\label{fig:ternaryPlot}
+\end{figure}
+
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/quaternaryPlot-1}
+
+}
+
+\caption{Adults' three-alternative forced choice judgments in the connective guessing game.}\label{fig:quaternaryPlot}
+\end{figure}
+
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/quinaryPlot-1}
+
+}
+
+\caption{Adults' three-alternative forced choice judgments in the connective guessing game.}\label{fig:quinaryPlot}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/unnamed-chunk-2-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  make sure to break down based on whether participants had logical
+  training or not.
+\end{itemize}
+
 \section{Analysis}\label{analysis}
+
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{}
+\end{figure}
+
+\begin{verbatim}
+## Warning in (function (fn, par, lower = rep.int(-Inf, n), upper =
+## rep.int(Inf, : failure to converge in 10000 evaluations
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in checkConv(attr(opt, "derivs"), opt$par, ctrl = control
+## $checkConv, : Model failed to converge with max|grad| = 0.524298 (tol =
+## 0.001, component 1)
+\end{verbatim}
+
+\begin{verbatim}
+## Generalized linear mixed model fit by maximum likelihood (Laplace
+##   Approximation) [glmerMod]
+##  Family: binomial  ( logit )
+## Formula: implicature ~ definition * response_type + trial_type + (1 +  
+##     response_type | card) + (1 | participant)
+##    Data: implicature_rate
+## 
+##      AIC      BIC   logLik deviance df.resid 
+##   1783.4   1899.0   -871.7   1743.4     2380 
+## 
+## Scaled residuals: 
+##     Min      1Q  Median      3Q     Max 
+## -7.8815 -0.2261 -0.1198  0.2334 10.0887 
+## 
+## Random effects:
+##  Groups      Name                    Variance Std.Dev. Corr             
+##  participant (Intercept)             5.224316 2.28568                   
+##  card        (Intercept)             0.008402 0.09166                   
+##              response_typequaternary 0.084138 0.29007  -1.00            
+##              response_typequinary    0.003720 0.06099  -0.79  0.81      
+##              response_typeternary    0.044946 0.21201   0.90 -0.89 -0.67
+## Number of obs: 2400, groups:  participant, 200; card, 3
+## 
+## Fixed effects:
+##                                       Estimate Std. Error z value Pr(>|z|)
+## (Intercept)                           -2.64555    0.43138  -6.133 8.63e-10
+## definitionlow                         -0.02508    0.24943  -0.101    0.920
+## response_typequaternary                3.47868    0.61328   5.672 1.41e-08
+## response_typequinary                   3.44163    0.55426   6.209 5.32e-10
+## response_typeternary                   0.29732    0.56967   0.522    0.602
+## trial_typescalar                       0.85657    0.13861   6.180 6.41e-10
+## definitionlow:response_typequaternary -6.08294    0.61009  -9.970  < 2e-16
+## definitionlow:response_typequinary    -5.71913    0.50693 -11.282  < 2e-16
+## definitionlow:response_typeternary    -1.21490    0.36931  -3.290    0.001
+##                                          
+## (Intercept)                           ***
+## definitionlow                            
+## response_typequaternary               ***
+## response_typequinary                  ***
+## response_typeternary                     
+## trial_typescalar                      ***
+## definitionlow:response_typequaternary ***
+## definitionlow:response_typequinary    ***
+## definitionlow:response_typeternary    ** 
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+## 
+## Correlation of Fixed Effects:
+##                     (Intr) dfntnl rspns_typqt rspns_typqn rspns_typt
+## definitinlw         -0.287                                          
+## rspns_typqt         -0.724  0.202                                   
+## rspns_typqn         -0.760  0.224  0.554                            
+## rspns_typtr         -0.643  0.218  0.418       0.510                
+## trl_typsclr         -0.218 -0.001  0.060       0.065       0.007    
+## dfntnlw:rspns_typqt  0.214 -0.408 -0.330      -0.167      -0.101    
+## dfntnlw:rspns_typqn  0.217 -0.492 -0.156      -0.309      -0.116    
+## dfntnlw:rspns_typt   0.220 -0.675 -0.155      -0.170      -0.280    
+##                     trl_ty dfntnlw:rspns_typqt dfntnlw:rspns_typqn
+## definitinlw                                                       
+## rspns_typqt                                                       
+## rspns_typqn                                                       
+## rspns_typtr                                                       
+## trl_typsclr                                                       
+## dfntnlw:rspns_typqt -0.098                                        
+## dfntnlw:rspns_typqn -0.103  0.266                                 
+## dfntnlw:rspns_typt  -0.036  0.298               0.349             
+## convergence code: 0
+## Model failed to converge with max|grad| = 0.524298 (tol = 0.001, component 1)
+## failure to converge in 10000 evaluations
+\end{verbatim}
 
@@
 
+\hypertarget{refs}{}
+\hypertarget{ref-bott2004}{}
+Bott, L., \& Noveck, I. (2004). Some utterances are underinformative:
+The onset and time course of scalar inferences. \emph{Journal of Memory
+and Language}, \emph{51}(3), 437--457.
+doi:\href{https://doi.org/10.1016/j.jml.2004.05.006}{10.1016/j.jml.2004.05.006}
+
+\hypertarget{ref-Breheny2006}{}
+Breheny, R., Katsos, N., \& Williams, J. (2006). Are generalised scalar
+implicatures generated by default? An on-line investigation into the
+role of context in generating pragmatic inferences. \emph{Cognition},
+\emph{100}(3), 434--63.
+doi:\href{https://doi.org/10.1016/j.cognition.2005.07.003}{10.1016/j.cognition.2005.07.003}
+
+\hypertarget{ref-DegenTanenhaus2015}{}
+Degen, J., \& Tanenhaus, M. K. (2015). Processing scalar implicature A
+constraint-based approach. \emph{Cognitive Science}, \emph{39}(4),
+667--710.
+doi:\href{https://doi.org/10.1111/cogs.12171}{10.1111/cogs.12171}
+
+\hypertarget{ref-Geurts2009}{}
+Geurts, B., \& Pouscoulous, N. (2009). Embedded implicatures?!?
+\emph{Semantics and Pragmatics}, \emph{2}, 1--34.
+doi:\href{https://doi.org/10.3765/sp.2.4}{10.3765/sp.2.4}
+
+\hypertarget{ref-grice1975}{}
+Grice, H. P. (1975). Logic and Conversation. \emph{Syntax and
+Semantics}, \emph{3}, 41--58. Retrieved from
+\href{http://books.google.com/books?hl=en\%7B/\&\%7Dlr=\%7B/\&\%7Did=hQCzOmaGeVYC\%7B/\&\%7Doi=fnd\%7B/\&\%7Dpg=PA121\%7B/\&\%7Ddq=Logic+and+conversation\%7B/\&\%7Dots=j7aijUymwm\%7B/\&\%7Dsig=iV1rz1eEm4ns6bQ6CevIURXFVO4}{http://books.google.com/books?hl=en\{\textbackslash{}\&\}lr=\{\textbackslash{}\&\}id=hQCzOmaGeVYC\{\textbackslash{}\&\}oi=fnd\{\textbackslash{}\&\}pg=PA121\{\textbackslash{}\&\}dq=Logic+and+conversation\{\textbackslash{}\&\}ots=j7aijUymwm\{\textbackslash{}\&\}sig=iV1rz1eEm4ns6bQ6CevIURXFVO4}
+
+\hypertarget{ref-Grodner2010}{}
+Grodner, D. J., Klein, N. M., Carbary, K. M., \& Tanenhaus, M. K.
+(2010). ``Some,'' and possibly all, scalar inferences are not delayed:
+Evidence for immediate pragmatic enrichment. \emph{Cognition},
+\emph{116}(1), 42--55.
+doi:\href{https://doi.org/10.1016/j.cognition.2010.03.014}{10.1016/j.cognition.2010.03.014}
+
+\hypertarget{ref-huang2009}{}
+Huang, Y. T., \& Snedeker, J. (2009). On-line interpretationf of scalar
+quantifiers: Insight into the semantics-pragmatics interface.
+\emph{Cognitive Psychology}, \emph{58}, 376--415.
+
+\hypertarget{ref-noveck2008}{}
+Noveck, I. A., \& Reboul, A. (2008). Experimental pragmatics: a Gricean
+turn in the study of language. \emph{Trends in Cognitive Sciences},
+\emph{12}(11), 425--431.
+doi:\href{https://doi.org/10.1016/j.tics.2008.07.009}{10.1016/j.tics.2008.07.009}
+
 \end{document}

### 2018-04-29 writeup.Rmd
added to intro

@@
 Because the basic reconstruction of the inference is much more easily characterized for  scalar implicatures than for other implicatures, scalar implicatures have served as a test bed for many questions in experimental pragmatics, including, but not limited to:
+
 1. Are scalar inferences default inferences, in the sense that they arise unless blocked by (marked) contexts [@horn1984; @levinson2000; @Degen2015]?
+
 2.
-Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009]?
+Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Politzer-Ahles2013;Tomlinson2013]?
+
 3.
-What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @DegenGoodman2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffeTonhauser;@DeNeys2007;@Bonnefon2009]?
-4. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; Frank; @Musolino2004]? 
-5. How much diversity is there across implicature types, and within scalar implicatures across scale types, in whether or not an implicature is computed [@Doran2012;@VanTiel2014]?
+What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@Zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @DegenGoodman2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffeTonhauser;@DeNeys2007;@Bonnefon2009;Chemla2011;Potts2015]?
 
-CONTINUE HERE: motivation for examining implicature rate assumptions:
+4. How much diversity is there across implicature types, and within scalar implicatures across scale types, in whether or not an implicature is computed [@Doran2012;@VanTiel2014]?
 
-* surging interest in differences in implicature rates (eg van tiel, dgen tanenhaus)
-* implicature rates serve as basis for claims about online processing (bott & noveck, degen tanenhaus)
-* implicature rates serve as basis for claims about children (bishop katsos, barner, frank)
+5. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; Frank; @Musolino2004;@Katsos2011]?
 
-* add @deneys2007
-* @demarneffetonhauser for investigations of scalar adjectives, and @vantiel
+In addressing all of these questions, it has been crucial to obtain estimates of **implicature rates**.
+For 1., implicature rates from experimental tasks can be taken to inform whether scalar implicatures should be considered default inferences.
+For 2., processing measures on responses that indicate implicatures can be compared to processing measures on responses that indicate literal interpretations.
+For 3., contextual effects can be examined by comparing implicature rates across contexts.
+For 4., implicature rates can be compared across scales (or across implicature types).
+For 5., implicature rates can be compared across age groups.
+
+A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;Degen2014].
+In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
+They are then asked to judge whether a sentence intended to describe those facts is true or false (or alternatively, whether it is right or wrong, or they are asked whether they agree or disagree with the sentence).
+The crucial condition for assessing implicature rates in these kinds of studies typically consists of a case where the facts are such that the stronger alternative is true and the utterance is underinformative.
+For instance, @Bott2004 asked participants to judge sentences like 'Some elephants are mammals', when world knowledge dictates that all elephants are mammals.
+Similarly, @DegenTanenhaus2015 asked participants to judge sentences like 'You got some of the gumballs' in situations where the visual evidence indicated that the participant received all the gumballs from a gumball machine.
+In these kinds of scenarios, the story goes, if a participant responds 'FALSE', that indicates that they computed a scalar implicature, eg to the effect of 'Not all elephants are mammals' or 'You didn't get all of the gumballs'.
+If instead a participant responds 'TRUE', that is taken to indicate that they interpreted the utterance literally as `Some, and possibly all, elephants are mammals' or 'You god some, and possibly all, of the gumballs'.
+
+People who have discussed issues with the TVJP:
+@BenzGotzner; @Geurts2009; @Geurts2010; @Katsos2011
+
+* @demarneffetonhauser for investigations of scalar adjectives,
 

### 2018-04-29 writeup.Rmd
finished intro draft

@@
 
-The past 15 years have seen the rise and development of a bustling and exciting new field at the intersection of linguistics, psychology, and philosophy: *experimental pragmatics* [@bott2004;@Breheny2006;@DegenTanenhaus2015;@Grodner2010;@huang2009;@Geurts2009;@noveck2008] **XXX ADD MORE**.
+The past 15 years have seen the rise and development of a bustling and exciting new field at the intersection of linguistics, psychology, and philosophy: *experimental pragmatics* [@Bott2004;@Breheny2006;@DegenTanenhaus2015;@Grodner2010;@huang2009;@Geurts2009;@noveck2008] **XXX ADD MORE**.
 Experimental pragmatics is devoted to experimentally testing theories of how language is used in context.
@@
 2.
-Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Politzer-Ahles2013;Tomlinson2013]?
+Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@Bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Politzer-Ahles2013;Tomlinson2013]?
 
 3.
-What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@Zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @DegenGoodman2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffeTonhauser;@DeNeys2007;@Bonnefon2009;Chemla2011;Potts2015]?
+What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@Zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @Degen2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffe2017;@DeNeys2007;@Bonnefon2009;Chemla2011;Potts2015]?
 
@@
 
-A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;Degen2014].
+A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;Degen2014].
 In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
 They are then asked to judge whether a sentence intended to describe those facts is true or false (or alternatively, whether it is right or wrong, or they are asked whether they agree or disagree with the sentence).
-The crucial condition for assessing implicature rates in these kinds of studies typically consists of a case where the facts are such that the stronger alternative is true and the utterance is underinformative.
+The crucial condition for assessing implicature rates in these kinds of studies typically consists of a case where the facts are such that the stronger alternative is true and the target utterance is thus also true but underinformative.
 For instance, @Bott2004 asked participants to judge sentences like 'Some elephants are mammals', when world knowledge dictates that all elephants are mammals.
 Similarly, @DegenTanenhaus2015 asked participants to judge sentences like 'You got some of the gumballs' in situations where the visual evidence indicated that the participant received all the gumballs from a gumball machine.
-In these kinds of scenarios, the story goes, if a participant responds 'FALSE', that indicates that they computed a scalar implicature, eg to the effect of 'Not all elephants are mammals' or 'You didn't get all of the gumballs'.
-If instead a participant responds 'TRUE', that is taken to indicate that they interpreted the utterance literally as `Some, and possibly all, elephants are mammals' or 'You god some, and possibly all, of the gumballs'.
+In these kinds of scenarios, the story goes, if a participant responds 'FALSE', that indicates that they computed a scalar implicature, eg to the effect of 'Not all elephants are mammals' or 'You didn't get all of the gumballs', which is (globally or contextually) false.
+If instead a participant responds 'TRUE', that is taken to indicate that they interpreted the utterance literally as `Some, and possibly all, elephants are mammals' or 'You got some, and possibly all, of the gumballs'.
 
-People who have discussed issues with the TVJP:
-@BenzGotzner; @Geurts2009; @Geurts2010; @Katsos2011
+Given the centrality of the theoretical notion of 'implicature rate' to much of experimental pragmatics, there is to date a surprising lack of discussion of the basic assumption that it is adequately captured by the  proportion of FALSE responses in truth-value judgment tasks (but see @BenzGotzner; @Geurts2009; @Degen2014; @Katsos2011).
+Indeed, the scalar implicature acquisition literature was shaken up when @Katsos2011 showed that simply by introducing an additional response option, children started looking much more pragmatic than had been previously observed in a binary judgment paradigm.
+@Katsos allowed children to distribute 1, 2, or 3 strawberries to a puppet depending on 'how good the puppet said it'.
+The result was that children gave on average fewer strawberries to the puppet when he produced underinformative utterances compared to when he produced literally true and pragmatically felicitous utterances, suggesting that children do, in fact, display pragmatic ability even at ages when they had previously appeared not to.
 
-* @demarneffetonhauser for investigations of scalar adjectives,
+But this raises an important question: in truth-value judgment task, how do we know whether an interpretation is literal or the result of an implicature computation?
+The binary choice task typically used is appealing in part because it allows for a direct mapping from response options -- TRUE and FALSE -- to interpretations -- literal and pragmatic.
+That the seeming simplicity of this mapping is illusory becomes apparent once a third response option is introduced, as in the @Katsos2011 case.
+How is the researcher to interpret the intermediate option?
+@Katsos2011 grouped the intermediate option with the negative endpoint of the scale for the purpose of categorizing judgments as literal vs.
+pragmatic.
+But it seems just as plausible that they could have grouped it with the positive endpoint of the scale and taken the hard line that only truly FALSE responses constitute a full-fledged implicature.
+The point here is that there has been remarkably little consideration of **linking functions** between behavioral measures and theoretical constructs in experimental pragmatics, a problem in many subfields of psycholinguistics @TanenhausXXX.
+We argue that it is time to engage more seriously with these issues.
+
+We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth-value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates?
+Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of **interpretation**.
+And second, that listeners either do or do not compute an implicature on any given occasion.
+In the Discussion we will discuss both of these issues.
+First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' **production** probabilities.
+This will suggest a completely different class of linking functions.
+And second, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics.
+This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.
+
+Consider a setup in which a listener is presented a card with a depiction of either one or two animals (see the figure below for an example).
+As in a standard truth-value judgment task, the listener then observes an underinformative utterance about this card (e.g., 'There is a cat or a dog on the card') and is asked to provide a judgment on a scale from 2 to 5 response options, with endpoints 'wrong' and 'right'.
+In the binary case, this reproduces the standard truth-value judgment task.
+**XXX say briefly sth about wrong/right vs true/false and agree/disagree**.
+The figure below exemplifies (some of) the researcher's options for grouping responses.
+Under what we will call the 'Strong link' assumption, only the negative endpoint of the scale is interpreted as evidence for a scalar implicature having been computed.
+Under the 'Weak link' assumption, in contrast, any response that does not correspond to the positive endpoint of the scale is interpreted as evidence for a scalar implicature having been computed.
+Intermediate grouping schemes are also possible, but these are the ones we will consider here.
+Note that for the binary case, the Weak and Strong link return the same categorization scheme, but for any number of response options greater than 2, the Weak and Strong link can in principle lead to differences in inferences about implicature rate.
 
@@
 
-* In a truth-value judgment task, how do we know whether an interpretation is literal or the result of an implicature computation?
+Let's examine an example.
+Assume three response options (wrong, neither, right).
+Assume further that a third of participants each gave each of the three responses, i.e., the distributions of responses is 1/3, 1/3, and 1/3.
+Under the Strong link, we infer that this task yielded an implicature rate of 2/3.
+Under the Weak link, we infer that this task yielded an implicature rate of 1/3.
+This is quite a drastic difference if we are for instance interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
+Under the Strong link, we would conclude that scalar implicatures are not defaults.
+Under the Weak link, we would conclude that they are.
 
-Explain the setup
-* the speaker produces weaker alternative from the scale
-* the facts are such that the stronger alternative is true
+In the experiment reported in the following section, we presented participants with exactly this setup.
+Different groups of participants were presented with different numbers of response options.
+We categorized their responses according to the Weak and the Strong link and tested whether number of response options and categorization scheme leads to different conclusions about implicature rates.
 
-Traditional Linking Hypotheses:
-* If an implicature is calculated, the participant chooses a Non-True/Non-Right response
-* If an implicature is calculated, the participant chooses the Wrong/False response
-* If an implicature is calculated, the participant chooses the lower end of the scale (2: wrong/False, 3: wrong, 4: wrong/kinda-wrong, 5: wrong/kinda-wrong)
+# Experiment
 
-Questions:
-* Do these linking hypotheses give us different measures of implicature computation?
-* If they do differ, which one is most stable?
-
-Alternative Linking Hypothesis:
-* RSA: Response behavior across conditions (utterance-card combinations) and dependent measures can be predicted by a linking hypothesis that assumes that participants are behaving like soft-optimal RSA speakers and provide a particular response (eg TRUE) to an utterance u if the RSA speaker probability of u (given the card) is within a particular probability interval (eg, within the interval [theta, 1]).
-
-* Differences between traditional approaches and RSA: 1.
-The traditional linking hypotheses are based on a binary implicature/literal theory of pragmatic reasoning but RSA gives a continuous measure of pragmatic reasoning and allows for better predicting response behavior with multiple options.
-
-# Background
-
-* discussing the ways people in tha past have measured the "implicature rate".
-* it seems like the literature takes the n(not-True)/n(Total) as the proporition of responses caused by implicature calculation
-* BUT, I remember that Jesse Snedeker said it's NOT n(not-True)/n(Total) but it is n(False)/n(Total)
-* However, this is probably not a consensus in the field because Katsos & Bishop consider the mid-point response "big" on the scale small-big-huge (strawberry) to be the result of implicture caculation
-
-* what is the most common measure of "implicature rate" in the literature?
-Binary True/False: Noveck 2001, Chemla & Spector 2011, 
-Ternary: Katsos & Bishop 2011
-
-# Methods
+## Methods
 
@@
 
-## Participants
+###  Participants
 
@@
 
-## Procedure
+### Procedure
 
-The study was administered online and through Amazon Mechanical Turk.
+The study was administered online through Amazon Mechanical Turk.
 Participants were introduced to a set of cards with pictures of one or two animals (Figure \@ref(fig:stimuli)).
 They were told that a blindfolded fictional character called Bob is going to guess what animals are on the card.
-In each trial, participants saw a card as well as a sentence representing Bob's guess.
-For example they saw a card with a cat on it and read the sentence "there is a cat on the card." The study ended after 24 trials.
-At the end participants were asked about their
-You can access and view [the online study here]().
+On each trial, participants saw a card as well as a sentence representing Bob's guess.
+For example, they saw a card with a cat on it and read the sentence "There is a cat on the card." The study ended after 24 trials.
+At the end participants optionally provided demographic information.
+You can access and view [the online study here](**XXX masoud insert link**).
 
-## Design and Materials
+### Design and Materials
 
@@
 
-## Pre-registered Analysis
+## Results
 
@@
 A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.
-
-# Results
 
@@
 
-# Analysis
+### Analysis
 
@@
 
-# Modeling
+# Discussion
 
-# Discussion
+Alternative Linking Hypothesis:
+* RSA: Response behavior across conditions (utterance-card combinations) and dependent measures can be predicted by a linking hypothesis that assumes that participants are behaving like soft-optimal RSA speakers and provide a particular response (eg TRUE) to an utterance u if the RSA speaker probability of u (given the card) is within a particular probability interval (eg, within the interval [theta, 1]).
+
+* Differences between traditional approaches and RSA: 1.
+The traditional linking hypotheses are based on a binary implicature/literal theory of pragmatic reasoning but RSA gives a continuous measure of pragmatic reasoning and allows for better predicting response behavior with multiple options.
 

### 2018-04-29 writeup.tex
added writeup files

@@
 scalar implicatures have served as a test bed for many questions in
-experimental pragmatics, including, but not limited to: 1. Are scalar
-inferences default inferences (in the sense of default as arising unless
-blocked by marked contexts \textbf{XXX horn, levinson, degen2015)}? 2.
-Are scalar inferences default inferences (in the sense that they are
+experimental pragmatics, including, but not limited to:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Are scalar inferences default inferences, in the sense that they arise
+  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
+  Levinson, 2000)?
+\item
+  Are scalar inferences default inferences, in the sense that they are
   computed automatically in online processing and only cancelled by
-context in a second effortful step if required by context)
-({\textbf{???}}; Bott \& Noveck, 2004; Breheny et al., 2006; Grodner et
-al., 2010; Huang \& Snedeker, 2009)? 3. What are the (linguistic and
-extra-linguistic) factors that affect whether a scalar implicature is
-derived {[}({\textbf{???}});DegenTanenhaus2015; DegenTanenhaus2016;
-Degen2015; DegenGoodman2014; BergenGrodner2012; Breheny2006;
-FergusonBreheny2013;DeMarneffeTonhauser;DeNeys2007;Bonnefon{]}? 4. At
-what age do children acquire the ability to compute implicatures
-{[}Noveck2001; Reboul; Papafragou; Barner; Frank; Musolino{]}?
-\textbf{XXX fill in refs}
+  context in a second effortful step if required by context) {[}Bott and
+  Noveck (2004);Breheny et al. (2006);Degen and Tanenhaus (2016);Grodner
+  et al. (2010);Huang and Snedeker (2009);Politzer-Ahles and Fiorentino
+  (2013);Tomlinson2013{]}?
+\item
+  What are the (linguistic and extra-linguistic) factors that affect
+  whether a scalar implicature is derived {[}Zondervan (2010);Degen and
+  Tanenhaus (2015); Degen and Tanenhaus (2016); Degen (2015); Degen and
+  Goodman (2014); Bergen and Grodner (2012); Breheny et al. (2006);
+  Breheny, Ferguson, and Katsos (2013);Marneffe and Tonhauser (2016);De
+  Neys and Schaeken (2007);Bonnefon, Feeney, and Villejoubert
+  (2009);Chemla2011;Potts2015{]}?
+\item
+  How much diversity is there across implicature types, and within
+  scalar implicatures across scale types, in whether or not an
+  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
+  Tiel, Miltenburg, Zevakhina, \& Geurts, 2014)?
+\item
+  At what age do children acquire the ability to compute implicatures
+  (Barner, Brooks, \& Bale, 2011; Katsos \& Bishop, 2011; Frank;
+  Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou, 2004)?
+\end{enumerate}
 
-CONTINUE HERE: motivation for examining implicature rate assumptions:
+In addressing all of these questions, it has been crucial to obtain
+estimates of \textbf{implicature rates}. For 1., implicature rates from
+experimental tasks can be taken to inform whether scalar implicatures
+should be considered default inferences. For 2., processing measures on
+responses that indicate implicatures can be compared to processing
+measures on responses that indicate literal interpretations. For 3.,
+contextual effects can be examined by comparing implicature rates across
+contexts. For 4., implicature rates can be compared across scales (or
+across implicature types). For 5., implicature rates can be compared
+across age groups.
 
-\begin{itemize}
-\item
-  surging interest in differences in implicature rates (eg van tiel,
-  dgen tanenhaus)
-\item
-  implicature rates serve as basis for claims about online processing
-  (bott \& noveck, degen tanenhaus)
-\item
-  implicature rates serve as basis for claims about children (bishop
-  katsos, barner, frank)
-\item
-  add ({\textbf{???}})
-\item
-  ({\textbf{???}}) for investigations of scalar adjectives, and
-  ({\textbf{???}})
-\end{itemize}
+A standard measure that has stood proxy for implicature rate across many
+studies is the proportion of \enquote{pragmatic} judgments in
+truth-value judgment paradigms {[}Bott and Noveck (2004);Noveck
+(2001);Noveck and Posada (2003);Chemla and Spector (2011);Geurts and
+Pouscoulous (2009);Degen and Tanenhaus (2015);De Neys and Schaeken
+(2007);Degen2014{]}. In these kinds of tasks, participants are provided
+a set of facts, either presented visually or via their own knowledge of
+the world. They are then asked to judge whether a sentence intended to
+describe those facts is true or false (or alternatively, whether it is
+right or wrong, or they are asked whether they agree or disagree with
+the sentence). The crucial condition for assessing implicature rates in
+these kinds of studies typically consists of a case where the facts are
+such that the stronger alternative is true and the target utterance is
+thus also true but underinformative. For instance, Bott and Noveck
+(2004) asked participants to judge sentences like \enquote{Some
+elephants are mammals}, when world knowledge dictates that all elephants
+are mammals. Similarly, Degen and Tanenhaus (2015) asked participants to
+judge sentences like \enquote{You got some of the gumballs} in
+situations where the visual evidence indicated that the participant
+received all the gumballs from a gumball machine. In these kinds of
+scenarios, the story goes, if a participant responds \enquote{FALSE},
+that indicates that they computed a scalar implicature, eg to the effect
+of \enquote{Not all elephants are mammals} or \enquote{You didn't get
+all of the gumballs}, which is (globally or contextually) false. If
+instead a participant responds \enquote{TRUE}, that is taken to indicate
+that they interpreted the utterance literally as `Some, and possibly
+all, elephants are mammals' or \enquote{You got some, and possibly all,
+of the gumballs}.
+
+Given the centrality of the theoretical notion of \enquote{implicature
+rate} to much of experimental pragmatics, there is to date a surprising
+lack of discussion of the basic assumption that it is adequately
+captured by the proportion of FALSE responses in truth-value judgment
+tasks (but see ({\textbf{???}}); Geurts and Pouscoulous (2009); Degen
+and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
+implicature acquisition literature was shaken up when Katsos and Bishop
+(2011) showed that simply by introducing an additional response option,
+children started looking much more pragmatic than had been previously
+observed in a binary judgment paradigm. ({\textbf{???}}) allowed
+children to distribute 1, 2, or 3 strawberries to a puppet depending on
+\enquote{how good the puppet said it}. The result was that children gave
+on average fewer strawberries to the puppet when he produced
+underinformative utterances compared to when he produced literally true
+and pragmatically felicitous utterances, suggesting that children do, in
+fact, display pragmatic ability even at ages when they had previously
+appeared not to.
+
+But this raises an important question: in truth-value judgment task, how
+do we know whether an interpretation is literal or the result of an
+implicature computation? The binary choice task typically used is
+appealing in part because it allows for a direct mapping from response
+options -- TRUE and FALSE -- to interpretations -- literal and
+pragmatic. That the seeming simplicity of this mapping is illusory
+becomes apparent once a third response option is introduced, as in the
+Katsos and Bishop (2011) case. How is the researcher to interpret the
+intermediate option? Katsos and Bishop (2011) grouped the intermediate
+option with the negative endpoint of the scale for the purpose of
+categorizing judgments as literal vs.~pragmatic. But it seems just as
+plausible that they could have grouped it with the positive endpoint of
+the scale and taken the hard line that only truly FALSE responses
+constitute a full-fledged implicature. The point here is that there has
+been remarkably little consideration of \textbf{linking functions}
+between behavioral measures and theoretical constructs in experimental
+pragmatics, a problem in many subfields of psycholinguistics
+({\textbf{???}}). We argue that it is time to engage more seriously with
+these issues.
+
+We begin by reporting an experiment that addresses the following
+question: do the number of response options provided in a truth-value
+judgment task and the way that responses are grouped into pragmatic
+(\enquote{SI}) and literal (\enquote{no SI}) change inferences about
+scalar implicature rates? Note that this way of asking the question
+presupposes two things: first, that whatever participants are doing in a
+truth-value judgment task, the behavioral measure can be interpreted as
+providing a measure of \textbf{interpretation}. And second, that
+listeners either do or do not compute an implicature on any given
+occasion. In the Discussion we will discuss both of these issues. First,
+following Degen and Goodman (2014), we will offer some remarks on why
+truth-value judgment tasks are better thought of as measuring
+participants' estimates of speakers' \textbf{production} probabilities.
+This will suggest a completely different class of linking functions. And
+second, we discuss an alternative conception of scalar implicature as a
+probabilistic phenomeonen, a view that has recently rose to prominence
+in the subfield of probabilistic pragmatics. This alternative conception
+of scalar implicature, we argue, affords developing and testing
+quantitative linking functions in a rigorous and motivated way.
+
+Consider a setup in which a listener is presented a card with a
+depiction of either one or two animals (see the figure below for an
+example). As in a standard truth-value judgment task, the listener then
+observes an underinformative utterance about this card (e.g.,
+\enquote{There is a cat or a dog on the card}) and is asked to provide a
+judgment on a scale from 2 to 5 response options, with endpoints
+\enquote{wrong} and \enquote{right}. In the binary case, this reproduces
+the standard truth-value judgment task. \textbf{XXX say briefly sth
+about wrong/right vs true/false and agree/disagree}. The figure below
+exemplifies (some of) the researcher's options for grouping responses.
+Under what we will call the \enquote{Strong link} assumption, only the
+negative endpoint of the scale is interpreted as evidence for a scalar
+implicature having been computed. Under the \enquote{Weak link}
+assumption, in contrast, any response that does not correspond to the
+positive endpoint of the scale is interpreted as evidence for a scalar
+implicature having been computed. Intermediate grouping schemes are also
+possible, but these are the ones we will consider here. Note that for
+the binary case, the Weak and Strong link return the same categorization
+scheme, but for any number of response options greater than 2, the Weak
+and Strong link can in principle lead to differences in inferences about
+implicature rate.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  In a truth-value judgment task, how do we know whether an
-  interpretation is literal or the result of an implicature computation?
-\end{itemize}
+Let's examine an example. Assume three response options (wrong, neither,
+right). Assume further that a third of participants each gave each of
+the three responses, i.e., the distributions of responses is 1/3, 1/3,
+and 1/3. Under the Strong link, we infer that this task yielded an
+implicature rate of 2/3. Under the Weak link, we infer that this task
+yielded an implicature rate of 1/3. This is quite a drastic difference
+if we are for instance interested in whether scalar implicatures are
+inference defaults and we would like to interpret an implicature rate of
+above an arbitrary threshold (e.g., 50\%) as evidence for such a claim.
+Under the Strong link, we would conclude that scalar implicatures are
+not defaults. Under the Weak link, we would conclude that they are.
 
-Explain the setup * the speaker produces weaker alternative from the
-scale * the facts are such that the stronger alternative is true
+In the experiment reported in the following section, we presented
+participants with exactly this setup. Different groups of participants
+were presented with different numbers of response options. We
+categorized their responses according to the Weak and the Strong link
+and tested whether number of response options and categorization scheme
+leads to different conclusions about implicature rates.
 
-Traditional Linking Hypotheses: * If an implicature is calculated, the
-participant chooses a Non-True/Non-Right response * If an implicature is
-calculated, the participant chooses the Wrong/False response * If an
-implicature is calculated, the participant chooses the lower end of the
-scale (2: wrong/False, 3: wrong, 4: wrong/kinda-wrong, 5:
-wrong/kinda-wrong)
+\section{Experiment}\label{experiment}
 
-Questions: * Do these linking hypotheses give us different measures of
-implicature computation? * If they do differ, which one is most stable?
+\subsection{Methods}\label{methods}
 
-Alternative Linking Hypothesis: * RSA: Response behavior across
-conditions (utterance-card combinations) and dependent measures can be
-predicted by a linking hypothesis that assumes that participants are
-behaving like soft-optimal RSA speakers and provide a particular
-response (eg TRUE) to an utterance u if the RSA speaker probability of u
-(given the card) is within a particular probability interval (eg, within
-the interval {[}theta, 1{]}).
-
-\begin{itemize}
-\tightlist
-\item
-  Differences between traditional approaches and RSA: 1. The traditional
-  linking hypotheses are based on a binary implicature/literal theory of
-  pragmatic reasoning but RSA gives a continuous measure of pragmatic
-  reasoning and allows for better predicting response behavior with
-  multiple options.
-\end{itemize}
-
-\section{Background}\label{background}
-
-\begin{itemize}
-\item
-  discussing the ways people in tha past have measured the
-  \enquote{implicature rate}.
-\item
-  it seems like the literature takes the n(not-True)/n(Total) as the
-  proporition of responses caused by implicature calculation
-\item
-  BUT, I remember that Jesse Snedeker said it's NOT n(not-True)/n(Total)
-  but it is n(False)/n(Total)
-\item
-  However, this is probably not a consensus in the field because Katsos
-  \& Bishop consider the mid-point response \enquote{big} on the scale
-  small-big-huge (strawberry) to be the result of implicture caculation
-\item
-  what is the most common measure of \enquote{implicature rate} in the
-  literature? Binary True/False: Noveck 2001, Chemla \& Spector 2011,
-  Ternary: Katsos \& Bishop 2011
-\end{itemize}
-
-\section{Methods}\label{methods}
-
-\subsection{Participants}\label{participants}
+\subsubsection{Participants}\label{participants}
 
@@
 
-\subsection{Procedure}\label{procedure}
+\subsubsection{Procedure}\label{procedure}
 
-The study was administered online and through Amazon Mechanical Turk.
+The study was administered online through Amazon Mechanical Turk.
 Participants were introduced to a set of cards with pictures of one or
@@
 blindfolded fictional character called Bob is going to guess what
-animals are on the card. In each trial, participants saw a card as well
-as a sentence representing Bob's guess. For example they saw a card with
-a cat on it and read the sentence \enquote{there is a cat on the card.}
-The study ended after 24 trials. At the end participants were asked
-about their\\
-You can access and view \href{}{the online study here}.
+animals are on the card. On each trial, participants saw a card as well
+as a sentence representing Bob's guess. For example, they saw a card
+with a cat on it and read the sentence \enquote{There is a cat on the
+card.} The study ended after 24 trials. At the end participants
+optionally provided demographic information. You can access and view
+\href{**XXX\%20masoud\%20insert\%20link**}{the online study here}.
 
-\subsection{Design and Materials}\label{design-and-materials}
+\subsubsection{Design and Materials}\label{design-and-materials}
 
@@
 
-\subsection{Pre-registered Analysis}\label{pre-registered-analysis}
+\subsection{Results}\label{results}
 
@@
 implicature in the experimental task.
-
-\section{Results}\label{results}
 
@@
 
-\section{Analysis}\label{analysis}
+\subsubsection{Analysis}\label{analysis}
 
@@
 
-\section{Modeling}\label{modeling}
+\section{Discussion}\label{discussion}
 
-\section{Discussion}\label{discussion}
+Alternative Linking Hypothesis: * RSA: Response behavior across
+conditions (utterance-card combinations) and dependent measures can be
+predicted by a linking hypothesis that assumes that participants are
+behaving like soft-optimal RSA speakers and provide a particular
+response (eg TRUE) to an utterance u if the RSA speaker probability of u
+(given the card) is within a particular probability interval (eg, within
+the interval {[}theta, 1{]}).
+
+\begin{itemize}
+\tightlist
+\item
+  Differences between traditional approaches and RSA: 1. The traditional
+  linking hypotheses are based on a binary implicature/literal theory of
+  pragmatic reasoning but RSA gives a continuous measure of pragmatic
+  reasoning and allows for better predicting response behavior with
+  multiple options.
+\end{itemize}
 
@@
 \hypertarget{refs}{}
-\hypertarget{ref-bott2004}{}
+\hypertarget{ref-Barner2011}{}
+Barner, D., Brooks, N., \& Bale, A. (2011). Accessing the unsaid: the
+role of scalar alternatives in children's pragmatic inference.
+\emph{Cognition}, \emph{118}(1), 84--93.
+doi:\href{https://doi.org/10.1016/j.cognition.2010.10.010}{10.1016/j.cognition.2010.10.010}
+
+\hypertarget{ref-Bergen2012}{}
+Bergen, L., \& Grodner, D. J. (2012). Speaker knowledge influences the
+comprehension of pragmatic inferences. \emph{Journal of Experimental
+Psychology. Learning, Memory, and Cognition}, \emph{38}(5), 1450--60.
+doi:\href{https://doi.org/10.1037/a0027850}{10.1037/a0027850}
+
+\hypertarget{ref-Bonnefon2009}{}
+Bonnefon, J.-F., Feeney, A., \& Villejoubert, G. (2009). When some is
+actually all: scalar inferences in face-threatening contexts.
+\emph{Cognition}, \emph{112}(2), 249--58.
+doi:\href{https://doi.org/10.1016/j.cognition.2009.05.005}{10.1016/j.cognition.2009.05.005}
+
+\hypertarget{ref-Bott2004}{}
 Bott, L., \& Noveck, I. (2004). Some utterances are underinformative:
@@
 doi:\href{https://doi.org/10.1016/j.jml.2004.05.006}{10.1016/j.jml.2004.05.006}
+
+\hypertarget{ref-Breheny2013}{}
+Breheny, R., Ferguson, H. J., \& Katsos, N. (2013). Taking the epistemic
+step: Toward a model of on-line access to conversational implicatures.
+\emph{Cognition}, \emph{126}(3), 423--40.
+doi:\href{https://doi.org/10.1016/j.cognition.2012.11.012}{10.1016/j.cognition.2012.11.012}
 
@@
 
+\hypertarget{ref-Chemla2011}{}
+Chemla, E., \& Spector, B. (2011). Experimental Evidence for Embedded
+Scalar Implicatures. \emph{Journal of Semantics}, \emph{28}(3),
+359--400.
+
+\hypertarget{ref-DeNeys2007}{}
+De Neys, W., \& Schaeken, W. (2007). When People Are More Logical Under
+Cognitive Load - Dual Task Impact on Scalar Implicature.
+\emph{Experimental Psychology}, \emph{54}(2), 128--133.
+doi:\href{https://doi.org/10.1027/1618-3169.54.2.128}{10.1027/1618-3169.54.2.128}
+
+\hypertarget{ref-Degen2015}{}
+Degen, J. (2015). Investigating the distribution of 'some' (but not
+'all') implicatures using corpora and web-based methods. \emph{Semantics
+and Pragmatics}, \emph{8}(11), 1--55.
+doi:\href{https://doi.org/10.3765/sp.8.11}{10.3765/sp.8.11}
+
+\hypertarget{ref-Degen2014}{}
+Degen, J., \& Goodman, N. D. (2014). Lost your marbles? The puzzle of
+dependent measures in experimental pragmatics. \emph{Proceedings of the
+36th Annual Conference of the Cognitive Science Society}, 397--402.
+
 \hypertarget{ref-DegenTanenhaus2015}{}
@@
 doi:\href{https://doi.org/10.1111/cogs.12171}{10.1111/cogs.12171}
+
+\hypertarget{ref-DegenTanenhaus2016}{}
+Degen, J., \& Tanenhaus, M. K. (2016). Availability of Alternatives and
+the Processing of Scalar Implicatures: A Visual World Eye-Tracking
+Study. \emph{Cognitive Science}, \emph{40}(1), 172--201.
+doi:\href{https://doi.org/10.1111/cogs.12227}{10.1111/cogs.12227}
+
+\hypertarget{ref-Doran2012}{}
+Doran, R., Ward, G., Larson, M., McNabb, Y., \& Baker, R. E. (2012). A
+novel experimental paradigm for distinguishing between what is said and
+what is implicated. \emph{Language}, \emph{88}, 124--154.
 
@@
 
+\hypertarget{ref-horn1984}{}
+Horn, L. (1984). Toward a new taxonomy for pragmatic inference: Q-based
+and R-based implicature. In D. Schiffrin (Ed.), \emph{Meaning, form, and
+use in context: Linguistic applications} (pp. 11--42). Washington:
+Georgetown University Press.
+
 \hypertarget{ref-huang2009}{}
@@
 \emph{Cognitive Psychology}, \emph{58}, 376--415.
+
+\hypertarget{ref-Katsos2011}{}
+Katsos, N., \& Bishop, D. V. M. (2011). Pragmatic tolerance:
+implications for the acquisition of informativeness and implicature.
+\emph{Cognition}, \emph{120}(1), 67--81.
+doi:\href{https://doi.org/10.1016/j.cognition.2011.02.015}{10.1016/j.cognition.2011.02.015}
+
+\hypertarget{ref-levinson2000}{}
+Levinson, S. C. (2000). \emph{Presumptive Meanings - The Theory of
+Generalized Conversational Implicature}. MIT Press.
+
+\hypertarget{ref-DeMarneffe2017}{}
+Marneffe, M.-C. de, \& Tonhauser, J. (2016). Inferring meaning from
+indirect answers to polar questions: The contribution of the
+rise-fall-rise contour. In E. Onea, M. Zimmermann, \& K. von Heusinger
+(Eds.), \emph{Questions in discourse}. Leiden: Brill Publishing.
+
+\hypertarget{ref-Musolino2004}{}
+Musolino, J. (2004). The semantics and acquisition of number words:
+integrating linguistic and developmental perspectives. \emph{Cognition},
+\emph{93}(1), 1--41.
+doi:\href{https://doi.org/10.1016/j.cognition.2003.10.002}{10.1016/j.cognition.2003.10.002}
+
+\hypertarget{ref-Noveck2001}{}
+Noveck, I. (2001). When children are more logical than adults:
+experimental investigations of scalar implicature. \emph{Cognition},
+\emph{78}(2), 165--188. Retrieved from
+\url{http://www.ncbi.nlm.nih.gov/pubmed/11074249}
 
@@
 
+\hypertarget{ref-Noveck2003}{}
+Noveck, I., \& Posada, A. (2003). Characterizing the Time Course of an
+Implicature: an Evoked Potentials Study. \emph{Brain and Language},
+\emph{85}(2), 203--210.
+doi:\href{https://doi.org/10.1016/S0093-934X(03)00053-1}{10.1016/S0093-934X(03)00053-1}
+
+\hypertarget{ref-Papafragou2004}{}
+Papafragou, A., \& Tantalou, N. (2004). Children's Computation of
+Implicatures. \emph{Language Acquisition}, \emph{12}(1), 71--82.
+
+\hypertarget{ref-Politzer-Ahles2013}{}
+Politzer-Ahles, S., \& Fiorentino, R. (2013). The Realization of Scalar
+Inferences: Context Sensitivity without Processing Cost. \emph{PLoS
+ONE}, \emph{8}(5).
+doi:\href{https://doi.org/10.1371/journal.pone.0063943}{10.1371/journal.pone.0063943}
+
+\hypertarget{ref-VanTiel2014}{}
+Tiel, B. van, Miltenburg, E. van, Zevakhina, N., \& Geurts, B. (2014).
+Scalar diversity. \emph{Journal of Semantics}.
+doi:\href{https://doi.org/10.1093/jos/ffu017}{10.1093/jos/ffu017}
+
+\hypertarget{ref-Zondervan2010}{}
+Zondervan, A. (2010). \emph{Scalar implicatures or focus: an
+experimental approach} (PhD thesis). Universiteit Utrecht, Amsterdam.
+
 \end{document}

### 2018-04-29 writeup.Rmd
edits to discussion section

@@
 
+A simple visual inspection of our results suggests that any variant of the Traditional Linking Hypothesis will yield unsatisfying empirical coverage with regards to participants’ behavior in truth value judgment tasks.
+Recall that according to this hypothesis, scalar implicature is conceptualized as a binary, categorical affair: an implicature is either ‘calculated,’ or it isn’t.
+This assumption has implications for how we approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had a cat and a dog on it?
+
+On the Traditional story, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
+“Wrong”)  due to some other cognitive reflex which ‘overrode’ the implicature; or some mixture of (b) and (c).
+We might similarly posit that one or both of these factors underlie the variation in the ternary, quatenary, and quinary conditions (e.g.
+why were participants roughly split between “Right” and “Kind of right” when the utterance was cat or dog and the card had a cat and a dog?).
+There is an established cottage industry of pragmatics research which approaches the problem of behavioral variation in exactly these ways, exploring the factors which “license” implicature calculation or “suppress” its anticipated behavioral expression (c.f.
+__), but the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data (and we should stress that even in this respect, the industry has yet to fully deliver the goods!).
+
+The Alternative Linking Hypothesis contrasts with the Traditional Linking Hypothesis in that the former is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+[recap RSA model here?
+Maybe show how it gets the right basic qualitative pattern, i.e.
+$P_L$(a and b| “a or b”) $<$ $P_L$(a | “or”); $P_L$(a and b| “a or b”) $<$ $P_L$(b | “or”) ]
+
+Following Degen & Goodman (2014), we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA).
+For a given utterance u and an intended communicated meaning w, $S_1$(u | w) outputs a conditional probability of u given w.
+For example, in the binary condition of our experiment where a participant evaluated cat or dog when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of hearing the utterance cat or dog given a dog and cat card $S_1$(cat or dog | cat and dog).
+
+One desideratum of a linking hypothesis given this view of pragmatic competence is to transform this probability value into a categorical output (e.g.
+“Right”/”Wrong” in the case of the binary condition).
+This can be achieved by positing that participants ‘filter out’ low-probability utterances given an intended communicated meaning.
+We model a responder, R, who in the binary condition responds “Right” to an utterance u in world w just in case $S_1$(u | w) exceeds some probability threshold $\theta$:
+
+R(u, w, $\theta$) 
+    = “Right” iff $S_1$(u | w) $>$ $\theta$
+    = “Wrong” otherwise
+
+In the experiment conditions where there are more than two choices, we model the range of possible behavioral responses for R with the introduction of intermediate probability thresholds.
+For example, in the ternary condition, R(u, w, $\theta_1$ , $\theta_2$)  is “Right” iff $S_1$(u | w) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | w) > $\theta_2$.
+To fully generalize the model to our five experimental conditions, we say that R takes as its input an utterance u and a world state w and a number of threshold variables dependent on a variable c, corresponding to the experimental condition in which the participant finds herself (e.g.
+the range of possible responses available to R).
+
+Given c = “ternary”
+
+R(u, w, $\theta_1$ , $\theta_2$)  
+    = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+    = “Neither” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$  
+    = “Wrong” otherwise
+
+Given c = “quatenary”
+
+R(u, w, $\theta_1$ , $\theta_2$, $\theta_3$)  
+    = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+    = “Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$  
+    = “Kinda Wrong” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$ 
+    = “Wrong” otherwise
+
+Given c = “quinary”
+
+R(u, w, $\theta_1$ , $\theta_2$, $\theta_3$. $\theta_4$)  
+    = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+    =“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$ 
+    = “Neither” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$  
+    = “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | w) $>$ $\theta_4$ 
+    = “Wrong” otherwise
+
 \newpage

### 2018-04-30 writeup.Rmd
added bda to discussion/analysis

@@
 library(forcats)
+library(webppl)
 # library(brms)
@@
 There is an established cottage industry of pragmatics research which approaches the problem of behavioral variation in exactly these ways, exploring the factors which “license” implicature calculation or “suppress” its anticipated behavioral expression (c.f.
-__), but the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data (and we should stress that even in this respect, the industry has yet to fully deliver the goods!).
+__), but the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
 
@@
 R(u, w, $\theta$)
+
 = “Right” iff $S_1$(u | w) $>$ $\theta$
+
 = “Wrong” otherwise
@@
 R(u, w, $\theta_1$ , $\theta_2$)
+
 = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+
 = “Neither” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
+
 = “Wrong” otherwise
@@
 R(u, w, $\theta_1$ , $\theta_2$, $\theta_3$)
+
 = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+
 = “Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
+
 = “Kinda Wrong” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$
+
 = “Wrong” otherwise
@@
 R(u, w, $\theta_1$ , $\theta_2$, $\theta_3$. $\theta_4$)
+
 = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+
 =“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
+
 = “Neither” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$
+
 = “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | w) $>$ $\theta_4$
+
 = “Wrong” otherwise
 
+```{r echo=TRUE, message=FALSE}
+bda <- webppl(program_file = "models/webppl_models/bda_model.wppl")
+
+binary_graph <- ggplot(filter(bda, Parameter == "binary_theta"), aes(x=value))+
+  # facet_wrap(~Parameter, scales = "free") +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, binary condition:")
+
+ternary_graph <- ggplot(filter(bda, Parameter == c("ternary_theta1", "ternary_theta2")), aes(x=value))+
+  facet_wrap(~Parameter, scales = "free") +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, ternary condition:")
+
+quatenary_graph <- ggplot(filter(bda, Parameter == c("quatenary_theta1", "quatenary_theta2", "quatenary_theta3")), aes(x=value))+
+  facet_wrap(~Parameter, scales = "free") +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, quatenary condition:")
+
+quinary_graph <- ggplot(filter(bda, Parameter == c("quinary_theta1", "quinary_theta2", "quinary_theta3", "quinary_theta4")), aes(x=value))+
+  facet_wrap(~Parameter, scales = "free") +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, quinary condition:")
+binary_graph
+ternary_graph
+quatenary_graph
+quinary_graph
+```
 \newpage

### 2018-04-30 writeup.Rmd
completed results section

--- 2018-04-29 writeup.Rmd
@@
 editor_options: 
-  chunk_output_type: console
+  chunk_output_type: inline
 ---
@@
 library(forcats)
-# library(brms)
+library(brms)
 theme_set(theme_bw(18))
@@
 At the end participants optionally provided demographic information.
-You can access and view [the online study here](**XXX masoud insert link**).
+We also asked participants if they had any prior training in logic.
+You can access and view on the study's [online repository](https://github.com/thegricean/si-paradigms/).
 
@@
 
-```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3, fig.height=1.5, set.cap.width=T, num.cols.cap=1, fig.width=1.5,fig.cap = "Cards used in the connective guessing game."}
+```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=2, fig.height=1.5, set.cap.width=T, num.cols.cap=1, fig.width=1.5,fig.cap = "Cards used in the connective guessing game."}
 cards_img <- jpeg::readJPEG("experiments/figs/cards.jpg")
@@
 
-The design had two main manipulaitons: the type of card and the type of guess.
+The study had two main manipulaitons within participants: the type of card and the type of guess.
 There were two types of cards.
@@
 *There is a cat or a dog*).
-
 In each trial, the animal labels used in the guess and the animal images on the card may have no overlap (e.g.
-Image: dog, Guess: *There is a cat or an elephant*), a partial overlap (e.g.
-Image: Cat, Guess: *There is a cat or an elephant*), or a total overlap (e.g.
-Image: cat and elephant, Guess: *There is a cat or an elephant*).
+Image: cat, Guess: *There is an elephant*), a partial overlap (e.g.
+Image: cat, Guess: *There is a cat or a dog*), or a total overlap (e.g.
+Image: cat and dog, Guess: *There is a cat or a dog*).
 Crossing the number of animals on the card, the type of guess, and the overlap between the guess and the card results in 12 different possible trial types.
@@
 false trials.
+Three trials were randomly selected from each of the 8 trial-types, for a total of 24 trials.
+The order of these 24 trials was randomized as well.
 
-The study used five different types of measurements.
-1.
-two-options (true vs.
-false) 2.
-two-options (wrong vs.
-right) 3.
-three-options (wrong, neither, right) 4.
-four-options (wrong, kinda wrong, kinda right, right) 5.
-five-options (wrong, kinda wrong, neither, kinda right, right).
+Participants could derive implicatures in two trial types.
+First, the trial type in which two animals were present on the card (e.g.
+cat and dog) but Bob guessed only one of them (e.g.
+"there is a cat").
+Such trials can have a literal interpretation (cat and possibly more) or an exhaustive interpretation (only cat).
+We refer to them as "exhaustive".
+The second trial type with implicatures was the one in which two animals were on the card (e.g.
+cat and dog) and Bob used a disjunciton (e.g.
+cat or dog).
+These trials can have a literal (inclusive) interpretation (e.g.
+cat or dog or both), or an exclusive interpretation (e.g.
+cat or dog, not both).
+We refer to these trials as "scalar".
+The following four trial types were used as experimental control: two trial types where there was no overlap between the guess (e.g.
+elephant) and the animal(s) on the card (e.g.
+cat, cat and dog); and two trial types where the animal(s) on the card were correctly guessed.
+For example, if there was only a cat on the card, Bob said "there is a cat" and if there was a cat and a dog, Bob said "there is a cat and a dog".
+
+The study also had a between participant manipulation of the number of response options in the forced choice task.
+Participants were randomly assigned to one of four different conditions.
+The conditions differed with respect to the number of response options: binary (wrong vs.
+right), ternary (wrong, neither, right), quaternary (wrong, kinda wrong, kinda right, right), and quinary (wrong, kinda wrong, neither, kinda right, right).
+We wanted to see if the number of response options in the forced choice task would affect our estimate of the task's "implicature rate".
 
@@
 
-We are primarily concerned with the "rate of implicatures" in an experimental study.
-Two trial types are predicted to include pragmatic implicatures.
-First, trials where there are two animals on the card but the fictional character guesses using the connective *or*; for example "cat or dog" when the card has both a cat and a dog on it.
-We call such trials "scalar" trials.
-Second, trials where there are two animals on the card but the character guesses only one; for example "cat" when the card has a cat and a dog on it.
-We call such trials "exhaustive".
-In our assessment of implicature rate we focus on these two types of trials.
-
-We define "implicature rate" in two ways:
-
-This study set out to test two hypotheses.
-First, that the proportion of pragmatic vs.
-literal responses in a truth values judgement task changes based on the number of response options available to the participants.
-We test this hypothesis formally using a binomial mixed effects model with the fixed effect of response type and the random intercept for participants as well as random intercept and slope for
-
-A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.
-
-```{r binaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' two-alternative forced choice judgments in the connective guessing game."}
+```{r binaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game."}
 
@@
 grid.draw(binary_plot_g)
+
+binaryExh_wrong <- binary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Wrong")
+binaryScalar_wrong <- binary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Wrong")
 ```
 
-```{r ternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
+Here we present the proportion that participants chose the response options in each of the 8 trial types of the binary, ternary, quaternary, and quinary tasks.
+Figure \@ref(fig:binaryPlot) shows the proportion of "right" and "wrong" responses in the binary task.
+Starting from the leftmost column, participants considered a guess "wrong" if the guessed animal was not on the card.
+Moving to the second column, participants considered a guess "right" if the animal on the card was mentioned.
+However, if only one of the two animals on the card was mentioned (exhaustive trials), `r round(binaryExh_wrong$proportion*100)`% of the times participants considered the guess "wrong".
+Moving to the third column, if a conjunction of animals was guessed while only one animal was on the card, participants considered the guess to be "wrong".
+If a conjunction of animals was guessed and both animals were present on the card, all participants considered the guess to be "right" as expected.
+Moving to the forth column, if a disjunction of animals was guessed and only one of the animals was on the card, participants considered the guess to be "right" almost all the time.
+However, if both animals were present (scalar trials), `r round(binaryScalar_wrong$proportion*100)`% of the times participants considered the guess to be "wrong".
+
+```{r ternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game."}
 
@@
 grid.draw(ternary_plot_g)
+
+ternaryExh_wrong <- ternary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Wrong")
+ternaryScalar_wrong <- ternary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Wrong")
+ternaryExh_neither <- ternary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Neither")
+ternaryScalar_neither <- ternary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Neither")
 ```
 
-```{r quaternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
+Figure \@ref(fig:ternaryPlot) shows the proportion of "right", "neither", and "wrong" responses in the ternary task.
+Similar to the binary task, participants considered a guess wrong when the mentioned animal was not on the card.
+They considered the guess "right" when the mentioned animal was on the card.
+However, in exhaustive trials when the fictional character only guessed one of the two animals on the card, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
+If a conjunction of animals was guessed and only one animal was present on the card, participants considered the guess "wrong".
+As expected, when a conjunction was used and both animals were present, participants considered the guess "right".
+Similarly, participants considerd the guess "right" when a disjunction was used and only one of the animals was on the card.
+However, in scalar trials that both animals were on the card and a disjunction was gueassed, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time.
+
+```{r quaternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game."}
 
@@
 grid.draw(quaternary_plot_g)
+
+quaternaryExh_kindaRight <- quaternary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Kinda Right")
+quaternaryExh_wrong <- quaternary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Wrong")
+quaternaryExh_kindaWrong <- quaternary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Kinda Wrong")
+
+quaternaryScalar_wrong <- quaternary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Wrong")
+quaternaryScalar_kindaWrong <- quaternary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Kinda Wrong")
+quaternaryScalar_kindaRight <- quaternary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Kinda Right")
 ```
 
-```{r quinaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' three-alternative forced choice judgments in the connective guessing game."}
+Figure \@ref(fig:quaternaryPlot) shows the proportion of "right", "kinda right", "kinda wrong", and "wrong" responses in the quaternary task.
+Similar to the results seen previously, the control trials turned outas expected.
+Participants considered a guess "wrong" if the animal guessed was not on the card and "right" if it was the only animal on the card.
+If a conjunctin of animals was guessed and both animals were on the card the guess was "right".
+However, when only one of the animals on the card was guessed (exhaustive trials), participants judged the guess "wrong" `r round(quaternaryExh_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quaternaryExh_kindaWrong$proportion*100)`% of the time, and "kinda right" `r round(quaternaryExh_kindaRight$proportion*100)`% of the times.
+Perhaps surprisingly, when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right".
+This suggests that perhaps participants considered a notion of partially true or correct statement in our experimental setting.
+Disjunctive guesses with one or two animals on the card showed similar response patterns with participants choosing the "kinda right" and "right" options most of the time.
+When both animals were on the card with a disjunctive guess (scalar trials), participants judged the guess "wrong" `r round(quaternaryScalar_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quaternaryScalar_kindaWrong$proportion*100)`% of the time, and "kinda right" `r round(quaternaryScalar_kindaRight$proportion*100)`% of the times.
+
+```{r quinaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game."}
 
@@
 grid.draw(quinary_plot_g)
+
+quinaryExh_kindaRight <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Kinda Right")
+quinaryExh_wrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Wrong")
+quinaryExh_kindaWrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Kinda Wrong")
+quinaryExh_Neither <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat", response=="Neither")
+
+quinaryyScalar_wrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Wrong")
+quinaryScalar_kindaWrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Kinda Wrong")
+quinaryScalar_kindaRight <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Kinda Right")
+quinaryScalar_Neither <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Neither")
 ```
 
-```{r}
-results<-
-  data %>%
-  group_by(response_type, trial_type, response) %>%
-  summarize(counts = n()) %>%
-  group_by(trial_type, response_type) %>%
-  mutate(total = sum(counts), proportion = counts/total)
-```
+Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of "right", "kinda right", "neither", "kinda wrong", and "wrong" responses in the quinary task.
+Since the results for the control trials were identical to previous tasks, we do not repeat them here.
+In exhaustive trials where two animals were on the card and only one of them was guessed, participants chose "kinda right" the majority of times (`r round(quinaryExh_kindaRight$proportion*100)`%).
+Again perhaps surprisingly, when only one animal was on the card and the guess was a conjunction, responses were equally split among "wrong", "kinda wrong", and "kinda right" responses.
+With disjunctive guesses, partitipants were more likely to choose "right" and "kinda right" options.
+When only one animal was on the card, participants considered the disjunctive guess as "right" more often.
+When both animals were on the card (scalar trials), participants judged the disjunctive guess as "kinda right" `r round(quinaryScalar_kindaRight$proportion*100)`% of the time.
 
-```{r}
-ggplot(results, aes(x=response,y=proportion)) +
-  geom_bar(stat="identity") +
-  facet_grid(response_type~trial_type, drop = TRUE) +
-  theme_few()
-```
-
-* make sure to break down based on whether participants had logical training or not.
+Comparing the response patterns in binary to quinary tasks (Figures \@ref(fig:binaryPlot) to \@ref(fig:quinaryPlot)), we can observe that in implicature trials, participants are less likely to choose the endpoints of the scale (i.e.
+"wrong" and "right") as they are given more intermediate options.
+This raises the possibilty that the strict "wrong/right" responses in the tasks with fewer options (binary and ternary) were not accurately reflecting participant judgments of implicature trials and pushed their judgments to the extreme ends.
+More generally, the data suggest that participant judgments in contexts that give rise to implicatures fall within the intermrediate level of the response scale and forced choice tasks with few options (especially binary tasks) may risk depicting judgments more extreme than they actually are.
 
 ### Analysis
+
+Our primary goal in this study was to check whether the estimated "implicature rate" in the experimental task is affected by the linking assumption and the number of response options available in the task.
+Our analysis in this section focuses on these three elements.
+As mentioned before, two trial types were predicted to include pragmatic implicatures.
+First, trials where two animals were on the card but the fictional character guessed with a disjunction (scalar); for example "cat or dog" when the card has both a cat and a dog on it.
+Second, trials where there were two animals on the card but the character guessed only one (exhaustive); for example "cat" when the card had a cat and a dog on it.
+We called such trials "exhaustive".
+In our assessment of implicature rate, we focus on these two trial types.
+
+This study set out to test two linking assumptions.
+
+We test this hypothesis formally using a binomial mixed effects model with the fixed effect of response type and the random intercept for participants as well as random intercept and slope for
+
+A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.
+
+All the analytical decisions described here were pre-registered in an as.predicted format. You can access the preregistration
 
@@
 ```{r}
-ggplot(implicature_results, aes(x=as.factor(implicature),y=proportion)) +
-  geom_bar(stat="identity", position = "dodge") +
-  facet_grid(response_type~definition + trial_type, drop = TRUE) +
-  theme_few() + 
-  labs(x="Implicature")
+implicature_results$response_type <- fct_relevel(implicature_results$response_type, "binary", "ternary", "quaternary", "quinary")
+implicature_results$implicature <- as.factor(implicature_results$implicature)
+implicature_results$implicature <- fct_recode(implicature_results$implicature, yes = "1", no = "0")
 ```
 
-```{r}
-implicature_rate$card <- implicature_rate$card %>% tolower()
+```{r implicatureRatePlot}
+ggplot(implicature_results, aes(x=response_type,y=proportion)) +
+  geom_bar(aes(fill = implicature), stat="identity") +
+  facet_grid(definition ~ trial_type, drop = TRUE) +
+  theme_few() + 
+  labs(x="Implicature") +
+  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1))
+```
 
+```{r implicatureRate, echo=FALSE, eval=FALSE}
 implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)
@@
 summary(implicature_analysis_a)
+library(brms)
+implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="bernoulli", data=implicature_rate)
+```
 
-# implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
-```
+* Was logical training a significant predictor of "implicature rate"?
 

### 2018-04-30 writeup.tex
completed results section

@@
 \usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
+\newtheorem{definition}{Definition}
+\newtheorem{corollary}{Corollary}
+\newtheorem{proposition}{Proposition}
 \theoremstyle{definition}
-\newtheorem{example}{Example}[section]
+\newtheorem{example}{Example}
 \theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
+\newtheorem{exercise}{Exercise}
 \theoremstyle{remark}
@@
 card.} The study ended after 24 trials. At the end participants
-optionally provided demographic information. You can access and view
-\href{**XXX\%20masoud\%20insert\%20link**}{the online study here}.
+optionally provided demographic information. We also asked participants
+if they had any prior training in logic. You can access and view on the
+study's \href{https://github.com/thegricean/si-paradigms/}{online
+repository}.
 
@@
 
-The design had two main manipulaitons: the type of card and the type of
-guess. There were two types of cards. Cards with only one animal on them
-and cards with two animals. Animals were chosen from the following set:
-cat, dog, and elephant There were three types of guesses: simple (e.g.
-\emph{There is a cat}), conjunctive (e.g. \emph{There is a cat and a
-dog}), and disjunctive (e.g. \emph{There is a cat or a dog}).
+The study had two main manipulaitons within participants: the type of
+card and the type of guess. There were two types of cards. Cards with
+only one animal on them and cards with two animals. Animals were chosen
+from the following set: cat, dog, and elephant There were three types of
+guesses: simple (e.g. \emph{There is a cat}), conjunctive (e.g.
+\emph{There is a cat and a dog}), and disjunctive (e.g. \emph{There is a
+cat or a dog}). In each trial, the animal labels used in the guess and
+the animal images on the card may have no overlap (e.g.~Image: cat,
+Guess: \emph{There is an elephant}), a partial overlap (e.g.~Image: cat,
+Guess: \emph{There is a cat or a dog}), or a total overlap (e.g.~Image:
+cat and dog, Guess: \emph{There is a cat or a dog}). Crossing the number
+of animals on the card, the type of guess, and the overlap between the
+guess and the card results in 12 different possible trial types. We
+chose 8 trial types (Figure \ref{fig:trials}), balancing the number of
+one-animal vs.~two-animal cards, simple vs.~connective guesses, and
+expected true vs.~false trials. Three trials were randomly selected from
+each of the 8 trial-types, for a total of 24 trials. The order of these
+24 trials was randomized as well.
 
-In each trial, the animal labels used in the guess and the animal images
-on the card may have no overlap (e.g.~Image: dog, Guess: \emph{There is
-a cat or an elephant}), a partial overlap (e.g.~Image: Cat, Guess:
-\emph{There is a cat or an elephant}), or a total overlap (e.g.~Image:
-cat and elephant, Guess: \emph{There is a cat or an elephant}). Crossing
-the number of animals on the card, the type of guess, and the overlap
-between the guess and the card results in 12 different possible trial
-types. We chose 8 trial types (Figure \ref{fig:trials}), balancing the
-number of one-animal vs.~two-animal cards, simple vs.~connective
-guesses, and expected true vs.~false trials.
+Participants could derive implicatures in two trial types. First, the
+trial type in which two animals were present on the card (e.g.~cat and
+dog) but Bob guessed only one of them (e.g. \enquote{there is a cat}).
+Such trials can have a literal interpretation (cat and possibly more) or
+an exhaustive interpretation (only cat). We refer to them as
+\enquote{exhaustive}. The second trial type with implicatures was the
+one in which two animals were on the card (e.g.~cat and dog) and Bob
+used a disjunciton (e.g.~cat or dog). These trials can have a literal
+(inclusive) interpretation (e.g.~cat or dog or both), or an exclusive
+interpretation (e.g.~cat or dog, not both). We refer to these trials as
+\enquote{scalar}. The following four trial types were used as
+experimental control: two trial types where there was no overlap between
+the guess (e.g.~elephant) and the animal(s) on the card (e.g.~cat, cat
+and dog); and two trial types where the animal(s) on the card were
+correctly guessed. For example, if there was only a cat on the card, Bob
+said \enquote{there is a cat} and if there was a cat and a dog, Bob said
+\enquote{there is a cat and a dog}.
 
-The study used five different types of measurements. 1. two-options
-(true vs.~false) 2. two-options (wrong vs.~right) 3. three-options
-(wrong, neither, right) 4. four-options (wrong, kinda wrong, kinda
-right, right) 5. five-options (wrong, kinda wrong, neither, kinda right,
-right).
+The study also had a between participant manipulation of the number of
+response options in the forced choice task. Participants were randomly
+assigned to one of four different conditions. The conditions differed
+with respect to the number of response options: binary (wrong
+vs.~right), ternary (wrong, neither, right), quaternary (wrong, kinda
+wrong, kinda right, right), and quinary (wrong, kinda wrong, neither,
+kinda right, right). We wanted to see if the number of response options
+in the forced choice task would affect our estimate of the task's
+\enquote{implicature rate}.
 
@@
 
-We are primarily concerned with the \enquote{rate of implicatures} in an
-experimental study. Two trial types are predicted to include pragmatic
-implicatures. First, trials where there are two animals on the card but
-the fictional character guesses using the connective \emph{or}; for
-example \enquote{cat or dog} when the card has both a cat and a dog on
-it. We call such trials \enquote{scalar} trials. Second, trials where
-there are two animals on the card but the character guesses only one;
-for example \enquote{cat} when the card has a cat and a dog on it. We
-call such trials \enquote{exhaustive}. In our assessment of implicature
-rate we focus on these two types of trials.
+\begin{figure}[t]
 
-We define \enquote{implicature rate} in two ways:
+{\centering \includegraphics{writeup_files/figure-latex/binaryPlot-1}
+
+}
+
+\caption{Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game.}\label{fig:binaryPlot}
+\end{figure}
+
+Here we present the proportion that participants chose the response
+options in each of the 8 trial types of the binary, ternary, quaternary,
+and quinary tasks. Figure \ref{fig:binaryPlot} shows the proportion of
+\enquote{right} and \enquote{wrong} responses in the binary task.
+Starting from the leftmost column, participants considered a guess
+\enquote{wrong} if the guessed animal was not on the card. Moving to the
+second column, participants considered a guess \enquote{right} if the
+animal on the card was mentioned. However, if only one of the two
+animals on the card was mentioned (exhaustive trials), 14\% of the times
+participants considered the guess \enquote{wrong}. Moving to the third
+column, if a conjunction of animals was guessed while only one animal
+was on the card, participants considered the guess to be
+\enquote{wrong}. If a conjunction of animals was guessed and both
+animals were present on the card, all participants considered the guess
+to be \enquote{right} as expected. Moving to the forth column, if a
+disjunction of animals was guessed and only one of the animals was on
+the card, participants considered the guess to be \enquote{right} almost
+all the time. However, if both animals were present (scalar trials),
+38\% of the times participants considered the guess to be
+\enquote{wrong}.
+
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/ternaryPlot-1}
+
+}
+
+\caption{Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game.}\label{fig:ternaryPlot}
+\end{figure}
+
+Figure \ref{fig:ternaryPlot} shows the proportion of \enquote{right},
+\enquote{neither}, and \enquote{wrong} responses in the ternary task.
+Similar to the binary task, participants considered a guess wrong when
+the mentioned animal was not on the card. They considered the guess
+\enquote{right} when the mentioned animal was on the card. However, in
+exhaustive trials when the fictional character only guessed one of the
+two animals on the card, participants considered the guess
+\enquote{wrong} 8\% of the time and neither wrong nor right 12\% of the
+time. If a conjunction of animals was guessed and only one animal was
+present on the card, participants considered the guess \enquote{wrong}.
+As expected, when a conjunction was used and both animals were present,
+participants considered the guess \enquote{right}. Similarly,
+participants considerd the guess \enquote{right} when a disjunction was
+used and only one of the animals was on the card. However, in scalar
+trials that both animals were on the card and a disjunction was
+gueassed, participants judged the guess \enquote{wrong} 23\% of the time
+and \enquote{neither} 11\% of the time.
+
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/quaternaryPlot-1}
+
+}
+
+\caption{Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game.}\label{fig:quaternaryPlot}
+\end{figure}
+
+Figure \ref{fig:quaternaryPlot} shows the proportion of \enquote{right},
+\enquote{kinda right}, \enquote{kinda wrong}, and \enquote{wrong}
+responses in the quaternary task. Similar to the results seen
+previously, the control trials turned outas expected. Participants
+considered a guess \enquote{wrong} if the animal guessed was not on the
+card and \enquote{right} if it was the only animal on the card. If a
+conjunctin of animals was guessed and both animals were on the card the
+guess was \enquote{right}. However, when only one of the animals on the
+card was guessed (exhaustive trials), participants judged the guess
+\enquote{wrong} 2\% of the time, \enquote{kinda wrong} 5\% of the time,
+and \enquote{kinda right} 66\% of the times. Perhaps surprisingly, when
+a conjunction was used and only one of the animals was on the card,
+participants considered the guess \enquote{wrong} most of the time, but
+they often considered it \enquote{kinda wrong} or even \enquote{kinda
+right}. This suggests that perhaps participants considered a notion of
+partially true or correct statement in our experimental setting.
+Disjunctive guesses with one or two animals on the card showed similar
+response patterns with participants choosing the \enquote{kinda right}
+and \enquote{right} options most of the time. When both animals were on
+the card with a disjunctive guess (scalar trials), participants judged
+the guess \enquote{wrong} 6\% of the time, \enquote{kinda wrong} 12\% of
+the time, and \enquote{kinda right} 43\% of the times.
+
+\begin{figure}[t]
+
+{\centering \includegraphics{writeup_files/figure-latex/quinaryPlot-1}
+
+}
+
+\caption{Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game.}\label{fig:quinaryPlot}
+\end{figure}
+
+Finally, Figure \ref{fig:quinaryPlot} shows the proportion of
+\enquote{right}, \enquote{kinda right}, \enquote{neither},
+\enquote{kinda wrong}, and \enquote{wrong} responses in the quinary
+task. Since the results for the control trials were identical to
+previous tasks, we do not repeat them here. In exhaustive trials where
+two animals were on the card and only one of them was guessed,
+participants chose \enquote{kinda right} the majority of times (72\%).
+Again perhaps surprisingly, when only one animal was on the card and the
+guess was a conjunction, responses were equally split among
+\enquote{wrong}, \enquote{kinda wrong}, and \enquote{kinda right}
+responses. With disjunctive guesses, partitipants were more likely to
+choose \enquote{right} and \enquote{kinda right} options. When only one
+animal was on the card, participants considered the disjunctive guess as
+\enquote{right} more often. When both animals were on the card (scalar
+trials), participants judged the disjunctive guess as \enquote{kinda
+right} 52\% of the time.
+
+Comparing the response patterns in binary to quinary tasks (Figures
+\ref{fig:binaryPlot} to \ref{fig:quinaryPlot}), we can observe that in
+implicature trials, participants are less likely to choose the endpoints
+of the scale (i.e. \enquote{wrong} and \enquote{right}) as they are
+given more intermediate options. This raises the possibilty that the
+strict \enquote{wrong/right} responses in the tasks with fewer options
+(binary and ternary) were not accurately reflecting participant
+judgments of implicature trials and pushed their judgments to the
+extreme ends. More generally, the data suggest that participant
+judgments in contexts that give rise to implicatures fall within the
+intermrediate level of the response scale and forced choice tasks with
+few options (especially binary tasks) may risk depicting judgments more
+extreme than they actually are.
+
+\subsubsection{Analysis}\label{analysis}
+
+The goal of this study is to see if the estimated \enquote{implicature
+rate} in the experimental task is affected by the linking assumptions
+and the number of response options available in the task. Our analysis
+in this section focuses on these three elements. Two trial types are
+predicted to include pragmatic implicatures. First, trials where two
+animals were on the card but the fictional character guessed with a
+disjunction; for example \enquote{cat or dog} when the card has both a
+cat and a dog on it. We called such trials \enquote{scalar}. Second,
+trials where there were two animals on the card but the character
+guessed only one; for example \enquote{cat} when the card had a cat and
+a dog on it. We called such trials \enquote{exhaustive}. In our
+assessment of implicature rate, we focus on these two types of trials.
 
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/binaryPlot-1}
-
-}
-
-\caption{Adults' two-alternative forced choice judgments in the connective guessing game.}\label{fig:binaryPlot}
-\end{figure}
-
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/ternaryPlot-1}
-
-}
-
-\caption{Adults' three-alternative forced choice judgments in the connective guessing game.}\label{fig:ternaryPlot}
-\end{figure}
-
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/quaternaryPlot-1}
-
-}
-
-\caption{Adults' three-alternative forced choice judgments in the connective guessing game.}\label{fig:quaternaryPlot}
-\end{figure}
-
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/quinaryPlot-1}
-
-}
-
-\caption{Adults' three-alternative forced choice judgments in the connective guessing game.}\label{fig:quinaryPlot}
-\end{figure}
-
 \begin{figure}
 \centering
-\includegraphics{writeup_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{writeup_files/figure-latex/implicatureRatePlot-1.pdf}
 \caption{}
@@
 \item
-  make sure to break down based on whether participants had logical
-  training or not.
+  Was logical training a significant predictor of \enquote{implicature
+  rate}?
 \end{itemize}
-
-\subsubsection{Analysis}\label{analysis}
-
-\begin{figure}
-\centering
-\includegraphics{writeup_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{}
-\end{figure}
-
-\begin{verbatim}
-## Warning in (function (fn, par, lower = rep.int(-Inf, n), upper =
-## rep.int(Inf, : failure to converge in 10000 evaluations
-\end{verbatim}
-
-\begin{verbatim}
-## Warning in checkConv(attr(opt, "derivs"), opt$par, ctrl = control
-## $checkConv, : Model failed to converge with max|grad| = 0.524298 (tol =
-## 0.001, component 1)
-\end{verbatim}
-
-\begin{verbatim}
-## Generalized linear mixed model fit by maximum likelihood (Laplace
-##   Approximation) [glmerMod]
-##  Family: binomial  ( logit )
-## Formula: implicature ~ definition * response_type + trial_type + (1 +  
-##     response_type | card) + (1 | participant)
-##    Data: implicature_rate
-## 
-##      AIC      BIC   logLik deviance df.resid 
-##   1783.4   1899.0   -871.7   1743.4     2380 
-## 
-## Scaled residuals: 
-##     Min      1Q  Median      3Q     Max 
-## -7.8815 -0.2261 -0.1198  0.2334 10.0887 
-## 
-## Random effects:
-##  Groups      Name                    Variance Std.Dev. Corr             
-##  participant (Intercept)             5.224316 2.28568                   
-##  card        (Intercept)             0.008402 0.09166                   
-##              response_typequaternary 0.084138 0.29007  -1.00            
-##              response_typequinary    0.003720 0.06099  -0.79  0.81      
-##              response_typeternary    0.044946 0.21201   0.90 -0.89 -0.67
-## Number of obs: 2400, groups:  participant, 200; card, 3
-## 
-## Fixed effects:
-##                                       Estimate Std. Error z value Pr(>|z|)
-## (Intercept)                           -2.64555    0.43138  -6.133 8.63e-10
-## definitionlow                         -0.02508    0.24943  -0.101    0.920
-## response_typequaternary                3.47868    0.61328   5.672 1.41e-08
-## response_typequinary                   3.44163    0.55426   6.209 5.32e-10
-## response_typeternary                   0.29732    0.56967   0.522    0.602
-## trial_typescalar                       0.85657    0.13861   6.180 6.41e-10
-## definitionlow:response_typequaternary -6.08294    0.61009  -9.970  < 2e-16
-## definitionlow:response_typequinary    -5.71913    0.50693 -11.282  < 2e-16
-## definitionlow:response_typeternary    -1.21490    0.36931  -3.290    0.001
-##                                          
-## (Intercept)                           ***
-## definitionlow                            
-## response_typequaternary               ***
-## response_typequinary                  ***
-## response_typeternary                     
-## trial_typescalar                      ***
-## definitionlow:response_typequaternary ***
-## definitionlow:response_typequinary    ***
-## definitionlow:response_typeternary    ** 
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Correlation of Fixed Effects:
-##                     (Intr) dfntnl rspns_typqt rspns_typqn rspns_typt
-## definitinlw         -0.287                                          
-## rspns_typqt         -0.724  0.202                                   
-## rspns_typqn         -0.760  0.224  0.554                            
-## rspns_typtr         -0.643  0.218  0.418       0.510                
-## trl_typsclr         -0.218 -0.001  0.060       0.065       0.007    
-## dfntnlw:rspns_typqt  0.214 -0.408 -0.330      -0.167      -0.101    
-## dfntnlw:rspns_typqn  0.217 -0.492 -0.156      -0.309      -0.116    
-## dfntnlw:rspns_typt   0.220 -0.675 -0.155      -0.170      -0.280    
-##                     trl_ty dfntnlw:rspns_typqt dfntnlw:rspns_typqn
-## definitinlw                                                       
-## rspns_typqt                                                       
-## rspns_typqn                                                       
-## rspns_typtr                                                       
-## trl_typsclr                                                       
-## dfntnlw:rspns_typqt -0.098                                        
-## dfntnlw:rspns_typqn -0.103  0.266                                 
-## dfntnlw:rspns_typt  -0.036  0.298               0.349             
-## convergence code: 0
-## Model failed to converge with max|grad| = 0.524298 (tol = 0.001, component 1)
-## failure to converge in 10000 evaluations
-\end{verbatim}
 
@@
 \end{itemize}
+
+A simple visual inspection of our results suggests that any variant of
+the Traditional Linking Hypothesis will yield unsatisfying empirical
+coverage with regards to participants' behavior in truth value judgment
+tasks. Recall that according to this hypothesis, scalar implicature is
+conceptualized as a binary, categorical affair: an implicature is either
+\enquote{calculated,} or it isn't. This assumption has implications for
+how we approach analysis of variation in behavior on a truth value
+judgment task; for example, why did the majority of respondents in the
+binary condition of our experiment answer \enquote{Right} to an
+utterance of cat or dog when the card had a cat and a dog on it?
+
+On the Traditional story, we are forced to say that a) not all
+participants calculated the implicature; or that b) some participants
+who calculated the implicature did not choose the anticipated response
+(i.e. \enquote{Wrong}) due to some other cognitive reflex which
+\enquote{overrode} the implicature; or some mixture of (b) and (c). We
+might similarly posit that one or both of these factors underlie the
+variation in the ternary, quatenary, and quinary conditions (e.g.~why
+were participants roughly split between \enquote{Right} and
+\enquote{Kind of right} when the utterance was cat or dog and the card
+had a cat and a dog?). There is an established cottage industry of
+pragmatics research which approaches the problem of behavioral variation
+in exactly these ways, exploring the factors which \enquote{license}
+implicature calculation or \enquote{suppress} its anticipated behavioral
+expression (c.f. \_\_), but the best we can hope for on this approach is
+an analysis which traces the general qualitative patterns in the data
+(and we should stress that even in this respect, the industry has yet to
+fully deliver the goods!).
+
+The Alternative Linking Hypothesis contrasts with the Traditional
+Linking Hypothesis in that the former is rooted in a quantitative
+formalization of pragmatic competence which provides us a continuous
+measure of pragmatic reasoning. {[}recap RSA model here? Maybe show how
+it gets the right basic qualitative pattern, i.e. \(P_L\)(a and
+b\textbar{} \enquote{a or b}) \(<\) \(P_L\)(a \textbar{} \enquote{or});
+\(P_L\)(a and b\textbar{} \enquote{a or b}) \(<\) \(P_L\)(b \textbar{}
+\enquote{or}) {]}
+
+Following Degen \& Goodman (2014), we proceed on the assumption that
+behavior on sentence verification tasks, such as truth value judgment
+tasks, is best modeled as a function of an individual's mental
+representation of a cooperative interlocutor (\(S_1\) in the language of
+RSA). For a given utterance u and an intended communicated meaning w,
+\(S_1\)(u \textbar{} w) outputs a conditional probability of u given w.
+For example, in the binary condition of our experiment where a
+participant evaluated cat or dog when there were both animals on the
+card, the participant has access to the mental representation of \(S_1\)
+and hence to the \(S_1\) conditional probability of hearing the
+utterance cat or dog given a dog and cat card \(S_1\)(cat or dog
+\textbar{} cat and dog).
+
+One desideratum of a linking hypothesis given this view of pragmatic
+competence is to transform this probability value into a categorical
+output (e.g. \enquote{Right}/''Wrong'' in the case of the binary
+condition). This can be achieved by positing that participants
+\enquote{filter out} low-probability utterances given an intended
+communicated meaning. We model a responder, R, who in the binary
+condition responds \enquote{Right} to an utterance u in world w just in
+case \(S_1\)(u \textbar{} w) exceeds some probability threshold
+\(\theta\):
+
+R(u, w, \(\theta\)) = \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\)
+\(\theta\) = \enquote{Wrong} otherwise
+
+In the experiment conditions where there are more than two choices, we
+model the range of possible behavioral responses for R with the
+introduction of intermediate probability thresholds. For example, in the
+ternary condition, R(u, w, \(\theta_1\) , \(\theta_2\)) is
+\enquote{Right} iff \(S_1\)(u \textbar{} w) \textgreater{} \(\theta_1\)
+and \enquote{Neither} iff \(\theta_1\) \textgreater{} \(S_1\)(u
+\textbar{} w) \textgreater{} \(\theta_2\). To fully generalize the model
+to our five experimental conditions, we say that R takes as its input an
+utterance u and a world state w and a number of threshold variables
+dependent on a variable c, corresponding to the experimental condition
+in which the participant finds herself (e.g.~the range of possible
+responses available to R).
+
+Given c = \enquote{ternary}
+
+R(u, w, \(\theta_1\) , \(\theta_2\))\\
+= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\) =
+\enquote{Neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w) \(>\)
+\(\theta_2\)\\
+= \enquote{Wrong} otherwise
+
+Given c = \enquote{quatenary}
+
+R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\))\\
+= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\) =
+\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
+\(>\) \(\theta_2\)\\
+= \enquote{Kinda Wrong} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} w)
+\(>\) \(\theta_3\) = \enquote{Wrong} otherwise
+
+Given c = \enquote{quinary}
+
+R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\). \(\theta_4\))\\
+= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\)
+=\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
+\(>\) \(\theta_2\) = \enquote{Neither} iff \(\theta_2\) \(>\) \(S_1\)(u
+\textbar{} w) \(>\) \(\theta_3\)\\
+= \enquote{Kinda Wrong} iff \(\theta_3\) \(>\) \(S_1\)(u \textbar{} w)
+\(>\) \(\theta_4\) = \enquote{Wrong} otherwise
 

### 2018-04-30 writeup.Rmd
made visualization changes so axes are labeled and links are labeled like in paper

--- 2018-04-30 writeup.Rmd
@@
 library(webppl)
-# library(brms)
+library(brms)
 theme_set(theme_bw(18))
@@
 
-# high definition only considers the highest point on the scale as "literal"
-pragmatic_trials$high<-1
-pragmatic_trials[pragmatic_trials$response=="Right",]$high <-0
+# high definition only considers the highest point on the scale as "literal" (Weak link in paper)
+pragmatic_trials$weak<-1
+pragmatic_trials[pragmatic_trials$response=="Right",]$weak <-0
 
-# low definition only considers the lowers point on the scale as implicature 
-pragmatic_trials$low<-0
-pragmatic_trials[pragmatic_trials$response=="Wrong",]$low <-1
+# low definition only considers the lowest point on the scale as implicature (Strong link in paper)
+pragmatic_trials$strong<-0
+pragmatic_trials[pragmatic_trials$response=="Wrong",]$strong <-1
 
 implicature_rate <- 
-  pragmatic_trials %>% gather("definition","implicature", high:low)
+  pragmatic_trials %>% gather("definition","implicature", weak:strong)
 
@@
   facet_grid(card_type~guess_type) +
-  labs(x="", y="")+
+  labs(x="Response", y="Proportion of response")+
   theme_few() +
@@
   facet_grid(card_type~guess_type) +
-  labs(x="", y="")+
+  labs(x="Response", y="Proportion of response")+
   theme_few() +
-  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1,vjust=1)) +
   scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)
@@
   facet_grid(card_type~guess_type) +
-  labs(x="", y="")+
+  labs(x="Response", y="Proportion of response")+
   theme_few() +
-  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1, vjust=1)) +
   scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)
@@
   geom_bar(stat="identity") +
-  facet_grid(response_type~trial_type, drop = TRUE) +
+  facet_grid(trial_type~response_type, drop = TRUE) +
   theme_few()
@@
   group_by(response_type, trial_type, definition) %>%
-  mutate(total = sum(counts), proportion = counts/total)
+  mutate(total = sum(counts), proportion = counts/total) %>%
+  ungroup() %>%
+  mutate(response_type=fct_relevel(response_type,"binary","ternary","quaternary","quinary"))
+
+dodge = position_dodge(.9)
 ```
@@
 ```{r}
-ggplot(implicature_results, aes(x=as.factor(implicature),y=proportion)) +
-  geom_bar(stat="identity", position = "dodge") +
-  facet_grid(response_type~definition + trial_type, drop = TRUE) +
+ggplot(implicature_results[implicature_results$implicature == 1,], aes(x=definition,y=proportion,fill=definition)) +
+  geom_bar(stat="identity") +
+  facet_grid(trial_type~response_type, drop = TRUE) +
   theme_few() + 
-  labs(x="Implicature")
+  labs(x="Link",y="Inferred implicature rate")
 ```
@@
 
-implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)
+implicature_analysis_a <- glmer(implicature ~ definition * response_type * trial_type + (1|card) + (1|participant), family="binomial", data=implicature_rate)
 

### 2018-05-01 writeup.Rmd
made writeup non-webppl dependent; semifinal edits to discussion section

@@
 library(forcats)
-library(webppl)
+library(rwebppl)
 library(brms)
@@
 
-Alternative Linking Hypothesis:
-* RSA: Response behavior across conditions (utterance-card combinations) and dependent measures can be predicted by a linking hypothesis that assumes that participants are behaving like soft-optimal RSA speakers and provide a particular response (eg TRUE) to an utterance u if the RSA speaker probability of u (given the card) is within a particular probability interval (eg, within the interval [theta, 1]).
+On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
+This assumption has concerning implications for how we must approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had both a cat and a dog on it?
 
-* Differences between traditional approaches and RSA: 1.
-The traditional linking hypotheses are based on a binary implicature/literal theory of pragmatic reasoning but RSA gives a continuous measure of pragmatic reasoning and allows for better predicting response behavior with multiple options.
-
-A simple visual inspection of our results suggests that any variant of the Traditional Linking Hypothesis will yield unsatisfying empirical coverage with regards to participants’ behavior in truth value judgment tasks.
-Recall that according to this hypothesis, scalar implicature is conceptualized as a binary, categorical affair: an implicature is either ‘calculated,’ or it isn’t.
-This assumption has implications for how we approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had a cat and a dog on it?
-
-On the Traditional story, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
+To explain the data on the traditional view, are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
 “Wrong”) due to some other cognitive reflex which ‘overrode’ the implicature; or some mixture of (b) and (c).
@@
 why were participants roughly split between “Right” and “Kind of right” when the utterance was cat or dog and the card had a cat and a dog?).
-There is an established cottage industry of pragmatics research which approaches the problem of behavioral variation in exactly these ways, exploring the factors which “license” implicature calculation or “suppress” its anticipated behavioral expression (c.f.
-__), but the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
+However, the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
 
-The Alternative Linking Hypothesis contrasts with the Traditional Linking Hypothesis in that the former is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
-[recap RSA model here?
-Maybe show how it gets the right basic qualitative pattern, i.e.
-$P_L$(a and b| “a or b”) $<$ $P_L$(a | “or”); $P_L$(a and b| “a or b”) $<$ $P_L$(b | “or”) ]
+We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis which assumes that participants' behavior can be represented using the model of a soft-optimal pragmatic speaker in the RSA framework.
+This alternative linking hypothesis contrasts with the traditional view in it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+Recall that in RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution of possible meanings given an utterance which that listener hears.
+The probability with which this listener $L_1$ ascribes a meaning s to an utterance u depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
+$S_1$ in turn is modeled as a continuous probabilistic distribution of possible utterances given an intended state of affairs the speaker intends to communicate.
+This distribution is sensitive to a rationality parameter $\alpha$, the production cost $C$ of potential utterances, and a representation of a literal listener $L_0$ whose interpretation of an utterance is in turn a function of that utterance's truth conditional content $[[u]](s)$ and her prior beliefs about the state of the world $P_w(s)$.
 
-Following Degen & Goodman (2014), we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA).
+    $P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
+
+    $P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $
+
+    $P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
+
+In this framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
+For example, exclusivity readings of disjunction or are represented in RSA as relatively low conditional probability of a conjunctive meaning on the $P_L$ distribution, given an utterance of or.
+Thus, it is not even possible to talk about 'rate' of implicature calculation in the RSA framework.
+The upshot, as we show below, is that this view of pragmatic competence does allow us to talk explicitly and quantitatively about rates of observed behavior in sentence verification tasks.
+
+First, following Degen & Goodman (2014), we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
+In their paper, Degen & Goodman argue that sentence verification tasks are relatively more sensitive to contextual manipulations (such as manipulation of the Question Under Discussion) than are sentence interpretation tasks, and that this follows if sentence interpretation tasks - but not sentence verification tasks - require an additional layer of counterfactual reasoning about the intentions of a cooperative speaker.
+
+A main desideratum of a behavioral linking hypothesis given the RSA view of pragmatic competence is to transform continuous probability distributions into categorical outputs (e.g.
+responses of “Right”/”Wrong” in the case of the binary condition of our experiment).
 For a given utterance u and an intended communicated meaning w, $S_1$(u | w) outputs a conditional probability of u given w.
-For example, in the binary condition of our experiment where a participant evaluated cat or dog when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of hearing the utterance cat or dog given a dog and cat card $S_1$(cat or dog | cat and dog).
-
-One desideratum of a linking hypothesis given this view of pragmatic competence is to transform this probability value into a categorical output (e.g.
-“Right”/”Wrong” in the case of the binary condition).
-This can be achieved by positing that participants ‘filter out’ low-probability utterances given an intended communicated meaning.
+For example, in the binary condition of our experiment where a participant evaluated cat or dog when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of hearing the utterance cat or dog given a dog and cat card: $S_1$(cat or dog | cat and dog).
+According to the linking hypothesis advanced here, the participant provides a particular response to u if the RSA speaker probability of u lies within a particular probability interval, given an observed state of the world (i.e.
+the configuration of animals on the card in our experiment).
 We model a responder, R, who in the binary condition responds “Right” to an utterance u in world w just in case $S_1$(u | w) exceeds some probability threshold $\theta$:
@@
 For example, in the ternary condition, R(u, w, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | w) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | w) > $\theta_2$.
-To fully generalize the model to our five experimental conditions, we say that R takes as its input an utterance u and a world state w and a number of threshold variables dependent on a variable c, corresponding to the experimental condition in which the participant finds herself (e.g.
+To fully generalize the model to our five experimental conditions, we say that R takes as its input an utterance u, a world state w, and a number of threshold variables dependent on a variable c, corresponding to the experimental condition in which the participant finds herself (e.g.
 the range of possible responses available to R).
@@
 
-```{r echo=TRUE, message=FALSE}
-bda <- webppl(program_file = "models/webppl_models/bda_model.wppl")
+Bayesian statistical methods provide us a means for estimating the values of these probability thresholds in our RSA model.
+The basis for the model is a set of possible states of the world, given a universe of three animals - X, Y, and Z - that each may be on some card.
+We next define a set of possible sentences a speaker might utter, assuming the speaker intends to communicate which animals are on the card.
+We assume a uniform prior probability of different states of the world and a uniform cost function on utterances.
+We define a literal listener $L_0$, a pragmatic speaker $S_1$, and a responder $R$ according to our definitions above.
+Lastly, and assuming a uniform prior distribution over possible values of probability thresholds, we use Bayesian inference to recover a posterior distribution of these thresholds in each experimental condition, given the actual observed rate of response in each condition of the experiment.
+The results of this parameter estimation analysis are shown in the figures below, where the X axis of each figure corresponds to a threshold value between 0 and 1 and the Y axis corresponds to the posterior probability density of possible values of the threshold.
+
+```{r echo=FALSE, message=FALSE}
+bda <- read.csv("/models/webppl_models/bda.csv")
 
@@
   # facet_wrap(~Parameter, scales = "free") +
+  theme_few() +
   geom_density() +
@@
   theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
-  ggtitle("Threshold distributions, binary condition:")
+  ggtitle("Threshold distribution, binary condition:")
 
@@
   facet_wrap(~Parameter, scales = "free") +
+  theme_few() +
   geom_density() +
@@
 ```
-\newpage
+
+The above analysis is a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
 

### 2018-05-02 writeup.Rmd
added all confidence intervals and editted some more

--- 2018-04-30 writeup.Rmd
@@
 library(brms)
+library(DescTools)
+library(binom)
 theme_set(theme_bw(18))
@@
 
-```{r linkvisualization, fig.env = "figure", fig.align='center', fig.width=5, set.cap.width=T, num.cols.cap=1,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
+```{r linkvisualization, fig.asp=0.2,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
 link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
@@
 
-# high definition only considers the highest point on the scale as "literal"
-pragmatic_trials$high<-1
-pragmatic_trials[pragmatic_trials$response=="Right",]$high <-0
+# weak definition only considers the highest point on the scale as "literal"
+pragmatic_trials$weak<-1
+pragmatic_trials[pragmatic_trials$response=="Right",]$weak <-0
 
-# low definition only considers the lowers point on the scale as implicature 
-pragmatic_trials$low<-0
-pragmatic_trials[pragmatic_trials$response=="Wrong",]$low <-1
+# strong definition only considers the lowest point on the scale as implicature 
+pragmatic_trials$strong<-0
+pragmatic_trials[pragmatic_trials$response=="Wrong",]$strong <-1
 
 implicature_rate <- 
-  pragmatic_trials %>% gather("definition","implicature", high:low)
+  pragmatic_trials %>% gather("definition","implicature", weak:strong)
 
@@
 
-```{r stimuli, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=2, fig.height=1.5, set.cap.width=T, num.cols.cap=1, fig.width=1.5,fig.cap = "Cards used in the connective guessing game."}
+```{r stimuli, fig.asp=0.35, fig.cap = "Cards used in the connective guessing game."}
 cards_img <- jpeg::readJPEG("experiments/figs/cards.jpg")
@@
 For example, if there was only a cat on the card, Bob said "there is a cat" and if there was a cat and a dog, Bob said "there is a cat and a dog".
+Since the fictional character was blindfolded and did not see the outcome of the game, the ignorance inference commonly associated with disjunction was already common ground in the experimental setting.
+If the character was seeing the cards or knew what was on them, a disjunction would have violated the expectation that the speaker does not know which alternative actually holds.
+Our study controls for the possibile effect of ignorance violations on exclusivity and exhaustive inferences.
 
@@
 
-```{r trials, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.width=1.5, fig.cap = "Trial types represented by example cards and guesses."}
+```{r trials, fig.asp=0.35, fig.cap = "Trial types represented by example cards and guesses."}
 trials_img <- jpeg::readJPEG("experiments/figs/trialTypes.jpg")
@@
 
-```{r binaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game."}
-
+```{r binaryData}
 binary_summary<-
@@
   group_by(card_type, guess_type) %>%
-  mutate(total = sum(count), proportion=count/total)
+  mutate(total = sum(count), est=count/total)
+
+binary_summary_X_cat <-
+  binary_summary %>%
+  filter(card_type=="X", guess_type=="X")
+binary_summary_X_cat_confint <-
+  binary_summary_X_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_X_cat <- binary_summary_X_cat %>% full_join(binary_summary_X_cat_confint, by="est")
+
+binary_summary_XY_cat <-
+  binary_summary %>%
+  filter(card_type=="XY", guess_type=="X")
+binary_summary_XY_cat_confint <-
+  binary_summary_XY_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_XY_cat <- binary_summary_XY_cat %>% full_join(binary_summary_XY_cat_confint, by="est")
+
+binary_summary_XY_ele <-
+  binary_summary %>%
+  filter(card_type=="XY", guess_type=="Z")
+binary_summary_XY_ele_confint <-
+  binary_summary_XY_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_XY_ele <- binary_summary_XY_ele %>% full_join(binary_summary_XY_ele_confint, by="est") %>% unique()
+
+binary_summary_X_ele <-
+  binary_summary %>%
+  filter(card_type=="X", guess_type=="Z")
+binary_summary_X_ele_confint <-
+  binary_summary_X_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_X_ele <- binary_summary_X_ele %>% full_join(binary_summary_X_ele_confint, by="est") %>% unique()
+
+binary_summary_XY_and <-
+  binary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+binary_summary_XY_and_confint <-
+  binary_summary_XY_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_XY_and <- binary_summary_XY_and %>% full_join(binary_summary_XY_and_confint, by="est") %>% unique()
+
+binary_summary_X_and <-
+  binary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+binary_summary_X_and_confint <-
+  binary_summary_X_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_X_and <- binary_summary_X_and %>% full_join(binary_summary_X_and_confint, by="est") %>% unique()
+
+binary_summary_XY_or <-
+  binary_summary %>%
+  filter(card_type=="XY", guess_type=="XorY")
+binary_summary_XY_or_confint <-
+  binary_summary_XY_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_XY_or <- binary_summary_XY_or %>% full_join(binary_summary_XY_or_confint, by="est") %>% unique()
+
+binary_summary_X_or <-
+  binary_summary %>%
+  filter(card_type=="X", guess_type=="XorY")
+binary_summary_X_or_confint <-
+  binary_summary_X_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+binary_summary_X_or <- binary_summary_X_or %>% full_join(binary_summary_X_or_confint, by="est") %>% unique()
+
+binary_summary <- bind_rows(binary_summary_X_cat, binary_summary_XY_cat, binary_summary_XY_ele, binary_summary_X_ele,
+                                binary_summary_XY_and, binary_summary_X_and, binary_summary_XY_or, binary_summary_X_or)
 
@@
 binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+binary_summary <- binary_summary %>% rename(proportion = "est")
+```
 
+```{r binaryPlot, fig.height=3.5, fig.cap = "Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game."}
 binary_plot<-
@@
   geom_bar(stat = "identity", position="dodge", width = 0.6) +
-#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
   facet_grid(card_type~guess_type) +
@@
   theme_few() +
-  theme(text = element_text(size=15)) +
-  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)
+  theme(text = element_text(size=12)) +
+  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE) +
+  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))
 
@@
 
-```{r ternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game."}
-
+```{r ternaryData}
 ternary_summary<-
@@
   group_by(card_type, guess_type) %>%
-  mutate(total = sum(count), proportion=count/total)
+  mutate(total = sum(count), est=count/total)
+
+ternary_summary_X_cat <-
+  ternary_summary %>%
+  filter(card_type=="X", guess_type=="X")
+ternary_summary_X_cat_confint <-
+  ternary_summary_X_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_X_cat <- ternary_summary_X_cat %>% full_join(ternary_summary_X_cat_confint, by="est")
+
+ternary_summary_XY_cat <-
+  ternary_summary %>%
+  filter(card_type=="XY", guess_type=="X")
+ternary_summary_XY_cat_confint <-
+  ternary_summary_XY_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_XY_cat <- ternary_summary_XY_cat %>% full_join(ternary_summary_XY_cat_confint, by="est")
+
+ternary_summary_XY_ele <-
+  ternary_summary %>%
+  filter(card_type=="XY", guess_type=="Z")
+ternary_summary_XY_ele_confint <-
+  ternary_summary_XY_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_XY_ele <- ternary_summary_XY_ele %>% full_join(ternary_summary_XY_ele_confint, by="est") %>% unique()
+
+ternary_summary_X_ele <-
+  ternary_summary %>%
+  filter(card_type=="X", guess_type=="Z")
+ternary_summary_X_ele_confint <-
+  ternary_summary_X_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_X_ele <- ternary_summary_X_ele %>% full_join(ternary_summary_X_ele_confint, by="est") %>% unique()
+
+ternary_summary_XY_and <-
+  ternary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+ternary_summary_XY_and_confint <-
+  ternary_summary_XY_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_XY_and <- ternary_summary_XY_and %>% full_join(ternary_summary_XY_and_confint, by="est") %>% unique()
+
+ternary_summary_X_and <-
+  ternary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+ternary_summary_X_and_confint <-
+  ternary_summary_X_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_X_and <- ternary_summary_X_and %>% full_join(ternary_summary_X_and_confint, by="est") %>% unique()
+
+ternary_summary_XY_or <-
+  ternary_summary %>%
+  filter(card_type=="XY", guess_type=="XorY")
+ternary_summary_XY_or_confint <-
+  ternary_summary_XY_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_XY_or <- ternary_summary_XY_or %>% full_join(ternary_summary_XY_or_confint, by="est") %>% unique()
+
+ternary_summary_X_or <-
+  ternary_summary %>%
+  filter(card_type=="X", guess_type=="XorY")
+ternary_summary_X_or_confint <-
+  ternary_summary_X_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+ternary_summary_X_or <- ternary_summary_X_or %>% full_join(ternary_summary_X_or_confint, by="est") %>% unique()
+
+ternary_summary <- bind_rows(ternary_summary_X_cat, ternary_summary_XY_cat, ternary_summary_XY_ele, ternary_summary_X_ele,
+                                ternary_summary_XY_and, ternary_summary_X_and, ternary_summary_XY_or, ternary_summary_X_or)
 
@@
 ternary_summary$guess_type <- recode(ternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+ternary_summary <- ternary_summary %>% rename(proportion = "est")
+```
 
+```{r ternaryPlot, fig.height=3.5, fig.cap = "Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game."}
 ternary_plot<-
@@
   theme_few() +
-  theme(text = element_text(size=15)) +
-  scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE)
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 90, hjust = 1)) +
+    scale_fill_manual(values = c("red4","grey", "springgreen3"), guide=FALSE) +
+  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))
 
@@
 
-```{r quaternaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game."}
-
+```{r quaternaryData}
 quaternary_summary<-
@@
   group_by(card_type, guess_type) %>%
-  mutate(total = sum(count), proportion=count/total)
+  mutate(total = sum(count), est=count/total)
+
+quaternary_summary_X_cat <-
+  quaternary_summary %>%
+  filter(card_type=="X", guess_type=="X")
+quaternary_summary_X_cat_confint <-
+  quaternary_summary_X_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_X_cat <- quaternary_summary_X_cat %>% full_join(quaternary_summary_X_cat_confint, by="est")
+
+quaternary_summary_XY_cat <-
+  quaternary_summary %>%
+  filter(card_type=="XY", guess_type=="X")
+quaternary_summary_XY_cat_confint <-
+  quaternary_summary_XY_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_XY_cat <- quaternary_summary_XY_cat %>% full_join(quaternary_summary_XY_cat_confint, by="est")
+
+quaternary_summary_XY_ele <-
+  quaternary_summary %>%
+  filter(card_type=="XY", guess_type=="Z")
+quaternary_summary_XY_ele_confint <-
+  quaternary_summary_XY_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_XY_ele <- quaternary_summary_XY_ele %>% full_join(quaternary_summary_XY_ele_confint, by="est") %>% unique()
+
+quaternary_summary_X_ele <-
+  quaternary_summary %>%
+  filter(card_type=="X", guess_type=="Z")
+quaternary_summary_X_ele_confint <-
+  quaternary_summary_X_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_X_ele <- quaternary_summary_X_ele %>% full_join(quaternary_summary_X_ele_confint, by="est") %>% unique()
+
+quaternary_summary_XY_and <-
+  quaternary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+quaternary_summary_XY_and_confint <-
+  quaternary_summary_XY_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_XY_and <- quaternary_summary_XY_and %>% full_join(quaternary_summary_XY_and_confint, by="est") %>% unique()
+
+quaternary_summary_X_and <-
+  quaternary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+quaternary_summary_X_and_confint <-
+  quaternary_summary_X_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_X_and <- quaternary_summary_X_and %>% full_join(quaternary_summary_X_and_confint, by="est") %>% unique()
+
+quaternary_summary_XY_or <-
+  quaternary_summary %>%
+  filter(card_type=="XY", guess_type=="XorY")
+quaternary_summary_XY_or_confint <-
+  quaternary_summary_XY_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_XY_or <- quaternary_summary_XY_or %>% full_join(quaternary_summary_XY_or_confint, by="est") %>% unique()
+
+quaternary_summary_X_or <-
+  quaternary_summary %>%
+  filter(card_type=="X", guess_type=="XorY")
+quaternary_summary_X_or_confint <-
+  quaternary_summary_X_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quaternary_summary_X_or <- quaternary_summary_X_or %>% full_join(quaternary_summary_X_or_confint, by="est") %>% unique()
+
+quaternary_summary <- bind_rows(quaternary_summary_X_cat, quaternary_summary_XY_cat, quaternary_summary_XY_ele, quaternary_summary_X_ele,
+                                quaternary_summary_XY_and, quaternary_summary_X_and, quaternary_summary_XY_or, quaternary_summary_X_or)
 
@@
 quaternary_summary$guess_type <- recode(quaternary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+quaternary_summary <- quaternary_summary %>% rename(proportion = "est")
+```
 
+```{r quaternaryPlot, fig.height=4, fig.cap = "Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game."}
 quaternary_plot<-
@@
   theme_few() +
-  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
-  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE)
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  scale_fill_manual(values = c("red4", "red3", "springgreen2", "springgreen3"), guide=FALSE) + 
+  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))
 
@@
 
-```{r quinaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game."}
-
+```{r quinaryData}
 quinary_summary<-
@@
   group_by(card_type, guess_type) %>%
-  mutate(total = sum(count), proportion=count/total)
+  mutate(total = sum(count), est=count/total)
+
+quinary_summary_X_cat <-
+  quinary_summary %>%
+  filter(card_type=="X", guess_type=="X")
+quinary_summary_X_cat_confint <-
+  quinary_summary_X_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_X_cat <- quinary_summary_X_cat %>% full_join(quinary_summary_X_cat_confint, by="est")
+
+quinary_summary_XY_cat <-
+  quinary_summary %>%
+  filter(card_type=="XY", guess_type=="X")
+quinary_summary_XY_cat_confint <-
+  quinary_summary_XY_cat$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_XY_cat <- quinary_summary_XY_cat %>% full_join(quinary_summary_XY_cat_confint, by="est")
+
+quinary_summary_XY_ele <-
+  quinary_summary %>%
+  filter(card_type=="XY", guess_type=="Z")
+quinary_summary_XY_ele_confint <-
+  quinary_summary_XY_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_XY_ele <- quinary_summary_XY_ele %>% full_join(quinary_summary_XY_ele_confint, by="est") %>% unique()
+
+quinary_summary_X_ele <-
+  quinary_summary %>%
+  filter(card_type=="X", guess_type=="Z")
+quinary_summary_X_ele_confint <-
+  quinary_summary_X_ele$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_X_ele <- quinary_summary_X_ele %>% full_join(quinary_summary_X_ele_confint, by="est") %>% unique()
+
+quinary_summary_XY_and <-
+  quinary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+quinary_summary_XY_and_confint <-
+  quinary_summary_XY_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_XY_and <- quinary_summary_XY_and %>% full_join(quinary_summary_XY_and_confint, by="est") %>% unique()
+
+quinary_summary_X_and <-
+  quinary_summary %>%
+  filter(card_type=="X", guess_type=="XandY")
+quinary_summary_X_and_confint <-
+  quinary_summary_X_and$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_X_and <- quinary_summary_X_and %>% full_join(quinary_summary_X_and_confint, by="est") %>% unique()
+
+quinary_summary_XY_or <-
+  quinary_summary %>%
+  filter(card_type=="XY", guess_type=="XorY")
+quinary_summary_XY_or_confint <-
+  quinary_summary_XY_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_XY_or <- quinary_summary_XY_or %>% full_join(quinary_summary_XY_or_confint, by="est") %>% unique()
+
+quinary_summary_X_or <-
+  quinary_summary %>%
+  filter(card_type=="X", guess_type=="XorY")
+quinary_summary_X_or_confint <-
+  quinary_summary_X_or$count %>%
+  MultinomCI(conf.level = 0.95, method = "sisonglaz") %>% data.frame()
+quinary_summary_X_or <- quinary_summary_X_or %>% full_join(quinary_summary_X_or_confint, by="est") %>% unique()
+
+quinary_summary <- bind_rows(quinary_summary_X_cat, quinary_summary_XY_cat, quinary_summary_XY_ele, quinary_summary_X_ele,
+                                quinary_summary_XY_and, quinary_summary_X_and, quinary_summary_XY_or, quinary_summary_X_or)
 
@@
 quinary_summary$guess_type <- recode(quinary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")
+quinary_summary <- quinary_summary %>% rename(proportion = "est")
+```
 
+```{r quinaryPlot, fig.height=4, fig.cap = "Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game."}
 quinary_plot<-
@@
   theme_few() +
-  theme(text = element_text(size=17), axis.text.x = element_text(angle = 90, hjust = 1)) +
-  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE)
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 90, hjust = 1)) +
+  scale_fill_manual(values = c("red4", "red3", "grey", "springgreen2", "springgreen3"), guide=FALSE) +
+  geom_linerange(aes(ymin=lwr.ci,ymax=upr.ci))
 
@@
 
-### Analysis
+## Analysis
+
+```{r implicatureResultss}
+implicature_results<-
+  implicature_rate %>%
+  group_by(response_type, trial_type, implicature, definition) %>%
+  summarize(counts = n()) %>%
+  group_by(response_type, trial_type, definition) %>%
+  mutate(total = sum(counts), proportion = counts/total)
+
+implicature_plot <- 
+  implicature_results %>% filter(implicature==1)
+
+binomial_confint<- binom.confint(implicature_plot$counts, implicature_plot$total, method="logit") %>%
+  rename(counts = "x", total="n")
+
+implicature_results <- implicature_plot %>% full_join(binomial_confint, by=c("total", "counts")) %>% unique
+
+implicature_results$response_type <- fct_relevel(implicature_results$response_type, "binary", "ternary", "quaternary", "quinary")
+implicature_results$implicature <- as.factor(implicature_results$implicature)
+```
 
@@
 
-This study set out to test two linking assumptions.
+We considered two linking assumptions.
+First we defined a weak (lenient) linking assumption in which any response lower than the maximum point on the scale (i.e.
+"right") is considered evidence for implicature computation.
+Second, we defined a strong (strict) linking assumption that only considered the lowest point on the scale (i.e.
+"wrong") as evidence for implicature computation.
+For each condition in our study (binary, ternary, quaternary, and quinary) and each implicature trial type (exhaustive and scalar), we computed a weak and a strong implicature rate.
+Figure \@ref(fig:implicatureRatePlot) shows these computed rates.
 
-We test this hypothesis formally using a binomial mixed effects model with the fixed effect of response type and the random intercept for participants as well as random intercept and slope for
+Comparing the strong and weak rows on Figure \@ref(fig:implicatureRatePlot), we see that a weak linking assumption tends to estimate higher implicature rates, especially in tasks with more response options.
+With a strong linking assumption, the binary and possibly ternary judgment tasks derive higher implicature rates than quaternary and quinary tasks.
+With a weak linking assumption, the pattern is reversed.
+Quaternary and quinary tasks estimate higher rates than binary and ternary tasks.
+The patterns show that estimates of "implicature rate" depend on linking assumptions and the number of responses available to participants in the study.
 
-A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.
+Comparing the exhaustive and scalar columns of Figure \@ref(fig:implicatureRatePlot), we see that with a strong linking assumption, there are slightly higher rates for scalar implicatures in the binary and ternary tasks.
+With a weak linking assumption, there may be slightly higher rates for scalar implicatures in the binary and ternary while the rates may be lower in the quaternary and quinary tasks.
+In what follows, we test the effect of linking assumption and response options on exhaustive and scalar implicature rates more formally.
 
-All the analytical decisions described here were pre-registered in an as.predicted format. You can access the preregistration
-
-```{r implicatureResultss}
-implicature_results<-
-  implicature_rate %>%
-  group_by(response_type, trial_type, implicature, definition) %>%
-  summarize(counts = n()) %>%
-  group_by(response_type, trial_type, definition) %>%
-  mutate(total = sum(counts), proportion = counts/total)
-```
-
-```{r}
-implicature_results$response_type <- fct_relevel(implicature_results$response_type, "binary", "ternary", "quaternary", "quinary")
-implicature_results$implicature <- as.factor(implicature_results$implicature)
-implicature_results$implicature <- fct_recode(implicature_results$implicature, yes = "1", no = "0")
-```
-
-```{r implicatureRatePlot}
+```{r implicatureRatePlot, fig.width=5, fig.height=3, fig.cap = "Implicature rate in exhaustive and scalar trials of the binary, ternary, quaternary, and quinary versions of the guessing game, computed once with a strong linking assumption and once with a weak linking assumption."}
 ggplot(implicature_results, aes(x=response_type,y=proportion)) +
-  geom_bar(aes(fill = implicature), stat="identity") +
+  geom_bar(aes(fill=definition), stat="identity") +
   facet_grid(definition ~ trial_type, drop = TRUE) +
@@
   labs(x="Implicature") +
-  theme(text = element_text(size=17), axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1)) +
+  geom_linerange(aes(ymin=lower,ymax=upper)) + guides(fill=FALSE)
 ```
@@
 ```{r implicatureRate, echo=FALSE, eval=FALSE}
-implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)
+implicature_analysis_a <- glmer(implicature ~ definition + response_type + (1|card) + (1|participant), family="binomial", data=implicature_rate)
 
 summary(implicature_analysis_a)
+
 library(brms)
-implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="bernoulli", data=implicature_rate)
+
+implicature_analysis_b <- brm(implicature ~ definition * response_type * trial_type + (definition*trial_type*response_type|card) + (definition*trial_type|participant), family="bernoulli", data=implicature_rate, control = list(adapt_delta = 0.99))
+
+saveRDS(implicature_analysis_b, file = "implicature_analysis_b")
+
+summary(implicature_analysis_b)
 ```
+
+For our formal analysis, we use a binomial mixed effects model with the fixed effect of response type (binary, ternary, quaternary, quinary), linking assumption (strong vs.
+weak), and trial type (exhaustive vs.
+scalar), as wellas the random intercept for participants as well as random intercept and slope for items (the card they saw).
+
+All the analytical decisions described here were pre-registered and you can access them through the following link: [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
 

### 2018-05-02 writeup.tex
added all confidence intervals and editted some more

@@
 \begin{figure}
-
-{\centering \includegraphics{writeup_files/figure-latex/linkvisualization-1}
-
-}
-
-\caption{Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true.}\label{fig:linkvisualization}
+\centering
+\includegraphics{writeup_files/figure-latex/linkvisualization-1.pdf}
+\caption{\label{fig:linkvisualization}Strong and weak link from response
+options to researcher inference about scalar implicature rate,
+exemplified for the disjunctive utterance when the conjunction is true.}
 \end{figure}
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/stimuli-1}
-
-}
-
-\caption{Cards used in the connective guessing game.}\label{fig:stimuli}
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/stimuli-1.pdf}
+\caption{\label{fig:stimuli}Cards used in the connective guessing game.}
 \end{figure}
@@
 said \enquote{there is a cat} and if there was a cat and a dog, Bob said
-\enquote{there is a cat and a dog}.
+\enquote{there is a cat and a dog}. Since the fictional character was
+blindfolded and did not see the outcome of the game, the ignorance
+inference commonly associated with disjunction was already common ground
+in the experimental setting. If the character was seeing the cards or
+knew what was on them, a disjunction would have violated the expectation
+that the speaker does not know which alternative actually holds. Our
+study controls for the possibile effect of ignorance violations on
+exclusivity and exhaustive inferences.
 
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/trials-1}
-
-}
-
-\caption{Trial types represented by example cards and guesses.}\label{fig:trials}
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/trials-1.pdf}
+\caption{\label{fig:trials}Trial types represented by example cards and
+guesses.}
 \end{figure}
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/binaryPlot-1}
-
-}
-
-\caption{Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game.}\label{fig:binaryPlot}
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/binaryPlot-1.pdf}
+\caption{\label{fig:binaryPlot}Proportion responses for the two-alternative
+(binary) forced choice judgments in the guessing game.}
 \end{figure}
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/ternaryPlot-1}
-
-}
-
-\caption{Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game.}\label{fig:ternaryPlot}
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/ternaryPlot-1.pdf}
+\caption{\label{fig:ternaryPlot}Proportion responses for the
+three-alternative (ternary) forced choice judgments in the guessing
+game.}
 \end{figure}
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/quaternaryPlot-1}
-
-}
-
-\caption{Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game.}\label{fig:quaternaryPlot}
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/quaternaryPlot-1.pdf}
+\caption{\label{fig:quaternaryPlot}Proportion responses for the
+four-alternative (quatenary) forced choice judgments in the guessing
+game.}
 \end{figure}
@@
 
-\begin{figure}[t]
-
-{\centering \includegraphics{writeup_files/figure-latex/quinaryPlot-1}
-
-}
-
-\caption{Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game.}\label{fig:quinaryPlot}
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/quinaryPlot-1.pdf}
+\caption{\label{fig:quinaryPlot}Proportion responses for the
+five-alternative (quinary) forced choice judgments in the guessing
+game.}
 \end{figure}
@@
 
-\subsubsection{Analysis}\label{analysis}
+\subsection{Analysis}\label{analysis}
 
-The goal of this study is to see if the estimated \enquote{implicature
-rate} in the experimental task is affected by the linking assumptions
-and the number of response options available in the task. Our analysis
-in this section focuses on these three elements. Two trial types are
-predicted to include pragmatic implicatures. First, trials where two
-animals were on the card but the fictional character guessed with a
-disjunction; for example \enquote{cat or dog} when the card has both a
-cat and a dog on it. We called such trials \enquote{scalar}. Second,
-trials where there were two animals on the card but the character
-guessed only one; for example \enquote{cat} when the card had a cat and
-a dog on it. We called such trials \enquote{exhaustive}. In our
-assessment of implicature rate, we focus on these two types of trials.
+Our primary goal in this study was to check whether the estimated
+\enquote{implicature rate} in the experimental task is affected by the
+linking assumption and the number of response options available in the
+task. Our analysis in this section focuses on these three elements. As
+mentioned before, two trial types were predicted to include pragmatic
+implicatures. First, trials where two animals were on the card but the
+fictional character guessed with a disjunction (scalar); for example
+\enquote{cat or dog} when the card has both a cat and a dog on it.
+Second, trials where there were two animals on the card but the
+character guessed only one (exhaustive); for example \enquote{cat} when
+the card had a cat and a dog on it. We called such trials
+\enquote{exhaustive}. In our assessment of implicature rate, we focus on
+these two trial types.
 
-This study set out to test two hypotheses. First, that the proportion of
-pragmatic vs.~literal responses in a truth values judgement task changes
-based on the number of response options available to the participants.
+We considered two linking assumptions. First we defined a weak (lenient)
+linking assumption in which any response lower than the maximum point on
+the scale (i.e. \enquote{right}) is considered evidence for implicature
+computation. Second, we defined a strong (strict) linking assumption
+that only considered the lowest point on the scale (i.e.
+\enquote{wrong}) as evidence for implicature computation. For each
+condition in our study (binary, ternary, quaternary, and quinary) and
+each implicature trial type (exhaustive and scalar), we computed a weak
+and a strong implicature rate. Figure \ref{fig:implicatureRatePlot}
+shows these computed rates.
+
+Comparing the strong and weak rows on Figure
+\ref{fig:implicatureRatePlot}, we see that a weak linking assumption
+tends to estimate higher implicature rates, especially in tasks with
+more response options. With a strong linking assumption, the binary and
+possibly ternary judgment tasks derive higher implicature rates than
+quaternary and quinary tasks. With a weak linking assumption, the
+pattern is reversed. Quaternary and quinary tasks estimate higher rates
+than binary and ternary tasks.
+
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/implicatureRatePlot-1.pdf}
+\caption{\label{fig:implicatureRatePlot}Implicature rate in exhaustive and
+scalar trials of the binary, ternary, quaternary, and quinary versions
+of the guessing game, computed once with a strong linking assumption and
+once with a weak linking assumption.}
+\end{figure}
+
 We test this hypothesis formally using a binomial mixed effects model
@@
 
-A second hypothesis was that the definition of what responses count as
-participants computing an implicature may affect the estimated rate of
-implicature in the experimental task.
-
-\begin{figure}
-\centering
-\includegraphics{writeup_files/figure-latex/implicatureRatePlot-1.pdf}
-\caption{}
-\end{figure}
+All the analytical decisions described here were pre-registered and you
+can access them through the following link:
+\url{https://aspredicted.org/tq3sz.pdf}
 

### 2018-05-02 writeup.Rmd

@@
 
-# weak definition only considers the highest point on the scale as "literal"
+# weak definition only considers the highest point on the scale as "literal" (Weak link in paper)
 pragmatic_trials$weak<-1
@@
 
-# strong definition only considers the lowest point on the scale as implicature 
+# strong definition only considers the lowest point on the scale as implicature (Strong link in paper)
 pragmatic_trials$strong<-0
@@
 # Discussion
-
-Alternative Linking Hypothesis:
-* RSA: Response behavior across conditions (utterance-card combinations) and dependent measures can be predicted by a linking hypothesis that assumes that participants are behaving like soft-optimal RSA speakers and provide a particular response (eg TRUE) to an utterance u if the RSA speaker probability of u (given the card) is within a particular probability interval (eg, within the interval [theta, 1]).
-
-* Differences between traditional approaches and RSA: 1.
-The traditional linking hypotheses are based on a binary implicature/literal theory of pragmatic reasoning but RSA gives a continuous measure of pragmatic reasoning and allows for better predicting response behavior with multiple options.
-
-A simple visual inspection of our results suggests that any variant of the Traditional Linking Hypothesis will yield unsatisfying empirical coverage with regards to participants’ behavior in truth value judgment tasks.
-Recall that according to this hypothesis, scalar implicature is conceptualized as a binary, categorical affair: an implicature is either ‘calculated,’ or it isn’t.
-This assumption has implications for how we approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had a cat and a dog on it?
-
-On the Traditional story, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
+=======
+On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
+This assumption has concerning implications for how we must approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had both a cat and a dog on it?
+
+To explain the data on the traditional view, are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
 “Wrong”) due to some other cognitive reflex which ‘overrode’ the implicature; or some mixture of (b) and (c).
@@
 why were participants roughly split between “Right” and “Kind of right” when the utterance was cat or dog and the card had a cat and a dog?).
-There is an established cottage industry of pragmatics research which approaches the problem of behavioral variation in exactly these ways, exploring the factors which “license” implicature calculation or “suppress” its anticipated behavioral expression (c.f.
-__), but the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data (and we should stress that even in this respect, the industry has yet to fully deliver the goods!).
-
-The Alternative Linking Hypothesis contrasts with the Traditional Linking Hypothesis in that the former is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
-[recap RSA model here?
-Maybe show how it gets the right basic qualitative pattern, i.e.
-$P_L$(a and b| “a or b”) $<$ $P_L$(a | “or”); $P_L$(a and b| “a or b”) $<$ $P_L$(b | “or”) ]
-
-Following Degen & Goodman (2014), we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA).
+However, the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
+
+We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis which assumes that participants' behavior can be represented using the model of a soft-optimal pragmatic speaker in the RSA framework.
+This alternative linking hypothesis contrasts with the traditional view in it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+Recall that in RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution of possible meanings given an utterance which that listener hears.
+The probability with which this listener $L_1$ ascribes a meaning s to an utterance u depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
+$S_1$ in turn is modeled as a continuous probabilistic distribution of possible utterances given an intended state of affairs the speaker intends to communicate.
+This distribution is sensitive to a rationality parameter $\alpha$, the production cost $C$ of potential utterances, and a representation of a literal listener $L_0$ whose interpretation of an utterance is in turn a function of that utterance's truth conditional content $[[u]](s)$ and her prior beliefs about the state of the world $P_w(s)$.
+
+    $P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
+
+    $P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $
+
+    $P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
+
+In this framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
+For example, exclusivity readings of disjunction or are represented in RSA as relatively low conditional probability of a conjunctive meaning on the $P_L$ distribution, given an utterance of or.
+Thus, it is not even possible to talk about 'rate' of implicature calculation in the RSA framework.
+The upshot, as we show below, is that this view of pragmatic competence does allow us to talk explicitly and quantitatively about rates of observed behavior in sentence verification tasks.
+
+First, following Degen & Goodman (2014), we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
+In their paper, Degen & Goodman argue that sentence verification tasks are relatively more sensitive to contextual manipulations (such as manipulation of the Question Under Discussion) than are sentence interpretation tasks, and that this follows if sentence interpretation tasks - but not sentence verification tasks - require an additional layer of counterfactual reasoning about the intentions of a cooperative speaker.
+
+A main desideratum of a behavioral linking hypothesis given the RSA view of pragmatic competence is to transform continuous probability distributions into categorical outputs (e.g.
+responses of “Right”/”Wrong” in the case of the binary condition of our experiment).
 For a given utterance u and an intended communicated meaning w, $S_1$(u | w) outputs a conditional probability of u given w.
-For example, in the binary condition of our experiment where a participant evaluated cat or dog when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of hearing the utterance cat or dog given a dog and cat card $S_1$(cat or dog | cat and dog).
-
-One desideratum of a linking hypothesis given this view of pragmatic competence is to transform this probability value into a categorical output (e.g.
-“Right”/”Wrong” in the case of the binary condition).
-This can be achieved by positing that participants ‘filter out’ low-probability utterances given an intended communicated meaning.
+For example, in the binary condition of our experiment where a participant evaluated cat or dog when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of hearing the utterance cat or dog given a dog and cat card: $S_1$(cat or dog | cat and dog).
+According to the linking hypothesis advanced here, the participant provides a particular response to u if the RSA speaker probability of u lies within a particular probability interval, given an observed state of the world (i.e.
+the configuration of animals on the card in our experiment).
 We model a responder, R, who in the binary condition responds “Right” to an utterance u in world w just in case $S_1$(u | w) exceeds some probability threshold $\theta$:
@@
 R(u, w, $\theta_1$ , $\theta_2$, $\theta_3$. $\theta_4$)
+
 = “Right” iff $S_1$(u | w) $>$ $\theta_1$
+
 =“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
+
 = “Neither” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$
+
 = “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | w) $>$ $\theta_4$
+
 = “Wrong” otherwise
 
-\newpage
+Bayesian statistical methods provide us a means for estimating the values of these probability thresholds in our RSA model.
+The basis for the model is a set of possible states of the world, given a universe of three animals - X, Y, and Z - that each may be on some card.
+We next define a set of possible sentences a speaker might utter, assuming the speaker intends to communicate which animals are on the card.
+We assume a uniform prior probability of different states of the world and a uniform cost function on utterances.
+We define a literal listener $L_0$, a pragmatic speaker $S_1$, and a responder $R$ according to our definitions above.
+Lastly, and assuming a uniform prior distribution over possible values of probability thresholds, we use Bayesian inference to recover a posterior distribution of these thresholds in each experimental condition, given the actual observed rate of response in each condition of the experiment.
+The results of this parameter estimation analysis are shown in the figures below, where the X axis of each figure corresponds to a threshold value between 0 and 1 and the Y axis corresponds to the posterior probability density of possible values of the threshold.
+
+```{r echo=FALSE, message=FALSE}
+bda <- read.csv("models/webppl_models/bda.csv")
+
+binary_graph <- ggplot(filter(bda, Parameter == "binary_theta"), aes(x=value))+
+  # facet_wrap(~Parameter, scales = "free") +
+  theme_few() +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distribution, binary condition:")
+
+ternary_graph <- ggplot(filter(bda, Parameter == c("ternary_theta1", "ternary_theta2")), aes(x=value))+
+  facet_wrap(~Parameter, scales = "free") +
+  theme_few() +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, ternary condition:")
+
+quatenary_graph <- ggplot(filter(bda, Parameter == c("quatenary_theta1", "quatenary_theta2", "quatenary_theta3")), aes(x=value))+
+  facet_wrap(~Parameter, scales = "free") +
+  theme_few() +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, quatenary condition:")
+
+quinary_graph <- ggplot(filter(bda, Parameter == c("quinary_theta1", "quinary_theta2", "quinary_theta3", "quinary_theta4")), aes(x=value))+
+  facet_wrap(~Parameter, scales = "free") +
+  theme_few() +
+  geom_density() +
+  scale_fill_grey(guide=FALSE) +
+  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
+  ggtitle("Threshold distributions, quinary condition:")
+binary_graph
+ternary_graph
+quatenary_graph
+quinary_graph
+```
+
+The above analysis is a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
 

### 2018-05-02 writeup.tex

@@
 pattern is reversed. Quaternary and quinary tasks estimate higher rates
-than binary and ternary tasks.
+than binary and ternary tasks. The patterns show that estimates of
+\enquote{implicature rate} depend on linking assumptions and the number
+of responses available to participants in the study.
+
+Comparing the exhaustive and scalar columns of Figure
+\ref{fig:implicatureRatePlot}, we see that with a strong linking
+assumption, there are slightly higher rates for scalar implicatures in
+the binary and ternary tasks. With a weak linking assumption, there may
+be slightly higher rates for scalar implicatures in the binary and
+ternary while the rates may be lower in the quaternary and quinary
+tasks. In what follows, we test the effect of linking assumption and
+response options on exhaustive and scalar implicature rates more
+formally.
 
@@
 
-We test this hypothesis formally using a binomial mixed effects model
-with the fixed effect of response type and the random intercept for
-participants as well as random intercept and slope for
+For our formal analysis, we use a binomial mixed effects model with the
+fixed effect of response type (binary, ternary, quaternary, quinary),
+linking assumption (strong vs.~weak), and trial type (exhaustive
+vs.~scalar), as wellas the random intercept for participants as well as
+random intercept and slope for items (the card they saw).
 
@@
 
-\section{Discussion}\label{discussion}
-
-Alternative Linking Hypothesis: * RSA: Response behavior across
-conditions (utterance-card combinations) and dependent measures can be
-predicted by a linking hypothesis that assumes that participants are
-behaving like soft-optimal RSA speakers and provide a particular
-response (eg TRUE) to an utterance u if the RSA speaker probability of u
-(given the card) is within a particular probability interval (eg, within
-the interval {[}theta, 1{]}).
-
-\begin{itemize}
-\tightlist
-\item
-  Differences between traditional approaches and RSA: 1. The traditional
-  linking hypotheses are based on a binary implicature/literal theory of
-  pragmatic reasoning but RSA gives a continuous measure of pragmatic
-  reasoning and allows for better predicting response behavior with
-  multiple options.
-\end{itemize}
-
-A simple visual inspection of our results suggests that any variant of
-the Traditional Linking Hypothesis will yield unsatisfying empirical
-coverage with regards to participants' behavior in truth value judgment
-tasks. Recall that according to this hypothesis, scalar implicature is
-conceptualized as a binary, categorical affair: an implicature is either
-\enquote{calculated,} or it isn't. This assumption has implications for
-how we approach analysis of variation in behavior on a truth value
-judgment task; for example, why did the majority of respondents in the
-binary condition of our experiment answer \enquote{Right} to an
-utterance of cat or dog when the card had a cat and a dog on it?
-
-On the Traditional story, we are forced to say that a) not all
-participants calculated the implicature; or that b) some participants
-who calculated the implicature did not choose the anticipated response
-(i.e. \enquote{Wrong}) due to some other cognitive reflex which
-\enquote{overrode} the implicature; or some mixture of (b) and (c). We
-might similarly posit that one or both of these factors underlie the
-variation in the ternary, quatenary, and quinary conditions (e.g.~why
-were participants roughly split between \enquote{Right} and
+\section{\# Discussion}\label{discussion}
+
+On the traditional view of the link between implicature and behavior in
+sentence verification tasks, scalar implicature is conceptualized as a
+binary, categorical affair - that is, an implicature is either
+\enquote{calculated} or it isn't, and the behavioral reflexes of this
+categorical interpretation process should be straightforwardly observed
+in experimental paradigms. This assumption has concerning implications
+for how we must approach analysis of variation in behavior on a truth
+value judgment task; for example, why did the majority of respondents in
+the binary condition of our experiment answer \enquote{Right} to an
+utterance of cat or dog when the card had both a cat and a dog on it?
+
+To explain the data on the traditional view, are forced to say that a)
+not all participants calculated the implicature; or that b) some
+participants who calculated the implicature did not choose the
+anticipated response (i.e. \enquote{Wrong}) due to some other cognitive
+reflex which \enquote{overrode} the implicature; or some mixture of (b)
+and (c). We might similarly posit that one or both of these factors
+underlie the variation in the ternary, quatenary, and quinary conditions
+(e.g.~why were participants roughly split between \enquote{Right} and
 \enquote{Kind of right} when the utterance was cat or dog and the card
-had a cat and a dog?). There is an established cottage industry of
-pragmatics research which approaches the problem of behavioral variation
-in exactly these ways, exploring the factors which \enquote{license}
-implicature calculation or \enquote{suppress} its anticipated behavioral
-expression (c.f. \_\_), but the best we can hope for on this approach is
-an analysis which traces the general qualitative patterns in the data
-(and we should stress that even in this respect, the industry has yet to
-fully deliver the goods!).
-
-The Alternative Linking Hypothesis contrasts with the Traditional
-Linking Hypothesis in that the former is rooted in a quantitative
+had a cat and a dog?). However, the best we can hope for on this
+approach is an analysis which traces the general qualitative patterns in
+the data.
+
+We contrast the above view of implicature and its behavioral reflexes
+with an alternative linking hypothesis which assumes that participants'
+behavior can be represented using the model of a soft-optimal pragmatic
+speaker in the RSA framework. This alternative linking hypothesis
+contrasts with the traditional view in it is rooted in a quantitative
 formalization of pragmatic competence which provides us a continuous
-measure of pragmatic reasoning. {[}recap RSA model here? Maybe show how
-it gets the right basic qualitative pattern, i.e. \(P_L\)(a and
-b\textbar{} \enquote{a or b}) \(<\) \(P_L\)(a \textbar{} \enquote{or});
-\(P_L\)(a and b\textbar{} \enquote{a or b}) \(<\) \(P_L\)(b \textbar{}
-\enquote{or}) {]}
-
-Following Degen \& Goodman (2014), we proceed on the assumption that
-behavior on sentence verification tasks, such as truth value judgment
-tasks, is best modeled as a function of an individual's mental
+measure of pragmatic reasoning. Recall that in RSA, pragmatically
+competent listeners are modeled as a continuous probabilistic
+distribution of possible meanings given an utterance which that listener
+hears. The probability with which this listener \(L_1\) ascribes a
+meaning s to an utterance u depends upon a prior probability
+distribution of potential states of the world \(P_w\), and upon
+reasoning about the communicative behavior of a speaker \(S_1\). \(S_1\)
+in turn is modeled as a continuous probabilistic distribution of
+possible utterances given an intended state of affairs the speaker
+intends to communicate. This distribution is sensitive to a rationality
+parameter \(\alpha\), the production cost \(C\) of potential utterances,
+and a representation of a literal listener \(L_0\) whose interpretation
+of an utterance is in turn a function of that utterance's truth
+conditional content \([[u]](s)\) and her prior beliefs about the state
+of the world \(P_w(s)\).
+
+\begin{verbatim}
+$P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
+
+$P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $
+
+$P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
+\end{verbatim}
+
+In this framework, individuals never categorically draw (or fail to
+draw) pragmatic inferences about the utterances they hear. For example,
+exclusivity readings of disjunction or are represented in RSA as
+relatively low conditional probability of a conjunctive meaning on the
+\(P_L\) distribution, given an utterance of or. Thus, it is not even
+possible to talk about \enquote{rate} of implicature calculation in the
+RSA framework. The upshot, as we show below, is that this view of
+pragmatic competence does allow us to talk explicitly and quantitatively
+about rates of observed behavior in sentence verification tasks.
+
+First, following Degen \& Goodman (2014), we proceed on the assumption
+that behavior on sentence verification tasks, such as truth value
+judgment tasks, is best modeled as a function of an individual's mental
 representation of a cooperative interlocutor (\(S_1\) in the language of
-RSA). For a given utterance u and an intended communicated meaning w,
-\(S_1\)(u \textbar{} w) outputs a conditional probability of u given w.
-For example, in the binary condition of our experiment where a
-participant evaluated cat or dog when there were both animals on the
+RSA) rather than of a pragmatic listener who interprets utterances
+(\(P_{L_1}\)). In their paper, Degen \& Goodman argue that sentence
+verification tasks are relatively more sensitive to contextual
+manipulations (such as manipulation of the Question Under Discussion)
+than are sentence interpretation tasks, and that this follows if
+sentence interpretation tasks - but not sentence verification tasks -
+require an additional layer of counterfactual reasoning about the
+intentions of a cooperative speaker.
+
+A main desideratum of a behavioral linking hypothesis given the RSA view
+of pragmatic competence is to transform continuous probability
+distributions into categorical outputs (e.g.~responses of
+\enquote{Right}/''Wrong'' in the case of the binary condition of our
+experiment). For a given utterance u and an intended communicated
+meaning w, \(S_1\)(u \textbar{} w) outputs a conditional probability of
+u given w. For example, in the binary condition of our experiment where
+a participant evaluated cat or dog when there were both animals on the
 card, the participant has access to the mental representation of \(S_1\)
 and hence to the \(S_1\) conditional probability of hearing the
-utterance cat or dog given a dog and cat card \(S_1\)(cat or dog
-\textbar{} cat and dog).
-
-One desideratum of a linking hypothesis given this view of pragmatic
-competence is to transform this probability value into a categorical
-output (e.g. \enquote{Right}/''Wrong'' in the case of the binary
-condition). This can be achieved by positing that participants
-\enquote{filter out} low-probability utterances given an intended
-communicated meaning. We model a responder, R, who in the binary
-condition responds \enquote{Right} to an utterance u in world w just in
-case \(S_1\)(u \textbar{} w) exceeds some probability threshold
+utterance cat or dog given a dog and cat card: \(S_1\)(cat or dog
+\textbar{} cat and dog). According to the linking hypothesis advanced
+here, the participant provides a particular response to u if the RSA
+speaker probability of u lies within a particular probability interval,
+given an observed state of the world (i.e.~the configuration of animals
+on the card in our experiment). We model a responder, R, who in the
+binary condition responds \enquote{Right} to an utterance u in world w
+just in case \(S_1\)(u \textbar{} w) exceeds some probability threshold
 \(\theta\):
 
-R(u, w, \(\theta\)) = \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\)
-\(\theta\) = \enquote{Wrong} otherwise
+R(u, w, \(\theta\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta\)
+
+= \enquote{Wrong} otherwise
 
@@
 to our five experimental conditions, we say that R takes as its input an
-utterance u and a world state w and a number of threshold variables
+utterance u, a world state w, and a number of threshold variables
 dependent on a variable c, corresponding to the experimental condition
@@
 
-R(u, w, \(\theta_1\) , \(\theta_2\))\\
-= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\) =
-\enquote{Neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w) \(>\)
-\(\theta_2\)\\
+R(u, w, \(\theta_1\) , \(\theta_2\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\)
+
+= \enquote{Neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w) \(>\)
+\(\theta_2\)
+
 = \enquote{Wrong} otherwise
@@
 
-R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\))\\
-= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\) =
-\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_2\)\\
+R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\)
+
+= \enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
+\(>\) \(\theta_2\)
+
 = \enquote{Kinda Wrong} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_3\) = \enquote{Wrong} otherwise
+\(>\) \(\theta_3\)
+
+= \enquote{Wrong} otherwise
 
@@
 
-R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\). \(\theta_4\))\\
+R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\). \(\theta_4\))
+
 = \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\)
+
 =\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_2\) = \enquote{Neither} iff \(\theta_2\) \(>\) \(S_1\)(u
-\textbar{} w) \(>\) \(\theta_3\)\\
+\(>\) \(\theta_2\)
+
+= \enquote{Neither} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} w) \(>\)
+\(\theta_3\)
+
 = \enquote{Kinda Wrong} iff \(\theta_3\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_4\) = \enquote{Wrong} otherwise
-
-\newpage
+\(>\) \(\theta_4\)
+
+= \enquote{Wrong} otherwise
+
+Bayesian statistical methods provide us a means for estimating the
+values of these probability thresholds in our RSA model. The basis for
+the model is a set of possible states of the world, given a universe of
+three animals - X, Y, and Z - that each may be on some card. We next
+define a set of possible sentences a speaker might utter, assuming the
+speaker intends to communicate which animals are on the card. We assume
+a uniform prior probability of different states of the world and a
+uniform cost function on utterances. We define a literal listener
+\(L_0\), a pragmatic speaker \(S_1\), and a responder \(R\) according to
+our definitions above. Lastly, and assuming a uniform prior distribution
+over possible values of probability thresholds, we use Bayesian
+inference to recover a posterior distribution of these thresholds in
+each experimental condition, given the actual observed rate of response
+in each condition of the experiment. The results of this parameter
+estimation analysis are shown in the figures below, where the X axis of
+each figure corresponds to a threshold value between 0 and 1 and the Y
+axis corresponds to the posterior probability density of possible values
+of the threshold.
+
+\begin{verbatim}
+## Warning in is.na(e1) | is.na(e2): longer object length is not a multiple of
+## shorter object length
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in `==.default`(Parameter, c("quatenary_theta1",
+## "quatenary_theta2", : longer object length is not a multiple of shorter
+## object length
+\end{verbatim}
+
+\includegraphics{writeup_files/figure-latex/unnamed-chunk-1-1.pdf}
+\includegraphics{writeup_files/figure-latex/unnamed-chunk-1-2.pdf}
+\includegraphics{writeup_files/figure-latex/unnamed-chunk-1-3.pdf}
+\includegraphics{writeup_files/figure-latex/unnamed-chunk-1-4.pdf}
+
+The above analysis is a proof of concept for the following idea: by
+relaxing the assumptions of the traditional view of scalar implicature
+(namely, that scalar implicatures either are or are not calculated, and
+that behavior on sentence verification tasks directly reflects this
+binary interpretation process), we can propose quantitative models of
+the variation in behavior we observe in experimental settings.
 

### 2018-05-02 writeup.Rmd
minor gd edits

@@
 And second, that listeners either do or do not compute an implicature on any given occasion.
-In the Discussion we will discuss both of these issues.
+In the General Discussion we will discuss both of these issues.
 First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' **production** probabilities.
@@
 
-# Discussion
+# General Discussion
 =======
+
 On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
-This assumption has concerning implications for how we must approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had both a cat and a dog on it?
-
-To explain the data on the traditional view, are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
-“Wrong”) due to some other cognitive reflex which ‘overrode’ the implicature; or some mixture of (b) and (c).
-We might similarly posit that one or both of these factors underlie the variation in the ternary, quatenary, and quinary conditions (e.g.
-why were participants roughly split between “Right” and “Kind of right” when the utterance was cat or dog and the card had a cat and a dog?).
+This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
+
+To explain the data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "Wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
+We might similarly posit that one or both of these factors underlie the variation in the ternary, quaternary, and quinary conditions.
 However, the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
-
-We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis which assumes that participants' behavior can be represented using the model of a soft-optimal pragmatic speaker in the RSA framework.
-This alternative linking hypothesis contrasts with the traditional view in it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
-Recall that in RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution of possible meanings given an utterance which that listener hears.
-The probability with which this listener $L_1$ ascribes a meaning s to an utterance u depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
-$S_1$ in turn is modeled as a continuous probabilistic distribution of possible utterances given an intended state of affairs the speaker intends to communicate.
-This distribution is sensitive to a rationality parameter $\alpha$, the production cost $C$ of potential utterances, and a representation of a literal listener $L_0$ whose interpretation of an utterance is in turn a function of that utterance's truth conditional content $[[u]](s)$ and her prior beliefs about the state of the world $P_w(s)$.
+**XXX Brandon, can you be more specific about what you mean by 'tracing a general qualitative pattern'?**
+
+We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis.
+Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2014; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
+We take inspiration from this approach and treat participants' behavior in our experimental tasks as the result of a soft-optimal pragmatic speaker in the RSA framework.
+This alternative linking hypothesis contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+In RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution over possible meanings (states of the world) given an utterance which that listener observes.
+The probability with which this listener $L_1$ ascribes a meaning $s$ to an utterance $u$ depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
+$S_1$ in turn is modeled as a continuous probabilistic distribution over possible utterances given an intended state of the world the speaker intends to communicate.
+This distribution is sensitive to a rationality parameter $\alpha$, the production cost $C$ of potential utterances, and the informativeness of the utterance, quantified via a representation of a literal listener $L_0$ whose interpretation of an utterance is in turn a function of that utterance's truth conditional content $[[u]](s)$ and her prior beliefs about the state of the world $P_w(s)$.
 
@@
 In this framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
-For example, exclusivity readings of disjunction or are represented in RSA as relatively low conditional probability of a conjunctive meaning on the $P_L$ distribution, given an utterance of or.
-Thus, it is not even possible to talk about 'rate' of implicature calculation in the RSA framework.
+For example, exclusivity readings of disjunction are represented in RSA as relatively lower conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared to its prior probability.
+Thus, it is not even possible **XXX or at least not without auxiliary assumptions** to talk about 'rate' of implicature calculation in the RSA framework.
 The upshot, as we show below, is that this view of pragmatic competence does allow us to talk explicitly and quantitatively about rates of observed behavior in sentence verification tasks.
 
-First, following Degen & Goodman (2014), we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
+First, following @Degen2014, we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
 In their paper, Degen & Goodman argue that sentence verification tasks are relatively more sensitive to contextual manipulations (such as manipulation of the Question Under Discussion) than are sentence interpretation tasks, and that this follows if sentence interpretation tasks - but not sentence verification tasks - require an additional layer of counterfactual reasoning about the intentions of a cooperative speaker.
@@
 responses of “Right”/”Wrong” in the case of the binary condition of our experiment).
-For a given utterance u and an intended communicated meaning w, $S_1$(u | w) outputs a conditional probability of u given w.
-For example, in the binary condition of our experiment where a participant evaluated cat or dog when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of hearing the utterance cat or dog given a dog and cat card: $S_1$(cat or dog | cat and dog).
-According to the linking hypothesis advanced here, the participant provides a particular response to u if the RSA speaker probability of u lies within a particular probability interval, given an observed state of the world (i.e.
+For a given utterance $u$ and an intended communicated meaning $s$, $S_1$(u | s) outputs a conditional probability of $u$ given $s$.
+For example, in the binary condition of our experiment where a participant evaluated "There is a cat or a dog" when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of producing the utterance "cat or dog"" given a dog and cat card: $S_1$("cat or dog" | cat and dog).
+According to the linking hypothesis advanced here, the participant provides a particular response to $u$ if the RSA speaker probability of $u$ lies within a particular probability interval, given an observed state of the world (i.e.
 the configuration of animals on the card in our experiment).
-We model a responder, R, who in the binary condition responds “Right” to an utterance u in world w just in case $S_1$(u | w) exceeds some probability threshold $\theta$:
+We model a responder, $R$, who in the binary condition responds “Right” to an utterance $u$ in world $s$ just in case $S_1(u | s)$ exceeds some probability threshold $\theta$:
 
@@
 
-= “Right” iff $S_1$(u | w) $>$ $\theta$
+= “Right” iff $S_1$(u | s) $>$ $\theta$
 
@@
 
-In the experiment conditions where there are more than two choices, we model the range of possible behavioral responses for R with the introduction of intermediate probability thresholds.
-For example, in the ternary condition, R(u, w, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | w) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | w) > $\theta_2$.
-To fully generalize the model to our five experimental conditions, we say that R takes as its input an utterance u, a world state w, and a number of threshold variables dependent on a variable c, corresponding to the experimental condition in which the participant finds herself (e.g.
-the range of possible responses available to R).
+In the experiment conditions where there are more than two choices, we model the range of possible behavioral responses for $R$ with the introduction of intermediate probability thresholds.
+For example, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | s) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
+To fully generalize the model to our five experimental conditions, we say that $R$ takes as its input an utterance $u$, a world state $s$, and a number of threshold variables dependent on a variable $c$, corresponding to the experimental condition in which the participant finds herself (e.g.
+the range of possible responses available to $R$).
 

### 2018-05-07 writeup.Rmd
Masoud completed his tasks for draft 1

--- 2018-05-02 writeup.Rmd
@@
 library(binom)
+library(knitr)
 theme_set(theme_bw(18))
@@
 Under the Weak link, we would conclude that they are.
-
 In the experiment reported in the following section, we presented participants with exactly this setup.
-Different groups of participants were presented with different numbers of response options.
-We categorized their responses according to the Weak and the Strong link and tested whether number of response options and categorization scheme leads to different conclusions about implicature rates.
 
 # Experiment
+
+In this study, we presented participants with an online card game.
+Different groups of participants were presented with different numbers of response options for the task.
+In critical trials, participants were presented with descriptions for the cards that typically result in exhaustive or scalar implicatures.
+We categorized their responses in such trials according to the "weak" and the "strong" link, and tested whether the number of response options and the linking assumptions lead to different conclusions about the rate of computed implicatures in the experimental task.
 
@@
   summarise(count = n()/24)
-```
-
-200 participants were recruited using Amazon Mechanical Turk (binary=`r participants_info$count[1]`, ternary`r participants_info$count[4]`, quaternary=`r participants_info$count[2]`, quinary=`r participants_info$count[3]`).
+
+mean_age <- mean(data$age)
+
+logic <- data %>% select(participant, logical_training) %>% unique()
+
+logicTraining <- table(logic$logical_training)
+```
+
+200 participants were recruited using Amazon Mechanical Turk.
+They optionally provided demographic information at the end of the study.
+Mean age of the participnats was `r round(mean_age)`.
+We also asked participants if they had any prior training in logic.
+`r logicTraining[[2]]` participants reported that they had while `r logicTraining[[1]]` had no prior training in logic.
 No participant was excluded from the final analysis.
 
-### Procedure
+### Materials and Procedure
 
 The study was administered online through Amazon Mechanical Turk.
-Participants were introduced to a set of cards with pictures of one or two animals (Figure \@ref(fig:stimuli)).
-They were told that a blindfolded fictional character called Bob is going to guess what animals are on the card.
-On each trial, participants saw a card as well as a sentence representing Bob's guess.
-For example, they saw a card with a cat on it and read the sentence "There is a cat on the card." The study ended after 24 trials.
-At the end participants optionally provided demographic information.
-We also asked participants if they had any prior training in logic.
-You can access and view on the study's [online repository](https://github.com/thegricean/si-paradigms/).
-
-### Design and Materials
+Participants were first introduced to the set of cards we used in the study (Figure \@ref(fig:stimuli)).
+Each card had pictures of one or two animals.
+Animals were chosen from the following set: cat, dog, and elephant.
+Then participants were introduced to a blindfolded fictional character called Bob.
+Bob was blindfolded to control for violations of ignorance expectations with disjunction.
+Participants were told that Bob is going to guess what animals are on the card.
+We asked participants to let us know whether Bob's guess is wrong or right.
+In each trial, participants saw a card as well as a sentence representing Bob's guess.
+For example, they saw a card with a cat and read the sentence "There is a cat on the card." Depending on the task participants were assigned to, they had to choose between two (binary task), three (ternary task), four (quaternary task), or five (quinary task) response options.
+The study ended after 24 trials.
+You can access and view the study using the paper's [online repository](https://github.com/thegricean/si-paradigms/).
+
+### Design
 
@@
 Cards with only one animal on them and cards with two animals.
-Animals were chosen from the following set: cat, dog, and elephant  There were three types of guesses: simple (e.g.
+There were three types of guesses: simple (e.g.
 *There is a cat*), conjunctive (e.g.
@@
 Crossing the number of animals on the card, the type of guess, and the overlap between the guess and the card results in 12 different possible trial types.
-We chose 8 trial types (Figure \@ref(fig:trials)), balancing the number of one-animal vs.
+We chose 8 trial types, balancing the number of one-animal vs.
 two-animal cards, simple vs.
@@
 The study also had a between participant manipulation of the number of response options in the forced choice task.
-Participants were randomly assigned to one of four different conditions.
-The conditions differed with respect to the number of response options: binary (wrong vs.
+Participants were randomly assigned to one of four different conditions or tasks.
+The tasks differed with respect to the number of response options: binary (wrong vs.
 right), ternary (wrong, neither, right), quaternary (wrong, kinda wrong, kinda right, right), and quinary (wrong, kinda wrong, neither, kinda right, right).
@@
 
-```{r trials, fig.asp=0.35, fig.cap = "Trial types represented by example cards and guesses."}
-trials_img <- jpeg::readJPEG("experiments/figs/trialTypes.jpg")
-grid::grid.raster(trials_img)
-```
-
 ## Results
-
-<!--We used `r cite_r("r-references.bib")` for all our analyses.-->
 
@@
   binary_summary %>%
-  filter(card_type=="X", guess_type=="XandY")
+  filter(card_type=="XY", guess_type=="XandY")
 binary_summary_XY_and_confint <-
@@
 
-binary_summary <- bind_rows(binary_summary_X_cat, binary_summary_XY_cat, binary_summary_XY_ele, binary_summary_X_ele,
-                                binary_summary_XY_and, binary_summary_X_and, binary_summary_XY_or, binary_summary_X_or)
+binary_summary <- bind_rows(binary_summary_X_cat, binary_summary_XY_cat, binary_summary_XY_ele, binary_summary_X_ele, binary_summary_XY_and, binary_summary_X_and, binary_summary_XY_or, binary_summary_X_or)
 
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response", y="Proportion of response")+
+  labs(x="Response Options in the Binary Task", y="Proportions")+
   theme_few() +
@@
 
-Here we present the proportion that participants chose the response options in each of the 8 trial types of the binary, ternary, quaternary, and quinary tasks.
+The experiment had `r participants_info$count[1]` participants in the binary task, `r participants_info$count[4]` in the ternary task, `r participants_info$count[2]` in the quaternary task and `r participants_info$count[3]` in the quinary task.
+In this section, we present the proportion that participants chose different response options in each of the 8 trial types of these four tasks.
+
 Figure \@ref(fig:binaryPlot) shows the proportion of "right" and "wrong" responses in the binary task.
 Starting from the leftmost column, participants considered a guess "wrong" if the guessed animal was not on the card.
-Moving to the second column, participants considered a guess "right" if the animal on the card was mentioned.
-However, if only one of the two animals on the card was mentioned (exhaustive trials), `r round(binaryExh_wrong$proportion*100)`% of the times participants considered the guess "wrong".
+Moving to the second column, participants considered the guess "right" when the only animal on the card was mentioned.
+However, when only one of the two animals on the card was mentioned (exhaustive trials), `r round(binaryExh_wrong$proportion*100)`% of the times participants considered the guess "wrong".
 Moving to the third column, if a conjunction of animals was guessed while only one animal was on the card, participants considered the guess to be "wrong".
 If a conjunction of animals was guessed and both animals were present on the card, all participants considered the guess to be "right" as expected.
-Moving to the forth column, if a disjunction of animals was guessed and only one of the animals was on the card, participants considered the guess to be "right" almost all the time.
+Finally, if a disjunction of animals was guessed and only one of the animals was on the card, participants considered the guess to be "right" almost all the time.
 However, if both animals were present (scalar trials), `r round(binaryScalar_wrong$proportion*100)`% of the times participants considered the guess to be "wrong".
@@
   ternary_summary %>%
-  filter(card_type=="X", guess_type=="XandY")
+  filter(card_type=="XY", guess_type=="XandY")
 ternary_summary_XY_and_confint <-
@@
 
-ternary_summary <- bind_rows(ternary_summary_X_cat, ternary_summary_XY_cat, ternary_summary_XY_ele, ternary_summary_X_ele,
-                                ternary_summary_XY_and, ternary_summary_X_and, ternary_summary_XY_or, ternary_summary_X_or)
+ternary_summary <- bind_rows(ternary_summary_X_cat, ternary_summary_XY_cat, ternary_summary_XY_ele, ternary_summary_X_ele, ternary_summary_XY_and, ternary_summary_X_and, ternary_summary_XY_or, ternary_summary_X_or)
 
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response", y="Proportion of response")+
+  labs(x="Response Options in the Ternary Task", y="Proportions")+
   theme_few() +
@@
 Figure \@ref(fig:ternaryPlot) shows the proportion of "right", "neither", and "wrong" responses in the ternary task.
-Similar to the binary task, participants considered a guess wrong when the mentioned animal was not on the card.
-They considered the guess "right" when the mentioned animal was on the card.
+Similar to the binary task, participants considered a guess wrong when the mentioned animal was not on the card, and "right" when the mentioned animal was the only animal on the card.
 However, in exhaustive trials when the fictional character only guessed one of the two animals on the card, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
@@
   quaternary_summary %>%
-  filter(card_type=="X", guess_type=="XandY")
+  filter(card_type=="XY", guess_type=="XandY")
 quaternary_summary_XY_and_confint <-
@@
 
-quaternary_summary <- bind_rows(quaternary_summary_X_cat, quaternary_summary_XY_cat, quaternary_summary_XY_ele, quaternary_summary_X_ele,
-                                quaternary_summary_XY_and, quaternary_summary_X_and, quaternary_summary_XY_or, quaternary_summary_X_or)
+quaternary_summary <- bind_rows(quaternary_summary_X_cat, quaternary_summary_XY_cat, quaternary_summary_XY_ele, quaternary_summary_X_ele, quaternary_summary_XY_and, quaternary_summary_X_and, quaternary_summary_XY_or, quaternary_summary_X_or)
 
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response", y="Proportion of response")+
+  labs(x="Response Options for the Quaternary Task", y="Proportions")+
   theme_few() +
@@
 Figure \@ref(fig:quaternaryPlot) shows the proportion of "right", "kinda right", "kinda wrong", and "wrong" responses in the quaternary task.
-Similar to the results seen previously, the control trials turned outas expected.
+Similar to the results seen previously, the control trials turned out as expected.
 Participants considered a guess "wrong" if the animal guessed was not on the card and "right" if it was the only animal on the card.
@@
   quinary_summary %>%
-  filter(card_type=="X", guess_type=="XandY")
+  filter(card_type=="XY", guess_type=="XandY")
 quinary_summary_XY_and_confint <-
@@
 
-quinary_summary <- bind_rows(quinary_summary_X_cat, quinary_summary_XY_cat, quinary_summary_XY_ele, quinary_summary_X_ele,
-                                quinary_summary_XY_and, quinary_summary_X_and, quinary_summary_XY_or, quinary_summary_X_or)
+quinary_summary <- bind_rows(quinary_summary_X_cat, quinary_summary_XY_cat, quinary_summary_XY_ele, quinary_summary_X_ele, quinary_summary_XY_and, quinary_summary_X_and, quinary_summary_XY_or, quinary_summary_X_or)
 
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response", y="Proportion of response")+
+  labs(x="Response Options in the Quinary Task", y="Proportions")+
   theme_few() +
@@
 
-Comparing the response patterns in binary to quinary tasks (Figures \@ref(fig:binaryPlot) to \@ref(fig:quinaryPlot)), we can observe that in implicature trials, participants are less likely to choose the endpoints of the scale (i.e.
-"wrong" and "right") as they are given more intermediate options.
-This raises the possibilty that the strict "wrong/right" responses in the tasks with fewer options (binary and ternary) were not accurately reflecting participant judgments of implicature trials and pushed their judgments to the extreme ends.
-More generally, the data suggest that participant judgments in contexts that give rise to implicatures fall within the intermrediate level of the response scale and forced choice tasks with few options (especially binary tasks) may risk depicting judgments more extreme than they actually are.
+<!--
+In four trial types, participants provided the same responses regardless of how many response options were made available.
+The first two trial types include the guesses with an animal not on the card at all.
+In such trials, whether there was one or two animals on the card, participants considered the guess wrong.
+In the third and the fourth trial types, the gueses matched the aimal(s) on the card; if there was one animal on the card, that animal was mentioned and if there were two, both were mentioned using a conjunction.
+The fact that participants chose the extreme ends of the scale for these trial types and the responses did not change when intermediate options were provided suggests that participant judgments truly aligned with the opposite ends of the scale in these trial types.
+
+In the trial type where the guess was a conjunction but only one of the animals was on the card, participants considered the guess wrong when fewer options were provided.
+However, in tasks with more options (four and five), participant responses were distributed between "wrong", "kinda wrong", and "kinda right" options, with the majority of responses being "wrong" or "kinda wrong".
+The graded nature of the judgments in this trial type suggests that participants do not consider such guesses as completely wrong.
+Similarly,
+
+Finally, in exhaustive and scalar implicature trial types participants were less likely to choose the option "wrong" when they were given more intermediate options.
+Even though in the binary task task recorded participant judgments as
+
+semantic violations vs. pragmatic violations
+-->
 
@@
 With a weak linking assumption, there may be slightly higher rates for scalar implicatures in the binary and ternary while the rates may be lower in the quaternary and quinary tasks.
-In what follows, we test the effect of linking assumption and response options on exhaustive and scalar implicature rates more formally.
+In what follows, we formally test the effect of linking assumption and response options on exhaustive and scalar implicature rates.
 
@@
   geom_bar(aes(fill=definition), stat="identity") +
-  facet_grid(definition ~ trial_type, drop = TRUE) +
+  facet_grid(trial_type~definition, drop = TRUE) +
   theme_few() + 
-  labs(x="Implicature") +
+  labs(x="Number of Response Options in the Task", y="Inferred Implicature Rate") +
   theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1)) +
@@
 
-```{r implicatureRate, echo=FALSE, eval=FALSE}
-implicature_analysis_a <- glmer(implicature ~ definition + response_type + (1|card) + (1|participant), family="binomial", data=implicature_rate)
-
-summary(implicature_analysis_a)
-
-library(brms)
-
-implicature_analysis_b <- brm(implicature ~ definition * response_type * trial_type + (definition*trial_type*response_type|card) + (definition*trial_type|participant), family="bernoulli", data=implicature_rate, control = list(adapt_delta = 0.99))
-
-saveRDS(implicature_analysis_b, file = "implicature_analysis_b")
-
-summary(implicature_analysis_b)
-```
-
-For our formal analysis, we use a binomial mixed effects model with the fixed effect of response type (binary, ternary, quaternary, quinary), linking assumption (strong vs.
+```{r implicatureRate, warning=FALSE}
+# The analysis takes time to run. To reproduce please run the commented lines. We have saved the results we obtained as a dataframe.
+
+#library(brms)
+
+#implicature_analysis_b <- brm(implicature ~ definition * response_type * trial_type + (definition*trial_type*response_type|card) + (definition*trial_type|participant), family="bernoulli", data=implicature_rate, control = list(adapt_delta = 0.99, max_treedepth = 15))
+
+#saveRDS(implicature_analysis_b, file = "implicature_analysis_b")
+#implicature_analysis_b <- readRDS("implicature_analysis_b")
+
+#fixed_effects <- data.frame(fixef(implicature_analysis_b))
+#write.csv(fixed_effects, "experiments/main/fixed_effect_estimates.csv")
+
+fixed_effects <- read_csv("experiments/main/fixed_effect_estimates.csv")
+
+fixed_effects$X1 <- c("Intercept", "Link = Weak", "Task = Quaternary", "Task = Quinary", "Task = Ternary", "Implicature = Scalar", "Link = Weak : Task = Quaternary", "Link = Weak : Task = Quinary", "Link = Weak : Task = Ternary", "Link = Weak : Implicature = Scalar", "Task = Quaternary : Implicature = Scalar", "Task = Quinary : Implicature = Scalar", "Task = Ternary : Implicature = Scalar", "Link=Weak : Task=Quaternary : Implicature=Scalar", "Link=Weak : Task=Quinary : Implicature=Scalar", "Link=Weak : Task=Ternary : Implicature=Scalar")
+
+fixed_effects_table <- 
+  fixed_effects %>%
+  rename(Predictors = "X1", `2.5%` = "X2.5.ile", `97.5%` = "X97.5.ile") %>%
+  select(-Est.Error)
+
+kable(fixed_effects_table,digits = 2 , caption = "\\label{tab:modeltable}Model Parameter Estimates and Their Credible Intervals", booktabs = T)
+```
+
+For our formal analysis, we used a bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms].
+The model had the fixed effects of response type (binary, ternary, quaternary, quinary), linking assumption (strong vs.
 weak), and trial type (exhaustive vs.
-scalar), as wellas the random intercept for participants as well as random intercept and slope for items (the card they saw).
-
-All the analytical decisions described here were pre-registered and you can access them through the following link: [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
-
-* Was logical training a significant predictor of "implicature rate"?
-
-# Discussion
-=======
+scalar), as well as their two way and three way interactions.
+We also included random intercepts and slopes for items (cards) and participants.
+Following @barr2013random, we used the maximal random effects structure by including random slopes for all our fixed effects and their interactions.
+Since the number of response options was a between participant variable we did not include random slopes of response options for participants.
+Four chains converged after 2000 iterations each (warmup = 1000).
+Table \@ref(tab:modeltable) summarizes the mean parameter estimates and their 95% credible intervals.
+$\hat{R}=1$ for all estimated parameters.
+All the analytical decisions described here were pre-registered[^1].
+
+The model provided evidence for two effects in the study.
+First, there was a main effect of trials such that scalar trials had slightly higher implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]).
+Second, there was an interaction between linking assumption and number of resopnse options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a weak linking assumption had higher implicature rates.
+
+[^1]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
+
+## Discussion
+
+We asked whether the linking assumptions and the number of response options available to participants affects the inferred implicature rate in an experimental study.
+The results presented here suggest they do.
+A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (weak link) reported higher implicature rates in tasks with 4 or 5 options.
+A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (strong link) reported lower implicature rates in tasks with 4 or 5 options.
+The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions of truth value judgment tasks with more than two response options.
+The lower rate of implicatures with a strong linking assumption implies that in such studies, strong linking assumptions may underestimate participants' pragmatic competence.
+
+While the binary truth value judgement task avoids the analytic decision between strong and weak linking assumptions, our results suggest that binary tasks can also underestimate participants' pragmatic competence.
+In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs.
+"right") and are asked to report pragmatic infelicities using the lowest point (e.g.
+"wrong").
+Our study showed that in trials with true but infelicitous descriptions (implicature trials), participants often avoided the lowest point on the scale if they were given more intermediate options.
+Even though the option "wrong" was available to participants in all tasks, participants in tasks with intermediate options chose it less often.
+In computing implicature rate, this pattern manifested itself as a decrease in implicature rate with strong link when more response options were provided, and increase in implicature rate with weak link when more response options were provided.
+These conclusions are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much.
+Providing participants with only the extreme opposits of the scale (e.g.
+wrong/right, false/true) when pragmatic violations are considered to be of an intermediate nature risks misrepresentation of participants' pragmatic competence.
+
+This study did not investigate the effect of option labels on the inferred implicature rate.
+However, the results provided suggestive evidence that some options better capture participant intuitions of pragmatic infelicities than others.
+Among the intermediate options, "kinda right" was chosen most often to report pragmatic infelicities.
+The option "neither" was rarely used in the ternary and quinary tasks (where it was used as a midpoint), suggesting that participants found pragmatic infelicities as different degrees of being "right" and not "neither right nor wrong." Therefore, options that capture grades of being "right" like "kinda right" proved be most suitable for capturing true but infelicitous utterances.
+
+This study had three design features that we would like to investigate in future work.
+First, the utterances were by a blindfolded character because we wanted to control for violation of ignorance expectations with disjunction.
+A disjunction such as "A or B" often carries an implication or expectation that the speaker is not certain which alternative actually holds.
+In future work, we would like to see how the violation of the ignorance expectation would affect the inferred implicature rate by having the fictional character describe the cards while looking at them.
+Second, in this study we considered exhaustive and scalar implicatures with *or*.
+We would like to see if similar effects hold for the scalar implicatures with *some*.
+Finally, our experiment was designed as a guessing game and the exact goal of the game was left implicit.
+We expect that different goals, for example help the character win more points vs.
+help the character be more accurate, would affect how strict or lenient participants are with their judgments and ultimately affect the implicature rate in the task.
+In future work we would like to systematically vary the goal of the game and explore its effects on the inferred implicature rate.
+
+# General Discussion
+
 On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.

### 2018-05-07 writeup.tex
Masoud completed his tasks for draft 1

@@
 Under the Strong link, we would conclude that scalar implicatures are
-not defaults. Under the Weak link, we would conclude that they are.
-
-In the experiment reported in the following section, we presented
-participants with exactly this setup. Different groups of participants
-were presented with different numbers of response options. We
-categorized their responses according to the Weak and the Strong link
-and tested whether number of response options and categorization scheme
-leads to different conclusions about implicature rates.
+not defaults. Under the Weak link, we would conclude that they are. In
+the experiment reported in the following section, we presented
+participants with exactly this setup.
 
@@
 
+In this study, we presented participants with an online card game.
+Different groups of participants were presented with different numbers
+of response options for the task. In critical trials, participants were
+presented with descriptions for the cards that typically result in
+exhaustive or scalar implicatures. We categorized their responses in
+such trials according to the Weak and the Strong link, and tested
+whether the number of response options and the linking assumptions lead
+to different conclusions about the rate of computed implicatures in the
+experimental task.
+
 \subsection{Methods}\label{methods}
@@
 
-200 participants were recruited using Amazon Mechanical Turk (binary=50,
-ternary53, quaternary=43, quinary=54). No participant was excluded from
-the final analysis.
-
-\subsubsection{Procedure}\label{procedure}
+200 participants were recruited using Amazon Mechanical Turk. They
+optionally provided demographic information at the end of the study.
+Mean age of the participnats was 35. We also asked participants if they
+had any prior training in logic. 40 participants reported that they had
+while 160 had no prior training in logic. No participant was excluded
+from the final analysis.
+
+\subsubsection{Materials and Procedure}\label{materials-and-procedure}
 
 The study was administered online through Amazon Mechanical Turk.
-Participants were introduced to a set of cards with pictures of one or
-two animals (Figure \ref{fig:stimuli}). They were told that a
-blindfolded fictional character called Bob is going to guess what
-animals are on the card. On each trial, participants saw a card as well
-as a sentence representing Bob's guess. For example, they saw a card
-with a cat on it and read the sentence \enquote{There is a cat on the
-card.} The study ended after 24 trials. At the end participants
-optionally provided demographic information. We also asked participants
-if they had any prior training in logic. You can access and view on the
-study's \href{https://github.com/thegricean/si-paradigms/}{online
-repository}.
-
-\subsubsection{Design and Materials}\label{design-and-materials}
+Participants were first introduced to the set of cards we used in the
+study (Figure \ref{fig:stimuli}). Each card had pictures of one or two
+animals. Animals were chosen from the following set: cat, dog, and
+elephant. Then participants were introduced to a blindfolded fictional
+character called Bob. Bob was blindfolded to control for violations of
+ignorance expectations with disjunction. Participants were told that Bob
+is going to guess what animals are on the card. We asked participants to
+let us know whether Bob's guess is wrong or right. In each trial,
+participants saw a card as well as a sentence representing Bob's guess.
+For example, they saw a card with a cat and read the sentence
+\enquote{There is a cat on the card.} Depending on the task participants
+were assigned to, they had to choose between two (binary task), three
+(ternary task), four (quaternary task), or five (quinary task) response
+options. The study ended after 24 trials. You can access and view the
+study using the paper's
+\href{https://github.com/thegricean/si-paradigms/}{online repository}.
+
+\subsubsection{Design}\label{design}
 
@@
 card and the type of guess. There were two types of cards. Cards with
-only one animal on them and cards with two animals. Animals were chosen
-from the following set: cat, dog, and elephant There were three types of
-guesses: simple (e.g. \emph{There is a cat}), conjunctive (e.g.
+only one animal on them and cards with two animals. There were three
+types of guesses: simple (e.g. \emph{There is a cat}), conjunctive (e.g.
 \emph{There is a cat and a dog}), and disjunctive (e.g. \emph{There is a
@@
 guess and the card results in 12 different possible trial types. We
-chose 8 trial types (Figure \ref{fig:trials}), balancing the number of
-one-animal vs.~two-animal cards, simple vs.~connective guesses, and
-expected true vs.~false trials. Three trials were randomly selected from
-each of the 8 trial-types, for a total of 24 trials. The order of these
-24 trials was randomized as well.
+chose 8 trial types, balancing the number of one-animal vs.~two-animal
+cards, simple vs.~connective guesses, and expected true vs.~false
+trials. Three trials were randomly selected from each of the 8
+trial-types, for a total of 24 trials. The order of these 24 trials was
+randomized as well.
 
@@
 response options in the forced choice task. Participants were randomly
-assigned to one of four different conditions. The conditions differed
-with respect to the number of response options: binary (wrong
+assigned to one of four different conditions or tasks. The tasks
+differed with respect to the number of response options: binary (wrong
 vs.~right), ternary (wrong, neither, right), quaternary (wrong, kinda
@@
 \enquote{implicature rate}.
-
-\begin{figure}
-\centering
-\includegraphics{writeup_files/figure-latex/trials-1.pdf}
-\caption{\label{fig:trials}Trial types represented by example cards and
-guesses.}
-\end{figure}
 
@@
 
-Here we present the proportion that participants chose the response
-options in each of the 8 trial types of the binary, ternary, quaternary,
-and quinary tasks. Figure \ref{fig:binaryPlot} shows the proportion of
-\enquote{right} and \enquote{wrong} responses in the binary task.
-Starting from the leftmost column, participants considered a guess
-\enquote{wrong} if the guessed animal was not on the card. Moving to the
-second column, participants considered a guess \enquote{right} if the
-animal on the card was mentioned. However, if only one of the two
-animals on the card was mentioned (exhaustive trials), 14\% of the times
-participants considered the guess \enquote{wrong}. Moving to the third
-column, if a conjunction of animals was guessed while only one animal
-was on the card, participants considered the guess to be
-\enquote{wrong}. If a conjunction of animals was guessed and both
-animals were present on the card, all participants considered the guess
-to be \enquote{right} as expected. Moving to the forth column, if a
-disjunction of animals was guessed and only one of the animals was on
-the card, participants considered the guess to be \enquote{right} almost
-all the time. However, if both animals were present (scalar trials),
-38\% of the times participants considered the guess to be
-\enquote{wrong}.
+The experiment had 50 participants in the binary task, 53 in the ternary
+task, 43 in the quaternary task and 54 in the quinary task. In this
+section, we present the proportion that participants chose different
+response options in each of the 8 trial types of these four tasks.
+
+Figure \ref{fig:binaryPlot} shows the proportion of \enquote{right} and
+\enquote{wrong} responses in the binary task. Starting from the leftmost
+column, participants considered a guess \enquote{wrong} if the guessed
+animal was not on the card. Moving to the second column, participants
+considered a guess \enquote{right} if the animal on the card was
+mentioned. However, if only one of the two animals on the card was
+mentioned (exhaustive trials), 14\% of the times participants considered
+the guess \enquote{wrong}. Moving to the third column, if a conjunction
+of animals was guessed while only one animal was on the card,
+participants considered the guess to be \enquote{wrong}. If a
+conjunction of animals was guessed and both animals were present on the
+card, all participants considered the guess to be \enquote{right} as
+expected. Moving to the forth column, if a disjunction of animals was
+guessed and only one of the animals was on the card, participants
+considered the guess to be \enquote{right} almost all the time. However,
+if both animals were present (scalar trials), 38\% of the times
+participants considered the guess to be \enquote{wrong}.
 
@@
 Comparing the response patterns in binary to quinary tasks (Figures
-\ref{fig:binaryPlot} to \ref{fig:quinaryPlot}), we can observe that in
+\ref{fig:binaryPlot}-\ref{fig:quinaryPlot}), we observe that in
 implicature trials, participants are less likely to choose the endpoints
 of the scale (i.e. \enquote{wrong} and \enquote{right}) as they are
-given more intermediate options. This raises the possibilty that the
-strict \enquote{wrong/right} responses in the tasks with fewer options
-(binary and ternary) were not accurately reflecting participant
-judgments of implicature trials and pushed their judgments to the
-extreme ends. More generally, the data suggest that participant
-judgments in contexts that give rise to implicatures fall within the
-intermrediate level of the response scale and forced choice tasks with
-few options (especially binary tasks) may risk depicting judgments more
-extreme than they actually are.
+given more intermediate options.
+
+semantic violations vs.~pragmatic violations
 
@@
 ternary while the rates may be lower in the quaternary and quinary
-tasks. In what follows, we test the effect of linking assumption and
-response options on exhaustive and scalar implicature rates more
-formally.
+tasks. In what follows, we formally test the effect of linking
+assumption and response options on exhaustive and scalar implicature
+rates.
 
@@
 
-For our formal analysis, we use a binomial mixed effects model with the
-fixed effect of response type (binary, ternary, quaternary, quinary),
-linking assumption (strong vs.~weak), and trial type (exhaustive
-vs.~scalar), as wellas the random intercept for participants as well as
-random intercept and slope for items (the card they saw).
-
-All the analytical decisions described here were pre-registered and you
-can access them through the following link:
-\url{https://aspredicted.org/tq3sz.pdf}
-
-\begin{itemize}
-\tightlist
-\item
-  Was logical training a significant predictor of \enquote{implicature
-  rate}?
-\end{itemize}
-
-\section{\# Discussion}\label{discussion}
+\begin{table}
+
+\caption{\label{tab:implicatureRate}\label{tab:modeltable}Model Parameter Estimates and Their Credible Intervals}
+\centering
+\begin{tabular}[t]{lrrr}
+\toprule
+Predictors & Estimate & 2.5\% & 97.5\%\\
+\midrule
+Intercept & -8.60 & -13.98 & -4.53\\
+Link = Weak & -0.15 & -4.86 & 4.77\\
+Task = Quaternary & -1.83 & -8.08 & 4.20\\
+Task = Quinary & -4.05 & -10.90 & 2.38\\
+Task = Ternary & -1.45 & -7.31 & 4.56\\
+\addlinespace
+Implicature = Scalar & 6.09 & 1.00 & 12.29\\
+Link = Weak : Task = Quaternary & 14.03 & 7.24 & 21.88\\
+Link = Weak : Task = Quinary & 17.28 & 10.64 & 25.80\\
+Link = Weak : Task = Ternary & 3.81 & -1.49 & 9.22\\
+Link = Weak : Implicature = Scalar & 0.90 & -4.01 & 6.43\\
+\addlinespace
+Task = Quaternary : Implicature = Scalar & -5.67 & -13.66 & 1.54\\
+Task = Quinary : Implicature = Scalar & -2.31 & -9.30 & 4.61\\
+Task = Ternary : Implicature = Scalar & -1.31 & -7.70 & 4.65\\
+Link=Weak : Task=Quaternary : Implicature=Scalar & -3.29 & -12.07 & 4.55\\
+Link=Weak : Task=Quinary : Implicature=Scalar & -7.74 & -16.59 & -0.16\\
+Link=Weak : Task=Ternary : Implicature=Scalar & -1.44 & -7.00 & 4.22\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+For our formal analysis, we used a bayesian binomial mixed effects model
+using the R packge \enquote{brms} (Bürkner \& others, 2016). The model
+had the fixed effects of response type (binary, ternary, quaternary,
+quinary), linking assumption (strong vs.~weak), and trial type
+(exhaustive vs.~scalar), as well as their two way and three way
+interactions. We also included random intercepts and slopes for items
+(cards) and participants. Following Barr, Levy, Scheepers, and Tily
+(2013), we used the maximal random effects structure by including random
+slopes for all our fixed effects and their interactions. Since the
+number of response options was a between participant variable we did not
+include random slopes of response options for participants. Four chains
+converged after 2000 iterations each (warmup = 1000). Table
+\ref{tab:modeltable} summarizes the mean parameter estimates and their
+95\% credible intervals. \(\hat{R}=1\) for all estimated parameters. All
+the analytical decisions described here were pre-registered\footnote{You
+  can access our pre-registration at
+  \url{https://aspredicted.org/tq3sz.pdf}}.
+
+The model provided evidence for two effects in the study. First, there
+was a main effect of trials such that scalar trials had slightly higher
+implicature rates than exhaustive trials (Mean Estimate = 6.09, 95\%
+Credible Interval={[}1, 12.29{]}). Second, there was an interaction
+between linking assumption and number of resopnse options such that the
+quaternary task (Mean Estimate = 14.03, 95\% Credible Interval={[}7.24,
+21.88{]}) and the quinary task (Mean Estimate = 17.28, 95\% Credible
+Interval={[}10.64, 25.80{]}) with a weak linking assumption had higher
+implicature rates.
+
+\subsection{Discussion}\label{discussion}
+
+We asked whether the linking assumptions and the number of response
+options available to participants affects the inferred implicature rate
+in an experimental study. The results presented here suggest they do. A
+linking assupmtion that considered the highest point on the scale as
+literal and any lower point as pragmatic (weak link) reported higher
+implicature rates in tasks with 4 or 5 options. A linking assumption
+that considered the lowest point on the scale as pragmatic and any
+higher point as literal (strong link) reported lower implicature rates
+in tasks with 4 or 5 options. The results suggest that the choice of
+linking assumption is a crucial analytical step that can significantly
+impact the conclusions of truth value judgment tasks with more than two
+response options. The lower rate of implicatures with a strong linking
+assumption implies that in such studies, strong linking assumptions may
+underestimate participants' pragmatic competence.
+
+While the binary truth value judgement task avoids the analytic decision
+between strong and weak linking assumptions, our results suggest that
+binary tasks can also underestimate participants' pragmatic competence.
+In binary tasks, participants are often given the lowest and highest
+points on a scale (\enquote{wrong} vs. \enquote{right}) and are asked to
+report pragmatic infelicities using the lowest point (e.g.
+\enquote{wrong}). Our study showed that in trials with true but
+infelicitous descriptions (implicature trials), participants often
+avoided the lowest point on the scale if they were given more
+intermediate options. Even though the option \enquote{wrong} was
+available to participants in all tasks, participants in tasks with
+intermediate options chose it less often. In computing implicature rate,
+this pattern manifested itself as a decrease in implicature rate with
+strong link when more response options were provided, and increase in
+implicature rate with weak link when more response options were
+provided. These conclusions are in line with Katsos and Bishop
+(2011)\enquote{s argument that pragmatic violations are not as severe as
+semantic violations and participants do not penalize them as much.
+Providing participants with only the extreme opposits of the scale
+(e.g.~wrong/right, false/true) when pragmatic violations are considered
+to be of an intermediate nature risks misrepresentation of participants}
+pragmatic competence.
+
+This study did not investigate the effect of option labels on the
+inferred implicature rate. However, the results provided suggestive
+evidence that some options better capture participant intuitions of
+pragmatic infelicities than others. Among the intermediate options,
+\enquote{kinda right} was chosen most often to report pragmatic
+infelicities. The option \enquote{neither} was rarely used in the
+ternary and quinary tasks (where it was used as a midpoint), suggesting
+that participants found pragmatic infelicities as different degrees of
+being \enquote{right} and not \enquote{neither right nor wrong.}
+Therefore, options that capture grades of being \enquote{right} like
+\enquote{kinda right} proved be most suitable for capturing true but
+infelicitous utterances.
+
+This study had three design features that we would like to investigate
+in future work. First, the utterances were by a blindfolded character
+because we wanted to control for violation of ignorance expectations
+with disjunction. A disjunction such as \enquote{A or B} often carries
+an implication or expectation that the speaker is not certain which
+alternative actually holds. In future work, we would like to see how the
+violation of the ignorance expectation would affect the inferred
+implicature rate by having the fictional character describe the cards
+while looking at them. Second, in this study we considered exhaustive
+and scalar implicatures with \emph{or}. We would like to see if similar
+effects hold for the scalar implicatures with \emph{some}. Finally, our
+experiment was designed as a guessing game and the exact goal of the
+game was left implicit. We expect that different goals, for example help
+the character win more points vs.~help the character be more accurate,
+would affect how strict or lenient participants are with their judgments
+and ultimately affect the implicature rate in the task. In future work
+we would like to systematically vary the goal of the game and explore
+its effects on the inferred implicature rate.
+
+\section{General Discussion}\label{general-discussion}
 
@@
 
+\hypertarget{ref-barr2013random}{}
+Barr, D. J., Levy, R., Scheepers, C., \& Tily, H. J. (2013). Random
+effects structure for confirmatory hypothesis testing: Keep it maximal.
+\emph{Journal of Memory and Language}, \emph{68}(3), 255--278.
+
 \hypertarget{ref-Bergen2012}{}
@@
 
+\hypertarget{ref-burkner2016brms}{}
+Bürkner, P.-C., \& others. (2016). Brms: An r package for bayesian
+multilevel models using stan. \emph{Journal of Statistical Software},
+\emph{80}(1), 1--28.
+
 \hypertarget{ref-Chemla2011}{}

### 2018-05-07 writeup.Rmd

@@
 On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
-This assumption has concerning implications for how we must approach analysis of variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of cat or dog when the card had both a cat and a dog on it?
-
-To explain the data on the traditional view, are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated response (i.e.
-“Wrong”) due to some other cognitive reflex which ‘overrode’ the implicature; or some mixture of (b) and (c).
-We might similarly posit that one or both of these factors underlie the variation in the ternary, quatenary, and quinary conditions (e.g.
-why were participants roughly split between “Right” and “Kind of right” when the utterance was cat or dog and the card had a cat and a dog?).
+This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
+
+To explain the data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "Wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
+We might similarly posit that one or both of these factors underlie the variation in the ternary, quaternary, and quinary conditions.
 However, the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
-
-We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis which assumes that participants' behavior can be represented using the model of a soft-optimal pragmatic speaker in the RSA framework.
-This alternative linking hypothesis contrasts with the traditional view in it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
-Recall that in RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution of possible meanings given an utterance which that listener hears.
-The probability with which this listener $L_1$ ascribes a meaning s to an utterance u depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
-$S_1$ in turn is modeled as a continuous probabilistic distribution of possible utterances given an intended state of affairs the speaker intends to communicate.
-This distribution is sensitive to a rationality parameter $\alpha$, the production cost $C$ of potential utterances, and a representation of a literal listener $L_0$ whose interpretation of an utterance is in turn a function of that utterance's truth conditional content $[[u]](s)$ and her prior beliefs about the state of the world $P_w(s)$.
+**XXX Brandon, can you be more specific about what you mean by 'tracing a general qualitative pattern'?**
+
+We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis.
+Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2014; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
+We take inspiration from this approach and treat participants' behavior in our experimental tasks as the result of a soft-optimal pragmatic speaker in the RSA framework.
+This alternative linking hypothesis contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+In RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution over possible meanings (states of the world) given an utterance which that listener observes.
+The probability with which this listener $L_1$ ascribes a meaning $s$ to an utterance $u$ depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
+$S_1$ in turn is modeled as a continuous probabilistic distribution over possible utterances given an intended state of the world the speaker intends to communicate.
+This distribution is sensitive to a rationality parameter $\alpha$, the production cost $C$ of potential utterances, and the informativeness of the utterance, quantified via a representation of a literal listener $L_0$ whose interpretation of an utterance is in turn a function of that utterance's truth conditional content $[[u]](s)$ and her prior beliefs about the state of the world $P_w(s)$.
 

### 2018-05-07 writeup.Rmd
Brandon tasks for draft 1 (general discussion)

@@
 This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
-
-To explain the data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "Wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
+And why did a sizeable minority nonetheless choose "Wrong" in this same condition?
+
+To explain these data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "Wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
 We might similarly posit that one or both of these factors underlie the variation in the ternary, quaternary, and quinary conditions.
-However, the best we can hope for on this approach is an analysis which traces the general qualitative patterns in the data.
-**XXX Brandon, can you be more specific about what you mean by 'tracing a general qualitative pattern'?**
+However, without an understanding of how to quantitatively specify the link between implicature calculation and its behavioral expression, the best we can hope for on this approach is an analysis which predicts general qualitative patterns in the data (e.g.
+a prediction of relatively more "Right" responses than "Wrong" responses in a given trial of our binary truth-value judgment task, or a prediction of a rise in the rate of response of "Right"/"Wrong" between two experimental conditions, given some contextual manipulation).
+**XXX Judith, I was thinking of adding the sentence to end this paragraph: "However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks - much less the effect of the number of response choices on that behavior - is largely underdeveloped scalar implicature literature." But it might be way too strong a claim?
+**
+
+**XXX Brandon, can you be more specific about what you mean by 'tracing a general qualitative pattern'? XXX Judith: I've tried to offer some examples of what I mean by this, see above.**
 
@@
 Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2014; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
-We take inspiration from this approach and treat participants' behavior in our experimental tasks as the result of a soft-optimal pragmatic speaker in the RSA framework.
-This alternative linking hypothesis contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
-In RSA, pragmatically competent listeners are modeled as a continuous probabilistic distribution over possible meanings (states of the world) given an utterance which that listener observes.
+**XXX Judith: re: your Slack comments, in the following few sentences I've provided a summary of the intuition behind RSA (going off of the discussion in Goodman & Stuhlmueller 2013)** Much in the spirit of Gricean approaches to pragmatic competence, the RSA framework takes as its point of departure the idea that individuals are rational, goal-oriented communicative agents, who in turn assume that their interlocutors similarly behave according to general principles of cooperativity in communication.
+Just as in more traditional Gricean pragmatics, pragmatic inference and pragmatically-cooperative language production in the RSA framework are, at their core, the product of counterfactual reasoning about alternative utterances that one might produce (but does not, in the interest of cooperativity).
+However, the RSA framework explicitly and quantitatively models coooperative interlocutors as agents whose language production and comprehension is a function of Bayesian probalistic inference regarding other interlocutors' expected behavior in a discourse context.
+
+Specifically, in the RSA framework we model pragmatically competent listeners as continuous probabilistic distributions over possible meanings (states of the world) given an utterance which that listener observes.
 The probability with which this listener $L_1$ ascribes a meaning $s$ to an utterance $u$ depends upon a prior probability distribution of potential states of the world $P_w$, and upon reasoning about the communicative behavior of a speaker $S_1$.
@@
 
-In this framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
-For example, exclusivity readings of disjunction are represented in RSA as relatively lower conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared to its prior probability.
-Thus, it is not even possible **XXX or at least not without auxiliary assumptions** to talk about 'rate' of implicature calculation in the RSA framework.
+Thus, our alternative linking hypothesis contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+In the RSA framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
+For example, exclusivity readings of disjunction are represented in RSA as relatively lower posterior conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared the prior probability of that meaning.
+Thus, absent auxiliary assumptions about what exactly would constitute 'implicature', it is not even possible to talk about rate of implicature calculation in the RSA framework.
 The upshot, as we show below, is that this view of pragmatic competence does allow us to talk explicitly and quantitatively about rates of observed behavior in sentence verification tasks.
 
-First, following @Degen2014, we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
+We take inspiration from the RSA approach and treat participants' behavior in our experimental tasks as the result of a soft-optimal pragmatic speaker in the RSA framework.
+That is, following @Degen2014, we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
 In their paper, Degen & Goodman argue that sentence verification tasks are relatively more sensitive to contextual manipulations (such as manipulation of the Question Under Discussion) than are sentence interpretation tasks, and that this follows if sentence interpretation tasks - but not sentence verification tasks - require an additional layer of counterfactual reasoning about the intentions of a cooperative speaker.
@@
 
-In the experiment conditions where there are more than two choices, we model the range of possible behavioral responses for $R$ with the introduction of intermediate probability thresholds.
-For example, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | s) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
+**XXX The following paragraph is mostly new:** Because $\theta$ is a free parameter in our model, we have a straightforward understanding of between-subject response variation on a given trial of our experiment according to this linking hypothesis.
+That is, we can attribute this variation to individual differences vis a vis the value of the probability threshold against which utterances are evaluated in a given world state.
+Moreover, the model of a responder in the binary condition is extended intuitively to the condition where participants had three response options.
+In this case, we allow for two probability thresholds: $\theta_1$, the minimum standard for an utterance in a given world state to count as "Right", and $\theta_2$, the minimum standard for "Neither".
+Thus, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | s) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
 To fully generalize the model to our five experimental conditions, we say that $R$ takes as its input an utterance $u$, a world state $s$, and a number of threshold variables dependent on a variable $c$, corresponding to the experimental condition in which the participant finds herself (e.g.
@@
 
-= “Right” iff $S_1$(u | w) $>$ $\theta_1$
-
-= “Neither” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
+= “Right” iff $S_1$(u | s) $>$ $\theta_1$
+
+= “Neither” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
 
@@
 
-= “Right” iff $S_1$(u | w) $>$ $\theta_1$
-
-= “Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
-
-= “Kinda Wrong” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$
+= “Right” iff $S_1$(u | s) $>$ $\theta_1$
+
+= “Kinda Right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “Kinda Wrong” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
 
@@
 
-= “Right” iff $S_1$(u | w) $>$ $\theta_1$
-
-=“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | w) $>$ $\theta_2$
-
-= “Neither” iff $\theta_2$ $>$ $S_1$(u | w) $>$ $\theta_3$
-
-= “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | w) $>$ $\theta_4$
+= “Right” iff $S_1$(u | s) $>$ $\theta_1$
+
+=“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “Neither” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
+
+= “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | s) $>$ $\theta_4$
 
@@
 
-Bayesian statistical methods provide us a means for estimating the values of these probability thresholds in our RSA model.
-The basis for the model is a set of possible states of the world, given a universe of three animals - X, Y, and Z - that each may be on some card.
-We next define a set of possible sentences a speaker might utter, assuming the speaker intends to communicate which animals are on the card.
-We assume a uniform prior probability of different states of the world and a uniform cost function on utterances.
-We define a literal listener $L_0$, a pragmatic speaker $S_1$, and a responder $R$ according to our definitions above.
-Lastly, and assuming a uniform prior distribution over possible values of probability thresholds, we use Bayesian inference to recover a posterior distribution of these thresholds in each experimental condition, given the actual observed rate of response in each condition of the experiment.
-The results of this parameter estimation analysis are shown in the figures below, where the X axis of each figure corresponds to a threshold value between 0 and 1 and the Y axis corresponds to the posterior probability density of possible values of the threshold.
-
-```{r echo=FALSE, message=FALSE}
-bda <- read.csv("models/webppl_models/bda.csv")
-
-binary_graph <- ggplot(filter(bda, Parameter == "binary_theta"), aes(x=value))+
-  # facet_wrap(~Parameter, scales = "free") +
-  theme_few() +
-  geom_density() +
-  scale_fill_grey(guide=FALSE) +
-  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
-  ggtitle("Threshold distribution, binary condition:")
-
-ternary_graph <- ggplot(filter(bda, Parameter == c("ternary_theta1", "ternary_theta2")), aes(x=value))+
-  facet_wrap(~Parameter, scales = "free") +
-  theme_few() +
-  geom_density() +
-  scale_fill_grey(guide=FALSE) +
-  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
-  ggtitle("Threshold distributions, ternary condition:")
-
-quatenary_graph <- ggplot(filter(bda, Parameter == c("quatenary_theta1", "quatenary_theta2", "quatenary_theta3")), aes(x=value))+
-  facet_wrap(~Parameter, scales = "free") +
-  theme_few() +
-  geom_density() +
-  scale_fill_grey(guide=FALSE) +
-  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
-  ggtitle("Threshold distributions, quatenary condition:")
-
-quinary_graph <- ggplot(filter(bda, Parameter == c("quinary_theta1", "quinary_theta2", "quinary_theta3", "quinary_theta4")), aes(x=value))+
-  facet_wrap(~Parameter, scales = "free") +
-  theme_few() +
-  geom_density() +
-  scale_fill_grey(guide=FALSE) +
-  theme(axis.text.x=element_text(angle=20,hjust=1,vjust=1)) +
-  ggtitle("Threshold distributions, quinary condition:")
-binary_graph
-ternary_graph
-quatenary_graph
-quinary_graph
-```
-
 The above analysis is a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
+
+**XXX The following is entirely new:** However, this way of understanding behaivor in truth value jugdment tasks also raises new analytic and empirical questions which we must leave to future work.
+For instance, given the experimental results reported here, what is the range of plausible values for, e.g., the single probability threshold $\theta$, which separates "Right" from "Wrong" utterances in the binary condition?
+Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e.
+the actual rate of response of "Right" in each trial of the binary condition of the experiment.
+We may also ask, for example, whether the speaker probability threshold for an utterance being "Right" is relatively constant across conditions or changes systematically with the introduction of more response options.
+Again, Bayesian data analysis allows us to explore this question by investigating the extent to which the inferred posterior distribution of, e.g., possible values of the threshold for "Right" in the binary condition of the experiment differs from the inferred posterior distribution of possible values of the threshold for "Right" in the ternary, quatenary, and quinary conditions.
+
+Lastly, the linking analysis proposed here is just one in the space of possible analyses when traditional assumptions about scalar implicature are relaxed.
+For example, one might reject this threshold-based analysis in favor of one whereby responses are the outcomes of sampling on the (pragmatic speaker or pragmatic listener) probability distributions provided by an RSA model.
+We again must leave this investigation to future work, but for the time being we emphasize that such quantitative, data-driven and systematic model criticism/comparison is made available to researchers in experimental pragmatics by revising core assumptions about the nature of scalar implicature.
+Though we no longer have a crisp notion of scalar implicature as something that is or is not 'calculated' in interpretation, we have new flexibility to explicitly discuss categorical behavior in experimental settings.
 

### 2018-05-07 writeup.Rmd
intro and ref updates

@@
 ---
-title             : "The effect of linking assumptions and number of response options on inferred scalar implicature rate"
+title             : "Linking assumptions and number of response options modulate inferred scalar implicature rate"
 shorttitle        : "Linking assumptions and implicature rate"
@@
 The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*.
-Scalar implicatures arise in virtue of a speaker producing the weaker of two ordered scalemates [@grice1975; hornXXX; @hirschberg1985; @Geurts2010].
-Examples are provided in (1) and (2).
+Scalar implicatures arise in virtue of a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
+Examples are provided in (1-2).
 
@@
 
-A listener, upon observing the utterances in (1a) and (2a), typically infers that the speaker intended to convey the meanings in (1b) and (2b), respectively.
-Since @grice1975, the agreed-upon abstract rationalization the listener could give for their inference goes something like this: the speaker could have made a more informative statement by producing the stronger alternative (e.g., *All of her pets are cats.*).
+A listener, upon observing the utterances in (1-2a) typically infers that the speaker intended to convey the meanings in (1-2b), respectively.
+Since @grice1975, the agreed-upon abstract rationalization the listener could give for their inference goes something like this: the speaker could have made a more informative statement by producing the stronger alternative (e.g., *All of her pets are cats.* in (1)).
 If the stronger alternative is true, they should have produced it to comply with the Cooperative Principle.
@@
 Hence, it must not be true.
+The derivation procedure for ad hoc exhaustive inferences such as in (3) is assumed to be calculable in the same way as for scalar implicatures, though the scale is assumed to be contextually driven.
 
@@
 2.
-Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@Bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Politzer-Ahles2013;Tomlinson2013]?
+Are scalar inferences default inferences, in the sense that they are computed automatically in online processing and only cancelled by context in a second effortful step if required by context) [@Bott2004;@Breheny2006;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Politzer-Ahles2013;@Tomlinson2013]?
 
 3.
-What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@Zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @Degen2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffe2017;@DeNeys2007;@Bonnefon2009;Chemla2011;Potts2015]?
+What are the (linguistic and extra-linguistic) factors that affect whether a scalar implicature is derived [@Zondervan2010;@DegenTanenhaus2015; @DegenTanenhaus2016; @Degen2015; @Degen2014; @Bergen2012; @Breheny2006; @Breheny2013;@DeMarneffe2017;@DeNeys2007;@Bonnefon2009;@Chemla2011;@Potts2015]?
 
@@
 
-5. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; Frank; @Musolino2004;@Katsos2011]?
-
-In addressing all of these questions, it has been crucial to obtain estimates of **implicature rates**.
+5. At what age do children acquire the ability to compute implicatures [@Noveck2001; @Papafragou2004; @Barner2011; @Stiller2015; @Horowitz2017; @Musolino2004;@Katsos2011]?
+
+In addressing all of these questions, it has been crucial to obtain estimates of *implicature rates*.
 For 1., implicature rates from experimental tasks can be taken to inform whether scalar implicatures should be considered default inferences.
@@
 
-A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;Degen2014].
+A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
 In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
@@
 
-Given the centrality of the theoretical notion of 'implicature rate' to much of experimental pragmatics, there is to date a surprising lack of discussion of the basic assumption that it is adequately captured by the  proportion of FALSE responses in truth-value judgment tasks (but see @BenzGotzner; @Geurts2009; @Degen2014; @Katsos2011).
+Given the centrality of the theoretical notion of 'implicature rate' to much of experimental pragmatics, there is to date a surprising lack of discussion of the basic assumption that it is adequately captured by the  proportion of FALSE responses in truth-value judgment tasks (but see @BenzGotzner2014; @Geurts2009; @Degen2014; @Katsos2011).
 Indeed, the scalar implicature acquisition literature was shaken up when @Katsos2011 showed that simply by introducing an additional response option, children started looking much more pragmatic than had been previously observed in a binary judgment paradigm.
-@Katsos allowed children to distribute 1, 2, or 3 strawberries to a puppet depending on 'how good the puppet said it'.
+@Katsos2011 allowed children to distribute 1, 2, or 3 strawberries to a puppet depending on 'how good the puppet said it'.
 The result was that children gave on average fewer strawberries to the puppet when he produced underinformative utterances compared to when he produced literally true and pragmatically felicitous utterances, suggesting that children do, in fact, display pragmatic ability even at ages when they had previously appeared not to.
 
-But this raises an important question: in truth-value judgment task, how do we know whether an interpretation is literal or the result of an implicature computation?
+But this raises an important question: in truth-value judgment tasks, how does the researcher know whether an interpretation is literal or the result of an implicature computation?
 The binary choice task typically used is appealing in part because it allows for a direct mapping from response options -- TRUE and FALSE -- to interpretations -- literal and pragmatic.
@@
 @Katsos2011 grouped the intermediate option with the negative endpoint of the scale for the purpose of categorizing judgments as literal vs.
-pragmatic.
-But it seems just as plausible that they could have grouped it with the positive endpoint of the scale and taken the hard line that only truly FALSE responses constitute a full-fledged implicature.
-The point here is that there has been remarkably little consideration of **linking functions** between behavioral measures and theoretical constructs in experimental pragmatics, a problem in many subfields of psycholinguistics @TanenhausXXX.
+pragmatic, i.e., they interpreted the intermediate option as pragmatic.
+But it seems just as plausible that they could have grouped it with the positive endpoint of the scale and taken the hard line that only truly FALSE responses constitute evidence of a full-fledged implicature.
+The point here is that there has been remarkably little consideration of *linking functions* between behavioral measures and theoretical constructs in experimental pragmatics, a problem in many subfields of psycholinguistics [@Tanenhaus2004].
 We argue that it is time to engage more seriously with these issues.
@@
 We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth-value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates?
-Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of **interpretation**.
+Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of *interpretation*.
 And second, that listeners either do or do not compute an implicature on any given occasion.
 In the General Discussion we will discuss both of these issues.
-First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' **production** probabilities.
+First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' *production* probabilities.
 This will suggest a completely different class of linking functions.
-And second, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics.
+And second, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
 This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.
 
-Consider a setup in which a listener is presented a card with a depiction of either one or two animals (see the figure below for an example).
-As in a standard truth-value judgment task, the listener then observes an underinformative utterance about this card (e.g., 'There is a cat or a dog on the card') and is asked to provide a judgment on a scale from 2 to 5 response options, with endpoints 'wrong' and 'right'.
-In the binary case, this reproduces the standard truth-value judgment task.
-**XXX say briefly sth about wrong/right vs true/false and agree/disagree**.
-The figure below exemplifies (some of) the researcher's options for grouping responses.
+Consider a setup in which a listener is presented a card with a depiction of either one or two animals (see Figure 1 for an example).
+As in a standard truth-value judgment task, the listener then observes an underinformative utterance about this card (e.g., 'There is a cat or a dog on the card') and is asked to provide a judgment on a scale with 2, 3, 4, or 5 response options, with endpoints 'wrong' and 'right'.[^1] In the binary case, this reproduces the standard truth-value judgment task.
+Figure 1 exemplifies (some of) the researcher's options for grouping responses.
 Under what we will call the 'Strong link' assumption, only the negative endpoint of the scale is interpreted as evidence for a scalar implicature having been computed.
@@
 Note that for the binary case, the Weak and Strong link return the same categorization scheme, but for any number of response options greater than 2, the Weak and Strong link can in principle lead to differences in inferences about implicature rate.
+
+[^1]: An open question concerns the extent to which the labeling of points on the scale affects judgments (e.g., 'wrong'--'right' vs.
+'false'--'true' vs.
+'disagree'--'agree').
+While some studies have used 'false'--'true', others have argued that judging truth may lead to meta-linguistic reasoning in participants that could distort judgments.
 
@@
 In the experiment reported in the following section, we presented participants with exactly this setup.
+We manipulated the number of response options between participants and analyzed the results under different linking assumptions.
 
@@
 
-In this study, we presented participants with an online card game.
-Different groups of participants were presented with different numbers of response options for the task.
-In critical trials, participants were presented with descriptions for the cards that typically result in exhaustive or scalar implicatures.
-We categorized their responses in such trials according to the "weak" and the "strong" link, and tested whether the number of response options and the linking assumptions lead to different conclusions about the rate of computed implicatures in the experimental task.
+Participants played an online card game in which they were asked to judge descriptions of the contents of cards.
+Different groups of participants were presented with different numbers of response options.
+On critical trials, participants were presented with descriptions for the cards that typically result in exhaustive or scalar implicatures.
+We categorized their responses on such trials according to the "weak" and the "strong" link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.
 
@@
 $\hat{R}=1$ for all estimated parameters.
-All the analytical decisions described here were pre-registered[^1].
+All the analytical decisions described here were pre-registered[^2].
 
@@
 
-[^1]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
+[^2]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
 
@@
 We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis.
-Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2014; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
+Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2015; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
 **XXX Judith: re: your Slack comments, in the following few sentences I've provided a summary of the intuition behind RSA (going off of the discussion in Goodman & Stuhlmueller 2013)** Much in the spirit of Gricean approaches to pragmatic competence, the RSA framework takes as its point of departure the idea that individuals are rational, goal-oriented communicative agents, who in turn assume that their interlocutors similarly behave according to general principles of cooperativity in communication.

### 2018-05-08 writeup.Rmd
updated methods section

@@
 
-Consider a setup in which a listener is presented a card with a depiction of either one or two animals (see Figure 1 for an example).
+Consider a setup in which a listener is presented a card with a depiction of either one or two animals (see Figure \@ref(fig:linkvisualization) for an example).
 As in a standard truth-value judgment task, the listener then observes an underinformative utterance about this card (e.g., 'There is a cat or a dog on the card') and is asked to provide a judgment on a scale with 2, 3, 4, or 5 response options, with endpoints 'wrong' and 'right'.[^1] In the binary case, this reproduces the standard truth-value judgment task.
-Figure 1 exemplifies (some of) the researcher's options for grouping responses.
+Figure \@ref(fig:linkvisualization) exemplifies (some of) the researcher's options for grouping responses.
 Under what we will call the 'Strong link' assumption, only the negative endpoint of the scale is interpreted as evidence for a scalar implicature having been computed.
@@
 Different groups of participants were presented with different numbers of response options.
-On critical trials, participants were presented with descriptions for the cards that typically result in exhaustive or scalar implicatures.
-We categorized their responses on such trials according to the "weak" and the "strong" link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.
+On critical trials, participants were presented with descriptions for the cards that typically result in exhaustivity implicatures ("There is a cat on the card" when there was a cat and a dog) or scalar implicatures ("There is a cat or a dog on the card" when there was a cat and a dog).
+We categorized their responses on such trials according to the weak and the strong link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.
 
@@
 
-200 participants were recruited using Amazon Mechanical Turk.
+200 participants were recruited via Amazon Mechanical Turk.
 They optionally provided demographic information at the end of the study.
-Mean age of the participnats was `r round(mean_age)`.
+Participants' mean age was `r round(mean_age)`.
 We also asked participants if they had any prior training in logic.
-`r logicTraining[[2]]` participants reported that they had while `r logicTraining[[1]]` had no prior training in logic.
-No participant was excluded from the final analysis.
-
-### Materials and Procedure
-
-The study was administered online through Amazon Mechanical Turk.
-Participants were first introduced to the set of cards we used in the study (Figure \@ref(fig:stimuli)).
-Each card had pictures of one or two animals.
-Animals were chosen from the following set: cat, dog, and elephant.
+`r logicTraining[[2]]` participants reported that they did, while `r logicTraining[[1]]` had no prior training in logic.
+**JD: Do we do any analysis of logic training???** All participants' data was included in the final analysis.
+
+### Materials and procedure
+
+The study was administered online through Amazon Mechanical Turk.[^2] Participants were first introduced to the set of cards we used in the study (Figure \@ref(fig:stimuli)).
+Each card depicted one or two animals, where an animal could be either a cat, a dog, or an elephant.
 Then participants were introduced to a blindfolded fictional character called Bob.
-Bob was blindfolded to control for violations of ignorance expectations with disjunction.
-Participants were told that Bob is going to guess what animals are on the card.
-We asked participants to let us know whether Bob's guess is wrong or right.
-In each trial, participants saw a card as well as a sentence representing Bob's guess.
-For example, they saw a card with a cat and read the sentence "There is a cat on the card." Depending on the task participants were assigned to, they had to choose between two (binary task), three (ternary task), four (quaternary task), or five (quinary task) response options.
+Bob was blindfolded to avoid violations of ignorance expectations associated with the use of disjunction [@???] **JD: Masoud, can you insert citation pls?
+Geurts, Sauerland?**.
+Participants were told that Bob would guess the contents of the cards and their task was to indicate whether Bob's guess was wrong or right.
+On each trial, participants saw a card and a sentence representing Bob's guess.
+For example, they saw a card with a cat and read the sentence "There is a cat on the card." They then provided an assessment of Bob's guess.
 The study ended after 24 trials.
-You can access and view the study using the paper's [online repository](https://github.com/thegricean/si-paradigms/).
-
-### Design
+
+[^2]: The experiment can be viewed [here](https://github.com/thegricean/si-paradigms/). **JD: Masoud, please turn this into a working link to the actual experiment**
 
@@
 
-The study had two main manipulaitons within participants: the type of card and the type of guess.
-There were two types of cards.
-Cards with only one animal on them and cards with two animals.
+Two factors were manipulated within participants: card type and  guess type.
+There were two types of cards, cards with only one animal on them and cards with two animals.
 There were three types of guesses: simple (e.g.
@@
 *There is a cat or a dog*).
-In each trial, the animal labels used in the guess and the animal images on the card may have no overlap (e.g.
-Image: cat, Guess: *There is an elephant*), a partial overlap (e.g.
-Image: cat, Guess: *There is a cat or a dog*), or a total overlap (e.g.
-Image: cat and dog, Guess: *There is a cat or a dog*).
-Crossing the number of animals on the card, the type of guess, and the overlap between the guess and the card results in 12 different possible trial types.
-We chose 8 trial types, balancing the number of one-animal vs.
-two-animal cards, simple vs.
-connective guesses, and expected true vs.
-false trials.
-Three trials were randomly selected from each of the 8 trial-types, for a total of 24 trials.
-The order of these 24 trials was randomized as well.
-
-Participants could derive implicatures in two trial types.
-First, the trial type in which two animals were present on the card (e.g.
-cat and dog) but Bob guessed only one of them (e.g.
-"there is a cat").
-Such trials can have a literal interpretation (cat and possibly more) or an exhaustive interpretation (only cat).
-We refer to them as "exhaustive".
-The second trial type with implicatures was the one in which two animals were on the card (e.g.
-cat and dog) and Bob used a disjunciton (e.g.
-cat or dog).
-These trials can have a literal (inclusive) interpretation (e.g.
-cat or dog or both), or an exclusive interpretation (e.g.
-cat or dog, not both).
+Crossing card type and guess type yielded trials of varying theoretical interest (see Figure \@ref(fig:trials)): critical underinformative trials that were likely to elicit pragmatic  inferences  (either scalar or exhaustive) and  control trials that were either unambiguously true  or false.
+Each trial type occurred three times with randomly sampled animals and utterances that satisfied the constraint of the trial type.
+Trial order was randomized.
+
+```{r trials, fig.asp=0.35, fig.cap = "Trial types (critical and control). Headers indicate utterance types. Rows indicate card types. Critical trials are marked in bold."}
+ trials_img <- jpeg::readJPEG("writeup_files/figures/trialtypes.jpeg")
+ grid::grid.raster(trials_img)
+ ```
+
+On critical trials, participants could derive implicatures in two ways.
+First, on trials on which two animals were present on the card (e.g., cat and dog) but Bob guessed only one of them (e.g.
+"There is a cat on the card"), the utterance could have a literal interpretation ("There is a cat and possibly another animal on the card") or an exhaustive interpretation ("There is only a cat on the card").
+We refer to these trials as "exhaustive".
+Second, on trials on which two animals were on the card (e.g., a cat and a dog) and Bob used a disjunciton (e.g., "There is a cat or a dog on the card"), the utterance could have the literal, inclusive, interpretation, or a pragmatic, exclusive interpretation.
 We refer to these trials as "scalar".
-The following four trial types were used as experimental control: two trial types where there was no overlap between the guess (e.g.
-elephant) and the animal(s) on the card (e.g.
-cat, cat and dog); and two trial types where the animal(s) on the card were correctly guessed.
-For example, if there was only a cat on the card, Bob said "there is a cat" and if there was a cat and a dog, Bob said "there is a cat and a dog".
-Since the fictional character was blindfolded and did not see the outcome of the game, the ignorance inference commonly associated with disjunction was already common ground in the experimental setting.
-If the character was seeing the cards or knew what was on them, a disjunction would have violated the expectation that the speaker does not know which alternative actually holds.
-Our study controls for the possibile effect of ignorance violations on exclusivity and exhaustive inferences.
-
-The study also had a between participant manipulation of the number of response options in the forced choice task.
-Participants were randomly assigned to one of four different conditions or tasks.
-The tasks differed with respect to the number of response options: binary (wrong vs.
-right), ternary (wrong, neither, right), quaternary (wrong, kinda wrong, kinda right, right), and quinary (wrong, kinda wrong, neither, kinda right, right).
-We wanted to see if the number of response options in the forced choice task would affect our estimate of the task's "implicature rate".
+
+In order to assess the effect of the number of response options on implicature rate, we manipulated number of response options in the forced choice task between participants.
+We refer to the choice conditions as 'binary' (options: *wrong*, *right*), 'ternary' (options: *wrong*, *neither*, *right*), 'quaternary' (options: *wrong*, *kinda wrong*, *kinda right*, *right*), and 'quinary' (*wrong*, *kinda wrong*, *neither*, *kinda right*, *right*).
+Thus, the endpoint labels always remained the same.
+If there was an uneven number of response options, the central option was *neither*.
 
@@
 $\hat{R}=1$ for all estimated parameters.
-All the analytical decisions described here were pre-registered[^2].
+All the analytical decisions described here were pre-registered[^3].
 
@@
 
-[^2]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
+[^3]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
 
@@
 
+**JD: moved from Methods section: Since the fictional character was blindfolded and did not see the outcome of the game, the ignorance inference commonly associated with disjunction was already common ground in the experimental setting.
+If the character was seeing the cards or knew what was on them, a disjunction would have violated the expectation that the speaker does not know which alternative actually holds.
+Our study controls for the possibile effect of ignorance violations on exclusivity and exhaustive inferences.
+**
+
 # General Discussion
@@
 Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e.
-the actual rate of response of "Right" in each trial of the binary condition of the experiment.
+the actual rate of response of "Right" On each trial of the binary condition of the experiment.
 We may also ask, for example, whether the speaker probability threshold for an utterance being "Right" is relatively constant across conditions or changes systematically with the introduction of more response options.

### 2018-05-08 writeup.Rmd
rewrote qualitative results section

@@
 If there was an uneven number of response options, the central option was *neither*.
+Participants were randomly assigned to one of the four task conditions.
 
@@
 
-```{r binaryPlot, fig.height=3.5, fig.cap = "Proportion responses for the two-alternative (binary) forced choice judgments in the guessing game."}
+The collected dataset contains `r participants_info$count[1]` participants in the binary task, `r participants_info$count[4]` in the ternary task, `r participants_info$count[2]` in the quaternary task, and `r participants_info$count[3]` in the quinary task.
+Figures \@ref(fig:binaryPlot) to \@ref(fig:quinaryPlot)  show the proportions of response choices in each of the 8 trial types on each of the four response tasks, respectively.
+We report the relevant patterns of results qualitatively before turning to the quantitative analysis of interest.
+
+### Qualitative analysis
+
+```{r binaryPlot, fig.height=3.5, fig.cap = "Proportion of responses for the binary forced choice judgments. Error bars indicate 95% bootstrapped confidence intervals."}
 binary_plot<-
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response Options in the Binary Task", y="Proportions")+
+  labs(x="Response options (binary task)", y="Proportion of response")+
   theme_few() +
@@
 
-The experiment had `r participants_info$count[1]` participants in the binary task, `r participants_info$count[4]` in the ternary task, `r participants_info$count[2]` in the quaternary task and `r participants_info$count[3]` in the quinary task.
-In this section, we present the proportion that participants chose different response options in each of the 8 trial types of these four tasks.
-
-Figure \@ref(fig:binaryPlot) shows the proportion of "right" and "wrong" responses in the binary task.
-Starting from the leftmost column, participants considered a guess "wrong" if the guessed animal was not on the card.
-Moving to the second column, participants considered the guess "right" when the only animal on the card was mentioned.
-However, when only one of the two animals on the card was mentioned (exhaustive trials), `r round(binaryExh_wrong$proportion*100)`% of the times participants considered the guess "wrong".
-Moving to the third column, if a conjunction of animals was guessed while only one animal was on the card, participants considered the guess to be "wrong".
-If a conjunction of animals was guessed and both animals were present on the card, all participants considered the guess to be "right" as expected.
-Finally, if a disjunction of animals was guessed and only one of the animals was on the card, participants considered the guess to be "right" almost all the time.
-However, if both animals were present (scalar trials), `r round(binaryScalar_wrong$proportion*100)`% of the times participants considered the guess to be "wrong".
+In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)).
+However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time.
+That is, both under the weak and the strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.
 
@@
 
-```{r ternaryPlot, fig.height=3.5, fig.cap = "Proportion responses for the three-alternative (ternary) forced choice judgments in the guessing game."}
+```{r ternaryPlot, fig.height=3.5, fig.cap = "Proportion of responses for the ternary forced choice judgments. Error bars indicate 95% bootstrapped confidence intervals."}
 ternary_plot<-
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response Options in the Ternary Task", y="Proportions")+
+  labs(x="Response options (ternary task)", y="Proportion of response")+
   theme_few() +
@@
 
-Figure \@ref(fig:ternaryPlot) shows the proportion of "right", "neither", and "wrong" responses in the ternary task.
-Similar to the binary task, participants considered a guess wrong when the mentioned animal was not on the card, and "right" when the mentioned animal was the only animal on the card.
-However, in exhaustive trials when the fictional character only guessed one of the two animals on the card, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
-If a conjunction of animals was guessed and only one animal was present on the card, participants considered the guess "wrong".
-As expected, when a conjunction was used and both animals were present, participants considered the guess "right".
-Similarly, participants considerd the guess "right" when a disjunction was used and only one of the animals was on the card.
-However, in scalar trials that both animals were on the card and a disjunction was gueassed, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time.
+In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)).
+And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
+On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time.
+This means that the weak and strong link lead to different conclusions about implicature rates on the ternary task.
+Under the weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link it is only `r round(ternaryExh_wrong$proportion*100)`%.
+Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.
 
@@
 
-```{r quaternaryPlot, fig.height=4, fig.cap = "Proportion responses for the four-alternative (quatenary) forced choice judgments in the guessing game."}
+```{r quaternaryPlot, fig.height=4, fig.cap = "Proportion of responses for the quaternary forced choice judgments. Error bars indicate 95% bootstrapped confidence intervals."}
 quaternary_plot<-
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response Options for the Quaternary Task", y="Proportions")+
+  labs(x="Response options (quaternary task)", y="Proportion of response")+
   theme_few() +
@@
 
-Figure \@ref(fig:quaternaryPlot) shows the proportion of "right", "kinda right", "kinda wrong", and "wrong" responses in the quaternary task.
-Similar to the results seen previously, the control trials turned out as expected.
-Participants considered a guess "wrong" if the animal guessed was not on the card and "right" if it was the only animal on the card.
-If a conjunctin of animals was guessed and both animals were on the card the guess was "right".
-However, when only one of the animals on the card was guessed (exhaustive trials), participants judged the guess "wrong" `r round(quaternaryExh_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quaternaryExh_kindaWrong$proportion*100)`% of the time, and "kinda right" `r round(quaternaryExh_kindaRight$proportion*100)`% of the times.
-Perhaps surprisingly, when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right".
+In the quaternary task (Figure \@ref(fig:quaternaryPlot)), participants were again at or close to ceiling in responding 'right' and 'wrong' on 4 of the 6 unambiguously true and false trials.
+However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right".
 This suggests that perhaps participants considered a notion of partially true or correct statement in our experimental setting.
-Disjunctive guesses with one or two animals on the card showed similar response patterns with participants choosing the "kinda right" and "right" options most of the time.
-When both animals were on the card with a disjunctive guess (scalar trials), participants judged the guess "wrong" `r round(quaternaryScalar_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quaternaryScalar_kindaWrong$proportion*100)`% of the time, and "kinda right" `r round(quaternaryScalar_kindaRight$proportion*100)`% of the times.
+Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.
+
+On underinformative exhaustive trials, we observed pragmatic behavior as before: participants judged the guess "wrong" `r round(quaternaryExh_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quaternaryExh_kindaWrong$proportion*100)`% of the time, and "kinda right" `r round(quaternaryExh_kindaRight$proportion*100)`% of the time.
+On scalar trials, participants judged the guess "wrong" `r round(quaternaryScalar_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quaternaryScalar_kindaWrong$proportion*100)`% of the time, and "kinda right" `r round(quaternaryScalar_kindaRight$proportion*100)`% of the times.
+
+Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link.
+Under the weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%.
+Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.
 
@@
 
-```{r quinaryPlot, fig.height=4, fig.cap = "Proportion responses for the five-alternative (quinary) forced choice judgments in the guessing game."}
+```{r quinaryPlot, fig.height=4, fig.cap = "Proportion of responses for the quinary forced choice judgments. Error bars indicate 95% bootstrapped confidence intervals."}
 quinary_plot<-
@@
   facet_grid(card_type~guess_type) +
-  labs(x="Response Options in the Quinary Task", y="Proportions")+
+  labs(x="Response options (quinary task)", y="Proportion of response")+
   theme_few() +
@@
 
-quinaryyScalar_wrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Wrong")
+quinaryScalar_wrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Wrong")
 quinaryScalar_kindaWrong <- quinary_summary %>% filter(card_type=="XY", guess_type=="cat or dog", response=="Kinda Wrong")
@@
 
-Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of "right", "kinda right", "neither", "kinda wrong", and "wrong" responses in the quinary task.
-Since the results for the control trials were identical to previous tasks, we do not repeat them here.
-In exhaustive trials where two animals were on the card and only one of them was guessed, participants chose "kinda right" the majority of times (`r round(quinaryExh_kindaRight$proportion*100)`%).
-Again perhaps surprisingly, when only one animal was on the card and the guess was a conjunction, responses were equally split among "wrong", "kinda wrong", and "kinda right" responses.
-With disjunctive guesses, partitipants were more likely to choose "right" and "kinda right" options.
-When only one animal was on the card, participants considered the disjunctive guess as "right" more often.
-When both animals were on the card (scalar trials), participants judged the disjunctive guess as "kinda right" `r round(quinaryScalar_kindaRight$proportion*100)`% of the time.
+Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of  responses in the quinary task.
+Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively.
+The 2 control conditions that the quaternary task had revealed pragmatic infelicity in again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, requires fine-grained enough response options to be detected experimentally.
+
+On underinformative exhaustive trials, we observed pragmatic behavior as before: participants judged the guess "wrong" `r round(quinaryExh_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quinaryExh_kindaWrong$proportion*100)`% of the time, "neither" `r round(quinaryExh_Neither$proportion*100)`% of the time, and "kinda right" `r round(quinaryExh_kindaRight$proportion*100)`% of the time.
+On scalar trials, participants judged the guess "wrong" `r round(quinaryScalar_wrong$proportion*100)`% of the time, "kinda wrong" `r round(quinaryScalar_kindaWrong$proportion*100)`% of the time, "neither" `r round(quinaryScalar_Neither$proportion*100)`% of the time, and "kinda right" `r round(quinaryScalar_kindaRight$proportion*100)`% of the time.
+
+Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link.
+Under the weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryExh_wrong$proportion*100)`%.
+Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%.
 
@@
 
-## Analysis
+### Quantitative analysis
 
@@
 
-```{r implicatureRatePlot, fig.width=5, fig.height=3, fig.cap = "Implicature rate in exhaustive and scalar trials of the binary, ternary, quaternary, and quinary versions of the guessing game, computed once with a strong linking assumption and once with a weak linking assumption."}
+```{r implicatureRatePlot, fig.width=5, fig.height=3, fig.cap = "Inferred implicature rate on exhaustive and scalar trials with the binary, ternary, quaternary, and quinary response task.
+Columns indicate link from response to implicature rate (strong: proportion of "wrong" judgments; weak: proportion of non-"right" judgments)."}
 ggplot(implicature_results, aes(x=response_type,y=proportion)) +
@@
   theme_few() + 
-  labs(x="Number of Response Options in the Task", y="Inferred Implicature Rate") +
+  labs(x="Response task", y="Inferred implicature rate") +
   theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1)) +

### 2018-05-08 writeup.Rmd
rewrote quantitative results section

@@
 
-Our primary goal in this study was to check whether the estimated "implicature rate" in the experimental task is affected by the linking assumption and the number of response options available in the task.
-Our analysis in this section focuses on these three elements.
-As mentioned before, two trial types were predicted to include pragmatic implicatures.
-First, trials where two animals were on the card but the fictional character guessed with a disjunction (scalar); for example "cat or dog" when the card has both a cat and a dog on it.
-Second, trials where there were two animals on the card but the character guessed only one (exhaustive); for example "cat" when the card had a cat and a dog on it.
-We called such trials "exhaustive".
-In our assessment of implicature rate, we focus on these two trial types.
-
-We considered two linking assumptions.
-First we defined a weak (lenient) linking assumption in which any response lower than the maximum point on the scale (i.e.
-"right") is considered evidence for implicature computation.
-Second, we defined a strong (strict) linking assumption that only considered the lowest point on the scale (i.e.
-"wrong") as evidence for implicature computation.
-For each condition in our study (binary, ternary, quaternary, and quinary) and each implicature trial type (exhaustive and scalar), we computed a weak and a strong implicature rate.
-Figure \@ref(fig:implicatureRatePlot) shows these computed rates.
-
-Comparing the strong and weak rows on Figure \@ref(fig:implicatureRatePlot), we see that a weak linking assumption tends to estimate higher implicature rates, especially in tasks with more response options.
-With a strong linking assumption, the binary and possibly ternary judgment tasks derive higher implicature rates than quaternary and quinary tasks.
-With a weak linking assumption, the pattern is reversed.
-Quaternary and quinary tasks estimate higher rates than binary and ternary tasks.
-The patterns show that estimates of "implicature rate" depend on linking assumptions and the number of responses available to participants in the study.
-
-Comparing the exhaustive and scalar columns of Figure \@ref(fig:implicatureRatePlot), we see that with a strong linking assumption, there are slightly higher rates for scalar implicatures in the binary and ternary tasks.
-With a weak linking assumption, there may be slightly higher rates for scalar implicatures in the binary and ternary while the rates may be lower in the quaternary and quinary tasks.
-In what follows, we formally test the effect of linking assumption and response options on exhaustive and scalar implicature rates.
-
-```{r implicatureRatePlot, fig.width=5, fig.height=3, fig.cap = "Inferred implicature rate on exhaustive and scalar trials with the binary, ternary, quaternary, and quinary response task.
-Columns indicate link from response to implicature rate (strong: proportion of "wrong" judgments; weak: proportion of non-"right" judgments)."}
+Our primary goal in this study was to test whether the estimated implicature rate in the experimental task is affected by the linking assumption and the number of response options available to participants.
+To this end, we only analyzed the critical trials (exhaustive and scalar).
+In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the strong and weak link.
+Figure \@ref(fig:implicatureRatePlot) shows the resulting implicature rates by condition and link.
+
+Visually, the weak link tends to result in greater estimates of implicature rates, especially in tasks with more response options.
+Under the strong link, this latter pattern is reversed: the binary and ternary judgment tasks result in greater estimates of implicature rates than with more response options.
+
+```{r implicatureRatePlot, fig.width=4, fig.height=3, fig.cap = "Inferred implicature rates on exhaustive and scalar trials as obtained with the binary, ternary, quaternary, and quinary response task.
+Columns indicate link from response to implicature rate (strong: proportion of 'wrong judgments; weak: proportion of non-'right' judgments)."}
 ggplot(implicature_results, aes(x=response_type,y=proportion)) +
@@
   rename(Predictors = "X1", `2.5%` = "X2.5.ile", `97.5%` = "X97.5.ile") %>%
-  select(-Est.Error)
-
-kable(fixed_effects_table,digits = 2 , caption = "\\label{tab:modeltable}Model Parameter Estimates and Their Credible Intervals", booktabs = T)
-```
-
-For our formal analysis, we used a bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms].
-The model had the fixed effects of response type (binary, ternary, quaternary, quinary), linking assumption (strong vs.
-weak), and trial type (exhaustive vs.
-scalar), as well as their two way and three way interactions.
-We also included random intercepts and slopes for items (cards) and participants.
-Following @barr2013random, we used the maximal random effects structure by including random slopes for all our fixed effects and their interactions.
+  select(-Est.Error) %>%
+  mutate(Evidence=sign(`2.5%`)==sign(`97.5%`)) %>%
+  mutate(Evidence=replace(Evidence,Evidence==TRUE,"*")) %>%
+  mutate(Evidence=replace(Evidence,Evidence==FALSE,""))
+
+kable(fixed_effects_table,digits = 2 , caption = "\\label{tab:modeltable}Model parameter estimates and their credible intervals.
+Rows marked with an asterisk in the evidence column do not contain 0 in the credible interval, thereby providing evidence for an effect.", booktabs = T)
+```
+
+To analyze the effect of link and response options on inferred implicature rate, we used a Bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms] with uninformative priors **JD: Masoud is the uninformative prior part correct?**.
+The model predicted the log odds of implicature over no implicature from fixed effects of *response type* (binary, ternary, quaternary, quinary -- dummy-coded with binary as reference level), *link* (strong vs.
+weak -- dummy-coded with strong as reference level), and trial type (exhaustive vs.
+scalar -- dummy-coded, with exhaustive as reference level), as well as their two-way and three-way interactions.
+Following @barr2013random, we included the maximal random effects structure justified by the design: random intercepts for items (cards) and participants, random by-participant slopes for link, trial type, and their interaction, and random by-item slopes for link, trial type, response type, and their interactions.
 Since the number of response options was a between participant variable we did not include random slopes of response options for participants.
@@
 
-The model provided evidence for two effects in the study.
-First, there was a main effect of trials such that scalar trials had slightly higher implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]).
-Second, there was an interaction between linking assumption and number of resopnse options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a weak linking assumption had higher implicature rates.
+The model provided evidence for the following effects: First, there was a main effect of trial type such that scalar trials resulted in greater implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]).
+Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a weak link resulted in greater implicature rates.
+Finally, there was a three-way interaction between link, trial type, and number of response options (Mean Estimate = `r round(fixed_effects$Estimate[15],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[15],2)`, `r round(fixed_effects$X97.5.ile[15],2)`]).
+One interpretation of this interaction is that the difference between the weak and strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
+**JD: happy to throw out this last sentence** Crucially, both number of response options and link affect the inferred implicature rate.
 

### 2018-05-08 writeup.Rmd
minor discussion edits

@@
 The results presented here suggest they do.
-A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (weak link) reported higher implicature rates in tasks with 4 or 5 options.
+A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (weak link) resulted in higher implicature rates in tasks with 4 or 5 response options.
 A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (strong link) reported lower implicature rates in tasks with 4 or 5 options.
-The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions of truth value judgment tasks with more than two response options.
-The lower rate of implicatures with a strong linking assumption implies that in such studies, strong linking assumptions may underestimate participants' pragmatic competence.
-
-While the binary truth value judgement task avoids the analytic decision between strong and weak linking assumptions, our results suggest that binary tasks can also underestimate participants' pragmatic competence.
+The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions drawn from truth value judgment tasks.
+In particular, there is danger for pragmatic ability to be both under- and overestimated.
+
+While the binary truth value judgement task avoids the analytic decision between strong and weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
 In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs.
@@
 "wrong").
-Our study showed that in trials with true but infelicitous descriptions (implicature trials), participants often avoided the lowest point on the scale if they were given more intermediate options.
+The study reported here showed that on trials with true but pragmatically infelicitous descriptions, participants often avoided the lowest point on the scale if they were given more intermediate options.
 Even though the option "wrong" was available to participants in all tasks, participants in tasks with intermediate options chose it less often.
-In computing implicature rate, this pattern manifested itself as a decrease in implicature rate with strong link when more response options were provided, and increase in implicature rate with weak link when more response options were provided.
+In computing implicature rate, this pattern manifested itself as a decrease in implicature rate under the strong link when more response options were provided, and an increase in implicature rate under the weak link when more response options were provided.
 These conclusions are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much.
-Providing participants with only the extreme opposits of the scale (e.g.
+Providing participants with only the extreme ends of the scale (e.g.
 wrong/right, false/true) when pragmatic violations are considered to be of an intermediate nature risks misrepresentation of participants' pragmatic competence.
+It further suggests that in studies that use binary tasks to investigate response-contingent processing, proportions of "literal" responses may be a composite of both literal and pragmatic underlying interpretations that just happen to get mapped differently onto different response options by participants.
 
@@
 Among the intermediate options, "kinda right" was chosen most often to report pragmatic infelicities.
-The option "neither" was rarely used in the ternary and quinary tasks (where it was used as a midpoint), suggesting that participants found pragmatic infelicities as different degrees of being "right" and not "neither right nor wrong." Therefore, options that capture grades of being "right" like "kinda right" proved be most suitable for capturing true but infelicitous utterances.
-
-This study had three design features that we would like to investigate in future work.
-First, the utterances were by a blindfolded character because we wanted to control for violation of ignorance expectations with disjunction.
+The option "neither" was rarely used in the ternary and quinary tasks (where it was used as a midpoint), suggesting that participants interpreted pragmatic infelicities as different degrees of being "right" and not "neither right nor wrong." Therefore, options that capture degrees  of being "right" like "kinda right" may prove most suitable for capturing infelicity in the long run.
+We leave this as a methodological issue for future research.
+
+The study had three further design features worth investigating in future work.
+First, the utterances were ostensibly produced by a blindfolded character.
+This was an intentional decision to control for violation of ignorance expectations with disjunction.
 A disjunction such as "A or B" often carries an implication or expectation that the speaker is not certain which alternative actually holds.
-In future work, we would like to see how the violation of the ignorance expectation would affect the inferred implicature rate by having the fictional character describe the cards while looking at them.
+Future work should investigate how the violation of the ignorance expectation interacts with link and number of response options in inferred implicature rate.
 Second, in this study we considered exhaustive and scalar implicatures with *or*.
-We would like to see if similar effects hold for the scalar implicatures with *some*.
-Finally, our experiment was designed as a guessing game and the exact goal of the game was left implicit.
-We expect that different goals, for example help the character win more points vs.
-help the character be more accurate, would affect how strict or lenient participants are with their judgments and ultimately affect the implicature rate in the task.
-In future work we would like to systematically vary the goal of the game and explore its effects on the inferred implicature rate.
-
-**JD: moved from Methods section: Since the fictional character was blindfolded and did not see the outcome of the game, the ignorance inference commonly associated with disjunction was already common ground in the experimental setting.
-If the character was seeing the cards or knew what was on them, a disjunction would have violated the expectation that the speaker does not know which alternative actually holds.
-Our study controls for the possibile effect of ignorance violations on exclusivity and exhaustive inferences.
-**
+If the observed effects of link and number of response options hold in general, they should be observable using other scales, e.g., on implicatures with *some*.
+Finally, our experiment was designed as a guessing game and the exact goal or task-relevant Question Under Discussion of the game was left implicit.
+Given the past literature on QUD effects on scalar implicature, we expect that different goals -- e.g., to help the character win more points vs.
+to help the character be more accurate -- would affect how strict or lenient participants are with their judgments and ultimately affect implicature rate in the task [@Degen2014;@Zondervan2010].
+Future work should systematically vary the goal of the game and explore its effects on the inferred implicature rate.
 

### 2018-05-08 writeup.Rmd
edits to introduction

@@
 The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*.
-Scalar implicatures arise in virtue of a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
+Scalar implicatures arise in virtue of **bw: as a result of?** a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
 Examples are provided in (1-2).
@@
 
-A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
+A standard measure that has stood proxy **bw: stood as a proxy** for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
 In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
@@
 Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of *interpretation*.
-And second, that listeners either do or do not compute an implicature on any given occasion.
+And second, **bw: change to semicolon, i.e.
+"...
+interpretation; and second,**  that listeners either do or do not compute an implicature on any given occasion.
 In the General Discussion we will discuss both of these issues.
@@
 This will suggest a completely different class of linking functions.
-And second, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
+And second, **bw: Next, (to avoid redundancy -- see above)** we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
 This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.
@@
 Assume three response options (wrong, neither, right).
-Assume further that a third of participants each gave each of the three responses, i.e., the distributions of responses is 1/3, 1/3, and 1/3.
+Assume further that a third of participants each gave each of the three responses, **bw: Assume further that each of the three responses was selected by a third of participants,** i.e., the distributions of responses is 1/3, 1/3, and 1/3.
 Under the Strong link, we infer that this task yielded an implicature rate of 2/3.
 Under the Weak link, we infer that this task yielded an implicature rate of 1/3.
-This is quite a drastic difference if we are for instance interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
+This is quite a drastic difference if we are for instance **bw: if we are, for instance, **interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
 Under the Strong link, we would conclude that scalar implicatures are not defaults.

### 2018-05-08 writeup.Rmd
minor discussion edits

@@
 
-## Discussion
+# General Discussion
+
+## Summary and methodological discussion
 
@@
 
-# General Discussion
+## Revisiting linking assumptions
 
 On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
-This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
-And why did a sizeable minority nonetheless choose "Wrong" in this same condition?
+This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
+And why did a sizeable minority nonetheless choose "wrong" in this same condition?
 

### 2018-05-08 writeup.Rmd
minor edits and comments on gd

@@
 
-To explain these data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "Wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
+To explain these data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
 We might similarly posit that one or both of these factors underlie the variation in the ternary, quaternary, and quinary conditions.
 However, without an understanding of how to quantitatively specify the link between implicature calculation and its behavioral expression, the best we can hope for on this approach is an analysis which predicts general qualitative patterns in the data (e.g.
-a prediction of relatively more "Right" responses than "Wrong" responses in a given trial of our binary truth-value judgment task, or a prediction of a rise in the rate of response of "Right"/"Wrong" between two experimental conditions, given some contextual manipulation).
-**XXX Judith, I was thinking of adding the sentence to end this paragraph: "However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks - much less the effect of the number of response choices on that behavior - is largely underdeveloped scalar implicature literature." But it might be way too strong a claim?
-**
-
-**XXX Brandon, can you be more specific about what you mean by 'tracing a general qualitative pattern'? XXX Judith: I've tried to offer some examples of what I mean by this, see above.**
+a prediction of relatively more "right" responses than "wrong" responses in a given trial of our binary truth-value judgment task, or a prediction of a rise in the rate of response of "right"/"wrong" between two experimental conditions, given some contextual manipulation).
+However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks - much less the effect of the number of response choices on that behavior - is largely underdeveloped scalar implicature literature.
 
 We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis.
-Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2015; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
-**XXX Judith: re: your Slack comments, in the following few sentences I've provided a summary of the intuition behind RSA (going off of the discussion in Goodman & Stuhlmueller 2013)** Much in the spirit of Gricean approaches to pragmatic competence, the RSA framework takes as its point of departure the idea that individuals are rational, goal-oriented communicative agents, who in turn assume that their interlocutors similarly behave according to general principles of cooperativity in communication.
+Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework  [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2015; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
+Much in the spirit of Gricean approaches to pragmatic competence, the RSA framework takes as its point of departure the idea that individuals are rational, goal-oriented communicative agents, who in turn assume that their interlocutors similarly behave according to general principles of cooperativity in communication.
 Just as in more traditional Gricean pragmatics, pragmatic inference and pragmatically-cooperative language production in the RSA framework are, at their core, the product of counterfactual reasoning about alternative utterances that one might produce (but does not, in the interest of cooperativity).
-However, the RSA framework explicitly and quantitatively models coooperative interlocutors as agents whose language production and comprehension is a function of Bayesian probalistic inference regarding other interlocutors' expected behavior in a discourse context.
+However, the RSA framework explicitly and quantitatively models cooperative interlocutors as agents whose language production and comprehension is a function of Bayesian probabilistic inference regarding other interlocutors' expected behavior in a discourse context.
 
@@
 
-Thus, our alternative linking hypothesis contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+This view contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
 In the RSA framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
-For example, exclusivity readings of disjunction are represented in RSA as relatively lower posterior conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared the prior probability of that meaning.
+For example, exclusivity readings of disjunction are represented in RSA as relatively lower posterior conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared to the prior probability of that meaning.
 Thus, absent auxiliary assumptions about what exactly would constitute 'implicature', it is not even possible to talk about rate of implicature calculation in the RSA framework.
@@
 A main desideratum of a behavioral linking hypothesis given the RSA view of pragmatic competence is to transform continuous probability distributions into categorical outputs (e.g.
-responses of “Right”/”Wrong” in the case of the binary condition of our experiment).
+responses of “right”/”wrong” in the case of the binary condition of our experiment).
 For a given utterance $u$ and an intended communicated meaning $s$, $S_1$(u | s) outputs a conditional probability of $u$ given $s$.
@@
 the configuration of animals on the card in our experiment).
-We model a responder, $R$, who in the binary condition responds “Right” to an utterance $u$ in world $s$ just in case $S_1(u | s)$ exceeds some probability threshold $\theta$:
+We model a responder, $R$, who in the binary condition responds “right” to an utterance $u$ in world $s$ just in case $S_1(u | s)$ exceeds some probability threshold $\theta$:
 
@@
 
-= “Right” iff $S_1$(u | s) $>$ $\theta$
-
-= “Wrong” otherwise
-
-**XXX The following paragraph is mostly new:** Because $\theta$ is a free parameter in our model, we have a straightforward understanding of between-subject response variation on a given trial of our experiment according to this linking hypothesis.
-That is, we can attribute this variation to individual differences vis a vis the value of the probability threshold against which utterances are evaluated in a given world state.
+= “right” iff $S_1$(u | s) $>$ $\theta$
+
+= “wrong” otherwise
+
+Because $\theta$ is a free parameter in our model, we have a straightforward understanding of between-subject response variation on a given trial of our experiment according to this linking hypothesis.
+**JD: Hold on, Brandon, what's the link between being a free parameter hand having an understanding of between-subject response variation?** That is, we can attribute this variation to individual differences vis a vis the value of the probability threshold against which utterances are evaluated in a given world state.
 Moreover, the model of a responder in the binary condition is extended intuitively to the condition where participants had three response options.
-In this case, we allow for two probability thresholds: $\theta_1$, the minimum standard for an utterance in a given world state to count as "Right", and $\theta_2$, the minimum standard for "Neither".
-Thus, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | s) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
-To fully generalize the model to our five experimental conditions, we say that $R$ takes as its input an utterance $u$, a world state $s$, and a number of threshold variables dependent on a variable $c$, corresponding to the experimental condition in which the participant finds herself (e.g.
+In this case, we allow for two probability thresholds: $\theta_1$, the minimum standard for an utterance in a given world state to count as "right", and $\theta_2$, the minimum standard for "neither".
+Thus, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “right” iff $S_1$(u | s) > $\theta_1$ and “neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
+To fully generalize the model to our five experimental conditions, we say that $R$ takes as its input an utterance $u$, a world state $s$, and a number of threshold variables dependent on a variable $c$, corresponding to the experimental condition in which the participant finds themself (e.g.
 the range of possible responses available to $R$).
@@
 
-= “Right” iff $S_1$(u | s) $>$ $\theta_1$
-
-= “Neither” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
-
-= “Wrong” otherwise
-
-Given c = “quatenary”
+= “right” iff $S_1$(u | s) $>$ $\theta_1$
+
+= “neither” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “wrong” otherwise
+
+Given c = “quaternary”
 
@@
 
-= “Right” iff $S_1$(u | s) $>$ $\theta_1$
-
-= “Kinda Right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
-
-= “Kinda Wrong” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
-
-= “Wrong” otherwise
+= “right” iff $S_1$(u | s) $>$ $\theta_1$
+
+= “kinda right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “kinda wrong” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
+
+= “wrong” otherwise
 
@@
 
-= “Right” iff $S_1$(u | s) $>$ $\theta_1$
-
-=“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
-
-= “Neither” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
-
-= “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | s) $>$ $\theta_4$
-
-= “Wrong” otherwise
+= “right” iff $S_1$(u | s) $>$ $\theta_1$
+
+=“kinda right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “neither” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
+
+= “kinda wrong” iff $\theta_3$ $>$ $S_1$(u | s) $>$ $\theta_4$
+
+= “wrong” otherwise
 
 The above analysis is a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
-
-**XXX The following is entirely new:** However, this way of understanding behaivor in truth value jugdment tasks also raises new analytic and empirical questions which we must leave to future work.
-For instance, given the experimental results reported here, what is the range of plausible values for, e.g., the single probability threshold $\theta$, which separates "Right" from "Wrong" utterances in the binary condition?
-Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e.
-the actual rate of response of "Right" On each trial of the binary condition of the experiment.
-We may also ask, for example, whether the speaker probability threshold for an utterance being "Right" is relatively constant across conditions or changes systematically with the introduction of more response options.
-Again, Bayesian data analysis allows us to explore this question by investigating the extent to which the inferred posterior distribution of, e.g., possible values of the threshold for "Right" in the binary condition of the experiment differs from the inferred posterior distribution of possible values of the threshold for "Right" in the ternary, quatenary, and quinary conditions.
+**JD: Brandon, I feel what's still missing here is a demonstration that this is a _reasonable_ linking function.
+Maybe we can add the point that with this linking function, there's nothing inherently special about the implicature conditions -- the same linking function can work for any of the eight conditions in our experiment, because they're all the result of a participant having to make a behavioral choice in the face of an underlying speaker probability.**
+
+However, this way of understanding behavior in truth value judgment tasks also raises new analytic and empirical questions which we must leave to future work.
+For instance, given the experimental results reported here, what is the range of plausible values for, e.g., the single probability threshold $\theta$, which separates "right" from "wrong" utterances in the binary condition?
+Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e., the actual rate of response of "right" on each trial of the binary condition of the experiment.
+We may also ask, for example, whether the speaker probability threshold for an utterance being "right" is relatively constant across conditions or changes systematically with the introduction of more response options.
+Again, Bayesian data analysis allows us to explore this question by investigating the extent to which the inferred posterior distribution of, e.g., possible values of the threshold for "right" in the binary condition of the experiment differs from the inferred posterior distribution of possible values of the threshold for "right" in the ternary, quatenary, and quinary conditions.
 
@@
 
+**JD: We need a final concluding paragraph that reiterates the main points.**
+
 # References

### 2018-05-08 writeup.Rmd
inline edits to results section

@@
 In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)).
-However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time.
-That is, both under the weak and the strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.
+However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog) **bw: "(i.e.
+a "cat" or "cat or dog" description for a card with both a cat and a dog)"**, we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time.
+That is, both under the weak and the strong link **bw: Weak and Strong link assumptions (capitalization consistency with intro)** assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.
 
@@
 In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)).
-And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
+And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog) **bw: "(a "cat" and "cat or dog" description for a card with both a cat and a dog)"**, we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
 On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time.
-This means that the weak and strong link lead to different conclusions about implicature rates on the ternary task.
-Under the weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link it is only `r round(ternaryExh_wrong$proportion*100)`%.
-Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.
+This means that the weak and strong link **bw: Weak and Strong link** lead to different conclusions about implicature rates on the ternary task.
+Under the weak link **bw: Weak link**, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(ternaryExh_wrong$proportion*100)`%.
+Similarly, under the weak link **bw: Weak link**, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(ternaryScalar_wrong$proportion*100)`%.
 
@@
 However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right".
-This suggests that perhaps participants considered a notion of partially true or correct statement in our experimental setting.
+This suggests that perhaps participants considered a notion of partially true or correct statement **bw: considered the notion of a partially true or correct statement** in our experimental setting.
 Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.
@@
 Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.
+**bw: capitalize "Weak" and "Strong" in this paragraph**
 
@@
 Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively.
-The 2 control conditions that the quaternary task had revealed pragmatic infelicity in again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, requires fine-grained enough response options to be detected experimentally.
+The 2 control conditions that the quaternary task had revealed pragmatic infelicity in **bw: The 2 control conditions in which the quaternary task had revealed pragmatic infelicity ** again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, **bw: "nonetheless" rather than "however"?** requires fine-grained enough response options to be detected experimentally.
 
@@
 
-Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link.
-Under the weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryExh_wrong$proportion*100)`%.
-Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%.
-
+Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link **bw: Weak link or the Strong link**.
+Under the weak link **bw: Weak link**, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(quinaryExh_wrong$proportion*100)`%.
+Similarly, under the weak link **bw: Weak link**, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link **bw: Strong link** it is only `r round(quinaryScalar_wrong$proportion*100)`%.
 <!--

### 2018-05-09 writeup.Rmd
added brandons comments

--- 2018-05-08 writeup.Rmd
@@
 The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*.
-Scalar implicatures arise in virtue of **bw: as a result of?** a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
+Scalar implicatures arise as a result of a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
 Examples are provided in (1-2).
@@
 
-A standard measure that has stood proxy **bw: stood as a proxy** for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
+A standard measure that has stood as a proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
 In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
@@
 We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth-value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates?
-Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of *interpretation*.
-And second, **bw: change to semicolon, i.e.
-"...
-interpretation; and second,**  that listeners either do or do not compute an implicature on any given occasion.
+Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of interpretation; and second,  that listeners either do or do not compute an implicature on any given occasion.
 In the General Discussion we will discuss both of these issues.
@@
 This will suggest a completely different class of linking functions.
-And second, **bw: Next, (to avoid redundancy -- see above)** we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
+Next, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
 This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.
@@
 
-```{r linkvisualization, fig.asp=0.2,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
+```{r linkvisualization, fig.asp=0.2,fig.cap = "Strong and Weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
 link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
@@
 Assume three response options (wrong, neither, right).
-Assume further that a third of participants each gave each of the three responses, **bw: Assume further that each of the three responses was selected by a third of participants,** i.e., the distributions of responses is 1/3, 1/3, and 1/3.
+Assume further that each of the three responses was selected by a third of participants, i.e., the distributions of responses is 1/3, 1/3, and 1/3.
 Under the Strong link, we infer that this task yielded an implicature rate of 2/3.
 Under the Weak link, we infer that this task yielded an implicature rate of 1/3.
-This is quite a drastic difference if we are for instance **bw: if we are, for instance, **interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
+This is quite a drastic difference if we are, for instance, interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
 Under the Strong link, we would conclude that scalar implicatures are not defaults.
@@
 On critical trials, participants were presented with descriptions for the cards that typically result in exhaustivity implicatures ("There is a cat on the card" when there was a cat and a dog) or scalar implicatures ("There is a cat or a dog on the card" when there was a cat and a dog).
-We categorized their responses on such trials according to the weak and the strong link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.
+We categorized their responses on such trials according to the weak and the Strong link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.
 
@@
 In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)).
-However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time.
-That is, both under the weak and the strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.
+However, on underinformative trials (i.e.
+a "cat" or "cat or dog" description for a card with both a cat and a dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time.
+That is, both under the Weak and Strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.
 
@@
 In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)).
-And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
+And again, on underinformative trials (a "cat" and "cat or dog" description for a card with both a cat and a dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time.
 On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time.
-This means that the weak and strong link lead to different conclusions about implicature rates on the ternary task.
-Under the weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link it is only `r round(ternaryExh_wrong$proportion*100)`%.
-Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.
+This means that the Weak and Strong link lead to different conclusions about implicature rates on the ternary task.
+Under the Weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the Strong link it is only `r round(ternaryExh_wrong$proportion*100)`%.
+Similarly, under the Weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the Strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.
 
@@
 However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right".
-This suggests that perhaps participants considered a notion of partially true or correct statement in our experimental setting.
+This suggests that perhaps participants considered the notion of a partially true or correct statement in our experimental setting.
 Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.
@@
 
-Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link.
-Under the weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%.
-Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.
+Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the Weak link or the Strong link.
+Under the Weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%.
+Similarly, under the Weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.
 
@@
 Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively.
-The 2 control conditions that the quaternary task had revealed pragmatic infelicity in again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, requires fine-grained enough response options to be detected experimentally.
+The 2 control conditions in which the quaternary task had revealed pragmatic infelicity  again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, nonetheless, requires fine-grained enough response options to be detected experimentally.
 
@@
 
-Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link.
-Under the weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryExh_wrong$proportion*100)`%.
-Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%.
-
+Thus, we would again draw different conclusions about implicature rates depending on whether we assume the Weak link or the Strong link.
+Under the Weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quinaryExh_wrong$proportion*100)`%.
+Similarly, under the Weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%.
 <!--
@@
 To this end, we only analyzed the critical trials (exhaustive and scalar).
-In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the strong and weak link.
+In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the strong and Weak link.
 Figure \@ref(fig:implicatureRatePlot) shows the resulting implicature rates by condition and link.
 
-Visually, the weak link tends to result in greater estimates of implicature rates, especially in tasks with more response options.
-Under the strong link, this latter pattern is reversed: the binary and ternary judgment tasks result in greater estimates of implicature rates than with more response options.
+Visually, the Weak link tends to result in greater estimates of implicature rates, especially in tasks with more response options.
+Under the Strong link, this latter pattern is reversed: the binary and ternary judgment tasks result in greater estimates of implicature rates than with more response options.
 
@@
 The model provided evidence for the following effects: First, there was a main effect of trial type such that scalar trials resulted in greater implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]).
-Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a weak link resulted in greater implicature rates.
+Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a Weak link resulted in greater implicature rates.
 Finally, there was a three-way interaction between link, trial type, and number of response options (Mean Estimate = `r round(fixed_effects$Estimate[15],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[15],2)`, `r round(fixed_effects$X97.5.ile[15],2)`]).
-One interpretation of this interaction is that the difference between the weak and strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
+One interpretation of this interaction is that the difference between the weak and Strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
 **JD: happy to throw out this last sentence** Crucially, both number of response options and link affect the inferred implicature rate.
@@
 The results presented here suggest they do.
-A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (weak link) resulted in higher implicature rates in tasks with 4 or 5 response options.
-A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (strong link) reported lower implicature rates in tasks with 4 or 5 options.
+A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (Weak link) resulted in higher implicature rates in tasks with 4 or 5 response options.
+A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (Strong link) reported lower implicature rates in tasks with 4 or 5 options.
 The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions drawn from truth value judgment tasks.
@@
 
-While the binary truth value judgement task avoids the analytic decision between strong and weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
+While the binary truth value judgement task avoids the analytic decision between strong and Weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
 In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs.
@@
 Even though the option "wrong" was available to participants in all tasks, participants in tasks with intermediate options chose it less often.
-In computing implicature rate, this pattern manifested itself as a decrease in implicature rate under the strong link when more response options were provided, and an increase in implicature rate under the weak link when more response options were provided.
+In computing implicature rate, this pattern manifested itself as a decrease in implicature rate under the Strong link when more response options were provided, and an increase in implicature rate under the Weak link when more response options were provided.
 These conclusions are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much.

### 2018-05-09 writeup.Rmd
addressed comments

--- 2018-05-08 writeup.Rmd
@@
 The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*.
-Scalar implicatures arise in virtue of **bw: as a result of?** a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
+Scalar implicatures arise in virtue of a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010].
 Examples are provided in (1-2).
@@
 
-A standard measure that has stood proxy **bw: stood as a proxy** for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
+A standard measure that has stood proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
 In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
@@
 Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of *interpretation*.
-And second, **bw: change to semicolon, i.e.
-"...
-interpretation; and second,**  that listeners either do or do not compute an implicature on any given occasion.
+And second, that listeners either do or do not compute an implicature on any given occasion.
 In the General Discussion we will discuss both of these issues.
@@
 This will suggest a completely different class of linking functions.
-And second, **bw: Next, (to avoid redundancy -- see above)** we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
+And second, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
 This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.
@@
 Assume three response options (wrong, neither, right).
-Assume further that a third of participants each gave each of the three responses, **bw: Assume further that each of the three responses was selected by a third of participants,** i.e., the distributions of responses is 1/3, 1/3, and 1/3.
+Assume further that a third of participants each gave each of the three responses, i.e., the distributions of responses is 1/3, 1/3, and 1/3.
 Under the Strong link, we infer that this task yielded an implicature rate of 2/3.
 Under the Weak link, we infer that this task yielded an implicature rate of 1/3.
-This is quite a drastic difference if we are for instance **bw: if we are, for instance, **interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
+This is quite a drastic difference if we are for instance interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim.
 Under the Strong link, we would conclude that scalar implicatures are not defaults.
@@
 `r logicTraining[[2]]` participants reported that they did, while `r logicTraining[[1]]` had no prior training in logic.
-**JD: Do we do any analysis of logic training???** All participants' data was included in the final analysis.
+All participants' data was included in the final analysis.
 
@@
 Then participants were introduced to a blindfolded fictional character called Bob.
-Bob was blindfolded to avoid violations of ignorance expectations associated with the use of disjunction [@???] **JD: Masoud, can you insert citation pls?
-Geurts, Sauerland?**.
-Participants were told that Bob would guess the contents of the cards and their task was to indicate whether Bob's guess was wrong or right.
+Bob was blindfolded to avoid violations of ignorance expectations associated with the use of disjunction [@chierchia2001;@sauerland2004scalar] Participants were told that Bob would guess the contents of the cards and their task was to indicate whether Bob's guess was wrong or right.
 On each trial, participants saw a card and a sentence representing Bob's guess.
@@
 
-[^2]: The experiment can be viewed [here](https://github.com/thegricean/si-paradigms/). **JD: Masoud, please turn this into a working link to the actual experiment**
+[^2]: The experiment can be viewed [here](https://cdn.rawgit.com/thegricean/si-paradigms/94a590f0/experiments/main/1_methods/online_experiment/connective_game.html).
 
@@
 
-To analyze the effect of link and response options on inferred implicature rate, we used a Bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms] with uninformative priors **JD: Masoud is the uninformative prior part correct?**.
+To analyze the effect of link and response options on inferred implicature rate, we used a Bayesian binomial mixed effects model using the R packge "brms" [@burkner2016brms] with uninformative or weakly informative priors [^3].
 The model predicted the log odds of implicature over no implicature from fixed effects of *response type* (binary, ternary, quaternary, quinary -- dummy-coded with binary as reference level), *link* (strong vs.
@@
 
+[^3: To know more about the default priors of the "brms" package you can refer to [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]
+
 The model provided evidence for the following effects: First, there was a main effect of trial type such that scalar trials resulted in greater implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]).
@@
 One interpretation of this interaction is that the difference between the weak and strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
-**JD: happy to throw out this last sentence** Crucially, both number of response options and link affect the inferred implicature rate.
+Crucially, both number of response options and link affect the inferred implicature rate.
 
@@
 
-# General Discussion
-
-## Summary and methodological discussion
+## Discussion
 
@@
 
-## Revisiting linking assumptions
+# General Discussion
 
 On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
-This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
-And why did a sizeable minority nonetheless choose "wrong" in this same condition?
-
-To explain these data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
+This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “Right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
+And why did a sizeable minority nonetheless choose "Wrong" in this same condition?
+
+To explain these data on the traditional view, we are forced to say that a) not all participants calculated the implicature; or that b) some participants who calculated the implicature did not choose the anticipated (i.e., "Wrong") response due to some other cognitive process which overrode the 'correct' implicature behavior; or some mixture of (a) and (b).
 We might similarly posit that one or both of these factors underlie the variation in the ternary, quaternary, and quinary conditions.
 However, without an understanding of how to quantitatively specify the link between implicature calculation and its behavioral expression, the best we can hope for on this approach is an analysis which predicts general qualitative patterns in the data (e.g.
-a prediction of relatively more "right" responses than "wrong" responses in a given trial of our binary truth-value judgment task, or a prediction of a rise in the rate of response of "right"/"wrong" between two experimental conditions, given some contextual manipulation).
-However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks - much less the effect of the number of response choices on that behavior - is largely underdeveloped scalar implicature literature.
+a prediction of relatively more "Right" responses than "Wrong" responses in a given trial of our binary truth-value judgment task, or a prediction of a rise in the rate of response of "Right"/"Wrong" between two experimental conditions, given some contextual manipulation).
+**XXX Judith, I was thinking of adding the sentence to end this paragraph: "However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks - much less the effect of the number of response choices on that behavior - is largely underdeveloped scalar implicature literature." But it might be way too strong a claim?
+**
+
+**XXX Brandon, can you be more specific about what you mean by 'tracing a general qualitative pattern'? XXX Judith: I've tried to offer some examples of what I mean by this, see above.**
 
 We contrast the above view of implicature and its behavioral reflexes with an alternative linking hypothesis.
-Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework  [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2015; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
-Much in the spirit of Gricean approaches to pragmatic competence, the RSA framework takes as its point of departure the idea that individuals are rational, goal-oriented communicative agents, who in turn assume that their interlocutors similarly behave according to general principles of cooperativity in communication.
+Recent developments in the field of probabilistic pragmatics have demonstrated that pragmatic production and comprehension can be captured within the Rational Speech Act (RSA) framework, which treats listeners and speakers as agents that reason about each other and choose interpretations and utterances, respectively, that soft-maximize utility [@Frank2012; @Goodman2013; @Goodman2016; @Franke2016; @Qing2015; @Degen2013; @DegenTG2015; @Bergen2016; @Kao2014; @Scontras2017].
+**XXX Judith: re: your Slack comments, in the following few sentences I've provided a summary of the intuition behind RSA (going off of the discussion in Goodman & Stuhlmueller 2013)** Much in the spirit of Gricean approaches to pragmatic competence, the RSA framework takes as its point of departure the idea that individuals are rational, goal-oriented communicative agents, who in turn assume that their interlocutors similarly behave according to general principles of cooperativity in communication.
 Just as in more traditional Gricean pragmatics, pragmatic inference and pragmatically-cooperative language production in the RSA framework are, at their core, the product of counterfactual reasoning about alternative utterances that one might produce (but does not, in the interest of cooperativity).
-However, the RSA framework explicitly and quantitatively models cooperative interlocutors as agents whose language production and comprehension is a function of Bayesian probabilistic inference regarding other interlocutors' expected behavior in a discourse context.
+However, the RSA framework explicitly and quantitatively models coooperative interlocutors as agents whose language production and comprehension is a function of Bayesian probalistic inference regarding other interlocutors' expected behavior in a discourse context.
 
@@
 
-This view contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
+Thus, our alternative linking hypothesis contrasts with the traditional view in that it is rooted in a quantitative formalization of pragmatic competence which provides us a continuous measure of pragmatic reasoning.
 In the RSA framework, individuals never categorically draw (or fail to draw) pragmatic inferences about the utterances they hear.
-For example, exclusivity readings of disjunction are represented in RSA as relatively lower posterior conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared to the prior probability of that meaning.
+For example, exclusivity readings of disjunction are represented in RSA as relatively lower posterior conditional probability of a conjunctive meaning on the $P_L$ distribution given an utterance of "or", compared the prior probability of that meaning.
 Thus, absent auxiliary assumptions about what exactly would constitute 'implicature', it is not even possible to talk about rate of implicature calculation in the RSA framework.
@@
 A main desideratum of a behavioral linking hypothesis given the RSA view of pragmatic competence is to transform continuous probability distributions into categorical outputs (e.g.
-responses of “right”/”wrong” in the case of the binary condition of our experiment).
+responses of “Right”/”Wrong” in the case of the binary condition of our experiment).
 For a given utterance $u$ and an intended communicated meaning $s$, $S_1$(u | s) outputs a conditional probability of $u$ given $s$.
@@
 the configuration of animals on the card in our experiment).
-We model a responder, $R$, who in the binary condition responds “right” to an utterance $u$ in world $s$ just in case $S_1(u | s)$ exceeds some probability threshold $\theta$:
+We model a responder, $R$, who in the binary condition responds “Right” to an utterance $u$ in world $s$ just in case $S_1(u | s)$ exceeds some probability threshold $\theta$:
 
@@
 
-= “right” iff $S_1$(u | s) $>$ $\theta$
-
-= “wrong” otherwise
-
-Because $\theta$ is a free parameter in our model, we have a straightforward understanding of between-subject response variation on a given trial of our experiment according to this linking hypothesis.
-**JD: Hold on, Brandon, what's the link between being a free parameter hand having an understanding of between-subject response variation?** That is, we can attribute this variation to individual differences vis a vis the value of the probability threshold against which utterances are evaluated in a given world state.
+= “Right” iff $S_1$(u | s) $>$ $\theta$
+
+= “Wrong” otherwise
+
+**XXX The following paragraph is mostly new:** Because $\theta$ is a free parameter in our model, we have a straightforward understanding of between-subject response variation on a given trial of our experiment according to this linking hypothesis.
+That is, we can attribute this variation to individual differences vis a vis the value of the probability threshold against which utterances are evaluated in a given world state.
 Moreover, the model of a responder in the binary condition is extended intuitively to the condition where participants had three response options.
-In this case, we allow for two probability thresholds: $\theta_1$, the minimum standard for an utterance in a given world state to count as "right", and $\theta_2$, the minimum standard for "neither".
-Thus, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “right” iff $S_1$(u | s) > $\theta_1$ and “neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
-To fully generalize the model to our five experimental conditions, we say that $R$ takes as its input an utterance $u$, a world state $s$, and a number of threshold variables dependent on a variable $c$, corresponding to the experimental condition in which the participant finds themself (e.g.
+In this case, we allow for two probability thresholds: $\theta_1$, the minimum standard for an utterance in a given world state to count as "Right", and $\theta_2$, the minimum standard for "Neither".
+Thus, in the ternary condition, R(u, s, $\theta_1$ , $\theta_2$) is “Right” iff $S_1$(u | s) > $\theta_1$ and “Neither” iff $\theta_1$ > $S_1$(u | s) > $\theta_2$.
+To fully generalize the model to our five experimental conditions, we say that $R$ takes as its input an utterance $u$, a world state $s$, and a number of threshold variables dependent on a variable $c$, corresponding to the experimental condition in which the participant finds herself (e.g.
 the range of possible responses available to $R$).
@@
 
-= “right” iff $S_1$(u | s) $>$ $\theta_1$
-
-= “neither” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
-
-= “wrong” otherwise
-
-Given c = “quaternary”
+= “Right” iff $S_1$(u | s) $>$ $\theta_1$
+
+= “Neither” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “Wrong” otherwise
+
+Given c = “quatenary”
 
@@
 
-= “right” iff $S_1$(u | s) $>$ $\theta_1$
-
-= “kinda right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
-
-= “kinda wrong” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
-
-= “wrong” otherwise
+= “Right” iff $S_1$(u | s) $>$ $\theta_1$
+
+= “Kinda Right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “Kinda Wrong” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
+
+= “Wrong” otherwise
 
@@
 
-= “right” iff $S_1$(u | s) $>$ $\theta_1$
-
-=“kinda right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
-
-= “neither” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
-
-= “kinda wrong” iff $\theta_3$ $>$ $S_1$(u | s) $>$ $\theta_4$
-
-= “wrong” otherwise
+= “Right” iff $S_1$(u | s) $>$ $\theta_1$
+
+=“Kinda Right” iff $\theta_1$ $>$ $S_1$(u | s) $>$ $\theta_2$
+
+= “Neither” iff $\theta_2$ $>$ $S_1$(u | s) $>$ $\theta_3$
+
+= “Kinda Wrong” iff $\theta_3$ $>$ $S_1$(u | s) $>$ $\theta_4$
+
+= “Wrong” otherwise
 
 The above analysis is a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
-**JD: Brandon, I feel what's still missing here is a demonstration that this is a _reasonable_ linking function.
-Maybe we can add the point that with this linking function, there's nothing inherently special about the implicature conditions -- the same linking function can work for any of the eight conditions in our experiment, because they're all the result of a participant having to make a behavioral choice in the face of an underlying speaker probability.**
-
-However, this way of understanding behavior in truth value judgment tasks also raises new analytic and empirical questions which we must leave to future work.
-For instance, given the experimental results reported here, what is the range of plausible values for, e.g., the single probability threshold $\theta$, which separates "right" from "wrong" utterances in the binary condition?
-Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e., the actual rate of response of "right" on each trial of the binary condition of the experiment.
-We may also ask, for example, whether the speaker probability threshold for an utterance being "right" is relatively constant across conditions or changes systematically with the introduction of more response options.
-Again, Bayesian data analysis allows us to explore this question by investigating the extent to which the inferred posterior distribution of, e.g., possible values of the threshold for "right" in the binary condition of the experiment differs from the inferred posterior distribution of possible values of the threshold for "right" in the ternary, quatenary, and quinary conditions.
+
+**XXX The following is entirely new:** However, this way of understanding behaivor in truth value jugdment tasks also raises new analytic and empirical questions which we must leave to future work.
+For instance, given the experimental results reported here, what is the range of plausible values for, e.g., the single probability threshold $\theta$, which separates "Right" from "Wrong" utterances in the binary condition?
+Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e.
+the actual rate of response of "Right" On each trial of the binary condition of the experiment.
+We may also ask, for example, whether the speaker probability threshold for an utterance being "Right" is relatively constant across conditions or changes systematically with the introduction of more response options.
+Again, Bayesian data analysis allows us to explore this question by investigating the extent to which the inferred posterior distribution of, e.g., possible values of the threshold for "Right" in the binary condition of the experiment differs from the inferred posterior distribution of possible values of the threshold for "Right" in the ternary, quatenary, and quinary conditions.
 
@@
 
-**JD: We need a final concluding paragraph that reiterates the main points.**
-
 # References

### 2018-05-09 writeup.tex
addressed comments

--- 2018-05-02 writeup.tex
@@
             pdfauthor={},
-            pdftitle={The effect of linking assumptions and number of response options on inferred scalar implicature rate},
+            pdftitle={Linking assumptions and number of response options modulate inferred scalar implicature rate},
             colorlinks=true,
@@
 % Essential manuscript parts
-  \title{The effect of linking assumptions and number of response options on
-inferred scalar implicature rate}
+  \title{Linking assumptions and number of response options modulate inferred
+scalar implicature rate}
 
@@
 virtue of a speaker producing the weaker of two ordered scalemates
-(hornXXX; {\textbf{???}}, {\textbf{???}}; Grice, 1975). Examples are
-provided in (1) and (2).
+(Geurts, 2010; Grice, 1975; Hirschberg, 1985; Horn, 1972). Examples are
+provided in (1-2).
 
@@
 
-A listener, upon observing the utterances in (1a) and (2a), typically
-infers that the speaker intended to convey the meanings in (1b) and
-(2b), respectively. Since Grice (1975), the agreed-upon abstract
+A listener, upon observing the utterances in (1-2a) typically infers
+that the speaker intended to convey the meanings in (1-2b),
+respectively. Since Grice (1975), the agreed-upon abstract
 rationalization the listener could give for their inference goes
@@
 statement by producing the stronger alternative (e.g., \emph{All of her
-pets are cats.}). If the stronger alternative is true, they should have
-produced it to comply with the Cooperative Principle. They chose not to.
-I believe the speaker knows whether the stronger alternative is true.
-Hence, it must not be true.
+pets are cats.} in (1)). If the stronger alternative is true, they
+should have produced it to comply with the Cooperative Principle. They
+chose not to. I believe the speaker knows whether the stronger
+alternative is true. Hence, it must not be true. The derivation
+procedure for ad hoc exhaustive inferences such as in (3) is assumed to
+be calculable in the same way as for scalar implicatures, though the
+scale is assumed to be contextually driven.
 
@@
   computed automatically in online processing and only cancelled by
-  context in a second effortful step if required by context) {[}Bott and
-  Noveck (2004);Breheny et al. (2006);Degen and Tanenhaus (2016);Grodner
-  et al. (2010);Huang and Snedeker (2009);Politzer-Ahles and Fiorentino
-  (2013);Tomlinson2013{]}?
+  context in a second effortful step if required by context) (Bott \&
+  Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
+  et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
+  2013; Tomlinson, Bailey, \& Bott, 2013)?
 \item
   What are the (linguistic and extra-linguistic) factors that affect
-  whether a scalar implicature is derived {[}Zondervan (2010);Degen and
-  Tanenhaus (2015); Degen and Tanenhaus (2016); Degen (2015); Degen and
-  Goodman (2014); Bergen and Grodner (2012); Breheny et al. (2006);
-  Breheny, Ferguson, and Katsos (2013);Marneffe and Tonhauser (2016);De
-  Neys and Schaeken (2007);Bonnefon, Feeney, and Villejoubert
-  (2009);Chemla2011;Potts2015{]}?
+  whether a scalar implicature is derived (Bergen \& Grodner, 2012;
+  Bonnefon, Feeney, \& Villejoubert, 2009; Breheny, Ferguson, \& Katsos,
+  2013; Breheny et al., 2006; Chemla \& Spector, 2011; De Neys \&
+  Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014; Degen \&
+  Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts, Lassiter,
+  Levy, \& Frank, 2015; Zondervan, 2010)?
 \item
@@
   At what age do children acquire the ability to compute implicatures
-  (Barner, Brooks, \& Bale, 2011; Katsos \& Bishop, 2011; Frank;
-  Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou, 2004)?
+  (Barner, Brooks, \& Bale, 2011; Horowitz, Schneider, \& Frank, 2017;
+  Katsos \& Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \&
+  Tantalou, 2004; Stiller, Goodman, \& Frank, 2015)?
 \end{enumerate}
@@
 In addressing all of these questions, it has been crucial to obtain
-estimates of \textbf{implicature rates}. For 1., implicature rates from
+estimates of \emph{implicature rates}. For 1., implicature rates from
 experimental tasks can be taken to inform whether scalar implicatures
@@
 studies is the proportion of \enquote{pragmatic} judgments in
-truth-value judgment paradigms {[}Bott and Noveck (2004);Noveck
-(2001);Noveck and Posada (2003);Chemla and Spector (2011);Geurts and
-Pouscoulous (2009);Degen and Tanenhaus (2015);De Neys and Schaeken
-(2007);Degen2014{]}. In these kinds of tasks, participants are provided
-a set of facts, either presented visually or via their own knowledge of
-the world. They are then asked to judge whether a sentence intended to
+truth-value judgment paradigms (Bott \& Noveck, 2004; Chemla \& Spector,
+2011; De Neys \& Schaeken, 2007; Degen \& Goodman, 2014; Degen \&
+Tanenhaus, 2015; Geurts \& Pouscoulous, 2009; Noveck, 2001; Noveck \&
+Posada, 2003). In these kinds of tasks, participants are provided a set
+of facts, either presented visually or via their own knowledge of the
+world. They are then asked to judge whether a sentence intended to
 describe those facts is true or false (or alternatively, whether it is
@@
 captured by the proportion of FALSE responses in truth-value judgment
-tasks (but see ({\textbf{???}}); Geurts and Pouscoulous (2009); Degen
-and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
+tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
+Degen and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
 implicature acquisition literature was shaken up when Katsos and Bishop
@@
 children started looking much more pragmatic than had been previously
-observed in a binary judgment paradigm. ({\textbf{???}}) allowed
+observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
 children to distribute 1, 2, or 3 strawberries to a puppet depending on
@@
 
-But this raises an important question: in truth-value judgment task, how
-do we know whether an interpretation is literal or the result of an
-implicature computation? The binary choice task typically used is
-appealing in part because it allows for a direct mapping from response
-options -- TRUE and FALSE -- to interpretations -- literal and
+But this raises an important question: in truth-value judgment tasks,
+how does the researcher know whether an interpretation is literal or the
+result of an implicature computation? The binary choice task typically
+used is appealing in part because it allows for a direct mapping from
+response options -- TRUE and FALSE -- to interpretations -- literal and
 pragmatic. That the seeming simplicity of this mapping is illusory
@@
 option with the negative endpoint of the scale for the purpose of
-categorizing judgments as literal vs.~pragmatic. But it seems just as
-plausible that they could have grouped it with the positive endpoint of
-the scale and taken the hard line that only truly FALSE responses
-constitute a full-fledged implicature. The point here is that there has
-been remarkably little consideration of \textbf{linking functions}
-between behavioral measures and theoretical constructs in experimental
-pragmatics, a problem in many subfields of psycholinguistics
-({\textbf{???}}). We argue that it is time to engage more seriously with
-these issues.
+categorizing judgments as literal vs.~pragmatic, i.e., they interpreted
+the intermediate option as pragmatic. But it seems just as plausible
+that they could have grouped it with the positive endpoint of the scale
+and taken the hard line that only truly FALSE responses constitute
+evidence of a full-fledged implicature. The point here is that there has
+been remarkably little consideration of \emph{linking functions} between
+behavioral measures and theoretical constructs in experimental
+pragmatics, a problem in many subfields of psycholinguistics (Tanenhaus,
+2004). We argue that it is time to engage more seriously with these
+issues.
 
@@
 truth-value judgment task, the behavioral measure can be interpreted as
-providing a measure of \textbf{interpretation}. And second, that
-listeners either do or do not compute an implicature on any given
-occasion. In the Discussion we will discuss both of these issues. First,
+providing a measure of \emph{interpretation}. And second, that listeners
+either do or do not compute an implicature on any given occasion. In the
+General Discussion we will discuss both of these issues. First,
 following Degen and Goodman (2014), we will offer some remarks on why
 truth-value judgment tasks are better thought of as measuring
-participants' estimates of speakers' \textbf{production} probabilities.
+participants' estimates of speakers' \emph{production} probabilities.
 This will suggest a completely different class of linking functions. And
@@
 probabilistic phenomeonen, a view that has recently rose to prominence
-in the subfield of probabilistic pragmatics. This alternative conception
-of scalar implicature, we argue, affords developing and testing
-quantitative linking functions in a rigorous and motivated way.
+in the subfield of probabilistic pragmatics (Franke \& Jäger, 2016;
+Goodman \& Frank, 2016). This alternative conception of scalar
+implicature, we argue, affords developing and testing quantitative
+linking functions in a rigorous and motivated way.
 
 Consider a setup in which a listener is presented a card with a
-depiction of either one or two animals (see the figure below for an
-example). As in a standard truth-value judgment task, the listener then
-observes an underinformative utterance about this card (e.g.,
-\enquote{There is a cat or a dog on the card}) and is asked to provide a
-judgment on a scale from 2 to 5 response options, with endpoints
-\enquote{wrong} and \enquote{right}. In the binary case, this reproduces
-the standard truth-value judgment task. \textbf{XXX say briefly sth
-about wrong/right vs true/false and agree/disagree}. The figure below
+depiction of either one or two animals (see Figure
+\ref{fig:linkvisualization} for an example). As in a standard
+truth-value judgment task, the listener then observes an
+underinformative utterance about this card (e.g., \enquote{There is a
+cat or a dog on the card}) and is asked to provide a judgment on a scale
+with 2, 3, 4, or 5 response options, with endpoints \enquote{wrong} and
+\enquote{right.}\footnote{An open question concerns the extent to which
+  the labeling of points on the scale affects judgments (e.g.,
+  \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
+  vs. \enquote{disagree}--\enquote{agree}). While some studies have used
+  \enquote{false}--\enquote{true}, others have argued that judging truth
+  may lead to meta-linguistic reasoning in participants that could
+  distort judgments.} In the binary case, this reproduces the standard
+truth-value judgment task. Figure \ref{fig:linkvisualization}
 exemplifies (some of) the researcher's options for grouping responses.
@@
 Under the Strong link, we would conclude that scalar implicatures are
-not defaults. Under the Weak link, we would conclude that they are.
-
-In the experiment reported in the following section, we presented
-participants with exactly this setup. Different groups of participants
-were presented with different numbers of response options. We
-categorized their responses according to the Weak and the Strong link
-and tested whether number of response options and categorization scheme
-leads to different conclusions about implicature rates.
+not defaults. Under the Weak link, we would conclude that they are. In
+the experiment reported in the following section, we presented
+participants with exactly this setup. We manipulated the number of
+response options between participants and analyzed the results under
+different linking assumptions.
 
@@
 
+Participants played an online card game in which they were asked to
+judge descriptions of the contents of cards. Different groups of
+participants were presented with different numbers of response options.
+On critical trials, participants were presented with descriptions for
+the cards that typically result in exhaustivity implicatures
+(\enquote{There is a cat on the card} when there was a cat and a dog) or
+scalar implicatures (\enquote{There is a cat or a dog on the card} when
+there was a cat and a dog). We categorized their responses on such
+trials according to the weak and the strong link introduced above, and
+tested whether the number of response options and the linking
+assumptions led to different conclusions about the rate of computed
+implicatures in the experimental task.
+
 \subsection{Methods}\label{methods}
@@
 
-200 participants were recruited using Amazon Mechanical Turk (binary=50,
-ternary53, quaternary=43, quinary=54). No participant was excluded from
+200 participants were recruited via Amazon Mechanical Turk. They
+optionally provided demographic information at the end of the study.
+Participants' mean age was 35. We also asked participants if they had
+any prior training in logic. 40 participants reported that they did,
+while 160 had no prior training in logic. \textbf{JD: Do we do any
+analysis of logic training???} All participants' data was included in
 the final analysis.
 
-\subsubsection{Procedure}\label{procedure}
-
-The study was administered online through Amazon Mechanical Turk.
-Participants were introduced to a set of cards with pictures of one or
-two animals (Figure \ref{fig:stimuli}). They were told that a
-blindfolded fictional character called Bob is going to guess what
-animals are on the card. On each trial, participants saw a card as well
-as a sentence representing Bob's guess. For example, they saw a card
-with a cat on it and read the sentence \enquote{There is a cat on the
-card.} The study ended after 24 trials. At the end participants
-optionally provided demographic information. We also asked participants
-if they had any prior training in logic. You can access and view on the
-study's \href{https://github.com/thegricean/si-paradigms/}{online
-repository}.
-
-\subsubsection{Design and Materials}\label{design-and-materials}
+\subsubsection{Materials and procedure}\label{materials-and-procedure}
+
+The study was administered online through Amazon Mechanical
+Turk.\footnote{The experiment can be viewed
+  \href{https://cdn.rawgit.com/thegricean/si-paradigms/94a590f0/experiments/main/1_methods/online_experiment/connective_game.html}{here}.}
+Participants were first introduced to the set of cards we used in the
+study (Figure \ref{fig:stimuli}). Each card depicted one or two animals,
+where an animal could be either a cat, a dog, or an elephant. Then
+participants were introduced to a blindfolded fictional character called
+Bob. Bob was blindfolded to avoid violations of ignorance expectations
+associated with the use of disjunction ({\textbf{???}}; Chierchia et
+al., 2001) \textbf{JD: Masoud, can you insert citation pls? Geurts,
+Sauerland?}. Participants were told that Bob would guess the contents of
+the cards and their task was to indicate whether Bob's guess was wrong
+or right. On each trial, participants saw a card and a sentence
+representing Bob's guess. For example, they saw a card with a cat and
+read the sentence \enquote{There is a cat on the card.} They then
+provided an assessment of Bob's guess. The study ended after 24 trials.
 
@@
 
-The study had two main manipulaitons within participants: the type of
-card and the type of guess. There were two types of cards. Cards with
-only one animal on them and cards with two animals. Animals were chosen
-from the following set: cat, dog, and elephant There were three types of
-guesses: simple (e.g. \emph{There is a cat}), conjunctive (e.g.
-\emph{There is a cat and a dog}), and disjunctive (e.g. \emph{There is a
-cat or a dog}). In each trial, the animal labels used in the guess and
-the animal images on the card may have no overlap (e.g.~Image: cat,
-Guess: \emph{There is an elephant}), a partial overlap (e.g.~Image: cat,
-Guess: \emph{There is a cat or a dog}), or a total overlap (e.g.~Image:
-cat and dog, Guess: \emph{There is a cat or a dog}). Crossing the number
-of animals on the card, the type of guess, and the overlap between the
-guess and the card results in 12 different possible trial types. We
-chose 8 trial types (Figure \ref{fig:trials}), balancing the number of
-one-animal vs.~two-animal cards, simple vs.~connective guesses, and
-expected true vs.~false trials. Three trials were randomly selected from
-each of the 8 trial-types, for a total of 24 trials. The order of these
-24 trials was randomized as well.
-
-Participants could derive implicatures in two trial types. First, the
-trial type in which two animals were present on the card (e.g.~cat and
-dog) but Bob guessed only one of them (e.g. \enquote{there is a cat}).
-Such trials can have a literal interpretation (cat and possibly more) or
-an exhaustive interpretation (only cat). We refer to them as
-\enquote{exhaustive}. The second trial type with implicatures was the
-one in which two animals were on the card (e.g.~cat and dog) and Bob
-used a disjunciton (e.g.~cat or dog). These trials can have a literal
-(inclusive) interpretation (e.g.~cat or dog or both), or an exclusive
-interpretation (e.g.~cat or dog, not both). We refer to these trials as
-\enquote{scalar}. The following four trial types were used as
-experimental control: two trial types where there was no overlap between
-the guess (e.g.~elephant) and the animal(s) on the card (e.g.~cat, cat
-and dog); and two trial types where the animal(s) on the card were
-correctly guessed. For example, if there was only a cat on the card, Bob
-said \enquote{there is a cat} and if there was a cat and a dog, Bob said
-\enquote{there is a cat and a dog}. Since the fictional character was
-blindfolded and did not see the outcome of the game, the ignorance
-inference commonly associated with disjunction was already common ground
-in the experimental setting. If the character was seeing the cards or
-knew what was on them, a disjunction would have violated the expectation
-that the speaker does not know which alternative actually holds. Our
-study controls for the possibile effect of ignorance violations on
-exclusivity and exhaustive inferences.
-
-The study also had a between participant manipulation of the number of
-response options in the forced choice task. Participants were randomly
-assigned to one of four different conditions. The conditions differed
-with respect to the number of response options: binary (wrong
-vs.~right), ternary (wrong, neither, right), quaternary (wrong, kinda
-wrong, kinda right, right), and quinary (wrong, kinda wrong, neither,
-kinda right, right). We wanted to see if the number of response options
-in the forced choice task would affect our estimate of the task's
-\enquote{implicature rate}.
+Two factors were manipulated within participants: card type and guess
+type. There were two types of cards, cards with only one animal on them
+and cards with two animals. There were three types of guesses: simple
+(e.g. \emph{There is a cat}), conjunctive (e.g. \emph{There is a cat and
+a dog}), and disjunctive (e.g. \emph{There is a cat or a dog}). Crossing
+card type and guess type yielded trials of varying theoretical interest
+(see Figure \ref{fig:trials}): critical underinformative trials that
+were likely to elicit pragmatic inferences (either scalar or exhaustive)
+and control trials that were either unambiguously true or false. Each
+trial type occurred three times with randomly sampled animals and
+utterances that satisfied the constraint of the trial type. Trial order
+was randomized.
 
@@
 \includegraphics{writeup_files/figure-latex/trials-1.pdf}
-\caption{\label{fig:trials}Trial types represented by example cards and
-guesses.}
+\caption{\label{fig:trials}Trial types (critical and control). Headers
+indicate utterance types. Rows indicate card types. Critical trials are
+marked in bold.}
 \end{figure}
 
+On critical trials, participants could derive implicatures in two ways.
+First, on trials on which two animals were present on the card (e.g.,
+cat and dog) but Bob guessed only one of them (e.g. \enquote{There is a
+cat on the card}), the utterance could have a literal interpretation
+(\enquote{There is a cat and possibly another animal on the card}) or an
+exhaustive interpretation (\enquote{There is only a cat on the card}).
+We refer to these trials as \enquote{exhaustive}. Second, on trials on
+which two animals were on the card (e.g., a cat and a dog) and Bob used
+a disjunciton (e.g., \enquote{There is a cat or a dog on the card}), the
+utterance could have the literal, inclusive, interpretation, or a
+pragmatic, exclusive interpretation. We refer to these trials as
+\enquote{scalar}.
+
+In order to assess the effect of the number of response options on
+implicature rate, we manipulated number of response options in the
+forced choice task between participants. We refer to the choice
+conditions as \enquote{binary} (options: \emph{wrong}, \emph{right}),
+\enquote{ternary} (options: \emph{wrong}, \emph{neither}, \emph{right}),
+\enquote{quaternary} (options: \emph{wrong}, \emph{kinda wrong},
+\emph{kinda right}, \emph{right}), and \enquote{quinary} (\emph{wrong},
+\emph{kinda wrong}, \emph{neither}, \emph{kinda right}, \emph{right}).
+Thus, the endpoint labels always remained the same. If there was an
+uneven number of response options, the central option was
+\emph{neither}. Participants were randomly assigned to one of the four
+task conditions.
+
 \subsection{Results}\label{results}
+
+The collected dataset contains 50 participants in the binary task, 53 in
+the ternary task, 43 in the quaternary task, and 54 in the quinary task.
+Figures \ref{fig:binaryPlot} to \ref{fig:quinaryPlot} show the
+proportions of response choices in each of the 8 trial types on each of
+the four response tasks, respectively. We report the relevant patterns
+of results qualitatively before turning to the quantitative analysis of
+interest.
+
+\subsubsection{Qualitative analysis}\label{qualitative-analysis}
 
@@
 \includegraphics{writeup_files/figure-latex/binaryPlot-1.pdf}
-\caption{\label{fig:binaryPlot}Proportion responses for the two-alternative
-(binary) forced choice judgments in the guessing game.}
+\caption{\label{fig:binaryPlot}Proportion of responses for the binary forced
+choice judgments. Error bars indicate 95\% bootstrapped confidence
+intervals.}
 \end{figure}
 
-Here we present the proportion that participants chose the response
-options in each of the 8 trial types of the binary, ternary, quaternary,
-and quinary tasks. Figure \ref{fig:binaryPlot} shows the proportion of
-\enquote{right} and \enquote{wrong} responses in the binary task.
-Starting from the leftmost column, participants considered a guess
-\enquote{wrong} if the guessed animal was not on the card. Moving to the
-second column, participants considered a guess \enquote{right} if the
-animal on the card was mentioned. However, if only one of the two
-animals on the card was mentioned (exhaustive trials), 14\% of the times
-participants considered the guess \enquote{wrong}. Moving to the third
-column, if a conjunction of animals was guessed while only one animal
-was on the card, participants considered the guess to be
-\enquote{wrong}. If a conjunction of animals was guessed and both
-animals were present on the card, all participants considered the guess
-to be \enquote{right} as expected. Moving to the forth column, if a
-disjunction of animals was guessed and only one of the animals was on
-the card, participants considered the guess to be \enquote{right} almost
-all the time. However, if both animals were present (scalar trials),
-38\% of the times participants considered the guess to be
-\enquote{wrong}.
+In the binary task, participants were at or close to ceiling in
+responding \enquote{right} and \enquote{wrong} on unambiguously true and
+false trials, respectively (see Figure \ref{fig:binaryPlot}). However,
+on underinformative trials (\enquote{cat} and \enquote{cat or dog}
+description for card with cat and dog), we observe pragmatic behavior:
+on exhaustive trials, participants judged the utterance \enquote{wrong}
+14\% of the time; on scalar trials, participants judged the utterance
+\enquote{wrong} 38\% of the time. That is, both under the weak and the
+strong link assumptions introduced in the Introduction, inferred
+implicature rate on exhaustive trials is 14\% and on scalar trials 38\%.
 
@@
 \includegraphics{writeup_files/figure-latex/ternaryPlot-1.pdf}
-\caption{\label{fig:ternaryPlot}Proportion responses for the
-three-alternative (ternary) forced choice judgments in the guessing
-game.}
+\caption{\label{fig:ternaryPlot}Proportion of responses for the ternary
+forced choice judgments. Error bars indicate 95\% bootstrapped
+confidence intervals.}
 \end{figure}
 
-Figure \ref{fig:ternaryPlot} shows the proportion of \enquote{right},
-\enquote{neither}, and \enquote{wrong} responses in the ternary task.
-Similar to the binary task, participants considered a guess wrong when
-the mentioned animal was not on the card. They considered the guess
-\enquote{right} when the mentioned animal was on the card. However, in
-exhaustive trials when the fictional character only guessed one of the
-two animals on the card, participants considered the guess
+In the ternary task, participants were also at or close to ceiling in
+responding \enquote{right} and \enquote{wrong} on unambiguously true and
+false trials, respectively (see Figure \ref{fig:ternaryPlot}). And
+again, on underinformative trials (\enquote{cat} and \enquote{cat or
+dog} description for card with cat and dog), we observed pragmatic
+behavior: on exhaustive trials, participants considered the guess
 \enquote{wrong} 8\% of the time and neither wrong nor right 12\% of the
-time. If a conjunction of animals was guessed and only one animal was
-present on the card, participants considered the guess \enquote{wrong}.
-As expected, when a conjunction was used and both animals were present,
-participants considered the guess \enquote{right}. Similarly,
-participants considerd the guess \enquote{right} when a disjunction was
-used and only one of the animals was on the card. However, in scalar
-trials that both animals were on the card and a disjunction was
-gueassed, participants judged the guess \enquote{wrong} 23\% of the time
-and \enquote{neither} 11\% of the time.
+time. On scalar trials, participants judged the guess \enquote{wrong}
+23\% of the time and \enquote{neither} 11\% of the time. This means that
+the weak and strong link lead to different conclusions about implicature
+rates on the ternary task. Under the weak link, inferred implicature
+rate on exhaustive trials is 20\%; under the strong link it is only 8\%.
+Similarly, under the weak link, inferred implicature rate on scalar
+trials is 34\%; under the strong link it is only 23\%.
 
@@
 \includegraphics{writeup_files/figure-latex/quaternaryPlot-1.pdf}
-\caption{\label{fig:quaternaryPlot}Proportion responses for the
-four-alternative (quatenary) forced choice judgments in the guessing
-game.}
+\caption{\label{fig:quaternaryPlot}Proportion of responses for the
+quaternary forced choice judgments. Error bars indicate 95\%
+bootstrapped confidence intervals.}
 \end{figure}
 
-Figure \ref{fig:quaternaryPlot} shows the proportion of \enquote{right},
-\enquote{kinda right}, \enquote{kinda wrong}, and \enquote{wrong}
-responses in the quaternary task. Similar to the results seen
-previously, the control trials turned outas expected. Participants
-considered a guess \enquote{wrong} if the animal guessed was not on the
-card and \enquote{right} if it was the only animal on the card. If a
-conjunctin of animals was guessed and both animals were on the card the
-guess was \enquote{right}. However, when only one of the animals on the
-card was guessed (exhaustive trials), participants judged the guess
-\enquote{wrong} 2\% of the time, \enquote{kinda wrong} 5\% of the time,
-and \enquote{kinda right} 66\% of the times. Perhaps surprisingly, when
-a conjunction was used and only one of the animals was on the card,
-participants considered the guess \enquote{wrong} most of the time, but
-they often considered it \enquote{kinda wrong} or even \enquote{kinda
-right}. This suggests that perhaps participants considered a notion of
-partially true or correct statement in our experimental setting.
-Disjunctive guesses with one or two animals on the card showed similar
-response patterns with participants choosing the \enquote{kinda right}
-and \enquote{right} options most of the time. When both animals were on
-the card with a disjunctive guess (scalar trials), participants judged
-the guess \enquote{wrong} 6\% of the time, \enquote{kinda wrong} 12\% of
-the time, and \enquote{kinda right} 43\% of the times.
+In the quaternary task (Figure \ref{fig:quaternaryPlot}), participants
+were again at or close to ceiling in responding \enquote{right} and
+\enquote{wrong} on 4 of the 6 unambiguously true and false trials.
+However, with four response options, two of the control conditions
+appear to be showing signs of pragmatic infelicity: when a conjunction
+was used and only one of the animals was on the card, participants
+considered the guess \enquote{wrong} most of the time, but they often
+considered it \enquote{kinda wrong} or even \enquote{kinda right}. This
+suggests that perhaps participants considered a notion of partially true
+or correct statement in our experimental setting. Disjunctive
+descriptions of cards with only one animal, while previously at ceiling
+for \enquote{right} responses, were downgraded to only \enquote{kinda
+right} 26\% of the time, presumably because these utterances are also
+underinformative, though the degree of underinformativeness may be less
+egregious than on scalar trials.
+
+On underinformative exhaustive trials, we observed pragmatic behavior as
+before: participants judged the guess \enquote{wrong} 2\% of the time,
+\enquote{kinda wrong} 5\% of the time, and \enquote{kinda right} 66\% of
+the time. On scalar trials, participants judged the guess
+\enquote{wrong} 6\% of the time, \enquote{kinda wrong} 12\% of the time,
+and \enquote{kinda right} 43\% of the times.
+
+Thus, we are again forced to draw different conclusions about
+implicature rates depending on whether we assume the weak link or the
+strong link. Under the weak link, inferred implicature rate on
+exhaustive trials is 73\%; under the strong link it is only 2\%.
+Similarly, under the weak link, inferred implicature rate on scalar
+trials is 61\%; under the strong link it is only 6\%.
 
@@
 \includegraphics{writeup_files/figure-latex/quinaryPlot-1.pdf}
-\caption{\label{fig:quinaryPlot}Proportion responses for the
-five-alternative (quinary) forced choice judgments in the guessing
-game.}
+\caption{\label{fig:quinaryPlot}Proportion of responses for the quinary
+forced choice judgments. Error bars indicate 95\% bootstrapped
+confidence intervals.}
 \end{figure}
 
-Finally, Figure \ref{fig:quinaryPlot} shows the proportion of
-\enquote{right}, \enquote{kinda right}, \enquote{neither},
-\enquote{kinda wrong}, and \enquote{wrong} responses in the quinary
-task. Since the results for the control trials were identical to
-previous tasks, we do not repeat them here. In exhaustive trials where
-two animals were on the card and only one of them was guessed,
-participants chose \enquote{kinda right} the majority of times (72\%).
-Again perhaps surprisingly, when only one animal was on the card and the
-guess was a conjunction, responses were equally split among
-\enquote{wrong}, \enquote{kinda wrong}, and \enquote{kinda right}
-responses. With disjunctive guesses, partitipants were more likely to
-choose \enquote{right} and \enquote{kinda right} options. When only one
-animal was on the card, participants considered the disjunctive guess as
-\enquote{right} more often. When both animals were on the card (scalar
-trials), participants judged the disjunctive guess as \enquote{kinda
-right} 52\% of the time.
-
-Comparing the response patterns in binary to quinary tasks (Figures
-\ref{fig:binaryPlot} to \ref{fig:quinaryPlot}), we can observe that in
-implicature trials, participants are less likely to choose the endpoints
-of the scale (i.e. \enquote{wrong} and \enquote{right}) as they are
-given more intermediate options. This raises the possibilty that the
-strict \enquote{wrong/right} responses in the tasks with fewer options
-(binary and ternary) were not accurately reflecting participant
-judgments of implicature trials and pushed their judgments to the
-extreme ends. More generally, the data suggest that participant
-judgments in contexts that give rise to implicatures fall within the
-intermrediate level of the response scale and forced choice tasks with
-few options (especially binary tasks) may risk depicting judgments more
-extreme than they actually are.
-
-\subsection{Analysis}\label{analysis}
-
-Our primary goal in this study was to check whether the estimated
-\enquote{implicature rate} in the experimental task is affected by the
-linking assumption and the number of response options available in the
-task. Our analysis in this section focuses on these three elements. As
-mentioned before, two trial types were predicted to include pragmatic
-implicatures. First, trials where two animals were on the card but the
-fictional character guessed with a disjunction (scalar); for example
-\enquote{cat or dog} when the card has both a cat and a dog on it.
-Second, trials where there were two animals on the card but the
-character guessed only one (exhaustive); for example \enquote{cat} when
-the card had a cat and a dog on it. We called such trials
-\enquote{exhaustive}. In our assessment of implicature rate, we focus on
-these two trial types.
-
-We considered two linking assumptions. First we defined a weak (lenient)
-linking assumption in which any response lower than the maximum point on
-the scale (i.e. \enquote{right}) is considered evidence for implicature
-computation. Second, we defined a strong (strict) linking assumption
-that only considered the lowest point on the scale (i.e.
-\enquote{wrong}) as evidence for implicature computation. For each
-condition in our study (binary, ternary, quaternary, and quinary) and
-each implicature trial type (exhaustive and scalar), we computed a weak
-and a strong implicature rate. Figure \ref{fig:implicatureRatePlot}
-shows these computed rates.
-
-Comparing the strong and weak rows on Figure
-\ref{fig:implicatureRatePlot}, we see that a weak linking assumption
-tends to estimate higher implicature rates, especially in tasks with
-more response options. With a strong linking assumption, the binary and
-possibly ternary judgment tasks derive higher implicature rates than
-quaternary and quinary tasks. With a weak linking assumption, the
-pattern is reversed. Quaternary and quinary tasks estimate higher rates
-than binary and ternary tasks.
+Finally, Figure \ref{fig:quinaryPlot} shows the proportion of responses
+in the quinary task. Performance on the 4 pragmatically felicitous
+control trials was again at floor and ceiling, respectively. The 2
+control conditions that the quaternary task had revealed pragmatic
+infelicity in again displayed that pragmatic infelicity in the quinary
+task, suggesting that this is a robust type of pragmatic infelicity
+that, however, requires fine-grained enough response options to be
+detected experimentally.
+
+On underinformative exhaustive trials, we observed pragmatic behavior as
+before: participants judged the guess \enquote{wrong} 2\% of the time,
+\enquote{kinda wrong} 1 and 1\% of the time, \enquote{neither} 1 and 1\%
+of the time, and \enquote{kinda right} 72\% of the time. On scalar
+trials, participants judged the guess \enquote{wrong} 6\% of the time,
+\enquote{kinda wrong} 4\% of the time, \enquote{neither} 1\% of the
+time, and \enquote{kinda right} 52\% of the time.
+
+Thus, we would again draw different conclusions about implicature rates
+depending on whether we assume the weak link or the strong link. Under
+the weak link, inferred implicature rate on exhaustive trials is 76 and
+76\%; under the strong link it is only 2\%. Similarly, under the weak
+link, inferred implicature rate on scalar trials is 63\%; under the
+strong link it is only 6\%.
+
+\subsubsection{Quantitative analysis}\label{quantitative-analysis}
+
+Our primary goal in this study was to test whether the estimated
+implicature rate in the experimental task is affected by the linking
+assumption and the number of response options available to participants.
+To this end, we only analyzed the critical trials (exhaustive and
+scalar). In particular, we classified each data point from critical
+trials as constituting an implicature (1) or not (0) under the strong
+and weak link. Figure \ref{fig:implicatureRatePlot} shows the resulting
+implicature rates by condition and link.
+
+Visually, the weak link tends to result in greater estimates of
+implicature rates, especially in tasks with more response options. Under
+the strong link, this latter pattern is reversed: the binary and ternary
+judgment tasks result in greater estimates of implicature rates than
+with more response options.
 
@@
 \includegraphics{writeup_files/figure-latex/implicatureRatePlot-1.pdf}
-\caption{\label{fig:implicatureRatePlot}Implicature rate in exhaustive and
-scalar trials of the binary, ternary, quaternary, and quinary versions
-of the guessing game, computed once with a strong linking assumption and
-once with a weak linking assumption.}
+\caption{\label{fig:implicatureRatePlot}Inferred implicature rates on
+exhaustive and scalar trials as obtained with the binary, ternary,
+quaternary, and quinary response task. Columns indicate link from
+response to implicature rate (strong: proportion of \enquote{wrong
+judgments; weak: proportion of non-'right} judgments).}
 \end{figure}
 
-We test this hypothesis formally using a binomial mixed effects model
-with the fixed effect of response type and the random intercept for
-participants as well as random intercept and slope for
-
-All the analytical decisions described here were pre-registered and you
-can access them through the following link:
-\url{https://aspredicted.org/tq3sz.pdf}
-
-\begin{itemize}
-\tightlist
-\item
-  Was logical training a significant predictor of \enquote{implicature
-  rate}?
-\end{itemize}
-
-\section{Discussion}\label{discussion}
-
-Alternative Linking Hypothesis: * RSA: Response behavior across
-conditions (utterance-card combinations) and dependent measures can be
-predicted by a linking hypothesis that assumes that participants are
-behaving like soft-optimal RSA speakers and provide a particular
-response (eg TRUE) to an utterance u if the RSA speaker probability of u
-(given the card) is within a particular probability interval (eg, within
-the interval {[}theta, 1{]}).
-
-\begin{itemize}
-\tightlist
-\item
-  Differences between traditional approaches and RSA: 1. The traditional
-  linking hypotheses are based on a binary implicature/literal theory of
-  pragmatic reasoning but RSA gives a continuous measure of pragmatic
-  reasoning and allows for better predicting response behavior with
-  multiple options.
-\end{itemize}
-
-A simple visual inspection of our results suggests that any variant of
-the Traditional Linking Hypothesis will yield unsatisfying empirical
-coverage with regards to participants' behavior in truth value judgment
-tasks. Recall that according to this hypothesis, scalar implicature is
-conceptualized as a binary, categorical affair: an implicature is either
-\enquote{calculated,} or it isn't. This assumption has implications for
-how we approach analysis of variation in behavior on a truth value
-judgment task; for example, why did the majority of respondents in the
-binary condition of our experiment answer \enquote{Right} to an
-utterance of cat or dog when the card had a cat and a dog on it?
-
-On the Traditional story, we are forced to say that a) not all
-participants calculated the implicature; or that b) some participants
-who calculated the implicature did not choose the anticipated response
-(i.e. \enquote{Wrong}) due to some other cognitive reflex which
-\enquote{overrode} the implicature; or some mixture of (b) and (c). We
-might similarly posit that one or both of these factors underlie the
-variation in the ternary, quatenary, and quinary conditions (e.g.~why
-were participants roughly split between \enquote{Right} and
-\enquote{Kind of right} when the utterance was cat or dog and the card
-had a cat and a dog?). There is an established cottage industry of
-pragmatics research which approaches the problem of behavioral variation
-in exactly these ways, exploring the factors which \enquote{license}
-implicature calculation or \enquote{suppress} its anticipated behavioral
-expression (c.f. \_\_), but the best we can hope for on this approach is
-an analysis which traces the general qualitative patterns in the data
-(and we should stress that even in this respect, the industry has yet to
-fully deliver the goods!).
-
-The Alternative Linking Hypothesis contrasts with the Traditional
-Linking Hypothesis in that the former is rooted in a quantitative
-formalization of pragmatic competence which provides us a continuous
-measure of pragmatic reasoning. {[}recap RSA model here? Maybe show how
-it gets the right basic qualitative pattern, i.e. \(P_L\)(a and
-b\textbar{} \enquote{a or b}) \(<\) \(P_L\)(a \textbar{} \enquote{or});
-\(P_L\)(a and b\textbar{} \enquote{a or b}) \(<\) \(P_L\)(b \textbar{}
-\enquote{or}) {]}
-
-Following Degen \& Goodman (2014), we proceed on the assumption that
-behavior on sentence verification tasks, such as truth value judgment
-tasks, is best modeled as a function of an individual's mental
-representation of a cooperative interlocutor (\(S_1\) in the language of
-RSA). For a given utterance u and an intended communicated meaning w,
-\(S_1\)(u \textbar{} w) outputs a conditional probability of u given w.
-For example, in the binary condition of our experiment where a
-participant evaluated cat or dog when there were both animals on the
-card, the participant has access to the mental representation of \(S_1\)
-and hence to the \(S_1\) conditional probability of hearing the
-utterance cat or dog given a dog and cat card \(S_1\)(cat or dog
-\textbar{} cat and dog).
-
-One desideratum of a linking hypothesis given this view of pragmatic
-competence is to transform this probability value into a categorical
-output (e.g. \enquote{Right}/''Wrong'' in the case of the binary
-condition). This can be achieved by positing that participants
-\enquote{filter out} low-probability utterances given an intended
-communicated meaning. We model a responder, R, who in the binary
-condition responds \enquote{Right} to an utterance u in world w just in
-case \(S_1\)(u \textbar{} w) exceeds some probability threshold
+\begin{table}
+
+\caption{\label{tab:implicatureRate}\label{tab:modeltable}Model parameter estimates and their credible intervals.
+Rows marked with an asterisk in the evidence column do not contain 0 in the credible interval, thereby providing evidence for an effect.}
+\centering
+\begin{tabular}[t]{lrrrl}
+\toprule
+Predictors & Estimate & 2.5\% & 97.5\% & Evidence\\
+\midrule
+Intercept & -8.60 & -13.98 & -4.53 & *\\
+Link = Weak & -0.15 & -4.86 & 4.77 & \\
+Task = Quaternary & -1.83 & -8.08 & 4.20 & \\
+Task = Quinary & -4.05 & -10.90 & 2.38 & \\
+Task = Ternary & -1.45 & -7.31 & 4.56 & \\
+\addlinespace
+Implicature = Scalar & 6.09 & 1.00 & 12.29 & *\\
+Link = Weak : Task = Quaternary & 14.03 & 7.24 & 21.88 & *\\
+Link = Weak : Task = Quinary & 17.28 & 10.64 & 25.80 & *\\
+Link = Weak : Task = Ternary & 3.81 & -1.49 & 9.22 & \\
+Link = Weak : Implicature = Scalar & 0.90 & -4.01 & 6.43 & \\
+\addlinespace
+Task = Quaternary : Implicature = Scalar & -5.67 & -13.66 & 1.54 & \\
+Task = Quinary : Implicature = Scalar & -2.31 & -9.30 & 4.61 & \\
+Task = Ternary : Implicature = Scalar & -1.31 & -7.70 & 4.65 & \\
+Link=Weak : Task=Quaternary : Implicature=Scalar & -3.29 & -12.07 & 4.55 & \\
+Link=Weak : Task=Quinary : Implicature=Scalar & -7.74 & -16.59 & -0.16 & *\\
+Link=Weak : Task=Ternary : Implicature=Scalar & -1.44 & -7.00 & 4.22 & \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+To analyze the effect of link and response options on inferred
+implicature rate, we used a Bayesian binomial mixed effects model using
+the R packge \enquote{brms} (Bürkner \& others, 2016) with uninformative
+or weakly informative priors.\footnote{You can access our
+  pre-registration at \url{https://aspredicted.org/tq3sz.pdf}} The model
+predicted the log odds of implicature over no implicature from fixed
+effects of \emph{response type} (binary, ternary, quaternary, quinary --
+dummy-coded with binary as reference level), \emph{link} (strong
+vs.~weak -- dummy-coded with strong as reference level), and trial type
+(exhaustive vs.~scalar -- dummy-coded, with exhaustive as reference
+level), as well as their two-way and three-way interactions. Following
+Barr, Levy, Scheepers, and Tily (2013), we included the maximal random
+effects structure justified by the design: random intercepts for items
+(cards) and participants, random by-participant slopes for link, trial
+type, and their interaction, and random by-item slopes for link, trial
+type, response type, and their interactions. Since the number of
+response options was a between participant variable we did not include
+random slopes of response options for participants. Four chains
+converged after 2000 iterations each (warmup = 1000). Table
+\ref{tab:modeltable} summarizes the mean parameter estimates and their
+95\% credible intervals. \(\hat{R}=1\) for all estimated parameters. All
+the analytical decisions described here were pre-registered\footnote{You
+  can access our pre-registration at
+  \url{https://aspredicted.org/tq3sz.pdf}}.
+
+{[}\^{}3: To know more about the default priors of the \enquote{brms}
+package you can refer to
+\href{ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf}{the
+brms package manual}.{]}
+
+The model provided evidence for the following effects: First, there was
+a main effect of trial type such that scalar trials resulted in greater
+implicature rates than exhaustive trials (Mean Estimate = 6.09, 95\%
+Credible Interval={[}1, 12.29{]}). Second, there was an interaction
+between link and number of response options such that the quaternary
+task (Mean Estimate = 14.03, 95\% Credible Interval={[}7.24, 21.88{]})
+and the quinary task (Mean Estimate = 17.28, 95\% Credible
+Interval={[}10.64, 25.80{]}) with a weak link resulted in greater
+implicature rates. Finally, there was a three-way interaction between
+link, trial type, and number of response options (Mean Estimate = -7.74,
+95\% Credible Interval={[}-16.59, -0.16{]}). One interpretation of this
+interaction is that the difference between the weak and strong link on
+scalar trials in the quinary task was smaller than on exhaustive trials,
+though we believe this is not too interesting, given that the binary
+reference level implicature estimate was lower for exhaustive trials in
+the first place. Crucially, both number of response options and link
+affect the inferred implicature rate.
+
+\subsection{Discussion}\label{discussion}
+
+We asked whether the linking assumptions and the number of response
+options available to participants affects the inferred implicature rate
+in an experimental study. The results presented here suggest they do. A
+linking assupmtion that considered the highest point on the scale as
+literal and any lower point as pragmatic (weak link) resulted in higher
+implicature rates in tasks with 4 or 5 response options. A linking
+assumption that considered the lowest point on the scale as pragmatic
+and any higher point as literal (strong link) reported lower implicature
+rates in tasks with 4 or 5 options. The results suggest that the choice
+of linking assumption is a crucial analytical step that can
+significantly impact the conclusions drawn from truth value judgment
+tasks. In particular, there is danger for pragmatic ability to be both
+under- and overestimated.
+
+While the binary truth value judgement task avoids the analytic decision
+between strong and weak linking assumptions, the results reported here
+suggest that binary tasks can also underestimate participants' pragmatic
+competence. In binary tasks, participants are often given the lowest and
+highest points on a scale (\enquote{wrong} vs. \enquote{right}) and are
+asked to report pragmatic infelicities using the lowest point (e.g.
+\enquote{wrong}). The study reported here showed that on trials with
+true but pragmatically infelicitous descriptions, participants often
+avoided the lowest point on the scale if they were given more
+intermediate options. Even though the option \enquote{wrong} was
+available to participants in all tasks, participants in tasks with
+intermediate options chose it less often. In computing implicature rate,
+this pattern manifested itself as a decrease in implicature rate under
+the strong link when more response options were provided, and an
+increase in implicature rate under the weak link when more response
+options were provided. These conclusions are in line with Katsos and
+Bishop (2011)\enquote{s argument that pragmatic violations are not as
+severe as semantic violations and participants do not penalize them as
+much. Providing participants with only the extreme ends of the scale
+(e.g.~wrong/right, false/true) when pragmatic violations are considered
+to be of an intermediate nature risks misrepresentation of participants}
+pragmatic competence. It further suggests that in studies that use
+binary tasks to investigate response-contingent processing, proportions
+of \enquote{literal} responses may be a composite of both literal and
+pragmatic underlying interpretations that just happen to get mapped
+differently onto different response options by participants.
+
+This study did not investigate the effect of option labels on the
+inferred implicature rate. However, the results provided suggestive
+evidence that some options better capture participant intuitions of
+pragmatic infelicities than others. Among the intermediate options,
+\enquote{kinda right} was chosen most often to report pragmatic
+infelicities. The option \enquote{neither} was rarely used in the
+ternary and quinary tasks (where it was used as a midpoint), suggesting
+that participants interpreted pragmatic infelicities as different
+degrees of being \enquote{right} and not \enquote{neither right nor
+wrong.} Therefore, options that capture degrees of being \enquote{right}
+like \enquote{kinda right} may prove most suitable for capturing
+infelicity in the long run. We leave this as a methodological issue for
+future research.
+
+The study had three further design features worth investigating in
+future work. First, the utterances were ostensibly produced by a
+blindfolded character. This was an intentional decision to control for
+violation of ignorance expectations with disjunction. A disjunction such
+as \enquote{A or B} often carries an implication or expectation that the
+speaker is not certain which alternative actually holds. Future work
+should investigate how the violation of the ignorance expectation
+interacts with link and number of response options in inferred
+implicature rate. Second, in this study we considered exhaustive and
+scalar implicatures with \emph{or}. If the observed effects of link and
+number of response options hold in general, they should be observable
+using other scales, e.g., on implicatures with \emph{some}. Finally, our
+experiment was designed as a guessing game and the exact goal or
+task-relevant Question Under Discussion of the game was left implicit.
+Given the past literature on QUD effects on scalar implicature, we
+expect that different goals -- e.g., to help the character win more
+points vs.~to help the character be more accurate -- would affect how
+strict or lenient participants are with their judgments and ultimately
+affect implicature rate in the task (Degen \& Goodman, 2014; Zondervan,
+2010). Future work should systematically vary the goal of the game and
+explore its effects on the inferred implicature rate.
+
+\section{General Discussion}\label{general-discussion}
+
+On the traditional view of the link between implicature and behavior in
+sentence verification tasks, scalar implicature is conceptualized as a
+binary, categorical affair - that is, an implicature is either
+\enquote{calculated} or it isn't, and the behavioral reflexes of this
+categorical interpretation process should be straightforwardly observed
+in experimental paradigms. This assumption raises concerns for analyzing
+variation in behavior on a truth value judgment task; for example, why
+did the majority of respondents in the binary condition of our
+experiment answer \enquote{Right} to an utterance of the
+underinformative \enquote{There is a cat or dog} when the card had both
+a cat and a dog on it? And why did a sizeable minority nonetheless
+choose \enquote{Wrong} in this same condition?
+
+To explain these data on the traditional view, we are forced to say that
+a) not all participants calculated the implicature; or that b) some
+participants who calculated the implicature did not choose the
+anticipated (i.e., \enquote{Wrong}) response due to some other cognitive
+process which overrode the \enquote{correct} implicature behavior; or
+some mixture of (a) and (b). We might similarly posit that one or both
+of these factors underlie the variation in the ternary, quaternary, and
+quinary conditions. However, without an understanding of how to
+quantitatively specify the link between implicature calculation and its
+behavioral expression, the best we can hope for on this approach is an
+analysis which predicts general qualitative patterns in the data (e.g.~a
+prediction of relatively more \enquote{Right} responses than
+\enquote{Wrong} responses in a given trial of our binary truth-value
+judgment task, or a prediction of a rise in the rate of response of
+\enquote{Right}/\enquote{Wrong} between two experimental conditions,
+given some contextual manipulation). \textbf{XXX Judith, I was thinking
+of adding the sentence to end this paragraph: \enquote{However, we
+should stress that to the best of our knowledge, even a qualitative
+analysis of this kind of variation in behavior on sentence verification
+tasks - much less the effect of the number of response choices on that
+behavior - is largely underdeveloped scalar implicature literature.} But
+it might be way too strong a claim? }
+
+\textbf{XXX Brandon, can you be more specific about what you mean by
+\enquote{tracing a general qualitative pattern}? XXX Judith: I've tried
+to offer some examples of what I mean by this, see above.}
+
+We contrast the above view of implicature and its behavioral reflexes
+with an alternative linking hypothesis. Recent developments in the field
+of probabilistic pragmatics have demonstrated that pragmatic production
+and comprehension can be captured within the Rational Speech Act (RSA)
+framework, which treats listeners and speakers as agents that reason
+about each other and choose interpretations and utterances,
+respectively, that soft-maximize utility (Bergen, Levy, \& Goodman,
+2016; Degen, Franke, \& Jäger, 2013; Degen, Tessler, \& Goodman, 2015;
+Frank \& Goodman, 2012; Franke \& Jäger, 2016; Goodman \& Frank, 2016;
+Goodman \& Stuhlmüller, 2013; Kao, Wu, Bergen, \& Goodman, 2014; Qing \&
+Franke, 2015; Scontras, Degen, \& Goodman, 2017). \textbf{XXX Judith:
+re: your Slack comments, in the following few sentences I've provided a
+summary of the intuition behind RSA (going off of the discussion in
+Goodman \& Stuhlmueller 2013)} Much in the spirit of Gricean approaches
+to pragmatic competence, the RSA framework takes as its point of
+departure the idea that individuals are rational, goal-oriented
+communicative agents, who in turn assume that their interlocutors
+similarly behave according to general principles of cooperativity in
+communication. Just as in more traditional Gricean pragmatics, pragmatic
+inference and pragmatically-cooperative language production in the RSA
+framework are, at their core, the product of counterfactual reasoning
+about alternative utterances that one might produce (but does not, in
+the interest of cooperativity). However, the RSA framework explicitly
+and quantitatively models coooperative interlocutors as agents whose
+language production and comprehension is a function of Bayesian
+probalistic inference regarding other interlocutors' expected behavior
+in a discourse context.
+
+Specifically, in the RSA framework we model pragmatically competent
+listeners as continuous probabilistic distributions over possible
+meanings (states of the world) given an utterance which that listener
+observes. The probability with which this listener \(L_1\) ascribes a
+meaning \(s\) to an utterance \(u\) depends upon a prior probability
+distribution of potential states of the world \(P_w\), and upon
+reasoning about the communicative behavior of a speaker \(S_1\). \(S_1\)
+in turn is modeled as a continuous probabilistic distribution over
+possible utterances given an intended state of the world the speaker
+intends to communicate. This distribution is sensitive to a rationality
+parameter \(\alpha\), the production cost \(C\) of potential utterances,
+and the informativeness of the utterance, quantified via a
+representation of a literal listener \(L_0\) whose interpretation of an
+utterance is in turn a function of that utterance's truth conditional
+content \([[u]](s)\) and her prior beliefs about the state of the world
+\(P_w(s)\).
+
+\begin{verbatim}
+$P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
+
+$P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $
+
+$P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
+\end{verbatim}
+
+Thus, our alternative linking hypothesis contrasts with the traditional
+view in that it is rooted in a quantitative formalization of pragmatic
+competence which provides us a continuous measure of pragmatic
+reasoning. In the RSA framework, individuals never categorically draw
+(or fail to draw) pragmatic inferences about the utterances they hear.
+For example, exclusivity readings of disjunction are represented in RSA
+as relatively lower posterior conditional probability of a conjunctive
+meaning on the \(P_L\) distribution given an utterance of \enquote{or},
+compared the prior probability of that meaning. Thus, absent auxiliary
+assumptions about what exactly would constitute \enquote{implicature},
+it is not even possible to talk about rate of implicature calculation in
+the RSA framework. The upshot, as we show below, is that this view of
+pragmatic competence does allow us to talk explicitly and quantitatively
+about rates of observed behavior in sentence verification tasks.
+
+We take inspiration from the RSA approach and treat participants'
+behavior in our experimental tasks as the result of a soft-optimal
+pragmatic speaker in the RSA framework. That is, following Degen and
+Goodman (2014), we proceed on the assumption that behavior on sentence
+verification tasks, such as truth value judgment tasks, is best modeled
+as a function of an individual's mental representation of a cooperative
+interlocutor (\(S_1\) in the language of RSA) rather than of a pragmatic
+listener who interprets utterances (\(P_{L_1}\)). In their paper, Degen
+\& Goodman argue that sentence verification tasks are relatively more
+sensitive to contextual manipulations (such as manipulation of the
+Question Under Discussion) than are sentence interpretation tasks, and
+that this follows if sentence interpretation tasks - but not sentence
+verification tasks - require an additional layer of counterfactual
+reasoning about the intentions of a cooperative speaker.
+
+A main desideratum of a behavioral linking hypothesis given the RSA view
+of pragmatic competence is to transform continuous probability
+distributions into categorical outputs (e.g.~responses of
+\enquote{Right}/''Wrong'' in the case of the binary condition of our
+experiment). For a given utterance \(u\) and an intended communicated
+meaning \(s\), \(S_1\)(u \textbar{} s) outputs a conditional probability
+of \(u\) given \(s\). For example, in the binary condition of our
+experiment where a participant evaluated \enquote{There is a cat or a
+dog} when there were both animals on the card, the participant has
+access to the mental representation of \(S_1\) and hence to the \(S_1\)
+conditional probability of producing the utterance \enquote{cat or dog}"
+given a dog and cat card: \(S_1\)(\enquote{cat or dog} \textbar{} cat
+and dog). According to the linking hypothesis advanced here, the
+participant provides a particular response to \(u\) if the RSA speaker
+probability of \(u\) lies within a particular probability interval,
+given an observed state of the world (i.e.~the configuration of animals
+on the card in our experiment). We model a responder, \(R\), who in the
+binary condition responds \enquote{Right} to an utterance \(u\) in world
+\(s\) just in case \(S_1(u | s)\) exceeds some probability threshold
 \(\theta\):
 
-R(u, w, \(\theta\)) = \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\)
-\(\theta\) = \enquote{Wrong} otherwise
-
-In the experiment conditions where there are more than two choices, we
-model the range of possible behavioral responses for R with the
-introduction of intermediate probability thresholds. For example, in the
-ternary condition, R(u, w, \(\theta_1\) , \(\theta_2\)) is
-\enquote{Right} iff \(S_1\)(u \textbar{} w) \textgreater{} \(\theta_1\)
-and \enquote{Neither} iff \(\theta_1\) \textgreater{} \(S_1\)(u
-\textbar{} w) \textgreater{} \(\theta_2\). To fully generalize the model
-to our five experimental conditions, we say that R takes as its input an
-utterance u and a world state w and a number of threshold variables
-dependent on a variable c, corresponding to the experimental condition
-in which the participant finds herself (e.g.~the range of possible
-responses available to R).
+R(u, w, \(\theta\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta\)
+
+= \enquote{Wrong} otherwise
+
+\textbf{XXX The following paragraph is mostly new:} Because \(\theta\)
+is a free parameter in our model, we have a straightforward
+understanding of between-subject response variation on a given trial of
+our experiment according to this linking hypothesis. That is, we can
+attribute this variation to individual differences vis a vis the value
+of the probability threshold against which utterances are evaluated in a
+given world state. Moreover, the model of a responder in the binary
+condition is extended intuitively to the condition where participants
+had three response options. In this case, we allow for two probability
+thresholds: \(\theta_1\), the minimum standard for an utterance in a
+given world state to count as \enquote{Right}, and \(\theta_2\), the
+minimum standard for \enquote{Neither}. Thus, in the ternary condition,
+R(u, s, \(\theta_1\) , \(\theta_2\)) is \enquote{Right} iff \(S_1\)(u
+\textbar{} s) \textgreater{} \(\theta_1\) and \enquote{Neither} iff
+\(\theta_1\) \textgreater{} \(S_1\)(u \textbar{} s) \textgreater{}
+\(\theta_2\). To fully generalize the model to our five experimental
+conditions, we say that \(R\) takes as its input an utterance \(u\), a
+world state \(s\), and a number of threshold variables dependent on a
+variable \(c\), corresponding to the experimental condition in which the
+participant finds herself (e.g.~the range of possible responses
+available to \(R\)).
 
@@
 
-R(u, w, \(\theta_1\) , \(\theta_2\))\\
-= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\) =
-\enquote{Neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w) \(>\)
-\(\theta_2\)\\
+R(u, w, \(\theta_1\) , \(\theta_2\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
+
+= \enquote{Neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s) \(>\)
+\(\theta_2\)
+
 = \enquote{Wrong} otherwise
@@
 
-R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\))\\
-= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\) =
-\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_2\)\\
-= \enquote{Kinda Wrong} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_3\) = \enquote{Wrong} otherwise
+R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
+
+= \enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s)
+\(>\) \(\theta_2\)
+
+= \enquote{Kinda Wrong} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} s)
+\(>\) \(\theta_3\)
+
+= \enquote{Wrong} otherwise
 
@@
 
-R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\). \(\theta_4\))\\
-= \enquote{Right} iff \(S_1\)(u \textbar{} w) \(>\) \(\theta_1\)
-=\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_2\) = \enquote{Neither} iff \(\theta_2\) \(>\) \(S_1\)(u
-\textbar{} w) \(>\) \(\theta_3\)\\
-= \enquote{Kinda Wrong} iff \(\theta_3\) \(>\) \(S_1\)(u \textbar{} w)
-\(>\) \(\theta_4\) = \enquote{Wrong} otherwise
-
-\newpage
+R(u, w, \(\theta_1\) , \(\theta_2\), \(\theta_3\). \(\theta_4\))
+
+= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
+
+=\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s)
+\(>\) \(\theta_2\)
+
+= \enquote{Neither} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} s) \(>\)
+\(\theta_3\)
+
+= \enquote{Kinda Wrong} iff \(\theta_3\) \(>\) \(S_1\)(u \textbar{} s)
+\(>\) \(\theta_4\)
+
+= \enquote{Wrong} otherwise
+
+The above analysis is a proof of concept for the following idea: by
+relaxing the assumptions of the traditional view of scalar implicature
+(namely, that scalar implicatures either are or are not calculated, and
+that behavior on sentence verification tasks directly reflects this
+binary interpretation process), we can propose quantitative models of
+the variation in behavior we observe in experimental settings.
+
+\textbf{XXX The following is entirely new:} However, this way of
+understanding behaivor in truth value jugdment tasks also raises new
+analytic and empirical questions which we must leave to future work. For
+instance, given the experimental results reported here, what is the
+range of plausible values for, e.g., the single probability threshold
+\(\theta\), which separates \enquote{Right} from \enquote{Wrong}
+utterances in the binary condition? Bayesian statistical methods provide
+us the means for estimating the value of \(\theta\) in our RSA-based
+model, by allowing us to recover a posterior distribution of possible
+values of \(\theta\) given an assumption of a uniform prior and our
+empirically-observed data, i.e.~the actual rate of response of
+\enquote{Right} On each trial of the binary condition of the experiment.
+We may also ask, for example, whether the speaker probability threshold
+for an utterance being \enquote{Right} is relatively constant across
+conditions or changes systematically with the introduction of more
+response options. Again, Bayesian data analysis allows us to explore
+this question by investigating the extent to which the inferred
+posterior distribution of, e.g., possible values of the threshold for
+\enquote{Right} in the binary condition of the experiment differs from
+the inferred posterior distribution of possible values of the threshold
+for \enquote{Right} in the ternary, quatenary, and quinary conditions.
+
+Lastly, the linking analysis proposed here is just one in the space of
+possible analyses when traditional assumptions about scalar implicature
+are relaxed. For example, one might reject this threshold-based analysis
+in favor of one whereby responses are the outcomes of sampling on the
+(pragmatic speaker or pragmatic listener) probability distributions
+provided by an RSA model. We again must leave this investigation to
+future work, but for the time being we emphasize that such quantitative,
+data-driven and systematic model criticism/comparison is made available
+to researchers in experimental pragmatics by revising core assumptions
+about the nature of scalar implicature. Though we no longer have a crisp
+notion of scalar implicature as something that is or is not
+\enquote{calculated} in interpretation, we have new flexibility to
+explicitly discuss categorical behavior in experimental settings.
 
@@
 
+\hypertarget{ref-barr2013random}{}
+Barr, D. J., Levy, R., Scheepers, C., \& Tily, H. J. (2013). Random
+effects structure for confirmatory hypothesis testing: Keep it maximal.
+\emph{Journal of Memory and Language}, \emph{68}(3), 255--278.
+
+\hypertarget{ref-BenzGotzner2014}{}
+Benz, A., \& Gotzner, N. (2014). Embedded implicatures revisited: Issues
+with the Truth-Value Judgment Paradigm. In J. Degen, M. Franke, \& N. D.
+Goodman (Eds.), \emph{Proceedings of the formal \& experimental
+pragmatics workshop, european summer school for language, logic and
+information (esslli)} (pp. 1--6). Tübingen.
+
 \hypertarget{ref-Bergen2012}{}
@@
 doi:\href{https://doi.org/10.1037/a0027850}{10.1037/a0027850}
+
+\hypertarget{ref-Bergen2016}{}
+Bergen, L., Levy, R., \& Goodman, N. (2016). Pragmatic reasoning through
+semantic inference. \emph{Semantics and Pragmatics}, \emph{9}(1984),
+1--46. doi:\href{https://doi.org/10.3765/sp.9.20}{10.3765/sp.9.20}
 
@@
 359--400.
+
+\hypertarget{ref-chierchia2001}{}
+Chierchia, G., Crain, S., Teresa, M., Guasti, M. T., Gualmini, A., \&
+Meroni, L. (2001). The Acquisition of Disjunction: Evidence for a
+Grammatical View of Scalar Implicatures. In A. H.-J. D. Et al. (Ed.),
+\emph{BUCLD 25 proceedings} (pp. 157--168). Somerville, MA: Cascadilla
+Press.
 
@@
 
+\hypertarget{ref-Degen2013}{}
+Degen, J., Franke, M., \& Jäger, G. (2013). Cost-Based Pragmatic
+Inference about Referential Expressions. \emph{Proceedings of the 35th
+Annual Conference of the Cognitive Science Society (CogSci'13)},
+376--281.
+
+\hypertarget{ref-DegenTG2015}{}
+Degen, J., Tessler, M. H., \& Goodman, N. D. (2015). Wonky worlds:
+Listeners revise world knowledge when utterances are odd.
+\emph{Proceedings of the 37th Annual Conference of the Cognitive Science
+Society}, (2), 548--553.
+
 \hypertarget{ref-Doran2012}{}
@@
 
+\hypertarget{ref-Frank2012}{}
+Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning
+in language games. \emph{Science}, \emph{336}, 998.
+
+\hypertarget{ref-Franke2016}{}
+Franke, M., \& Jäger, G. (2016). Probabilistic pragmatics, or why Bayes
+' rule is probably important for pragmatics. \emph{Zeitschrift Für
+Sprachwissenschaft}, \emph{35}(1), 3--44.
+
+\hypertarget{ref-Geurts2010}{}
+Geurts, B. (2010). \emph{Quantity implicatures}. Cambridge: Cambridge
+Univ Press.
+
 \hypertarget{ref-Geurts2009}{}
@@
 doi:\href{https://doi.org/10.3765/sp.2.4}{10.3765/sp.2.4}
+
+\hypertarget{ref-Goodman2016}{}
+Goodman, N. D., \& Frank, M. C. (2016). Pragmatic Language
+Interpretation as Probabilistic Inference. \emph{Trends in Cognitive
+Sciences}, \emph{20}(11), 818--829.
+doi:\href{https://doi.org/10.1016/j.tics.2016.08.005}{10.1016/j.tics.2016.08.005}
+
+\hypertarget{ref-Goodman2013}{}
+Goodman, N. D., \& Stuhlmüller, A. (2013). Knowledge and implicature:
+modeling language understanding as social cognition. \emph{Topics in
+Cognitive Science}, \emph{5}(1), 173--84.
+doi:\href{https://doi.org/10.1111/tops.12007}{10.1111/tops.12007}
 
@@
 
+\hypertarget{ref-Hirschberg1985}{}
+Hirschberg, J. (1985). \emph{A Theory of Scalar Implicature} (PhD thesis
+No. MS-CIS-85-56). University of Pennsylvania; Garland Publishing
+Company.
+
+\hypertarget{ref-Horn1972}{}
+Horn, L. (1972). \emph{On the Semantic Properties of the Logical
+Operators in English} (PhD thesis). UCLA.
+
 \hypertarget{ref-horn1984}{}
@@
 
+\hypertarget{ref-Horowitz2017}{}
+Horowitz, A. C., Schneider, R. M., \& Frank, M. C. (2017). The Trouble
+With Quantifiers: Exploring Children's Deficits in Scalar Implicature.
+\emph{Child Development}, 1--40.
+doi:\href{https://doi.org/10.1111/cdev.13014}{10.1111/cdev.13014}
+
 \hypertarget{ref-huang2009}{}
@@
 \emph{Cognitive Psychology}, \emph{58}, 376--415.
+
+\hypertarget{ref-Kao2014}{}
+Kao, J., Wu, J., Bergen, L., \& Goodman, N. D. (2014). Nonliteral
+understanding of number words. \emph{Proceedings of the National Academy
+of Sciences of the United States of America}, \emph{111}(33),
+12002--12007.
+doi:\href{https://doi.org/10.1073/pnas.1407479111}{10.1073/pnas.1407479111}
 
@@
 
+\hypertarget{ref-Potts2015}{}
+Potts, C., Lassiter, D., Levy, R., \& Frank, M. C. (2015). Embedded
+implicatures as pragmatic inferences under compositional lexical
+uncertainty. \emph{Journal of Semantics}, \emph{33}(1975), 755--802.
+doi:\href{https://doi.org/10.1093/jos/ffv012}{10.1093/jos/ffv012}
+
+\hypertarget{ref-Qing2015}{}
+Qing, C., \& Franke, M. (2015). Variations on a bayesian theme:
+Comparing bayesian models of referential reasoning. In H. Zeevat \&
+H.-C. Schmitz (Eds.), \emph{Bayesian natural language semantics and
+pragmatics} (Vol. 2, pp. 201--220). Cham, Switzerland: Springer
+International Publishing.
+doi:\href{https://doi.org/10.1007/978-3-319-17064-0_9}{10.1007/978-3-319-17064-0\_9}
+
+\hypertarget{ref-Scontras2017}{}
+Scontras, G., Degen, J., \& Goodman, N. D. (2017). Subjectivity predicts
+adjective ordering preferences. \emph{Open Mind: Discoveries in
+Cognitive Science}, \emph{1}(1), 53--65.
+doi:\href{https://doi.org/10.1162/opmi}{10.1162/opmi}
+
+\hypertarget{ref-Stiller2015}{}
+Stiller, A. J., Goodman, N. D., \& Frank, M. C. (2015). Ad-hoc
+Implicature in Preschool Children. \emph{Language Learning and
+Development}, \emph{11}(2), 176--190.
+doi:\href{https://doi.org/10.1080/15475441.2014.927328}{10.1080/15475441.2014.927328}
+
+\hypertarget{ref-Tanenhaus2004}{}
+Tanenhaus, M. K. (2004). On-line sentence processing: past, present and
+future. In M. Carreiras \& C. Clifton (Eds.), \emph{On-line sentence
+processing: ERPS, eye movements and beyond} (pp. 371--392). London, UK:
+Psychology Press.
+
 \hypertarget{ref-VanTiel2014}{}
@@
 
+\hypertarget{ref-Tomlinson2013}{}
+Tomlinson, J. M., Bailey, T. M., \& Bott, L. (2013). Possibly all of
+that and then some: Scalar implicatures are understood in two steps.
+\emph{Journal of Memory and Language}, \emph{69}(1), 18--35.
+doi:\href{https://doi.org/10.1016/j.jml.2013.02.003}{10.1016/j.jml.2013.02.003}
+
 \hypertarget{ref-Zondervan2010}{}

### 2018-05-09 writeup.Rmd

--- 2018-05-09 writeup.Rmd
@@
 
+[^3: To know more about the default priors of the "brms" package you can refer to [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]
+
 The model provided evidence for the following effects: First, there was a main effect of trial type such that scalar trials resulted in greater implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]).
-Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a Weak link resulted in greater implicature rates.
+Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a weak link resulted in greater implicature rates.
 Finally, there was a three-way interaction between link, trial type, and number of response options (Mean Estimate = `r round(fixed_effects$Estimate[15],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[15],2)`, `r round(fixed_effects$X97.5.ile[15],2)`]).
-One interpretation of this interaction is that the difference between the weak and Strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
-**JD: happy to throw out this last sentence** Crucially, both number of response options and link affect the inferred implicature rate.
+One interpretation of this interaction is that the difference between the weak and strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
+Crucially, both number of response options and link affect the inferred implicature rate.
 

### 2018-05-09 writeup.Rmd
edits to general discussion section

@@
 
-Because $\theta$ is a free parameter in our model, we have a straightforward understanding of between-subject response variation on a given trial of our experiment according to this linking hypothesis.
-**JD: Hold on, Brandon, what's the link between being a free parameter hand having an understanding of between-subject response variation?** That is, we can attribute this variation to individual differences vis a vis the value of the probability threshold against which utterances are evaluated in a given world state.
-Moreover, the model of a responder in the binary condition is extended intuitively to the condition where participants had three response options.
+The model of a responder in the binary condition is extended intuitively to the condition where participants had three response options.
 In this case, we allow for two probability thresholds: $\theta_1$, the minimum standard for an utterance in a given world state to count as "right", and $\theta_2$, the minimum standard for "neither".
@@
 
-The above analysis is a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
-**JD: Brandon, I feel what's still missing here is a demonstration that this is a _reasonable_ linking function.
-Maybe we can add the point that with this linking function, there's nothing inherently special about the implicature conditions -- the same linking function can work for any of the eight conditions in our experiment, because they're all the result of a participant having to make a behavioral choice in the face of an underlying speaker probability.**
-
-However, this way of understanding behavior in truth value judgment tasks also raises new analytic and empirical questions which we must leave to future work.
-For instance, given the experimental results reported here, what is the range of plausible values for, e.g., the single probability threshold $\theta$, which separates "right" from "wrong" utterances in the binary condition?
-Bayesian statistical methods provide us the means for estimating the value of $\theta$ in our RSA-based model, by allowing us to recover a posterior distribution of possible values of $\theta$ given an assumption of a uniform prior and our empirically-observed data, i.e., the actual rate of response of "right" on each trial of the binary condition of the experiment.
-We may also ask, for example, whether the speaker probability threshold for an utterance being "right" is relatively constant across conditions or changes systematically with the introduction of more response options.
-Again, Bayesian data analysis allows us to explore this question by investigating the extent to which the inferred posterior distribution of, e.g., possible values of the threshold for "right" in the binary condition of the experiment differs from the inferred posterior distribution of possible values of the threshold for "right" in the ternary, quatenary, and quinary conditions.
-
-Lastly, the linking analysis proposed here is just one in the space of possible analyses when traditional assumptions about scalar implicature are relaxed.
+**The following is all new** In an RSA model, $S_1$(u | s) will be defined for any possible combination of utterance and world state.
+One upshot of this is that for the purposes of our linking hypothesis, participants are modeled as employing the same heuristic - does $S_1$(u | s) exceed the threshold?
+- in both 'implicature' and 'non-implicature' conditions of a truth value judgment task experiment.
+That is, participants never evaluate utterances directly on the basis of logical truth or falsity: for example, our blindfolded character Bob's guess of "cat and dog" on a cat and dog card trial is "right" to the vast majority of participants not because the guess is logically true but because $S_1$("cat and dog" | cat and dog) is exceedingly high.
+
+For further illustration, we use our definition of a pragmatically-competent speaker $S_1$ (as defined above) to calculate the speaker probabilities of utterance for "cat", "dog", "cat and dog", and "elephant" - given either a cat on the card, or both a cat and a dog on the card.
+In calculating these probabilities, we assume that the space of possible utterances is the set of utterances made by Bob in our experiment (i.e.
+any possible single, disjunctive, or conjunctive guess involving "cat", "dog", or "elephant").
+For the purposes of our model, we assume a uniform cost term on all utterances.
+We furthermore assume that the space of possible meanings corresponds to the set of possible card configurations that a participant may have seen in our experiment, and that the prior probability distribution over these world states is uniform.
+Lastly, we set $\alpha$ - the speaker rationality parameter - to 1.
+The resulting probability values are presented in Figure 8.
+**not sure that this is the right figure number**
+
+```{r message=FALSE, warning=FALSE, fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
+
+speaker_probs <- read.csv("models/webppl_models/speaker_probs.csv")
+
+speaker_probs %>%
+  ggplot(aes(x=u, y=prob)) +
+  geom_bar(stat = "identity", position="dodge", width = 0.6) +
+  facet_wrap(~s) +
+  labs(x="", y= paste("Speaker probability ", "S(u | s)"))+
+  theme_few() +
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1))
+  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)
+```
+
+The linking hypothesis under discussion assumes that speaker probabilities of utterance given meaning are invariant across a) our four different experimental conditions, b) across participants, and c) within participants (that is, participants are not capable of updating their $S_1$ distribution in a local discourse context).
+We note that the assumption (b) may conceivably be relaxed by allowing one or more of the parameters in the model - including the prior probability over world states $P_w$, the cost function on utterances $C$, or the rationality parameter $\alpha$ - to vary across participants.
+We also note that assumption (c) in particular is in tension with a growing body of empirical evidence that semantic and pragmatic interpretation is modulated by rapid adaptation to the linguistic and social features of one's interlocutors (c.f **TF Jaeger, Kurumada, Schuster & Degen in prep, et seq**).
+
+However, if we should like to keep the above assumptions in place, then we must look elsewhere to explain the observed variation in our experimental data.
+In particular, this linking hypothesis, coupled with our assumptions, commits us to explaining variation in the data in terms of the threshold parameters of our responder model $R$.
+Consider first the variation in response across different experimental conditions on a given trial, e.g.
+evaluation of a guess of "cat and dog" when the card contains both a cat and a dog.
+The variation in the proportion of responses of "right" on this trial between the binary, ternary, quaternary, and quinary conditions indicates that the threshold value for "right" responses must vary across conditions; that is, we predict that the $\theta$ of the binary condition will differ from, e.g., the $\theta_1$ of the ternary condition as well as the $\theta_1$ of the quaternary condition.
+We also observed variation in response on this trial within a single condition (for example, a sizeable minority of participants responded "wrong" to this trial in the binary condition).
+Thus, this linking hypothesis is committed to the notion that threshold values may vary across participants, such that a speaker probability of utterance $S_1$(u | s) can fall below $\theta$ for some subset of participants while $S_1$(u | s) itself remains constant across participants.
+
+Lastly, it is conceivable that for two utterances of the same conditional probability and in the same experimental condition, a participant in our experiment provided a judgment of, e.g.
+"right" to one utterance but "wrong" to the other.
+That is, it is possible that there was within-subject variation in this experiment.
+One way to represent such variation would be to posit that the parameterization of threshold values proceeds stochastically and that threshold values are recalibrated for every individual sentence verification task.
+Rather than representing a threshold as a discrete value N between 0 and 1, we can represent that threshold as a distribution over possible threshold values - with mass centered around N.
+Whenever an individual encounters a sentence verification task, such as a single trial of our truth value judgment task experiment, the threshold value is recalibrated by sampling from this distribution.
+If we allow values of $\theta$ to vary as a result of this schotastic process, for the possibility that $S_1$(u | s) sometimes falls below $\theta$ (and is otherwise above $\theta$) for a given participant.
+
+One outstanding empirical problem is the pattern of response we observed for "cat and dog" on trials where there was only a cat on the card.
+Because this utterance is strictly false in this world state, it is surprising - on both the traditional view as well as on the account developed here - that participants assigned this utterance ratings above "wrong" with any systematicity.
+However, this is exactly what we observed, particulary in the quaternary and quinary conditions of the experiment, where a sizeable minority of participants considered this utterance "kinda right".
+As Figure 8 demonstrates, the conditional speaker probability of this utterance in this world state is 0; thus, there is no conceivable threshold value that would allow this utterance to ever be rated above "wrong" (on the reasonable assumption that the thresholds in our responder model $R$ should be nonzero).
+Any linking hypothesis will have to engage with this data point, and we leave to future work an analysis which captures participants' behavior in this condition.
+
+For the time being, however, we present the above analysis as a proof of concept for the following idea: by relaxing the assumptions of the traditional view of scalar implicature (namely, that scalar implicatures either are or are not calculated, and that behavior on sentence verification tasks directly reflects this binary interpretation process), we can propose quantitative models of the variation in behavior we observe in experimental settings.
+We note that the linking analysis proposed here is just one in the space of possible analyses when traditional assumptions about scalar implicature are relaxed.
 For example, one might reject this threshold-based analysis in favor of one whereby responses are the outcomes of sampling on the (pragmatic speaker or pragmatic listener) probability distributions provided by an RSA model.
-We again must leave this investigation to future work, but for the time being we emphasize that such quantitative, data-driven and systematic model criticism/comparison is made available to researchers in experimental pragmatics by revising core assumptions about the nature of scalar implicature.
+We must leave this investigation to future work, but for the time being we emphasize that such quantitative, data-driven and systematic model criticism/comparison is made available to researchers in experimental pragmatics by revising core assumptions about the nature of scalar implicature.
 Though we no longer have a crisp notion of scalar implicature as something that is or is not 'calculated' in interpretation, we have new flexibility to explicitly discuss categorical behavior in experimental settings.

### 2018-05-09 models/webppl_models/graphingscript.r

@@ -1,0 +1,33 @@
+library(rwebppl)
+library(tidyverse)
+library(ggthemes)
+library(plyr)
+
+states = c("X", "X,Y");
+utterances = c('X', 'XorY', 'XandY', 'Z');
+
+f <- data.frame(utterance=character(),
+                state=character(), 
+                prob=integer(), 
+                stringsAsFactors=FALSE) 
+
+for (state in states){
+  for (utt in utterances){
+    d <- data.frame(u=character(),s=character())
+    d <- rbind(d, data.frame(s = state, u = utt))
+    f <- rbind(f, data.frame(s = state, u = utt, prob = webppl(program_file = "code_forgraphs.webppl", data = d, data_var = "input")))
+  }
+}
+
+f$s <- revalue(f$s, c("X"="s = Cat on card", "X,Y"="s = Cat and dog on card"))
+f$u <- revalue(f$u, c("X"="u = 'Cat'", "XorY" = "u = 'Cat or dog'", "XandY" = "u = 'Cat and dog'", "Z" = "u = 'Elephant'"))
+
+f %>%
+  ggplot(aes(x=u, y=prob)) +
+  geom_bar(stat = "identity", position="dodge", width = 0.6) +
+  facet_wrap(~s) +
+  labs(x="", y="RSA speaker probability S(u|s)")+
+  theme_few() +
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1))
+  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE) 
+

### 2018-05-09 writeup.Rmd
minor proofreading edits

@@
 To this end, we only analyzed the critical trials (exhaustive and scalar).
-In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the strong and Weak link.
+In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the Strong and Weak link.
 Figure \@ref(fig:implicatureRatePlot) shows the resulting implicature rates by condition and link.
@@
 Finally, there was a three-way interaction between link, trial type, and number of response options (Mean Estimate = `r round(fixed_effects$Estimate[15],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[15],2)`, `r round(fixed_effects$X97.5.ile[15],2)`]).
-One interpretation of this interaction is that the difference between the weak and strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
+One interpretation of this interaction is that the difference between the Weak and Strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place.
 Crucially, both number of response options and link affect the inferred implicature rate.
@@
 
-While the binary truth value judgement task avoids the analytic decision between strong and Weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
+While the binary truth value judgement task avoids the analytic decision between Strong and Weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
 In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs.
@@
 
-**The following is all new** In an RSA model, $S_1$(u | s) will be defined for any possible combination of utterance and world state.
+**The following is all new** In an RSA model, $S_1$(u | s) will be defined for any possible combination of possible utterance and possible world state.
 One upshot of this is that for the purposes of our linking hypothesis, participants are modeled as employing the same heuristic - does $S_1$(u | s) exceed the threshold?
@@
 For example, one might reject this threshold-based analysis in favor of one whereby responses are the outcomes of sampling on the (pragmatic speaker or pragmatic listener) probability distributions provided by an RSA model.
-We must leave this investigation to future work, but for the time being we emphasize that such quantitative, data-driven and systematic model criticism/comparison is made available to researchers in experimental pragmatics by revising core assumptions about the nature of scalar implicature.
+We must leave this investigation to future work, but for now we emphasize that this kind of quantitative, data-driven and systematic model criticism is made available to researchers in experimental pragmatics by revising core assumptions about the nature of scalar implicature.
 Though we no longer have a crisp notion of scalar implicature as something that is or is not 'calculated' in interpretation, we have new flexibility to explicitly discuss categorical behavior in experimental settings.

### 2018-05-10 writeup.Rmd
added abstract and conclusion and final edits'

@@
 ---
-title             : "Linking assumptions and number of response options modulate inferred scalar implicature rate"
-shorttitle        : "Linking assumptions and implicature rate"
+title             : "Linking hypothesis and number of response options modulate inferred scalar implicature rate"
+shorttitle        : "Linking hypotheses and implicature rate"
 author:
@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
+    address       : "XXX Postal address"
+    email         : "XXX my@email.com"
   - name          : "Brandon Waldon"
@@
 author_note: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  XXX Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
   Enter author note here.
 abstract: |
-  Enter abstract here. Each new line herein must be indented, like this line.
-
-keywords          : "scalar implicature; methodology; linking assumption; experimental pragmatics; truth-value judgment task"
+  The past 15 years have seen increasing experimental investigations of core pragmatic questions in the ever more active and lively field of experimental pragmatics.
+Within experimental pragmatics, many of the core questions have relied on the operationalization of the theoretical notion of 'implicature rate'.
+Implicature rate based results have informed the work on acquisition, online processing, and scalar diversity, inter alia.
+Despite its theoretical importance.
+Implicature rate has  typically been quantified as the proportion of 'pragmatic' judgments in two-alternative forced choice truth value judgment tasks.
+Despite its theoretical importance, this linking hypothesis from implicature rate to behavioral responses has never been extensively tested.
+Here we show that two factors dramatically affect the 'implicature rate' inferred from truth value judgment tasks: a) the number of responses provided to participants; and b) the linking hypothesis about what constitutes a 'pragmatic' judgment.
+We argue that it is time for the field of experimental pragmatics to engage more seriously with its foundational assumptions about how theoretical notions map onto behaviorally measurable quantities, and present a sketch of an alternative linking hypothesis that derives behavior in truth value judgment tasks from probabilistic utterance expectations.
+keywords          : "scalar implicature; methodology; linking hypothesis; experimental pragmatics; truth value judgment task"
 wordcount         : "X"
@@
 
-The past 15 years have seen the rise and development of a bustling and exciting new field at the intersection of linguistics, psychology, and philosophy: *experimental pragmatics* [@Bott2004;@Breheny2006;@DegenTanenhaus2015;@Grodner2010;@huang2009;@Geurts2009;@noveck2008] **XXX ADD MORE**.
+The past 15 years have seen the rise and development of a bustling and exciting new field at the intersection of linguistics, psychology, and philosophy: *experimental pragmatics* [@chierchia2001;@Noveck2003;@Bott2004;@Breheny2006;@DegenTanenhaus2015;@DegenTanenhaus2016;@Grodner2010;@huang2009;@Geurts2009;@noveck2008;@Bott2016;@Breheny2013;@VanTiel2014;@DeNeys2007;@Katsos2011;@Papafragou2004;@Barner2011;@Bonnefon2009;@Tomlinson2013].
 Experimental pragmatics is devoted to experimentally testing theories of how language is used in context.
@@
 
-A standard measure that has stood as a proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
+A standard measure that has stood as a proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014].
 In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world.
@@
 
-Given the centrality of the theoretical notion of 'implicature rate' to much of experimental pragmatics, there is to date a surprising lack of discussion of the basic assumption that it is adequately captured by the  proportion of FALSE responses in truth-value judgment tasks (but see @BenzGotzner2014; @Geurts2009; @Degen2014; @Katsos2011).
+Given the centrality of the theoretical notion of 'implicature rate' to much of experimental pragmatics, there is to date a surprising lack of discussion of the basic assumption that it is adequately captured by the  proportion of FALSE responses in truth value judgment tasks (but see @BenzGotzner2014; @Geurts2009; @Degen2014; @Katsos2011).
 Indeed, the scalar implicature acquisition literature was shaken up when @Katsos2011 showed that simply by introducing an additional response option, children started looking much more pragmatic than had been previously observed in a binary judgment paradigm.
@@
 
-But this raises an important question: in truth-value judgment tasks, how does the researcher know whether an interpretation is literal or the result of an implicature computation?
+But this raises an important question: in truth value judgment tasks, how does the researcher know whether an interpretation is literal or the result of an implicature computation?
 The binary choice task typically used is appealing in part because it allows for a direct mapping from response options -- TRUE and FALSE -- to interpretations -- literal and pragmatic.
@@
 But it seems just as plausible that they could have grouped it with the positive endpoint of the scale and taken the hard line that only truly FALSE responses constitute evidence of a full-fledged implicature.
-The point here is that there has been remarkably little consideration of *linking functions* between behavioral measures and theoretical constructs in experimental pragmatics, a problem in many subfields of psycholinguistics [@Tanenhaus2004].
+The point here is that there has been remarkably little consideration of *linking hypothesiss* between behavioral measures and theoretical constructs in experimental pragmatics, a problem in many subfields of psycholinguistics [@Tanenhaus2004].
 We argue that it is time to engage more seriously with these issues.
 
-We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth-value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates?
-Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of interpretation; and second,  that listeners either do or do not compute an implicature on any given occasion.
+We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates?
+Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth value judgment task, the behavioral measure can be interpreted as providing a measure of interpretation; and second,  that listeners either do or do not compute an implicature on any given occasion.
 In the General Discussion we will discuss both of these issues.
-First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' *production* probabilities.
-This will suggest a completely different class of linking functions.
+First, following @Degen2014, we will offer some remarks on why truth value judgment tasks are better thought of as measuring participants' estimates of speakers' *production* probabilities.
+This will suggest a completely different class of linking hypothesiss.
 Next, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016].
-This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.
+This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking hypothesiss in a rigorous and motivated way.
 
 Consider a setup in which a listener is presented a card with a depiction of either one or two animals (see Figure \@ref(fig:linkvisualization) for an example).
-As in a standard truth-value judgment task, the listener then observes an underinformative utterance about this card (e.g., 'There is a cat or a dog on the card') and is asked to provide a judgment on a scale with 2, 3, 4, or 5 response options, with endpoints 'wrong' and 'right'.[^1] In the binary case, this reproduces the standard truth-value judgment task.
+As in a standard truth value judgment task, the listener then observes an underinformative utterance about this card (e.g., 'There is a cat or a dog on the card') and is asked to provide a judgment on a scale with 2, 3, 4, or 5 response options, with endpoints 'wrong' and 'right'.[^1] In the binary case, this reproduces the standard truth value judgment task.
 Figure \@ref(fig:linkvisualization) exemplifies (some of) the researcher's options for grouping responses.
@@
 In the experiment reported in the following section, we presented participants with exactly this setup.
-We manipulated the number of response options between participants and analyzed the results under different linking assumptions.
+We manipulated the number of response options between participants and analyzed the results under different linking hypothesiss.
 
@@
 On critical trials, participants were presented with descriptions for the cards that typically result in exhaustivity implicatures ("There is a cat on the card" when there was a cat and a dog) or scalar implicatures ("There is a cat or a dog on the card" when there was a cat and a dog).
-We categorized their responses on such trials according to the weak and the Strong link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.
+We categorized their responses on such trials according to the weak and the Strong link introduced above, and tested whether the number of response options and the linking hypothesiss led to different conclusions about the rate of computed implicatures in the experimental task.
 
@@
 
-## Results
+## Results and discussion
 
@@
 
-Our primary goal in this study was to test whether the estimated implicature rate in the experimental task is affected by the linking assumption and the number of response options available to participants.
+Our primary goal in this study was to test whether the estimated implicature rate in the experimental task is affected by the linking hypothesis and the number of response options available to participants.
 To this end, we only analyzed the critical trials (exhaustive and scalar).
@@
 
-[^3: To know more about the default priors of the "brms" package you can refer to [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]
+[^3: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]
 
@@
 
-We asked whether the linking assumptions and the number of response options available to participants affects the inferred implicature rate in an experimental study.
+In this paper we asked whether linking hypothesiss and number of response options available to participants in truth value judgment tasks affects inferred implicature rates.
 The results presented here suggest they do.
-A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (Weak link) resulted in higher implicature rates in tasks with 4 or 5 response options.
-A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (Strong link) reported lower implicature rates in tasks with 4 or 5 options.
-The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions drawn from truth value judgment tasks.
+A linking assupmtion that considered the highest point on the scale literal and any lower point  pragmatic (Weak link) resulted in higher implicature rates in tasks with 4 or 5 response options compared to the standard two options.
+A linking hypothesis that considered the lowest point on the scale pragmatic and any higher point literal (Strong link) reported lower implicature rates in tasks with 4 or 5 options compared to the standard two options.
+The results suggest that the choice of linking hypothesis is a crucial analytical step that can significantly impact the conclusions drawn from truth value judgment tasks.
 In particular, there is danger for pragmatic ability to be both under- and overestimated.
 
-While the binary truth value judgement task avoids the analytic decision between Strong and Weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
+While the binary truth value judgement task avoids the analytic decision between Strong and Weak linking hypothesiss, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence.
 In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs.
@@
 In computing implicature rate, this pattern manifested itself as a decrease in implicature rate under the Strong link when more response options were provided, and an increase in implicature rate under the Weak link when more response options were provided.
-These conclusions are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much.
+These observations are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much.
 Providing participants with only the extreme ends of the scale (e.g.
@@
 
-This study did not investigate the effect of option labels on the inferred implicature rate.
+This study did not investigate the effect of response labels on the inferred implicature rate.
 However, the results provided suggestive evidence that some options better capture participant intuitions of pragmatic infelicities than others.
@@
 Future work should systematically vary the goal of the game and explore its effects on the inferred implicature rate.
-
-## Revisiting linking assumptions
-
-On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair - that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
+But crucially, it's unlikely that the observed effects of number of response options and linking hypothesis on inferred implicature rate are dependent on any of the discussed design choices.
+
+## Revisiting linking hypothesiss
+
+On the traditional view of the link between implicature and behavior in sentence verification tasks, scalar implicature is conceptualized as a binary, categorical affair -- that is, an implicature is either ‘calculated’ or it isn’t, and the behavioral reflexes of this categorical interpretation process should be straightforwardly observed in experimental paradigms.
 This assumption raises concerns for analyzing variation in behavior on a truth value judgment task; for example, why did the majority of respondents in the binary condition of our experiment answer “right” to an utterance of the underinformative "There is a cat or dog" when the card had both a cat and a dog on it?
@@
 However, without an understanding of how to quantitatively specify the link between implicature calculation and its behavioral expression, the best we can hope for on this approach is an analysis which predicts general qualitative patterns in the data (e.g.
-a prediction of relatively more "right" responses than "wrong" responses in a given trial of our binary truth-value judgment task, or a prediction of a rise in the rate of response of "right"/"wrong" between two experimental conditions, given some contextual manipulation).
-However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks - much less the effect of the number of response choices on that behavior - is largely underdeveloped scalar implicature literature.
+a prediction of relatively more "right" responses than "wrong" responses in a given trial of our binary truth value judgment task, or a prediction of a rise in the rate of response of "right"/"wrong" between two experimental conditions, given some contextual manipulation).
+However, we should stress that to the best of our knowledge, even a qualitative analysis of this kind of variation in behavior on sentence verification tasks -- much less the effect of the number of response choices on that behavior -- is largely underdeveloped in the scalar implicature literature.
 
@@
 That is, following @Degen2014, we proceed on the assumption that behavior on sentence verification tasks, such as truth value judgment tasks, is best modeled as a function of an individual’s mental representation of a cooperative interlocutor ($S_1$ in the language of RSA) rather than of a pragmatic listener who interprets utterances ($P_{L_1}$).
-In their paper, Degen & Goodman argue that sentence verification tasks are relatively more sensitive to contextual manipulations (such as manipulation of the Question Under Discussion) than are sentence interpretation tasks, and that this follows if sentence interpretation tasks - but not sentence verification tasks - require an additional layer of counterfactual reasoning about the intentions of a cooperative speaker.
+In their paper, Degen & Goodman argue that sentence verification tasks are relatively more sensitive to contextual manipulations (such as manipulation of the Question Under Discussion) than are sentence interpretation tasks, and that this follows if sentence interpretation tasks -- but not sentence verification tasks -- require an additional layer of counterfactual reasoning about the intentions of a cooperative speaker.
 
@@
 For a given utterance $u$ and an intended communicated meaning $s$, $S_1$(u | s) outputs a conditional probability of $u$ given $s$.
-For example, in the binary condition of our experiment where a participant evaluated "There is a cat or a dog" when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of producing the utterance "cat or dog"" given a dog and cat card: $S_1$("cat or dog" | cat and dog).
-According to the linking hypothesis advanced here, the participant provides a particular response to $u$ if the RSA speaker probability of $u$ lies within a particular probability interval, given an observed state of the world (i.e.
-the configuration of animals on the card in our experiment).
+For example, in the binary condition of our experiment where a participant evaluated "There is a cat or a dog" when there were both animals on the card, the participant has access to the mental representation of $S_1$ and hence to the $S_1$ conditional probability of producing the utterance "cat or dog" given a dog and cat card: $S_1$("cat or dog" | cat and dog).
+According to the linking hypothesis advanced here, the participant provides a particular response to $u$ if the RSA speaker probability of $u$ lies within a particular probability interval.
 We model a responder, $R$, who in the binary condition responds “right” to an utterance $u$ in world $s$ just in case $S_1(u | s)$ exceeds some probability threshold $\theta$:
@@
 
-**The following is all new** In an RSA model, $S_1$(u | s) will be defined for any possible combination of possible utterance and possible world state.
-One upshot of this is that for the purposes of our linking hypothesis, participants are modeled as employing the same heuristic - does $S_1$(u | s) exceed the threshold?
-- in both 'implicature' and 'non-implicature' conditions of a truth value judgment task experiment.
+In an RSA model, $S_1$(u | s) will be defined for any possible combination of possible utterance and possible world state.
+One consequence of this is that for the purposes of our linking hypothesis, participants are modeled as employing the same decision criterion -- does $S_1$(u | s) exceed the threshold?
+-- in both 'implicature' and 'non-implicature' conditions of a truth value judgment task experiment.
 That is, participants never evaluate utterances directly on the basis of logical truth or falsity: for example, our blindfolded character Bob's guess of "cat and dog" on a cat and dog card trial is "right" to the vast majority of participants not because the guess is logically true but because $S_1$("cat and dog" | cat and dog) is exceedingly high.
 
-For further illustration, we use our definition of a pragmatically-competent speaker $S_1$ (as defined above) to calculate the speaker probabilities of utterance for "cat", "dog", "cat and dog", and "elephant" - given either a cat on the card, or both a cat and a dog on the card.
+For further illustration, we use our definition of a pragmatically-competent speaker $S_1$ (as defined above) to calculate the speaker probabilities of utterances in states of the world corresponding to our experimental conditions (i.e., for "cat", "dog", "cat and dog", and "elephant", given either a cat on the card, or both a cat and a dog on the card).
 In calculating these probabilities, we assume that the space of possible utterances is the set of utterances made by Bob in our experiment (i.e.
@@
 We furthermore assume that the space of possible meanings corresponds to the set of possible card configurations that a participant may have seen in our experiment, and that the prior probability distribution over these world states is uniform.
-Lastly, we set $\alpha$ - the speaker rationality parameter - to 1.
-The resulting probability values are presented in Figure 8.
-**not sure that this is the right figure number**
-
-```{r message=FALSE, warning=FALSE, fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
+Lastly, we set $\alpha$ -- the speaker rationality parameter -- to 1.
+The resulting speaker probabilities are shown in Figure \@ref(fig:speakerprobs).[^4]
+
+[^4]: Note that the probabilities in each facet don't sum to 1 because the model considers all possible disjunctive, conjunctive, and simple utterances, while we are only visualizing the ones corresponding to the experimental conditions.
+
+```{r speakerprobs, message=FALSE, warning=FALSE,fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
 
@@
   labs(x="", y= paste("Speaker probability ", "S(u | s)"))+
-  theme_few() +
+  # theme_few() +
   theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1))
@@
 The linking hypothesis under discussion assumes that speaker probabilities of utterance given meaning are invariant across a) our four different experimental conditions, b) across participants, and c) within participants (that is, participants are not capable of updating their $S_1$ distribution in a local discourse context).
-We note that the assumption (b) may conceivably be relaxed by allowing one or more of the parameters in the model - including the prior probability over world states $P_w$, the cost function on utterances $C$, or the rationality parameter $\alpha$ - to vary across participants.
-We also note that assumption (c) in particular is in tension with a growing body of empirical evidence that semantic and pragmatic interpretation is modulated by rapid adaptation to the linguistic and social features of one's interlocutors (c.f **TF Jaeger, Kurumada, Schuster & Degen in prep, et seq**).
+We note that the assumption (b) may conceivably be relaxed by allowing one or more of the parameters in the model -- including the prior probability over world states $P_w$, the cost function on utterances $C$, or the rationality parameter $\alpha$ -- to vary across participants.
+We also note that assumption (c) in particular is in tension with a growing body of empirical evidence that semantic and pragmatic interpretation is modulated by rapid adaptation to the linguistic and social features of one's interlocutors [@Kleinschmidt2015;@Fine2013].
 
@@
 One way to represent such variation would be to posit that the parameterization of threshold values proceeds stochastically and that threshold values are recalibrated for every individual sentence verification task.
-Rather than representing a threshold as a discrete value N between 0 and 1, we can represent that threshold as a distribution over possible threshold values - with mass centered around N.
+Rather than representing a threshold as a discrete value N between 0 and 1, we can represent that threshold as a distribution over possible threshold values -- with mass centered around N.
 Whenever an individual encounters a sentence verification task, such as a single trial of our truth value judgment task experiment, the threshold value is recalibrated by sampling from this distribution.
@@
 One outstanding empirical problem is the pattern of response we observed for "cat and dog" on trials where there was only a cat on the card.
-Because this utterance is strictly false in this world state, it is surprising - on both the traditional view as well as on the account developed here - that participants assigned this utterance ratings above "wrong" with any systematicity.
+Because this utterance is strictly false in this world state, it is surprising -- on both the traditional view as well as on the account developed here -- that participants assigned this utterance ratings above "wrong" with any systematicity.
 However, this is exactly what we observed, particulary in the quaternary and quinary conditions of the experiment, where a sizeable minority of participants considered this utterance "kinda right".
-As Figure 8 demonstrates, the conditional speaker probability of this utterance in this world state is 0; thus, there is no conceivable threshold value that would allow this utterance to ever be rated above "wrong" (on the reasonable assumption that the thresholds in our responder model $R$ should be nonzero).
+As Figure  \@ref(fig:speakerprobs) demonstrates, the conditional speaker probability of this utterance in this world state is 0; thus, there is no conceivable threshold value that would allow this utterance to ever be rated above "wrong" (on the reasonable assumption that the thresholds in our responder model $R$ should be nonzero).
 Any linking hypothesis will have to engage with this data point, and we leave to future work an analysis which captures participants' behavior in this condition.
@@
 
-**JD: We need a final concluding paragraph that reiterates the main points.**
+Concluding, we have shown in this paper that inferred 'implicature rate' -- ubiquitous in theoretical and experimental pragmatics -- as estimated in truth value judgment tasks, depends on both the number of responses participants are provided with as well as on the linking hypothesis from proportion of behavioral responses to 'implicature rate'.
+We further sketched an alternate linking hypothesis that treats behavioral responses as the result of probabilistic reasoning about speakers' likely productions.
+While a thorough model comparison is still outstanding, this kind of linking hypothesis opens a door towards more systematic and rigorous formulation and testing of linking hypotheses between theoretical notions of interest in pragmatics and behavioral responses in experimental paradigms.
 

### 2018-05-10 writeup.tex
added abstract and conclusion and final edits'

@@
             pdfauthor={},
-            pdftitle={Linking assumptions and number of response options modulate inferred scalar implicature rate},
+            pdftitle={Linking hypothesis and number of response options modulate inferred scalar implicature rate},
             colorlinks=true,
@@
 % Essential manuscript parts
-  \title{Linking assumptions and number of response options modulate inferred
+  \title{Linking hypothesis and number of response options modulate inferred
 scalar implicature rate}
 
-  \shorttitle{Linking assumptions and implicature rate}
+  \shorttitle{Linking hypotheses and implicature rate}
 
@@
   \authornote{
-    Add complete departmental affiliations for each author here. Each new
-    line herein must be indented, like this line. Enter author note here.
+    XXX Add complete departmental affiliations for each author here. Each
+    new line herein must be indented, like this line. Enter author note
+    here.
 
     Correspondence concerning this article should be addressed to Masoud
-    Jasbi, Postal address. E-mail:
+    Jasbi, XXX Postal address. E-mail: XXX
     \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
@@
 
-  \abstract{Enter abstract here. Each new line herein must be indented, like this
-line.}
-  \keywords{scalar implicature; methodology; linking assumption; experimental
-pragmatics; truth-value judgment task \\
+  \abstract{The past 15 years have seen increasing experimental investigations of
+core pragmatic questions in the ever more active and lively field of
+experimental pragmatics. Within experimental pragmatics, many of the
+core questions have relied on the operationalization of the theoretical
+notion of `implicature rate'. Implicature rate based results have
+informed the work on acquisition, online processing, and scalar
+diversity, inter alia. Despite its theoretical importance. Implicature
+rate has typically been quantified as the proportion of `pragmatic'
+judgments in two-alternative forced choice truth value judgment tasks.
+Despite its theoretical importance, this linking hypothesis from
+implicature rate to behavioral responses has never been extensively
+tested. Here we show that two factors dramatically affect the
+`implicature rate' inferred from truth value judgment tasks: a) the
+number of responses provided to participants; and b) the linking
+hypothesis about what constitutes a `pragmatic' judgment. We argue that
+it is time for the field of experimental pragmatics to engage more
+seriously with its foundational assumptions about how theoretical
+notions map onto behaviorally measurable quantities, and present a
+sketch of an alternative linking hypothesis that derives behavior in
+truth value judgment tasks from probabilistic utterance expectations.}
+  \keywords{scalar implicature; methodology; linking hypothesis; experimental
+pragmatics; truth value judgment task \\
 
@@
 exciting new field at the intersection of linguistics, psychology, and
-philosophy: \emph{experimental pragmatics} (Bott \& Noveck, 2004;
-Breheny, Katsos, \& Williams, 2006; Degen \& Tanenhaus, 2015; Geurts \&
-Pouscoulous, 2009; Grodner, Klein, Carbary, \& Tanenhaus, 2010; Huang \&
-Snedeker, 2009; I. A. Noveck \& Reboul, 2008) \textbf{XXX ADD MORE}.
-Experimental pragmatics is devoted to experimentally testing theories of
-how language is used in context. How do listeners draw inferences about
-the -- often underspecified -- linguistic signal they receive from
-speakers? How do speakers choose between the many utterance alternatives
-they have at their disposal?
+philosophy: \emph{experimental pragmatics} (Barner, Brooks, \& Bale,
+2011; Bonnefon, Feeney, \& Villejoubert, 2009; Bott \& Chemla, 2016;
+Bott \& Noveck, 2004; Breheny, Ferguson, \& Katsos, 2013; Breheny,
+Katsos, \& Williams, 2006; Chierchia et al., 2001; De Neys \& Schaeken,
+2007; Degen \& Tanenhaus, 2015, 2016; Geurts \& Pouscoulous, 2009;
+Grodner, Klein, Carbary, \& Tanenhaus, 2010; Huang \& Snedeker, 2009;
+Katsos \& Bishop, 2011; I. A. Noveck \& Reboul, 2008; Noveck \& Posada,
+2003; Papafragou \& Tantalou, 2004; Tiel, Miltenburg, Zevakhina, \&
+Geurts, 2014; Tomlinson, Bailey, \& Bott, 2013). Experimental pragmatics
+is devoted to experimentally testing theories of how language is used in
+context. How do listeners draw inferences about the -- often
+underspecified -- linguistic signal they receive from speakers? How do
+speakers choose between the many utterance alternatives they have at
+their disposal?
 
 The most prominently studied phenomenon in experimental pragmatics is
-undoubtedly \emph{scalar implicature}. Scalar implicatures arise in
-virtue of a speaker producing the weaker of two ordered scalemates
+undoubtedly \emph{scalar implicature}. Scalar implicatures arise as a
+result of a speaker producing the weaker of two ordered scalemates
 (Geurts, 2010; Grice, 1975; Hirschberg, 1985; Horn, 1972). Examples are
@@
   et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
-  2013; Tomlinson, Bailey, \& Bott, 2013)?
+  2013; Tomlinson et al., 2013)?
 \item
@@
   whether a scalar implicature is derived (Bergen \& Grodner, 2012;
-  Bonnefon, Feeney, \& Villejoubert, 2009; Breheny, Ferguson, \& Katsos,
-  2013; Breheny et al., 2006; Chemla \& Spector, 2011; De Neys \&
-  Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014; Degen \&
-  Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts, Lassiter,
-  Levy, \& Frank, 2015; Zondervan, 2010)?
+  Bonnefon et al., 2009; Breheny et al., 2013, 2006; Chemla \& Spector,
+  2011; De Neys \& Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014;
+  Degen \& Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts,
+  Lassiter, Levy, \& Frank, 2015; Zondervan, 2010)?
 \item
@@
   implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
-  Tiel, Miltenburg, Zevakhina, \& Geurts, 2014)?
+  Tiel et al., 2014)?
 \item
   At what age do children acquire the ability to compute implicatures
-  (Barner, Brooks, \& Bale, 2011; Horowitz, Schneider, \& Frank, 2017;
-  Katsos \& Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \&
-  Tantalou, 2004; Stiller, Goodman, \& Frank, 2015)?
+  (Barner et al., 2011; Horowitz, Schneider, \& Frank, 2017; Katsos \&
+  Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou,
+  2004; Stiller, Goodman, \& Frank, 2015)?
 \end{enumerate}
@@
 
-A standard measure that has stood proxy for implicature rate across many
-studies is the proportion of \enquote{pragmatic} judgments in
-truth-value judgment paradigms (Bott \& Noveck, 2004; Chemla \& Spector,
-2011; De Neys \& Schaeken, 2007; Degen \& Goodman, 2014; Degen \&
-Tanenhaus, 2015; Geurts \& Pouscoulous, 2009; Noveck, 2001; Noveck \&
-Posada, 2003). In these kinds of tasks, participants are provided a set
-of facts, either presented visually or via their own knowledge of the
+A standard measure that has stood as a proxy for implicature rate across
+many studies is the proportion of \enquote{pragmatic} judgments in truth
+value judgment paradigms (Bott \& Noveck, 2004; Chemla \& Spector, 2011;
+De Neys \& Schaeken, 2007; Degen \& Goodman, 2014; Degen \& Tanenhaus,
+2015; Geurts \& Pouscoulous, 2009; Noveck, 2001; Noveck \& Posada,
+2003). In these kinds of tasks, participants are provided a set of
+facts, either presented visually or via their own knowledge of the
 world. They are then asked to judge whether a sentence intended to
@@
 lack of discussion of the basic assumption that it is adequately
-captured by the proportion of FALSE responses in truth-value judgment
+captured by the proportion of FALSE responses in truth value judgment
 tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
@@
 
-But this raises an important question: in truth-value judgment tasks,
+But this raises an important question: in truth value judgment tasks,
 how does the researcher know whether an interpretation is literal or the
@@
 evidence of a full-fledged implicature. The point here is that there has
-been remarkably little consideration of \emph{linking functions} between
-behavioral measures and theoretical constructs in experimental
+been remarkably little consideration of \emph{linking hypothesiss}
+between behavioral measures and theoretical constructs in experimental
 pragmatics, a problem in many subfields of psycholinguistics (Tanenhaus,
@@
 We begin by reporting an experiment that addresses the following
-question: do the number of response options provided in a truth-value
+question: do the number of response options provided in a truth value
 judgment task and the way that responses are grouped into pragmatic
@@
 presupposes two things: first, that whatever participants are doing in a
-truth-value judgment task, the behavioral measure can be interpreted as
-providing a measure of \emph{interpretation}. And second, that listeners
-either do or do not compute an implicature on any given occasion. In the
+truth value judgment task, the behavioral measure can be interpreted as
+providing a measure of interpretation; and second, that listeners either
+do or do not compute an implicature on any given occasion. In the
 General Discussion we will discuss both of these issues. First,
 following Degen and Goodman (2014), we will offer some remarks on why
-truth-value judgment tasks are better thought of as measuring
+truth value judgment tasks are better thought of as measuring
 participants' estimates of speakers' \emph{production} probabilities.
-This will suggest a completely different class of linking functions. And
-second, we discuss an alternative conception of scalar implicature as a
+This will suggest a completely different class of linking hypothesiss.
+Next, we discuss an alternative conception of scalar implicature as a
 probabilistic phenomeonen, a view that has recently rose to prominence
@@
 implicature, we argue, affords developing and testing quantitative
-linking functions in a rigorous and motivated way.
+linking hypothesiss in a rigorous and motivated way.
 
@@
 depiction of either one or two animals (see Figure
-\ref{fig:linkvisualization} for an example). As in a standard
-truth-value judgment task, the listener then observes an
-underinformative utterance about this card (e.g., \enquote{There is a
-cat or a dog on the card}) and is asked to provide a judgment on a scale
-with 2, 3, 4, or 5 response options, with endpoints \enquote{wrong} and
+\ref{fig:linkvisualization} for an example). As in a standard truth
+value judgment task, the listener then observes an underinformative
+utterance about this card (e.g., \enquote{There is a cat or a dog on the
+card}) and is asked to provide a judgment on a scale with 2, 3, 4, or 5
+response options, with endpoints \enquote{wrong} and
 \enquote{right.}\footnote{An open question concerns the extent to which
@@
   distort judgments.} In the binary case, this reproduces the standard
-truth-value judgment task. Figure \ref{fig:linkvisualization}
+truth value judgment task. Figure \ref{fig:linkvisualization}
 exemplifies (some of) the researcher's options for grouping responses.
@@
 \includegraphics{writeup_files/figure-latex/linkvisualization-1.pdf}
-\caption{\label{fig:linkvisualization}Strong and weak link from response
+\caption{\label{fig:linkvisualization}Strong and Weak link from response
 options to researcher inference about scalar implicature rate,
@@
 Let's examine an example. Assume three response options (wrong, neither,
-right). Assume further that a third of participants each gave each of
-the three responses, i.e., the distributions of responses is 1/3, 1/3,
-and 1/3. Under the Strong link, we infer that this task yielded an
+right). Assume further that each of the three responses was selected by
+a third of participants, i.e., the distributions of responses is 1/3,
+1/3, and 1/3. Under the Strong link, we infer that this task yielded an
 implicature rate of 2/3. Under the Weak link, we infer that this task
 yielded an implicature rate of 1/3. This is quite a drastic difference
-if we are for instance interested in whether scalar implicatures are
+if we are, for instance, interested in whether scalar implicatures are
 inference defaults and we would like to interpret an implicature rate of
@@
 response options between participants and analyzed the results under
-different linking assumptions.
+different linking hypothesiss.
 
@@
 there was a cat and a dog). We categorized their responses on such
-trials according to the weak and the strong link introduced above, and
+trials according to the weak and the Strong link introduced above, and
 tested whether the number of response options and the linking
-assumptions led to different conclusions about the rate of computed
+hypothesiss led to different conclusions about the rate of computed
 implicatures in the experimental task.
@@
 any prior training in logic. 40 participants reported that they did,
-while 160 had no prior training in logic. \textbf{JD: Do we do any
-analysis of logic training???} All participants' data was included in
-the final analysis.
+while 160 had no prior training in logic. All participants' data was
+included in the final analysis.
 
@@
 associated with the use of disjunction ({\textbf{???}}; Chierchia et
-al., 2001) \textbf{JD: Masoud, can you insert citation pls? Geurts,
-Sauerland?}. Participants were told that Bob would guess the contents of
+al., 2001) Participants were told that Bob would guess the contents of
 the cards and their task was to indicate whether Bob's guess was wrong
@@
 
-\subsection{Results}\label{results}
+\subsection{Results and discussion}\label{results-and-discussion}
 
@@
 false trials, respectively (see Figure \ref{fig:binaryPlot}). However,
-on underinformative trials (\enquote{cat} and \enquote{cat or dog}
-description for card with cat and dog), we observe pragmatic behavior:
-on exhaustive trials, participants judged the utterance \enquote{wrong}
-14\% of the time; on scalar trials, participants judged the utterance
-\enquote{wrong} 38\% of the time. That is, both under the weak and the
-strong link assumptions introduced in the Introduction, inferred
-implicature rate on exhaustive trials is 14\% and on scalar trials 38\%.
+on underinformative trials (i.e.~a \enquote{cat} or \enquote{cat or dog}
+description for a card with both a cat and a dog), we observe pragmatic
+behavior: on exhaustive trials, participants judged the utterance
+\enquote{wrong} 14\% of the time; on scalar trials, participants judged
+the utterance \enquote{wrong} 38\% of the time. That is, both under the
+Weak and Strong link assumptions introduced in the Introduction,
+inferred implicature rate on exhaustive trials is 14\% and on scalar
+trials 38\%.
 
@@
 false trials, respectively (see Figure \ref{fig:ternaryPlot}). And
-again, on underinformative trials (\enquote{cat} and \enquote{cat or
-dog} description for card with cat and dog), we observed pragmatic
-behavior: on exhaustive trials, participants considered the guess
-\enquote{wrong} 8\% of the time and neither wrong nor right 12\% of the
-time. On scalar trials, participants judged the guess \enquote{wrong}
-23\% of the time and \enquote{neither} 11\% of the time. This means that
-the weak and strong link lead to different conclusions about implicature
-rates on the ternary task. Under the weak link, inferred implicature
-rate on exhaustive trials is 20\%; under the strong link it is only 8\%.
-Similarly, under the weak link, inferred implicature rate on scalar
-trials is 34\%; under the strong link it is only 23\%.
+again, on underinformative trials (a \enquote{cat} and \enquote{cat or
+dog} description for a card with both a cat and a dog), we observed
+pragmatic behavior: on exhaustive trials, participants considered the
+guess \enquote{wrong} 8\% of the time and neither wrong nor right 12\%
+of the time. On scalar trials, participants judged the guess
+\enquote{wrong} 23\% of the time and \enquote{neither} 11\% of the time.
+This means that the Weak and Strong link lead to different conclusions
+about implicature rates on the ternary task. Under the Weak link,
+inferred implicature rate on exhaustive trials is 20\%; under the Strong
+link it is only 8\%. Similarly, under the Weak link, inferred
+implicature rate on scalar trials is 34\%; under the Strong link it is
+only 23\%.
 
@@
 considered it \enquote{kinda wrong} or even \enquote{kinda right}. This
-suggests that perhaps participants considered a notion of partially true
-or correct statement in our experimental setting. Disjunctive
+suggests that perhaps participants considered the notion of a partially
+true or correct statement in our experimental setting. Disjunctive
 descriptions of cards with only one animal, while previously at ceiling
@@
 Thus, we are again forced to draw different conclusions about
-implicature rates depending on whether we assume the weak link or the
-strong link. Under the weak link, inferred implicature rate on
-exhaustive trials is 73\%; under the strong link it is only 2\%.
-Similarly, under the weak link, inferred implicature rate on scalar
-trials is 61\%; under the strong link it is only 6\%.
+implicature rates depending on whether we assume the Weak link or the
+Strong link. Under the Weak link, inferred implicature rate on
+exhaustive trials is 73\%; under the Strong link it is only 2\%.
+Similarly, under the Weak link, inferred implicature rate on scalar
+trials is 61\%; under the Strong link it is only 6\%.
 
@@
 control trials was again at floor and ceiling, respectively. The 2
-control conditions that the quaternary task had revealed pragmatic
-infelicity in again displayed that pragmatic infelicity in the quinary
+control conditions in which the quaternary task had revealed pragmatic
+infelicity again displayed that pragmatic infelicity in the quinary
 task, suggesting that this is a robust type of pragmatic infelicity
-that, however, requires fine-grained enough response options to be
+that, nonetheless, requires fine-grained enough response options to be
 detected experimentally.
@@
 Thus, we would again draw different conclusions about implicature rates
-depending on whether we assume the weak link or the strong link. Under
-the weak link, inferred implicature rate on exhaustive trials is 76 and
-76\%; under the strong link it is only 2\%. Similarly, under the weak
+depending on whether we assume the Weak link or the Strong link. Under
+the Weak link, inferred implicature rate on exhaustive trials is 76 and
+76\%; under the Strong link it is only 2\%. Similarly, under the Weak
 link, inferred implicature rate on scalar trials is 63\%; under the
-strong link it is only 6\%.
+Strong link it is only 6\%.
 
@@
 implicature rate in the experimental task is affected by the linking
-assumption and the number of response options available to participants.
+hypothesis and the number of response options available to participants.
 To this end, we only analyzed the critical trials (exhaustive and
 scalar). In particular, we classified each data point from critical
-trials as constituting an implicature (1) or not (0) under the strong
-and weak link. Figure \ref{fig:implicatureRatePlot} shows the resulting
+trials as constituting an implicature (1) or not (0) under the Strong
+and Weak link. Figure \ref{fig:implicatureRatePlot} shows the resulting
 implicature rates by condition and link.
 
-Visually, the weak link tends to result in greater estimates of
+Visually, the Weak link tends to result in greater estimates of
 implicature rates, especially in tasks with more response options. Under
-the strong link, this latter pattern is reversed: the binary and ternary
+the Strong link, this latter pattern is reversed: the binary and ternary
 judgment tasks result in greater estimates of implicature rates than
@@
 
-{[}\^{}3: To know more about the default priors of the \enquote{brms}
-package you can refer to
+{[}\^{}3: For more information about the default priors of the
+\enquote{brms} package, see
 \href{ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf}{the
@@
 95\% Credible Interval={[}-16.59, -0.16{]}). One interpretation of this
-interaction is that the difference between the weak and strong link on
+interaction is that the difference between the Weak and Strong link on
 scalar trials in the quinary task was smaller than on exhaustive trials,
@@
 
-\subsection{Discussion}\label{discussion}
-
-We asked whether the linking assumptions and the number of response
-options available to participants affects the inferred implicature rate
-in an experimental study. The results presented here suggest they do. A
-linking assupmtion that considered the highest point on the scale as
-literal and any lower point as pragmatic (weak link) resulted in higher
-implicature rates in tasks with 4 or 5 response options. A linking
-assumption that considered the lowest point on the scale as pragmatic
-and any higher point as literal (strong link) reported lower implicature
-rates in tasks with 4 or 5 options. The results suggest that the choice
-of linking assumption is a crucial analytical step that can
+\section{General Discussion}\label{general-discussion}
+
+\subsection{Summary and methodological
+discussion}\label{summary-and-methodological-discussion}
+
+In this paper we asked whether linking hypothesiss and number of
+response options available to participants in truth value judgment tasks
+affects inferred implicature rates. The results presented here suggest
+they do. A linking assupmtion that considered the highest point on the
+scale literal and any lower point pragmatic (Weak link) resulted in
+higher implicature rates in tasks with 4 or 5 response options compared
+to the standard two options. A linking hypothesis that considered the
+lowest point on the scale pragmatic and any higher point literal (Strong
+link) reported lower implicature rates in tasks with 4 or 5 options
+compared to the standard two options. The results suggest that the
+choice of linking hypothesis is a crucial analytical step that can
 significantly impact the conclusions drawn from truth value judgment
@@
 While the binary truth value judgement task avoids the analytic decision
-between strong and weak linking assumptions, the results reported here
+between Strong and Weak linking hypothesiss, the results reported here
 suggest that binary tasks can also underestimate participants' pragmatic
@@
 this pattern manifested itself as a decrease in implicature rate under
-the strong link when more response options were provided, and an
-increase in implicature rate under the weak link when more response
-options were provided. These conclusions are in line with Katsos and
+the Strong link when more response options were provided, and an
+increase in implicature rate under the Weak link when more response
+options were provided. These observations are in line with Katsos and
 Bishop (2011)\enquote{s argument that pragmatic violations are not as
@@
 
-This study did not investigate the effect of option labels on the
+This study did not investigate the effect of response labels on the
 inferred implicature rate. However, the results provided suggestive
@@
 2010). Future work should systematically vary the goal of the game and
-explore its effects on the inferred implicature rate.
-
-\section{General Discussion}\label{general-discussion}
+explore its effects on the inferred implicature rate. But crucially,
+it's unlikely that the observed effects of number of response options
+and linking hypothesis on inferred implicature rate are dependent on any
+of the discussed design choices.
+
+\subsection{Revisiting linking
+hypothesiss}\label{revisiting-linking-hypothesiss}
 
@@
 sentence verification tasks, scalar implicature is conceptualized as a
-binary, categorical affair - that is, an implicature is either
+binary, categorical affair -- that is, an implicature is either
 \enquote{calculated} or it isn't, and the behavioral reflexes of this
@@
 did the majority of respondents in the binary condition of our
-experiment answer \enquote{Right} to an utterance of the
+experiment answer \enquote{right} to an utterance of the
 underinformative \enquote{There is a cat or dog} when the card had both
 a cat and a dog on it? And why did a sizeable minority nonetheless
-choose \enquote{Wrong} in this same condition?
+choose \enquote{wrong} in this same condition?
 
@@
 participants who calculated the implicature did not choose the
-anticipated (i.e., \enquote{Wrong}) response due to some other cognitive
+anticipated (i.e., \enquote{wrong}) response due to some other cognitive
 process which overrode the \enquote{correct} implicature behavior; or
@@
 analysis which predicts general qualitative patterns in the data (e.g.~a
-prediction of relatively more \enquote{Right} responses than
-\enquote{Wrong} responses in a given trial of our binary truth-value
+prediction of relatively more \enquote{right} responses than
+\enquote{wrong} responses in a given trial of our binary truth value
 judgment task, or a prediction of a rise in the rate of response of
-\enquote{Right}/\enquote{Wrong} between two experimental conditions,
-given some contextual manipulation). \textbf{XXX Judith, I was thinking
-of adding the sentence to end this paragraph: \enquote{However, we
-should stress that to the best of our knowledge, even a qualitative
-analysis of this kind of variation in behavior on sentence verification
-tasks - much less the effect of the number of response choices on that
-behavior - is largely underdeveloped scalar implicature literature.} But
-it might be way too strong a claim? }
-
-\textbf{XXX Brandon, can you be more specific about what you mean by
-\enquote{tracing a general qualitative pattern}? XXX Judith: I've tried
-to offer some examples of what I mean by this, see above.}
+\enquote{right}/\enquote{wrong} between two experimental conditions,
+given some contextual manipulation). However, we should stress that to
+the best of our knowledge, even a qualitative analysis of this kind of
+variation in behavior on sentence verification tasks -- much less the
+effect of the number of response choices on that behavior -- is largely
+underdeveloped in the scalar implicature literature.
 
@@
 and comprehension can be captured within the Rational Speech Act (RSA)
-framework, which treats listeners and speakers as agents that reason
-about each other and choose interpretations and utterances,
-respectively, that soft-maximize utility (Bergen, Levy, \& Goodman,
-2016; Degen, Franke, \& Jäger, 2013; Degen, Tessler, \& Goodman, 2015;
-Frank \& Goodman, 2012; Franke \& Jäger, 2016; Goodman \& Frank, 2016;
-Goodman \& Stuhlmüller, 2013; Kao, Wu, Bergen, \& Goodman, 2014; Qing \&
-Franke, 2015; Scontras, Degen, \& Goodman, 2017). \textbf{XXX Judith:
-re: your Slack comments, in the following few sentences I've provided a
-summary of the intuition behind RSA (going off of the discussion in
-Goodman \& Stuhlmueller 2013)} Much in the spirit of Gricean approaches
-to pragmatic competence, the RSA framework takes as its point of
-departure the idea that individuals are rational, goal-oriented
-communicative agents, who in turn assume that their interlocutors
-similarly behave according to general principles of cooperativity in
-communication. Just as in more traditional Gricean pragmatics, pragmatic
-inference and pragmatically-cooperative language production in the RSA
-framework are, at their core, the product of counterfactual reasoning
-about alternative utterances that one might produce (but does not, in
-the interest of cooperativity). However, the RSA framework explicitly
-and quantitatively models coooperative interlocutors as agents whose
-language production and comprehension is a function of Bayesian
-probalistic inference regarding other interlocutors' expected behavior
-in a discourse context.
+framework (Bergen, Levy, \& Goodman, 2016; Degen, Franke, \& Jäger,
+2013; Degen, Tessler, \& Goodman, 2015; Frank \& Goodman, 2012; Franke
+\& Jäger, 2016; Goodman \& Frank, 2016; Goodman \& Stuhlmüller, 2013;
+Kao, Wu, Bergen, \& Goodman, 2014; Qing \& Franke, 2015; Scontras,
+Degen, \& Goodman, 2017). Much in the spirit of Gricean approaches to
+pragmatic competence, the RSA framework takes as its point of departure
+the idea that individuals are rational, goal-oriented communicative
+agents, who in turn assume that their interlocutors similarly behave
+according to general principles of cooperativity in communication. Just
+as in more traditional Gricean pragmatics, pragmatic inference and
+pragmatically-cooperative language production in the RSA framework are,
+at their core, the product of counterfactual reasoning about alternative
+utterances that one might produce (but does not, in the interest of
+cooperativity). However, the RSA framework explicitly and quantitatively
+models cooperative interlocutors as agents whose language production and
+comprehension is a function of Bayesian probabilistic inference
+regarding other interlocutors' expected behavior in a discourse context.
 
@@
 
-Thus, our alternative linking hypothesis contrasts with the traditional
-view in that it is rooted in a quantitative formalization of pragmatic
-competence which provides us a continuous measure of pragmatic
-reasoning. In the RSA framework, individuals never categorically draw
-(or fail to draw) pragmatic inferences about the utterances they hear.
-For example, exclusivity readings of disjunction are represented in RSA
-as relatively lower posterior conditional probability of a conjunctive
-meaning on the \(P_L\) distribution given an utterance of \enquote{or},
-compared the prior probability of that meaning. Thus, absent auxiliary
-assumptions about what exactly would constitute \enquote{implicature},
-it is not even possible to talk about rate of implicature calculation in
-the RSA framework. The upshot, as we show below, is that this view of
-pragmatic competence does allow us to talk explicitly and quantitatively
-about rates of observed behavior in sentence verification tasks.
+This view contrasts with the traditional view in that it is rooted in a
+quantitative formalization of pragmatic competence which provides us a
+continuous measure of pragmatic reasoning. In the RSA framework,
+individuals never categorically draw (or fail to draw) pragmatic
+inferences about the utterances they hear. For example, exclusivity
+readings of disjunction are represented in RSA as relatively lower
+posterior conditional probability of a conjunctive meaning on the
+\(P_L\) distribution given an utterance of \enquote{or}, compared to the
+prior probability of that meaning. Thus, absent auxiliary assumptions
+about what exactly would constitute \enquote{implicature}, it is not
+even possible to talk about rate of implicature calculation in the RSA
+framework. The upshot, as we show below, is that this view of pragmatic
+competence does allow us to talk explicitly and quantitatively about
+rates of observed behavior in sentence verification tasks.
 
@@
 Question Under Discussion) than are sentence interpretation tasks, and
-that this follows if sentence interpretation tasks - but not sentence
-verification tasks - require an additional layer of counterfactual
+that this follows if sentence interpretation tasks -- but not sentence
+verification tasks -- require an additional layer of counterfactual
 reasoning about the intentions of a cooperative speaker.
@@
 distributions into categorical outputs (e.g.~responses of
-\enquote{Right}/''Wrong'' in the case of the binary condition of our
+\enquote{right}/''wrong'' in the case of the binary condition of our
 experiment). For a given utterance \(u\) and an intended communicated
@@
 access to the mental representation of \(S_1\) and hence to the \(S_1\)
-conditional probability of producing the utterance \enquote{cat or dog}"
+conditional probability of producing the utterance \enquote{cat or dog}
 given a dog and cat card: \(S_1\)(\enquote{cat or dog} \textbar{} cat
@@
 participant provides a particular response to \(u\) if the RSA speaker
-probability of \(u\) lies within a particular probability interval,
-given an observed state of the world (i.e.~the configuration of animals
-on the card in our experiment). We model a responder, \(R\), who in the
-binary condition responds \enquote{Right} to an utterance \(u\) in world
-\(s\) just in case \(S_1(u | s)\) exceeds some probability threshold
-\(\theta\):
+probability of \(u\) lies within a particular probability interval. We
+model a responder, \(R\), who in the binary condition responds
+\enquote{right} to an utterance \(u\) in world \(s\) just in case
+\(S_1(u | s)\) exceeds some probability threshold \(\theta\):
 
@@
 
-= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta\)
-
-= \enquote{Wrong} otherwise
-
-\textbf{XXX The following paragraph is mostly new:} Because \(\theta\)
-is a free parameter in our model, we have a straightforward
-understanding of between-subject response variation on a given trial of
-our experiment according to this linking hypothesis. That is, we can
-attribute this variation to individual differences vis a vis the value
-of the probability threshold against which utterances are evaluated in a
-given world state. Moreover, the model of a responder in the binary
-condition is extended intuitively to the condition where participants
-had three response options. In this case, we allow for two probability
-thresholds: \(\theta_1\), the minimum standard for an utterance in a
-given world state to count as \enquote{Right}, and \(\theta_2\), the
-minimum standard for \enquote{Neither}. Thus, in the ternary condition,
-R(u, s, \(\theta_1\) , \(\theta_2\)) is \enquote{Right} iff \(S_1\)(u
-\textbar{} s) \textgreater{} \(\theta_1\) and \enquote{Neither} iff
-\(\theta_1\) \textgreater{} \(S_1\)(u \textbar{} s) \textgreater{}
-\(\theta_2\). To fully generalize the model to our five experimental
-conditions, we say that \(R\) takes as its input an utterance \(u\), a
-world state \(s\), and a number of threshold variables dependent on a
-variable \(c\), corresponding to the experimental condition in which the
-participant finds herself (e.g.~the range of possible responses
-available to \(R\)).
+= \enquote{right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta\)
+
+= \enquote{wrong} otherwise
+
+The model of a responder in the binary condition is extended intuitively
+to the condition where participants had three response options. In this
+case, we allow for two probability thresholds: \(\theta_1\), the minimum
+standard for an utterance in a given world state to count as
+\enquote{right}, and \(\theta_2\), the minimum standard for
+\enquote{neither}. Thus, in the ternary condition, R(u, s, \(\theta_1\)
+, \(\theta_2\)) is \enquote{right} iff \(S_1\)(u \textbar{} s)
+\textgreater{} \(\theta_1\) and \enquote{neither} iff \(\theta_1\)
+\textgreater{} \(S_1\)(u \textbar{} s) \textgreater{} \(\theta_2\). To
+fully generalize the model to our five experimental conditions, we say
+that \(R\) takes as its input an utterance \(u\), a world state \(s\),
+and a number of threshold variables dependent on a variable \(c\),
+corresponding to the experimental condition in which the participant
+finds themself (e.g.~the range of possible responses available to
+\(R\)).
 
@@
 
-= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
-
-= \enquote{Neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s) \(>\)
+= \enquote{right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
+
+= \enquote{neither} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s) \(>\)
 \(\theta_2\)
 
-= \enquote{Wrong} otherwise
-
-Given c = \enquote{quatenary}
+= \enquote{wrong} otherwise
+
+Given c = \enquote{quaternary}
 
@@
 
-= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
-
-= \enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s)
+= \enquote{right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
+
+= \enquote{kinda right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s)
 \(>\) \(\theta_2\)
 
-= \enquote{Kinda Wrong} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} s)
+= \enquote{kinda wrong} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} s)
 \(>\) \(\theta_3\)
 
-= \enquote{Wrong} otherwise
+= \enquote{wrong} otherwise
 
@@
 
-= \enquote{Right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
-
-=\enquote{Kinda Right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s)
+= \enquote{right} iff \(S_1\)(u \textbar{} s) \(>\) \(\theta_1\)
+
+=\enquote{kinda right} iff \(\theta_1\) \(>\) \(S_1\)(u \textbar{} s)
 \(>\) \(\theta_2\)
 
-= \enquote{Neither} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} s) \(>\)
+= \enquote{neither} iff \(\theta_2\) \(>\) \(S_1\)(u \textbar{} s) \(>\)
 \(\theta_3\)
 
-= \enquote{Kinda Wrong} iff \(\theta_3\) \(>\) \(S_1\)(u \textbar{} s)
+= \enquote{kinda wrong} iff \(\theta_3\) \(>\) \(S_1\)(u \textbar{} s)
 \(>\) \(\theta_4\)
 
-= \enquote{Wrong} otherwise
-
-The above analysis is a proof of concept for the following idea: by
-relaxing the assumptions of the traditional view of scalar implicature
-(namely, that scalar implicatures either are or are not calculated, and
-that behavior on sentence verification tasks directly reflects this
-binary interpretation process), we can propose quantitative models of
-the variation in behavior we observe in experimental settings.
-
-\textbf{XXX The following is entirely new:} However, this way of
-understanding behaivor in truth value jugdment tasks also raises new
-analytic and empirical questions which we must leave to future work. For
-instance, given the experimental results reported here, what is the
-range of plausible values for, e.g., the single probability threshold
-\(\theta\), which separates \enquote{Right} from \enquote{Wrong}
-utterances in the binary condition? Bayesian statistical methods provide
-us the means for estimating the value of \(\theta\) in our RSA-based
-model, by allowing us to recover a posterior distribution of possible
-values of \(\theta\) given an assumption of a uniform prior and our
-empirically-observed data, i.e.~the actual rate of response of
-\enquote{Right} On each trial of the binary condition of the experiment.
-We may also ask, for example, whether the speaker probability threshold
-for an utterance being \enquote{Right} is relatively constant across
-conditions or changes systematically with the introduction of more
-response options. Again, Bayesian data analysis allows us to explore
-this question by investigating the extent to which the inferred
-posterior distribution of, e.g., possible values of the threshold for
-\enquote{Right} in the binary condition of the experiment differs from
-the inferred posterior distribution of possible values of the threshold
-for \enquote{Right} in the ternary, quatenary, and quinary conditions.
-
-Lastly, the linking analysis proposed here is just one in the space of
-possible analyses when traditional assumptions about scalar implicature
-are relaxed. For example, one might reject this threshold-based analysis
-in favor of one whereby responses are the outcomes of sampling on the
-(pragmatic speaker or pragmatic listener) probability distributions
-provided by an RSA model. We again must leave this investigation to
-future work, but for the time being we emphasize that such quantitative,
-data-driven and systematic model criticism/comparison is made available
-to researchers in experimental pragmatics by revising core assumptions
-about the nature of scalar implicature. Though we no longer have a crisp
-notion of scalar implicature as something that is or is not
-\enquote{calculated} in interpretation, we have new flexibility to
-explicitly discuss categorical behavior in experimental settings.
+= \enquote{wrong} otherwise
+
+In an RSA model, \(S_1\)(u \textbar{} s) will be defined for any
+possible combination of possible utterance and possible world state. One
+consequence of this is that for the purposes of our linking hypothesis,
+participants are modeled as employing the same decision criterion --
+does \(S_1\)(u \textbar{} s) exceed the threshold? -- in both
+\enquote{implicature} and \enquote{non-implicature} conditions of a
+truth value judgment task experiment. That is, participants never
+evaluate utterances directly on the basis of logical truth or falsity:
+for example, our blindfolded character Bob's guess of \enquote{cat and
+dog} on a cat and dog card trial is \enquote{right} to the vast majority
+of participants not because the guess is logically true but because
+\(S_1\)(\enquote{cat and dog} \textbar{} cat and dog) is exceedingly
+high.
+
+For further illustration, we use our definition of a
+pragmatically-competent speaker \(S_1\) (as defined above) to calculate
+the speaker probabilities of utterances in states of the world
+corresponding to our experimental conditions (i.e., for \enquote{cat},
+\enquote{dog}, \enquote{cat and dog}, and \enquote{elephant}, given
+either a cat on the card, or both a cat and a dog on the card). In
+calculating these probabilities, we assume that the space of possible
+utterances is the set of utterances made by Bob in our experiment
+(i.e.~any possible single, disjunctive, or conjunctive guess involving
+\enquote{cat}, \enquote{dog}, or \enquote{elephant}). For the purposes
+of our model, we assume a uniform cost term on all utterances. We
+furthermore assume that the space of possible meanings corresponds to
+the set of possible card configurations that a participant may have seen
+in our experiment, and that the prior probability distribution over
+these world states is uniform. Lastly, we set \(\alpha\) -- the speaker
+rationality parameter -- to 1. The resulting speaker probabilities are
+shown in Figure \ref{fig:speakerprobs}.\footnote{Note that the
+  probabilities in each facet don't sum to 1 because the model considers
+  all possible disjunctive, conjunctive, and simple utterances, while we
+  are only visualizing the ones corresponding to the experimental
+  conditions.}
+
+\begin{figure}
+\centering
+\includegraphics{writeup_files/figure-latex/speakerprobs-1.pdf}
+\caption{\label{fig:speakerprobs}Speaker probabilities of utterances on the
+exhaustive and scalar trials, as obtained using the model described in
+this section.}
+\end{figure}
+
+\begin{verbatim}
+## <ggproto object: Class ScaleDiscrete, Scale>
+##     aesthetics: fill
+##     axis_order: function
+##     break_info: function
+##     break_positions: function
+##     breaks: waiver
+##     call: call
+##     clone: function
+##     dimension: function
+##     drop: TRUE
+##     expand: waiver
+##     get_breaks: function
+##     get_breaks_minor: function
+##     get_labels: function
+##     get_limits: function
+##     guide: FALSE
+##     is_discrete: function
+##     is_empty: function
+##     labels: waiver
+##     limits: NULL
+##     make_sec_title: function
+##     make_title: function
+##     map: function
+##     map_df: function
+##     n.breaks.cache: NULL
+##     na.translate: TRUE
+##     na.value: NA
+##     name: waiver
+##     palette: function
+##     palette.cache: NULL
+##     position: left
+##     range: <ggproto object: Class RangeDiscrete, Range>
+##         range: NULL
+##         reset: function
+##         train: function
+##         super:  <ggproto object: Class RangeDiscrete, Range>
+##     reset: function
+##     scale_name: manual
+##     train: function
+##     train_df: function
+##     transform: function
+##     transform_df: function
+##     super:  <ggproto object: Class ScaleDiscrete, Scale>
+\end{verbatim}
+
+The linking hypothesis under discussion assumes that speaker
+probabilities of utterance given meaning are invariant across a) our
+four different experimental conditions, b) across participants, and c)
+within participants (that is, participants are not capable of updating
+their \(S_1\) distribution in a local discourse context). We note that
+the assumption (b) may conceivably be relaxed by allowing one or more of
+the parameters in the model -- including the prior probability over
+world states \(P_w\), the cost function on utterances \(C\), or the
+rationality parameter \(\alpha\) -- to vary across participants. We also
+note that assumption (c) in particular is in tension with a growing body
+of empirical evidence that semantic and pragmatic interpretation is
+modulated by rapid adaptation to the linguistic and social features of
+one's interlocutors (Fine, Jaeger, Farmer, \& Qian, 2013; Kleinschmidt
+\& Jaeger, 2015).
+
+However, if we should like to keep the above assumptions in place, then
+we must look elsewhere to explain the observed variation in our
+experimental data. In particular, this linking hypothesis, coupled with
+our assumptions, commits us to explaining variation in the data in terms
+of the threshold parameters of our responder model \(R\). Consider first
+the variation in response across different experimental conditions on a
+given trial, e.g.~evaluation of a guess of \enquote{cat and dog} when
+the card contains both a cat and a dog. The variation in the proportion
+of responses of \enquote{right} on this trial between the binary,
+ternary, quaternary, and quinary conditions indicates that the threshold
+value for \enquote{right} responses must vary across conditions; that
+is, we predict that the \(\theta\) of the binary condition will differ
+from, e.g., the \(\theta_1\) of the ternary condition as well as the
+\(\theta_1\) of the quaternary condition. We also observed variation in
+response on this trial within a single condition (for example, a
+sizeable minority of participants responded \enquote{wrong} to this
+trial in the binary condition). Thus, this linking hypothesis is
+committed to the notion that threshold values may vary across
+participants, such that a speaker probability of utterance \(S_1\)(u
+\textbar{} s) can fall below \(\theta\) for some subset of participants
+while \(S_1\)(u \textbar{} s) itself remains constant across
+participants.
+
+Lastly, it is conceivable that for two utterances of the same
+conditional probability and in the same experimental condition, a
+participant in our experiment provided a judgment of, e.g.
+\enquote{right} to one utterance but \enquote{wrong} to the other. That
+is, it is possible that there was within-subject variation in this
+experiment. One way to represent such variation would be to posit that
+the parameterization of threshold values proceeds stochastically and
+that threshold values are recalibrated for every individual sentence
+verification task. Rather than representing a threshold as a discrete
+value N between 0 and 1, we can represent that threshold as a
+distribution over possible threshold values -- with mass centered around
+N. Whenever an individual encounters a sentence verification task, such
+as a single trial of our truth value judgment task experiment, the
+threshold value is recalibrated by sampling from this distribution. If
+we allow values of \(\theta\) to vary as a result of this schotastic
+process, for the possibility that \(S_1\)(u \textbar{} s) sometimes
+falls below \(\theta\) (and is otherwise above \(\theta\)) for a given
+participant.
+
+One outstanding empirical problem is the pattern of response we observed
+for \enquote{cat and dog} on trials where there was only a cat on the
+card. Because this utterance is strictly false in this world state, it
+is surprising -- on both the traditional view as well as on the account
+developed here -- that participants assigned this utterance ratings
+above \enquote{wrong} with any systematicity. However, this is exactly
+what we observed, particulary in the quaternary and quinary conditions
+of the experiment, where a sizeable minority of participants considered
+this utterance \enquote{kinda right}. As Figure \ref{fig:speakerprobs}
+demonstrates, the conditional speaker probability of this utterance in
+this world state is 0; thus, there is no conceivable threshold value
+that would allow this utterance to ever be rated above \enquote{wrong}
+(on the reasonable assumption that the thresholds in our responder model
+\(R\) should be nonzero). Any linking hypothesis will have to engage
+with this data point, and we leave to future work an analysis which
+captures participants' behavior in this condition.
+
+For the time being, however, we present the above analysis as a proof of
+concept for the following idea: by relaxing the assumptions of the
+traditional view of scalar implicature (namely, that scalar implicatures
+either are or are not calculated, and that behavior on sentence
+verification tasks directly reflects this binary interpretation
+process), we can propose quantitative models of the variation in
+behavior we observe in experimental settings. We note that the linking
+analysis proposed here is just one in the space of possible analyses
+when traditional assumptions about scalar implicature are relaxed. For
+example, one might reject this threshold-based analysis in favor of one
+whereby responses are the outcomes of sampling on the (pragmatic speaker
+or pragmatic listener) probability distributions provided by an RSA
+model. We must leave this investigation to future work, but for now we
+emphasize that this kind of quantitative, data-driven and systematic
+model criticism is made available to researchers in experimental
+pragmatics by revising core assumptions about the nature of scalar
+implicature. Though we no longer have a crisp notion of scalar
+implicature as something that is or is not \enquote{calculated} in
+interpretation, we have new flexibility to explicitly discuss
+categorical behavior in experimental settings.
+
+Concluding, we have shown in this paper that inferred
+\enquote{implicature rate} -- ubiquitous in theoretical and experimental
+pragmatics -- as estimated in truth value judgment tasks, depends on
+both the number of responses participants are provided with as well as
+on the linking hypothesis from proportion of behavioral responses to
+\enquote{implicature rate}. We further sketched an alternate linking
+hypothesis that treats behavioral responses as the result of
+probabilistic reasoning about speakers' likely productions. While a
+thorough model comparison is still outstanding, this kind of linking
+hypothesis opens a door towards more systematic and rigorous formulation
+and testing of linking hypotheses between theoretical notions of
+interest in pragmatics and behavioral responses in experimental
+paradigms.
 
@@
 
+\hypertarget{ref-Bott2016}{}
+Bott, L., \& Chemla, E. (2016). Shared and distinct mechanisms in
+deriving linguistic enrichment. \emph{Journal of Memory and Language},
+\emph{91}, 117--140.
+doi:\href{https://doi.org/10.1016/j.jml.2016.04.004}{10.1016/j.jml.2016.04.004}
+
 \hypertarget{ref-Bott2004}{}
@@
 
+\hypertarget{ref-Fine2013}{}
+Fine, A. B., Jaeger, T. F., Farmer, T. F., \& Qian, T. (2013). Rapid
+expectation adaptation during syntactic comprehension. \emph{PLoS ONE},
+\emph{8}(10).
+doi:\href{https://doi.org/10.1371/\%20journal.pone.0077661}{10.1371/ journal.pone.0077661}
+
 \hypertarget{ref-Frank2012}{}
@@
 doi:\href{https://doi.org/10.1016/j.cognition.2011.02.015}{10.1016/j.cognition.2011.02.015}
+
+\hypertarget{ref-Kleinschmidt2015}{}
+Kleinschmidt, D. F., \& Jaeger, T. F. (2015). Robust speech perception:
+Recognize the familiar, generalize to the similar, and adapt to the
+novel. \emph{Psychological Review}, \emph{122}(2), 148--203.
+doi:\href{https://doi.org/10.1037/a0038695}{10.1037/a0038695}
 

### 2018-05-10 writeup.Rmd
formulae rendered as equations in gd
some styling changes

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "XXX Postal address"
-    email         : "XXX my@email.com"
+    address       : "Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA, 94305-2150"
+    email         : "masoudj@stanford.edu"
   - name          : "Brandon Waldon"
@@
   - id            : "1"
-    institution   : "Stanford University"
+    institution   : "Stanford University, Department of Linguistics"
 author_note: |
@@
 
-```{r speakerprobs, message=FALSE, warning=FALSE,fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
+```{r speakerprobs, message=FALSE, warning=FALSE, fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
 
@@
   # theme_few() +
-  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1))
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1)) +
   scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

### 2018-05-10 writeup.tex
some styling changes

@@
 Bob. Bob was blindfolded to avoid violations of ignorance expectations
-associated with the use of disjunction ({\textbf{???}}; Chierchia et
-al., 2001) Participants were told that Bob would guess the contents of
-the cards and their task was to indicate whether Bob's guess was wrong
-or right. On each trial, participants saw a card and a sentence
-representing Bob's guess. For example, they saw a card with a cat and
-read the sentence \enquote{There is a cat on the card.} They then
-provided an assessment of Bob's guess. The study ended after 24 trials.
+associated with the use of disjunction (Chierchia et al., 2001;
+Sauerland, 2004) Participants were told that Bob would guess the
+contents of the cards and their task was to indicate whether Bob's guess
+was wrong or right. On each trial, participants saw a card and a
+sentence representing Bob's guess. For example, they saw a card with a
+cat and read the sentence \enquote{There is a cat on the card.} They
+then provided an assessment of Bob's guess. The study ended after 24
+trials.
 
@@
 
-\begin{verbatim}
-## <ggproto object: Class ScaleDiscrete, Scale>
-##     aesthetics: fill
-##     axis_order: function
-##     break_info: function
-##     break_positions: function
-##     breaks: waiver
-##     call: call
-##     clone: function
-##     dimension: function
-##     drop: TRUE
-##     expand: waiver
-##     get_breaks: function
-##     get_breaks_minor: function
-##     get_labels: function
-##     get_limits: function
-##     guide: FALSE
-##     is_discrete: function
-##     is_empty: function
-##     labels: waiver
-##     limits: NULL
-##     make_sec_title: function
-##     make_title: function
-##     map: function
-##     map_df: function
-##     n.breaks.cache: NULL
-##     na.translate: TRUE
-##     na.value: NA
-##     name: waiver
-##     palette: function
-##     palette.cache: NULL
-##     position: left
-##     range: <ggproto object: Class RangeDiscrete, Range>
-##         range: NULL
-##         reset: function
-##         train: function
-##         super:  <ggproto object: Class RangeDiscrete, Range>
-##     reset: function
-##     scale_name: manual
-##     train: function
-##     train_df: function
-##     transform: function
-##     transform_df: function
-##     super:  <ggproto object: Class ScaleDiscrete, Scale>
-\end{verbatim}
-
 The linking hypothesis under discussion assumes that speaker
@@
 Goodman (Eds.), \emph{Proceedings of the formal \& experimental
-pragmatics workshop, european summer school for language, logic and
-information (esslli)} (pp. 1--6). Tübingen.
+pragmatics workshop, European Summer School for Language, Logic and
+Information (ESSLLI)} (pp. 1--6). Tübingen.
 
@@
 \hypertarget{ref-burkner2016brms}{}
-Bürkner, P.-C., \& others. (2016). Brms: An r package for bayesian
-multilevel models using stan. \emph{Journal of Statistical Software},
+Bürkner, P.-C., \& others. (2016). brms: An R package for bayesian
+multilevel models using Stan. \emph{Journal of Statistical Software},
 \emph{80}(1), 1--28.
@@
 \hypertarget{ref-Chemla2011}{}
-Chemla, E., \& Spector, B. (2011). Experimental Evidence for Embedded
-Scalar Implicatures. \emph{Journal of Semantics}, \emph{28}(3),
+Chemla, E., \& Spector, B. (2011). Experimental evidence for embedded
+scalar implicatures. \emph{Journal of Semantics}, \emph{28}(3),
 359--400.
@@
 Chierchia, G., Crain, S., Teresa, M., Guasti, M. T., Gualmini, A., \&
-Meroni, L. (2001). The Acquisition of Disjunction: Evidence for a
-Grammatical View of Scalar Implicatures. In A. H.-J. D. Et al. (Ed.),
-\emph{BUCLD 25 proceedings} (pp. 157--168). Somerville, MA: Cascadilla
-Press.
+Meroni, L. (2001). The acquisition of disjunction: Evidence for a
+grammatical view of scalar implicatures. In Anna H.-J. Do Laura
+Domínguez \& A. Johansen (Eds.), \emph{Proceedings of the 25th annual
+boston university conference on language development} (pp. 157--168).
+Somerville, MA: Cascadilla Press.
 
 \hypertarget{ref-DeNeys2007}{}
-De Neys, W., \& Schaeken, W. (2007). When People Are More Logical Under
-Cognitive Load - Dual Task Impact on Scalar Implicature.
+De Neys, W., \& Schaeken, W. (2007). When people are more logical under
+cognitive load - dual task impact on scalar implicature.
 \emph{Experimental Psychology}, \emph{54}(2), 128--133.
@@
 \hypertarget{ref-Degen2015}{}
-Degen, J. (2015). Investigating the distribution of 'some' (but not
-'all') implicatures using corpora and web-based methods. \emph{Semantics
-and Pragmatics}, \emph{8}(11), 1--55.
+Degen, J. (2015). Investigating the distribution of ``some'' (but not
+``all'') implicatures using corpora and web-based methods.
+\emph{Semantics and Pragmatics}, \emph{8}(11), 1--55.
 doi:\href{https://doi.org/10.3765/sp.8.11}{10.3765/sp.8.11}
@@
 Degen, J., \& Goodman, N. D. (2014). Lost your marbles? The puzzle of
-dependent measures in experimental pragmatics. \emph{Proceedings of the
-36th Annual Conference of the Cognitive Science Society}, 397--402.
+dependent measures in experimental pragmatics. In P. Bello, M. Guarini,
+M. McShane, \& B. Scassellati (Eds.), \emph{Proceedings of the 36th
+annual conference of the cognitive science society} (pp. 397--402).
 
@@
 \hypertarget{ref-DegenTanenhaus2016}{}
-Degen, J., \& Tanenhaus, M. K. (2016). Availability of Alternatives and
-the Processing of Scalar Implicatures: A Visual World Eye-Tracking
-Study. \emph{Cognitive Science}, \emph{40}(1), 172--201.
+Degen, J., \& Tanenhaus, M. K. (2016). Availability of alternatives and
+the processing of scalar implicatures: A visual world eye-tracking
+study. \emph{Cognitive Science}, \emph{40}(1), 172--201.
 doi:\href{https://doi.org/10.1111/cogs.12227}{10.1111/cogs.12227}
@@
 \hypertarget{ref-Degen2013}{}
-Degen, J., Franke, M., \& Jäger, G. (2013). Cost-Based Pragmatic
-Inference about Referential Expressions. \emph{Proceedings of the 35th
-Annual Conference of the Cognitive Science Society (CogSci'13)},
-376--281.
+Degen, J., Franke, M., \& Jäger, G. (2013). Cost-based pragmatic
+inference about referential expressions. \emph{Proceedings of the 35th
+Annual Conference of the Cognitive Science Society}, 376--281.
 
@@
 \hypertarget{ref-Franke2016}{}
-Franke, M., \& Jäger, G. (2016). Probabilistic pragmatics, or why Bayes
-' rule is probably important for pragmatics. \emph{Zeitschrift Für
+Franke, M., \& Jäger, G. (2016). Probabilistic pragmatics, or why Bayes'
+rule is probably important for pragmatics. \emph{Zeitschrift Für
 Sprachwissenschaft}, \emph{35}(1), 3--44.
@@
 \hypertarget{ref-Goodman2016}{}
-Goodman, N. D., \& Frank, M. C. (2016). Pragmatic Language
-Interpretation as Probabilistic Inference. \emph{Trends in Cognitive
+Goodman, N. D., \& Frank, M. C. (2016). Pragmatic language
+interpretation as probabilistic inference. \emph{Trends in Cognitive
 Sciences}, \emph{20}(11), 818--829.
@@
 \hypertarget{ref-grice1975}{}
-Grice, H. P. (1975). Logic and Conversation. \emph{Syntax and
-Semantics}, \emph{3}, 41--58. Retrieved from
-\href{http://books.google.com/books?hl=en\%7B/\&\%7Dlr=\%7B/\&\%7Did=hQCzOmaGeVYC\%7B/\&\%7Doi=fnd\%7B/\&\%7Dpg=PA121\%7B/\&\%7Ddq=Logic+and+conversation\%7B/\&\%7Dots=j7aijUymwm\%7B/\&\%7Dsig=iV1rz1eEm4ns6bQ6CevIURXFVO4}{http://books.google.com/books?hl=en\{\textbackslash{}\&\}lr=\{\textbackslash{}\&\}id=hQCzOmaGeVYC\{\textbackslash{}\&\}oi=fnd\{\textbackslash{}\&\}pg=PA121\{\textbackslash{}\&\}dq=Logic+and+conversation\{\textbackslash{}\&\}ots=j7aijUymwm\{\textbackslash{}\&\}sig=iV1rz1eEm4ns6bQ6CevIURXFVO4}
+Grice, H. P. (1975). Logic and conversation. \emph{Syntax and
+Semantics}, \emph{3}, 41--58.
 
@@
 \hypertarget{ref-Horowitz2017}{}
-Horowitz, A. C., Schneider, R. M., \& Frank, M. C. (2017). The Trouble
-With Quantifiers: Exploring Children's Deficits in Scalar Implicature.
+Horowitz, A. C., Schneider, R. M., \& Frank, M. C. (2017). The trouble
+with quantifiers: Exploring children's deficits in scalar implicature.
 \emph{Child Development}, 1--40.
@@
 experimental investigations of scalar implicature. \emph{Cognition},
-\emph{78}(2), 165--188. Retrieved from
-\url{http://www.ncbi.nlm.nih.gov/pubmed/11074249}
+\emph{78}(2), 165--188.
 
@@
 \hypertarget{ref-Noveck2003}{}
-Noveck, I., \& Posada, A. (2003). Characterizing the Time Course of an
-Implicature: an Evoked Potentials Study. \emph{Brain and Language},
+Noveck, I., \& Posada, A. (2003). Characterizing the time course of an
+implicature: An evoked potentials study. \emph{Brain and Language},
 \emph{85}(2), 203--210.
@@
 \hypertarget{ref-Papafragou2004}{}
-Papafragou, A., \& Tantalou, N. (2004). Children's Computation of
-Implicatures. \emph{Language Acquisition}, \emph{12}(1), 71--82.
+Papafragou, A., \& Tantalou, N. (2004). Children's computation of
+implicatures. \emph{Language Acquisition}, \emph{12}(1), 71--82.
 
@@
 \hypertarget{ref-Qing2015}{}
-Qing, C., \& Franke, M. (2015). Variations on a bayesian theme:
-Comparing bayesian models of referential reasoning. In H. Zeevat \&
+Qing, C., \& Franke, M. (2015). Variations on a Bayesian theme:
+Comparing Bayesian models of referential reasoning. In H. Zeevat \&
 H.-C. Schmitz (Eds.), \emph{Bayesian natural language semantics and
@@
 doi:\href{https://doi.org/10.1007/978-3-319-17064-0_9}{10.1007/978-3-319-17064-0\_9}
+
+\hypertarget{ref-sauerland2004scalar}{}
+Sauerland, U. (2004). Scalar implicatures in complex sentences.
+\emph{Linguistics and Philosophy}, \emph{27}(3), 367--391.
 
@@
 Stiller, A. J., Goodman, N. D., \& Frank, M. C. (2015). Ad-hoc
-Implicature in Preschool Children. \emph{Language Learning and
+implicature in preschool children. \emph{Language Learning and
 Development}, \emph{11}(2), 176--190.

### 2018-05-10 writeup.Rmd
added word count, linguistic exmpales, and conflict of interest statement

@@
 author_note: |
-  XXX Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-  Enter author note here.
+  The authors declare that they have no affiliations with, or involvement in any organization or entity with any financial interest, or non-financial interest in the subject matter or materials discussed in this manuscript.
 abstract: |
@@
 keywords          : "scalar implicature; methodology; linking hypothesis; experimental pragmatics; truth value judgment task"
-wordcount         : "X"
+wordcount         : "9037"
 bibliography      : ["r-references.bib"]
-figsintext        : yes
+figsintext        : no
 figurelist        : no
@@
 
-1. 
-  + *Utterance:* Some of her pets are cats.
-  + *Implicature:* Some, but not all, of her pets are cats.
-  + *Scale:* <all, some>
-
-2. 
-  + *Utterance:* She owns a cat or a dog.
-  + *Implicature:* She owns a cat or a dog, but not both.
-  + *Scale:* <and, or>
+(1) Some of her pets are cats.
+
+*Implicature:* Some, but not all, of her pets are cats.
+
+*Scale:* $<$all, some$>$
+
+(2) She owns a cat or a dog.
+
+*Implicature:* She owns a cat or a dog, but not both.
+
+*Scale:* $<$and, or$>$
 
@@
 
-    $P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
-
-    $P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $
-
-    $P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
+$$
+
+    P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\
+
+    P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\
+
+    P_{L_0}(s | u) \propto [[u]](s) * P_w(s)
+
+$$
 

### 2018-05-10 writeup.tex
added word count, linguistic exmpales, and conflict of interest statement

@@
-\documentclass[floatsintext,man]{apa6}
+\documentclass[man]{apa6}
 
@@
   {\end{ThreePartTable}\end{center}\end{landscape}}
+
+  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
+  \ifthenelse{\equal{\string man}{\string man}}{%
+   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
+   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
+   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
+  }{}%
 
@@
     \vspace{0.5cm}
-          \textsuperscript{1} Stanford University  }
+          \textsuperscript{1} Stanford University, Department of Linguistics  }
 
   \authornote{
-    XXX Add complete departmental affiliations for each author here. Each
-    new line herein must be indented, like this line. Enter author note
-    here.
+    The authors declare that they have no affiliations with, or involvement
+    in any organization or entity with any financial interest, or
+    non-financial interest in the subject matter or materials discussed in
+    this manuscript.
 
     Correspondence concerning this article should be addressed to Masoud
-    Jasbi, XXX Postal address. E-mail: XXX
-    \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+    Jasbi, Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA,
+    94305-2150. E-mail:
+    \href{mailto:masoudj@stanford.edu}{\nolinkurl{masoudj@stanford.edu}}
   }
@@
 
-    \indent Word count: X
+    \indent Word count: 9037
   }
@@
 \begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-\end{enumerate}
-
-\begin{itemize}
+\def\labelenumi{(\arabic{enumi})}
 \tightlist
 \item
-  \emph{Utterance:} Some of her pets are cats.
-\item
+  Some of her pets are cats.
+\end{enumerate}
+
 \emph{Implicature:} Some, but not all, of her pets are cats.
-\item
-  \emph{Scale:} 
-\end{itemize}
+
+\emph{Scale:} \(<\)all, some\(>\)
 
 \begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
+\def\labelenumi{(\arabic{enumi})}
 \setcounter{enumi}{1}
-\item
-\end{enumerate}
-
-\begin{itemize}
 \tightlist
 \item
-  \emph{Utterance:} She owns a cat or a dog.
-\item
+  She owns a cat or a dog.
+\end{enumerate}
+
 \emph{Implicature:} She owns a cat or a dog, but not both.
-\item
-  \emph{Scale:} 
-\end{itemize}
+
+\emph{Scale:} \(<\)and, or\(>\)
 
@@
 
+\$\$
+
 \begin{verbatim}
-$P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
-
-$P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $
-
-$P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
+P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\
+
+P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\
+
+P_{L_0}(s | u) \propto [[u]](s) * P_w(s)
 \end{verbatim}
+
+\$\$
 

### 2018-05-10 writeup.Rmd
fixed the equations, ready for final review

@@
 $\hat{R}=1$ for all estimated parameters.
-All the analytical decisions described here were pre-registered[^3].
-
-[^3: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]
+All the analytical decisions described here were pre-registered[^5].
+
+[^3]: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).
 
@@
 
-[^3]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
+[^5]: You can access our pre-registration at [https://aspredicted.org/tq3sz.pdf](https://aspredicted.org/tq3sz.pdf)
 
@@
 
-$$
-
-    P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\
-
-    P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\
-
-    P_{L_0}(s | u) \propto [[u]](s) * P_w(s)
-
-$$
+$P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$
+
+$P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u)))$
+
+$P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
 

### 2018-05-10 writeup.tex
some version
fixed the equations, ready for final review

@@
 the R packge \enquote{brms} (Bürkner \& others, 2016) with uninformative
-or weakly informative priors.\footnote{You can access our
-  pre-registration at \url{https://aspredicted.org/tq3sz.pdf}} The model
-predicted the log odds of implicature over no implicature from fixed
-effects of \emph{response type} (binary, ternary, quaternary, quinary --
-dummy-coded with binary as reference level), \emph{link} (strong
-vs.~weak -- dummy-coded with strong as reference level), and trial type
-(exhaustive vs.~scalar -- dummy-coded, with exhaustive as reference
-level), as well as their two-way and three-way interactions. Following
-Barr, Levy, Scheepers, and Tily (2013), we included the maximal random
-effects structure justified by the design: random intercepts for items
-(cards) and participants, random by-participant slopes for link, trial
-type, and their interaction, and random by-item slopes for link, trial
-type, response type, and their interactions. Since the number of
-response options was a between participant variable we did not include
-random slopes of response options for participants. Four chains
-converged after 2000 iterations each (warmup = 1000). Table
-\ref{tab:modeltable} summarizes the mean parameter estimates and their
-95\% credible intervals. \(\hat{R}=1\) for all estimated parameters. All
-the analytical decisions described here were pre-registered\footnote{You
-  can access our pre-registration at
+or weakly informative priors.\footnote{For more information about the
+  default priors of the \enquote{brms} package, see
+  \href{ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf}{the
+  brms package manual}.} The model predicted the log odds of implicature
+over no implicature from fixed effects of \emph{response type} (binary,
+ternary, quaternary, quinary -- dummy-coded with binary as reference
+level), \emph{link} (strong vs.~weak -- dummy-coded with strong as
+reference level), and trial type (exhaustive vs.~scalar -- dummy-coded,
+with exhaustive as reference level), as well as their two-way and
+three-way interactions. Following Barr, Levy, Scheepers, and Tily
+(2013), we included the maximal random effects structure justified by
+the design: random intercepts for items (cards) and participants, random
+by-participant slopes for link, trial type, and their interaction, and
+random by-item slopes for link, trial type, response type, and their
+interactions. Since the number of response options was a between
+participant variable we did not include random slopes of response
+options for participants. Four chains converged after 2000 iterations
+each (warmup = 1000). Table \ref{tab:modeltable} summarizes the mean
+parameter estimates and their 95\% credible intervals. \(\hat{R}=1\) for
+all estimated parameters. All the analytical decisions described here
+were pre-registered\footnote{You can access our pre-registration at
   \url{https://aspredicted.org/tq3sz.pdf}}.
-
-{[}\^{}3: For more information about the default priors of the
-\enquote{brms} package, see
-\href{ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf}{the
-brms package manual}.{]}
 
@@
 
-\$\$
-
-\begin{verbatim}
-P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\
-
-P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\
-
-P_{L_0}(s | u) \propto [[u]](s) * P_w(s)
-\end{verbatim}
-
-\$\$
+\(P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)\)
+
+\(P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u)))\)
+
+\(P_{L_0}(s | u) \propto [[u]](s) * P_w(s)\)
 

### 2018-05-10 manuscript.tex
edits to intro

--- 2018-05-10 writeup.tex
@@
 informed the work on acquisition, online processing, and scalar
-diversity, inter alia. Despite its theoretical importance. Implicature
+diversity, inter alia.  Implicature
 rate has typically been quantified as the proportion of `pragmatic'
@@
 
-\emph{Scale:} \(<\)all, some\(>\)
+\emph{Scale:} $\langle$all, some$\rangle$
 
@@
 
-\emph{Scale:} \(<\)and, or\(>\)
-
-A listener, upon observing the utterances in (1-2a) typically infers
-that the speaker intended to convey the meanings in (1-2b),
+\emph{Scale:} $\langle$and, or$\rangle$
+
+A listener, upon observing the utterances in (1-2) typically infers
+that the speaker intended to convey the meanings listed as \emph{Implicature}s,
 respectively. Since Grice (1975), the agreed-upon abstract
@@
 statement by producing the stronger alternative (e.g., \emph{All of her
-pets are cats.} in (1)). If the stronger alternative is true, they
+pets are cats} in (1)). If the stronger alternative is true, they
 should have produced it to comply with the Cooperative Principle. They
-chose not to. I believe the speaker knows whether the stronger
-alternative is true. Hence, it must not be true. The derivation
-procedure for ad hoc exhaustive inferences such as in (3) is assumed to
+chose not to. Assuming the speaker knows whether the stronger
+alternative is true, it must not be true. The derivation
+procedure for ad hoc exhaustivity inferences such as in (3) is assumed to
 be calculable in the same way as for scalar implicatures, though the
 scale is assumed to be contextually driven.
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  She owns a cat.
+\end{enumerate}
+
+\emph{Implicature:} She owns only a cat.
+
+\emph{Scale:} $\langle$cat and dog, cat$\rangle$
 
@@
 instead a participant responds \enquote{TRUE}, that is taken to indicate
-that they interpreted the utterance literally as `Some, and possibly
-all, elephants are mammals' or \enquote{You got some, and possibly all,
+that they interpreted the utterance literally as ``Some, and possibly
+all, elephants are mammals'' or \enquote{You got some, and possibly all,
 of the gumballs}.
@@
 lack of discussion of the basic assumption that it is adequately
-captured by the proportion of FALSE responses in truth value judgment
+captured by the proportion of ``FALSE' responses in truth value judgment
 tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
@@
 used is appealing in part because it allows for a direct mapping from
-response options -- TRUE and FALSE -- to interpretations -- literal and
+response options -- ``TRUE'' and ``FALSE' -- to interpretations -- literal and
 pragmatic. That the seeming simplicity of this mapping is illusory
@@
 that they could have grouped it with the positive endpoint of the scale
-and taken the hard line that only truly FALSE responses constitute
+and taken the hard line that only truly ``FALSE' responses constitute
 evidence of a full-fledged implicature. The point here is that there has
-been remarkably little consideration of \emph{linking hypothesiss}
+been remarkably little consideration of \emph{linking hypotheses}
 between behavioral measures and theoretical constructs in experimental
@@
 do or do not compute an implicature on any given occasion. In the
-General Discussion we will discuss both of these issues. First,
-following Degen and Goodman (2014), we will offer some remarks on why
+General Discussion we will discuss both of these issues.
+Following Degen and Goodman (2014), we will offer some remarks on why
 truth value judgment tasks are better thought of as measuring
 participants' estimates of speakers' \emph{production} probabilities.
-This will suggest a completely different class of linking hypothesiss.
-Next, we discuss an alternative conception of scalar implicature as a
+This will suggest a completely different class of linking hypotheses.
+We then discuss an alternative conception of scalar implicature as a
 probabilistic phenomeonen, a view that has recently rose to prominence
@@
 implicature, we argue, affords developing and testing quantitative
-linking hypothesiss in a rigorous and motivated way.
+linking hypotheses in a rigorous and motivated way.
 

### 2018-05-10 writeup_jd.Rmd
edits to intro

--- 2018-05-10 writeup.Rmd
@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA, 94305-2150"
-    email         : "masoudj@stanford.edu"
+    address       : "XXX Postal address"
+    email         : "XXX my@email.com"
   - name          : "Brandon Waldon"
@@
   - id            : "1"
-    institution   : "Stanford University, Department of Linguistics"
+    institution   : "Stanford University"
 author_note: |
@@
 
-[^3: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).]
+[^3]: For more information about the default priors of the "brms" package, see [the brms package manual](ftp://cran.r-project.org/pub/R/web/packages/brms/brms.pdf).
 
@@
 
-```{r speakerprobs, message=FALSE, warning=FALSE, fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
+```{r speakerprobs, message=FALSE, warning=FALSE,fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}
 
@@
   # theme_few() +
-  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1))
   scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

### 2018-05-10 manuscript.tex
final edits from jd

@@
 response options between participants and analyzed the results under
-different linking hypothesiss.
+different linking hypothesis.
 
@@
 there was a cat and a dog). We categorized their responses on such
-trials according to the weak and the Strong link introduced above, and
+trials according to the Weak and the Strong link introduced above, and
 tested whether the number of response options and the linking
-hypothesiss led to different conclusions about the rate of computed
+hypothesis led to different conclusions about the rate of computed
 implicatures in the experimental task.
@@
 associated with the use of disjunction (Chierchia et al., 2001;
-Sauerland, 2004) Participants were told that Bob would guess the
+Sauerland, 2004). Participants were told that Bob would guess the
 contents of the cards and their task was to indicate whether Bob's guess
@@
 
-In this paper we asked whether linking hypothesiss and number of
+In this paper we asked whether linking hypothesis and number of
 response options available to participants in truth value judgment tasks
@@
 While the binary truth value judgement task avoids the analytic decision
-between Strong and Weak linking hypothesiss, the results reported here
+between Strong and Weak linking hypothesis, the results reported here
 suggest that binary tasks can also underestimate participants' pragmatic
@@
 
-\subsection{Revisiting linking
-hypothesiss}\label{revisiting-linking-hypothesiss}
+\subsection{Revisiting the linking
+hypothesis}\label{revisiting-linking-hypothesis}
 
@@
 Concluding, we have shown in this paper that inferred
-\enquote{implicature rate} -- ubiquitous in theoretical and experimental
+\enquote{implicature rate} -- a ubiquitous notion in theoretical and experimental
 pragmatics -- as estimated in truth value judgment tasks, depends on

### 2018-05-16 manuscript.tex
submission version

@@
 \def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{1}
+\setcounter{enumi}{2}
 \tightlist
@@
 
-\emph{Scale:} $\langle$cat and dog, cat$\rangle$
+\emph{Scale:} $\langle$cat and dog, cat$\rangle$\\
+~\\
 
@@
 
+\section{Author Responsibilities}
+All authors contributed to the conception and design of the study.
+MJ conducted the online survey studies; reported the results and performed the statistical analysis; BW conducted the modeling and wrote the discussion section; JD wrote the theoretical introduction, and contributed to the experimental section and the discussion section and the modeling sections.
+All authors contributed to manuscript revision, read and approved the submitted version.
+
 \section{References}\label{references}

### 2018-10-31 manuscript.tex
minor edits to manuscript

@@
 
+\usepackage{color}
+\definecolor{Blue}{RGB}{0,0,250}
+\newcommand{\change}[1]{\textcolor{Blue}{[#1]}}
+
 \usepackage{tikz} % Variable definition to generate author note
@@
   computed automatically in online processing and only cancelled by
-  context in a second effortful step if required by context) (Bott \&
+  context in a second effortful step if required by context (Bott \&
   Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
@@
 
-In addressing all of these questions, it has been crucial to obtain
+In addressing all of these questions, it has been \change{important} to obtain
 estimates of \emph{implicature rates}. For 1., implicature rates from
@@
 observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
-children to distribute 1, 2, or 3 strawberries to a puppet depending on
+children to distribute \change{a small, a big, or a huge strawberry } to a puppet depending on
 \enquote{how good the puppet said it}. The result was that children gave
-on average fewer strawberries to the puppet when he produced
+on average \change{smaller} strawberries to the puppet when he produced
 underinformative utterances compared to when he produced literally true
@@
   vs. \enquote{disagree}--\enquote{agree}). While some studies have used
-  \enquote{false}--\enquote{true}, others have argued that judging truth
+  \enquote{false}--\enquote{true} \cite{bott2004, doran2012}, others have argued that judging truth
   may lead to meta-linguistic reasoning in participants that could
-  distort judgments.} In the binary case, this reproduces the standard
+  distort judgments \change{\cite{XXX} XXX FIX}.} In the binary case, this reproduces the standard
 truth value judgment task. Figure \ref{fig:linkvisualization}

### 2018-10-31 manuscript.tex
edits to manuscript that are mentioned in responses

@@
 tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
-Degen and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
+Degen and Goodman (2014); Katsos and Bishop (2011); \change{Sikos et al (this issue)}). Indeed, the scalar
 implicature acquisition literature was shaken up when Katsos and Bishop
@@
 used is appealing in part because it allows for a direct mapping from
-response options -- ``TRUE'' and ``FALSE' -- to interpretations -- literal and
+response options---``TRUE'' and ``FALSE'---to interpretations---literal and
 pragmatic. That the seeming simplicity of this mapping is illusory
@@
 scalar implicature rates? Note that this way of asking the question
-presupposes two things: first, that whatever participants are doing in a
+\change{assumes} two things: first, that whatever participants are doing in a
 truth value judgment task, the behavioral measure can be interpreted as
@@
   \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
-  vs. \enquote{disagree}--\enquote{agree}). While some studies have used
-  \enquote{false}--\enquote{true} \cite{bott2004, doran2012}, others have argued that judging truth
-  may lead to meta-linguistic reasoning in participants that could
-  distort judgments \change{\cite{XXX} XXX FIX}.} In the binary case, this reproduces the standard
+  vs. \enquote{disagree}--\enquote{agree}). \change{Studies vary in the labeling of scale points.}} In the binary case, this reproduces the standard
 truth value judgment task. Figure \ref{fig:linkvisualization}
@@
 Interval={[}10.64, 25.80{]}) with a weak link resulted in greater
-implicature rates. Finally, there was a three-way interaction between
+implicature rates \change{than with a strong link}. Finally, there was a three-way interaction between
 link, trial type, and number of response options (Mean Estimate = -7.74,
@@
 
+\change{\hypertarget{ref-Sikos2019}{}
+Sikos, L., Kim, M., \& Grodner, D.J. (in press). Social context modulates tolerance for pragmatic violations in binary but not graded judgments. \emph{Frontiers in Psychology}.}
+
 \hypertarget{ref-Stiller2015}{}

### 2018-10-31 manuscript.tex
added auxiliary analysis of 3-way interaction

@@
 implicature rates by condition and link.
-
-Visually, the Weak link tends to result in greater estimates of
-implicature rates, especially in tasks with more response options. Under
-the Strong link, this latter pattern is reversed: the binary and ternary
-judgment tasks result in greater estimates of implicature rates than
-with more response options.
+\change{It is immediately obvious that there is variability in inferred implicature rate.
+In particular, the Weak link appears to result in greater estimates of
+implicature rates in tasks with four or five response options, compared to the Strong link. For the binary and ternary task, the assumed link appears to play a much smaller role.}
 
@@
 implicature rate, we used a Bayesian binomial mixed effects model using
-the R packge \enquote{brms} (Bürkner \& others, 2016) with uninformative
-or weakly informative priors.\footnote{For more information about the
+the R packge \enquote{brms} (Bürkner \& others, 2016) with weakly informative priors.\footnote{For more information about the
   default priors of the \enquote{brms} package, see
@@
 random by-item slopes for link, trial type, response type, and their
-interactions. Since the number of response options was a between
-participant variable we did not include random slopes of response
+interactions. Since the number of response options was a between-participant variable we did not include random slopes of response
 options for participants. Four chains converged after 2000 iterations
@@
 all estimated parameters. All the analytical decisions described here
-were pre-registered\footnote{You can access our pre-registration at
+were pre-registered\footnote{Our preregistration can be accessed at
   \url{https://aspredicted.org/tq3sz.pdf}}.
@@
 and the quinary task (Mean Estimate = 17.28, 95\% Credible
-Interval={[}10.64, 25.80{]}) with a weak link resulted in greater
-implicature rates \change{than with a strong link}. Finally, there was a three-way interaction between
-link, trial type, and number of response options (Mean Estimate = -7.74,
-95\% Credible Interval={[}-16.59, -0.16{]}). One interpretation of this
-interaction is that the difference between the Weak and Strong link on
-scalar trials in the quinary task was smaller than on exhaustive trials,
-though we believe this is not too interesting, given that the binary
-reference level implicature estimate was lower for exhaustive trials in
-the first place. Crucially, both number of response options and link
-affect the inferred implicature rate.
+Interval={[}10.64, 25.80{]}) resulted in greater
+implicature rates \change{with a weak link than with a strong link, but there was no evidence of a link-dependent difference in inferred implicature rate for the binary and ternary task}.
+Finally, there was a three-way interaction between
+link, trial type, and number of response options, \change{driven by the binary/quinary contrast} (Mean Estimate = -7.74,
+95\% Credible Interval={[}-16.59, -0.16{]}).
+\change{Simple effects analysis on only the binary and and quinary trials, separately for the exhaustive and scalar subset of the data, revealed that the three-way interaction is driven by a different effect of number of response options under the Weak vs Strong link for the two inference types.
+Specifically, on exhaustive trials, number of response options (2 vs.~5) only resulted in greater implicature rates under the Weak ($\beta$ = .2, $p <$ .0001), but not the Strong link ($\beta$ = -.8, $p <$ .82).
+In contrast, on scalar trials, number of response options (2 vs.~5) resulted in greater implicature rates under the Weak ($\beta$ = 3.6, $p <$ .005) link, and in lower implicature rates under the Strong link ($\beta$ = -4.0, $p <$ .0007).}
+
+\change{In sum,} both number of response options and link
+affected the inferred implicature rate\change{, as did the type of inference (exhaustive vs.~scalar)}.
 

### 2018-10-31 manuscript.tex
added degen and goodman footnote

@@
 affects inferred implicature rates. The results presented here suggest
-they do. A linking assupmtion that considered the highest point on the
+they do. A linking assumption that considered the highest point on the
 scale literal and any lower point pragmatic (Weak link) resulted in
@@
 options were provided. These observations are in line with Katsos and
-Bishop (2011)\enquote{s argument that pragmatic violations are not as
+Bishop (2011)'s argument that pragmatic violations are not as
 severe as semantic violations and participants do not penalize them as
@@
 (e.g.~wrong/right, false/true) when pragmatic violations are considered
-to be of an intermediate nature risks misrepresentation of participants}
+to be of an intermediate nature risks misrepresentation of participants'
 pragmatic competence. It further suggests that in studies that use
@@
 \& Jäger, 2016; Goodman \& Frank, 2016; Goodman \& Stuhlmüller, 2013;
-Kao, Wu, Bergen, \& Goodman, 2014; Qing \& Franke, 2015; Scontras,
-Degen, \& Goodman, 2017). Much in the spirit of Gricean approaches to
+Kao, Wu, Bergen, \& Goodman, 2014; Qing \& Franke, 2015). Much in the spirit of Gricean approaches to
 pragmatic competence, the RSA framework takes as its point of departure
@@
 Goodman (2014), we proceed on the assumption that behavior on sentence
-verification tasks, such as truth value judgment tasks, is best modeled
+verification tasks such as truth value judgment tasks, is best modeled
 as a function of an individual's mental representation of a cooperative
-interlocutor (\(S_1\) in the language of RSA) rather than of a pragmatic
-listener who interprets utterances (\(P_{L_1}\)). In their paper, Degen
-\& Goodman argue that sentence verification tasks are relatively more
-sensitive to contextual manipulations (such as manipulation of the
-Question Under Discussion) than are sentence interpretation tasks, and
+\change{speaker} (\(S_1\) in the language of RSA) rather than of a pragmatic
+listener who interprets utterances (\(P_{L_1}\)).\footnote{\change{Degen and Goodman (2014) argue that sentence verification is more plausibly construed as a production task rather than as an interpretation task because participants, unlike in natural language comprehension, are provided with the ground truth about the state of the world that a speaker is describing.
+Thus, participants are in essence being asked to assess the quality of a speaker's utterance.
+In contrast, Degen and Goodman argue, true interpretation tasks are characterized by the listener inferring what the state of the world is that the speaker is describing, for instance by selecting from one of multiple interpretation options.}} In their paper, Degen
+\& Goodman \change{show} that sentence verification tasks are relatively more
+sensitive to contextual \change{features like} the
+Question Under Discussion than are sentence interpretation tasks, and
 that this follows if sentence interpretation tasks -- but not sentence

### 2018-10-31 manuscript.tex
updated change macro
Added discussion of exhaustive/scalar asymmetry to .tex file

@@
 \definecolor{Blue}{RGB}{0,0,250}
-\newcommand{\change}[1]{\textcolor{Blue}{[#1]}}
+\newcommand{\change}[1]{\textcolor{Blue}{#1}}
 
@@
 
-One outstanding empirical problem is the pattern of response we observed
+\change{However, the model in its present form already captures an interesting asymmetry in inferred implicature rates between exhaustive and scalar trials of the experiment: note specifically (c.f.
+Figure 8) that inferred implicature rates are greater in the binary and ternary conditions for scalar trials over exhaustive trials.
+This is expected given the model’s inferred speaker probabilities: the speaker probability of producing “There is a cat on the card” in the context of there being a cat and dog on the card (an exhaustive implicature-inducing trial) is greater than the speaker probability of producing “There is a cat or a dog on the card” in that same context (a scalar implicature-inducing trial).
+Recall that these probabilities were derived via the simplifying assumption of uniform cost on utterances; in fact, adding cost to relatively complex disjunctive sentences over simple declarative sentences only predicts a more pronounced asymmetry in the experimentally-observed direction.}
+
+\change{Less readily explained is why this asymmetry disappears with the introduction of more response options, i.e.
+in the quaternary and quinary conditions.
+If anything, the opposite numerical trend is observed in these conditions: that is, inferred implicature rates are slightly greater in exhaustive trials over scalar trials.
+Future work should investigate the interaction between trial type (exhaustive vs.
+scalar) and number of response options.}
+
+One \change{additional} empirical problem is the pattern of response we observed
 for \enquote{cat and dog} on trials where there was only a cat on the

### 2018-10-31 manuscript.tex
updated gd

--- 2018-10-31 manuscript.tex
@@
 four different experimental conditions, b) across participants, and c)
-within participants (that is, participants are not capable of updating
+within participants (that is, participants do not update
 their \(S_1\) distribution in a local discourse context). We note that
@@
 one's interlocutors (Fine, Jaeger, Farmer, \& Qian, 2013; Kleinschmidt
-\& Jaeger, 2015).
-
-However, if we should like to keep the above assumptions in place, then
-we must look elsewhere to explain the observed variation in our
-experimental data. In particular, this linking hypothesis, coupled with
-our assumptions, commits us to explaining variation in the data in terms
+\& Jaeger, 2015; \change{Yildirim, Degen, Tanenhaus, \& Jaeger, 2016)}.
+
+However, if we should like to keep the above \change{simplifying} assumptions in place, then
+this linking hypothesis commits us to explaining variation in the data in terms
 of the threshold parameters of our responder model \(R\). Consider first
@@
 
-Lastly, it is conceivable that for two utterances of the same
-conditional probability and in the same experimental condition, a
-participant in our experiment provided a judgment of, e.g.
+Lastly, for two utterances of the same
+conditional probability and in the same experimental condition, 
+participants in our experiment sometimes provided a judgment of
 \enquote{right} to one utterance but \enquote{wrong} to the other. That
-is, it is possible that there was within-subject variation in this
+is, there was within-subject variation in this
 experiment. One way to represent such variation would be to posit that
@@
 distribution over possible threshold values -- with mass centered around
-N. Whenever an individual encounters a sentence verification task, such
-as a single trial of our truth value judgment task experiment, the
-threshold value is recalibrated by sampling from this distribution. If
-we allow values of \(\theta\) to vary as a result of this schotastic
-process, for the possibility that \(S_1\)(u \textbar{} s) sometimes
-falls below \(\theta\) (and is otherwise above \(\theta\)) for a given
-participant.
-
-One outstanding empirical problem is the pattern of response we observed
+N. Whenever an individual encounters  a single trial of our truth value judgment task experiment, a
+threshold value is sampled from this distribution.
+\change{By  allowing values of \(\theta\) to vary stochastically in this way, we can capture that \(S_1\)(u \textbar{} s) can fall both above and below \(\theta\) for a given
+participant.}
+
+\change{The model in its present form already captures an interesting asymmetry in inferred implicature rates between exhaustive and scalar trials of the experiment: note specifically (c.f.
+Figure 8) that inferred implicature rates are greater in the binary and ternary conditions for scalar trials over exhaustive trials.
+This is expected given the model's inferred speaker probabilities: the speaker probability of producing ``There is a cat on the card'' in the context of there being a cat and dog on the card (an exhaustive implicature-inducing trial) is greater than the speaker probability of producing ``There is a cat or a dog on the card'' in that same context (a scalar implicature-inducing trial).
+Assuming noisy  $\theta$ values centered around N, participants are expected to respond `Right' more frequently on exhaustive than on scalar trials, which is precisely what is observed.
+Recall that these probabilities were derived via the simplifying assumption of uniform cost on utterances; in fact, adding cost to relatively complex disjunctive sentences over simple declarative sentences only predicts a more pronounced asymmetry in the experimentally-observed direction.}
+
+%\change{While we have offered only a preliminary qualitative sketch of the model's behavior here, future work should systematically analyze the quantitative fit between model predictions and the data.
+}
+
+%\change{Less readily explained is why this asymmetry disappears with the introduction of more response options, i.e.
+in the quaternary and quinary conditions.
+If anything, the opposite numerical trend is observed in these conditions: that is, inferred implicature rates are slightly greater in exhaustive trials over scalar trials.
+Future work should investigate the interaction between trial type (exhaustive vs.
+scalar) and number of response options.}
+
+One  empirical problem is the pattern of responses we observed
 for \enquote{cat and dog} on trials where there was only a cat on the
@@
 developed here -- that participants assigned this utterance ratings
-above \enquote{wrong} with any systematicity. However, this is exactly
+above \enquote{wrong} with any systematicity. However, this is 
 what we observed, particulary in the quaternary and quinary conditions
@@
 concept for the following idea: by relaxing the assumptions of the
-traditional view of scalar implicature (namely, that scalar implicatures
+traditional view of scalar implicature---namely, that scalar implicatures
 either are or are not calculated, and that behavior on sentence
 verification tasks directly reflects this binary interpretation
-process), we can propose quantitative models of the variation in
-behavior we observe in experimental settings. We note that the linking
-analysis proposed here is just one in the space of possible analyses
-when traditional assumptions about scalar implicature are relaxed. For
+process---we can propose quantitative models of the variation in
+behavior that is observed in experimental settings. We note that the linking
+hypothesis proposed here is just one in the space of possible hypotheses. For
 example, one might reject this threshold-based analysis in favor of one
@@
 or pragmatic listener) probability distributions provided by an RSA
-model. We must leave this investigation to future work, but for now we
-emphasize that this kind of quantitative, data-driven and systematic
-model criticism is made available to researchers in experimental
-pragmatics by revising core assumptions about the nature of scalar
-implicature. Though we no longer have a crisp notion of scalar
+model. We \change{leave this systematic, quantitative} investigation to future work. For now we
+emphasize that \change{explicit computational modeling of behavioral responses is a tool that is  available to researchers in experimental
+pragmatics. While using the RSA framework as the modeling tool requires revising traditional assumptions about the nature of scalar
+implicature by relaxing the crisp notion of scalar
 implicature as something that is or is not \enquote{calculated} in
-interpretation, we have new flexibility to explicitly discuss
-categorical behavior in experimental settings.
+interpretation, it provides new flexibility to explicitly discuss
+ behavior in experimental settings.
+One need not adopt the RSA framework as the tool for hypothesizing and testing the link between theoretical constructs and behavior in pragmatic experiments.
+However, the empirical findings we have reported here---that the inferences researchers draw about ``implicature rate'' are volatile and depend on various features of the paradigm and the linking hypothesis employed--- strongly suggest that experimental pragmatics  as a field must engage more seriously with the foundational questions of what we are measuring in the experiments we run.}
 
@@
 
+\change{\hypertarget{ref-Yildirim2016}{}
+Yildirim, I., Degen, J., Tanenhaus, M.K., \& Jaeger, T.F. (2016). Talker-specificity and adaptation in quantifier interpretation. \emph{Journal of Memory and Language}, \emph{87}, pp. 128-143.}
+
 \hypertarget{ref-Zondervan2010}{}

### 2018-11-01 manuscript.tex
Masoud revisions

--- 2018-10-31 manuscript.tex
@@
 
-\usepackage{color}
-\definecolor{Blue}{RGB}{0,0,250}
-\newcommand{\change}[1]{\textcolor{Blue}{[#1]}}
-
 \usepackage{tikz} % Variable definition to generate author note
@@
   computed automatically in online processing and only cancelled by
-  context in a second effortful step if required by context (Bott \&
+  context in a second effortful step if required by context) (Bott \&
   Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
@@
 
-In addressing all of these questions, it has been \change{important} to obtain
+In addressing all of these questions, it has been crucial to obtain
 estimates of \emph{implicature rates}. For 1., implicature rates from
@@
 tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
-Degen and Goodman (2014); Katsos and Bishop (2011); \change{Sikos et al (this issue)}). Indeed, the scalar
+Degen and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
 implicature acquisition literature was shaken up when Katsos and Bishop
@@
 observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
-children to distribute \change{a small, a big, or a huge strawberry } to a puppet depending on
+children to give a small, big, or huge strawberry to a puppet depending on
 \enquote{how good the puppet said it}. The result was that children gave
-on average \change{smaller} strawberries to the puppet when he produced
+the mid-size strawberry to the puppet when he produced
 underinformative utterances compared to when he produced literally true
@@
 used is appealing in part because it allows for a direct mapping from
-response options---``TRUE'' and ``FALSE'---to interpretations---literal and
+response options -- ``TRUE'' and ``FALSE' -- to interpretations -- literal and
 pragmatic. That the seeming simplicity of this mapping is illusory
@@
 scalar implicature rates? Note that this way of asking the question
-\change{assumes} two things: first, that whatever participants are doing in a
+suggests two things: first, that whatever participants are doing in a
 truth value judgment task, the behavioral measure can be interpreted as
@@
   \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
-  vs. \enquote{disagree}--\enquote{agree}). \change{Studies vary in the labeling of scale points.}} In the binary case, this reproduces the standard
+  vs. \enquote{disagree}--\enquote{agree}). While some studies have used
+  \enquote{false}--\enquote{true}, others have argued that judging truth
+  may lead to meta-linguistic reasoning in participants that could
+  distort judgments.} In the binary case, this reproduces the standard
 truth value judgment task. Figure \ref{fig:linkvisualization}
@@
 while 160 had no prior training in logic. All participants' data was
-included in the final analysis.
+included in the final analysis.\footnote{This study was carried out in accordance with the recommendations of the Common Rule, Federal Office for Human Research Protections.
+The protocol was approved by the Stanford University IRB 2 (non-medical research).
+All subjects gave Informed consent, documentation was waived by the IRB.}
 
@@
 implicature rates by condition and link.
-\change{It is immediately obvious that there is variability in inferred implicature rate.
-In particular, the Weak link appears to result in greater estimates of
-implicature rates in tasks with four or five response options, compared to the Strong link. For the binary and ternary task, the assumed link appears to play a much smaller role.}
+
+Visually, the Weak link tends to result in greater estimates of
+implicature rates, especially in tasks with more response options. Under
+the Strong link, this latter pattern is reversed: the binary and ternary
+judgment tasks result in greater estimates of implicature rates than
+with more response options.
 
@@
 implicature rate, we used a Bayesian binomial mixed effects model using
-the R packge \enquote{brms} (Bürkner \& others, 2016) with weakly informative priors.\footnote{For more information about the
+the R packge \enquote{brms} (Bürkner \& others, 2016) with uninformative
+or weakly informative priors.\footnote{For more information about the
   default priors of the \enquote{brms} package, see
@@
 random by-item slopes for link, trial type, response type, and their
-interactions. Since the number of response options was a between-participant variable we did not include random slopes of response
+interactions. Since the number of response options was a between
+participant variable we did not include random slopes of response
 options for participants. Four chains converged after 2000 iterations
@@
 all estimated parameters. All the analytical decisions described here
-were pre-registered\footnote{Our preregistration can be accessed at
+were pre-registered\footnote{You can access our pre-registration at
   \url{https://aspredicted.org/tq3sz.pdf}}.
@@
 and the quinary task (Mean Estimate = 17.28, 95\% Credible
-Interval={[}10.64, 25.80{]}) resulted in greater
-implicature rates \change{with a weak link than with a strong link, but there was no evidence of a link-dependent difference in inferred implicature rate for the binary and ternary task}.
-Finally, there was a three-way interaction between
-link, trial type, and number of response options, \change{driven by the binary/quinary contrast} (Mean Estimate = -7.74,
-95\% Credible Interval={[}-16.59, -0.16{]}).
-\change{Simple effects analysis on only the binary and and quinary trials, separately for the exhaustive and scalar subset of the data, revealed that the three-way interaction is driven by a different effect of number of response options under the Weak vs Strong link for the two inference types.
-Specifically, on exhaustive trials, number of response options (2 vs.~5) only resulted in greater implicature rates under the Weak ($\beta$ = .2, $p <$ .0001), but not the Strong link ($\beta$ = -.8, $p <$ .82).
-In contrast, on scalar trials, number of response options (2 vs.~5) resulted in greater implicature rates under the Weak ($\beta$ = 3.6, $p <$ .005) link, and in lower implicature rates under the Strong link ($\beta$ = -4.0, $p <$ .0007).}
-
-\change{In sum,} both number of response options and link
-affected the inferred implicature rate\change{, as did the type of inference (exhaustive vs.~scalar)}.
+Interval={[}10.64, 25.80{]}) with a weak link resulted in greater
+implicature rates than the strong link. Finally, there was a three-way interaction between
+link, trial type, and number of response options (Mean Estimate = -7.74,
+95\% Credible Interval={[}-16.59, -0.16{]}). One interpretation of this
+interaction is that the difference between the Weak and Strong link on
+scalar trials in the quinary task was smaller than on exhaustive trials,
+though we believe this is not too interesting, given that the binary
+reference level implicature estimate was lower for exhaustive trials in
+the first place. Crucially, both number of response options and link
+affect the inferred implicature rate.
 
@@
 affects inferred implicature rates. The results presented here suggest
-they do. A linking assumption that considered the highest point on the
+they do. A linking assupmtion that considered the highest point on the
 scale literal and any lower point pragmatic (Weak link) resulted in
@@
 options were provided. These observations are in line with Katsos and
-Bishop (2011)'s argument that pragmatic violations are not as
+Bishop (2011)\enquote{s argument that pragmatic violations are not as
 severe as semantic violations and participants do not penalize them as
@@
 (e.g.~wrong/right, false/true) when pragmatic violations are considered
-to be of an intermediate nature risks misrepresentation of participants'
+to be of an intermediate nature risks misrepresentation of participants}
 pragmatic competence. It further suggests that in studies that use
@@
 \& Jäger, 2016; Goodman \& Frank, 2016; Goodman \& Stuhlmüller, 2013;
-Kao, Wu, Bergen, \& Goodman, 2014; Qing \& Franke, 2015). Much in the spirit of Gricean approaches to
+Kao, Wu, Bergen, \& Goodman, 2014; Qing \& Franke, 2015; Scontras,
+Degen, \& Goodman, 2017). Much in the spirit of Gricean approaches to
 pragmatic competence, the RSA framework takes as its point of departure
@@
 Goodman (2014), we proceed on the assumption that behavior on sentence
-verification tasks such as truth value judgment tasks, is best modeled
+verification tasks, such as truth value judgment tasks, is best modeled
 as a function of an individual's mental representation of a cooperative
-\change{speaker} (\(S_1\) in the language of RSA) rather than of a pragmatic
-listener who interprets utterances (\(P_{L_1}\)).\footnote{\change{Degen and Goodman (2014) argue that sentence verification is more plausibly construed as a production task rather than as an interpretation task because participants, unlike in natural language comprehension, are provided with the ground truth about the state of the world that a speaker is describing.
-Thus, participants are in essence being asked to assess the quality of a speaker's utterance.
-In contrast, Degen and Goodman argue, true interpretation tasks are characterized by the listener inferring what the state of the world is that the speaker is describing, for instance by selecting from one of multiple interpretation options.}} In their paper, Degen
-\& Goodman \change{show} that sentence verification tasks are relatively more
-sensitive to contextual \change{features like} the
-Question Under Discussion than are sentence interpretation tasks, and
+interlocutor (\(S_1\) in the language of RSA) rather than of a pragmatic
+listener who interprets utterances (\(P_{L_1}\)). In their paper, Degen
+\& Goodman argue that sentence verification tasks are relatively more
+sensitive to contextual manipulations (such as manipulation of the
+Question Under Discussion) than are sentence interpretation tasks, and
 that this follows if sentence interpretation tasks -- but not sentence
@@
 
-\change{\hypertarget{ref-Sikos2019}{}
-Sikos, L., Kim, M., \& Grodner, D.J. (in press). Social context modulates tolerance for pragmatic violations in binary but not graded judgments. \emph{Frontiers in Psychology}.}
-
 \hypertarget{ref-Stiller2015}{}

### 2018-11-02 manuscript.tex

--- 2018-10-31 manuscript.tex
@@
 
-  \author{Masoud Jasbi\textsuperscript{1}, Brandon Waldon\textsuperscript{1}, \& Judith Degen\textsuperscript{1}}
+  \author{Masoud Jasbi\textsuperscript{1}, Brandon Waldon\textsuperscript{2}, \& Judith Degen\textsuperscript{2}}
 
@@
     \vspace{0.5cm}
-          \textsuperscript{1} Stanford University, Department of Linguistics  }
-
+       \textsuperscript{1} Harvard University, Department of Linguistics\\ 
+	\textsuperscript{2} Stanford University, Department of Linguistics }
   \authornote{
@@
     94305-2150. E-mail:
-    \href{mailto:masoudj@stanford.edu}{\nolinkurl{masoudj@stanford.edu}}
+    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoudj@stanford.edu}}
   }
@@
 Katsos \& Bishop, 2011; I. A. Noveck \& Reboul, 2008; Noveck \& Posada,
-2003; Papafragou \& Tantalou, 2004; Tiel, Miltenburg, Zevakhina, \&
-Geurts, 2014; Tomlinson, Bailey, \& Bott, 2013). Experimental pragmatics
+2003; Papafragou \& Tantalou, 2004; van Tiel, van Miltenburg, Zevakhina, \&
+Geurts, 2016; Tomlinson, Bailey, \& Bott, 2013). Experimental pragmatics
 is devoted to experimentally testing theories of how language is used in
@@
   implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
-  Tiel et al., 2014)?
+  van Tiel et al., 2016)?
 \item
@@
 scenarios, the story goes, if a participant responds \enquote{FALSE},
-that indicates that they computed a scalar implicature, eg to the effect
+that indicates that they computed a scalar implicature, e.g. to the effect
 of \enquote{Not all elephants are mammals} or \enquote{You didn't get
@@
 of the gumballs}.
+
+\change{Using the rate of \enquote{FALSE} responses in true but underinformative trials as a proxy for implicature calculation is relatively common in experimental pragmatics.
+For example, in the first study to investigate scalar implicatures experimentally, Noveck (2001) tested adults' and children's interpretations of the scalar items \emph{might} and \emph{some}.
+The dependent measure in Noveck (2001) was the rate of ``logically correct responses'', i.e.
+responding ``yes'' to statements such as \emph{Some giraffes have long necks} or \emph{There might be a parrot [in the box]} when there had to be a parrot in the box.
+He found that children show a higher rate of logically correct responses than adults, and concluded that children interpret scalar items \emph{some} and \emph{might} more logically (i.e.
+literally).
+Similarly in another landmark study, Papafragou and Musolino (2003) tested children and adults interpretation of the following set of scalar items: <\emph{two}, \emph{three}>, <\emph{some}, \emph{all}>, and <\emph{finish}, \emph{start}>.
+The dependent measure in this study was ``the proportion of \emph{No} responses to the puppet's [underinformative] statement''.
+The study concluded that ``while adults overwhelmingly rejected infelicitous descriptions, children almost never did so''.
+Furthermore, the study compared the implicature rates across scales and concluded that ``children also differed from from adults in that their rejection rate on the numerical scale was reliably higher than on the two other scales.'' In their final experiment, Papafragou and Musolino (2003) modified their task to invite scalar inferences more easily.
+They reported that this manipulation resulted in a significantly higher rejection rates.
+Based on these results, they concluded that children's ability to compute implicatures is affected by the type of scalar item as well as children's awareness of the task's goals.
+Since these early pioneering studies, many other studies have used the rate of false responses in underinformative trials as their dependent measure including Doran et al (2012), van Tiel et al (2016), Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), to name a few.}
 
@@
 
+\hypertarget{ref-Papafragou2003}{}
+Papafragou, A., \& Musolino, J. (2003). Scalar implicature: experiments at the semantics-pragmatics interface. \emph{Cognition}, \emph{86}(3), 253--282.
+
 \hypertarget{ref-Politzer-Ahles2013}{}
@@
 
-\hypertarget{ref-VanTiel2014}{}
-Tiel, B. van, Miltenburg, E. van, Zevakhina, N., \& Geurts, B. (2014).
-Scalar diversity. \emph{Journal of Semantics}.
-doi:\href{https://doi.org/10.1093/jos/ffu017}{10.1093/jos/ffu017}
-
 \hypertarget{ref-Tomlinson2013}{}
@@
 
+\hypertarget{ref-VanTiel2014}{}
+van Tiel, B., van Miltenburg, E., Zevakhina, N., \& Geurts, B. (2016).
+Scalar diversity. \emph{Journal of Semantics}.
+doi:\href{https://doi.org/10.1093/jos/ffu017}{10.1093/jos/ffu017}
+
 \change{\hypertarget{ref-Yildirim2016}{}

### 2018-11-02 writeup.Rmd

@@
 Rows marked with an asterisk in the evidence column do not contain 0 in the credible interval, thereby providing evidence for an effect.", booktabs = T)
+
+## auxiliary analysis of 3-way interaction
+
+# exhaustive trials
+sbq = implicature_rate %>%
+  filter(response_type %in% c("binary","quinary") & trial_type == "scalar") %>%
+  droplevels()
+m.simple <- glmer(implicature ~ definition*response_type - response_type + (1|card) + (1|participant), family="binomial", data=sbq)
+summary(m.simple)
+
+# scalar trials
+ebq = implicature_rate %>%
+  filter(response_type %in% c("binary","quinary") & trial_type == "exhaustive") %>%
+  droplevels()
+m.simple <- glmer(implicature ~ definition*response_type - response_type + (1|card) + (1|participant), family="binomial", data=ebq)
+summary(m.simple)
+
 ```

### 2018-11-02 manuscript.tex

@@
   Are scalar inferences default inferences, in the sense that they are
-  computed automatically in online processing and only cancelled by
-  context in a second effortful step if required by context (Bott \&
+  computed automatically in online processing and only cancelled in a second effortful step if required by context (Bott \&
   Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
@@
 
-\change{Using the rate of \enquote{FALSE} responses in true but underinformative trials as a proxy for implicature calculation is relatively common in experimental pragmatics.
-For example, in the first study to investigate scalar implicatures experimentally, Noveck (2001) tested adults' and children's interpretations of the scalar items \emph{might} and \emph{some}.
+\change{Using the proportion of \enquote{FALSE} responses on true but underinformative trials as a proxy for implicature rate is  common in experimental pragmatics.
+For example, in one of the first studies to investigate scalar implicatures experimentally, Noveck (2001) tested adults' and children's interpretations of the scalar items \emph{might} and \emph{some}.
 The dependent measure in Noveck (2001) was the rate of ``logically correct responses'', i.e.
 responding ``yes'' to statements such as \emph{Some giraffes have long necks} or \emph{There might be a parrot [in the box]} when there had to be a parrot in the box.
-He found that children show a higher rate of logically correct responses than adults, and concluded that children interpret scalar items \emph{some} and \emph{might} more logically (i.e.
+He found that children responded ``yes'' more frequently than adults, and concluded that children interpret scalar items \emph{some} and \emph{might} more logically (i.e.
 literally).
 Similarly in another landmark study, Papafragou and Musolino (2003) tested children and adults interpretation of the following set of scalar items: <\emph{two}, \emph{three}>, <\emph{some}, \emph{all}>, and <\emph{finish}, \emph{start}>.
-The dependent measure in this study was ``the proportion of \emph{No} responses to the puppet's [underinformative] statement''.
+The dependent measure in this study was the proportion of ``No'' responses to a puppet's underinformative] statement.
 The study concluded that ``while adults overwhelmingly rejected infelicitous descriptions, children almost never did so''.
-Furthermore, the study compared the implicature rates across scales and concluded that ``children also differed from from adults in that their rejection rate on the numerical scale was reliably higher than on the two other scales.'' In their final experiment, Papafragou and Musolino (2003) modified their task to invite scalar inferences more easily.
+Furthermore, the study compared  implicature rates across scales and concluded that ``children also differed from from adults in that their rejection rate on the numerical scale was reliably higher than on the two other scales.'' In their final experiment, Papafragou and Musolino (2003) modified their task to invite scalar inferences more easily.
 They reported that this manipulation resulted in a significantly higher rejection rates.
 Based on these results, they concluded that children's ability to compute implicatures is affected by the type of scalar item as well as children's awareness of the task's goals.
-Since these early pioneering studies, many other studies have used the rate of false responses in underinformative trials as their dependent measure including Doran et al (2012), van Tiel et al (2016), Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), to name a few.}
+Since these early pioneering studies, the rate of ``FALSE'' (or ``No'', ``Wrong'', ``Disagree'') responses on underinformative trials in truth-value judgment tasks has become a commonplace dependent measure (Doran et al (2012),  Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), inter alia.)}
 
@@
 implicature rates by condition and link.
-\change{It is immediately obvious that there is variability in inferred implicature rate.
+\change{It is immediately apparent that there is variability in inferred implicature rate.
 In particular, the Weak link appears to result in greater estimates of

### 2018-11-02 manuscript.tex
resubmission draft

@@
     94305-2150. E-mail:
-    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoudj@stanford.edu}}
+    \href{mailto:masoud_jasbi@fas.harvard.edu}{\nolinkurl{masoud_jasbi@fas.harvard.edu}}
   }
@@
 was used and only one of the animals was on the card, participants
-considered the guess \enquote{wrong} most of the time, but they often
-considered it \enquote{kinda wrong} or even \enquote{kinda right}. This
+considered the guess \enquote{wrong} most of the time (46\%), but they often
+considered it \enquote{kinda wrong} (32\%) or even \enquote{kinda right} (19\%). This
 suggests that perhaps participants considered the notion of a partially

### 2018-12-17 manuscript.tex
added paragraph on data analysis

@@
 
+\change{As suggested above, the quantitative predictions of our model will depend crucially on the values assigned to its free parameters - including (but not limited to) the probability thresholds and speaker costs of possible utterances.
+However, the values of these parameters can be estimated in a principled and informed manner through Bayesian statistical analysis of our experimental data.
+Samples from prior distributions over possible parameter values yield predicted patterns of response, which are then compared against empirically-observed response patterns in order to determine the a posteriori probability that these values are in fact the 'real' latent parameter values.
+The resulting posterior distributions are sampled from in turn, in order to parameterize the model and assess overall quantitative fit given the data.
+Though we leave a quantitative assessment of our model to future work (Waldon et al., in prep), we sketch the general procedure here to emphasize that the model is amenable to rigorous and data-driven evaluation.}
+
 One empirical problem is the pattern of responses we observed

### 2018-12-17 manuscript.tex
round 2 comment on weak/strong links

--- 2018-11-02 manuscript.tex
@@
     Correspondence concerning this article should be addressed to Masoud
-    Jasbi, Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA,
+    Jasbi, Department of Linguistics, Boylston Hall, Cambridge, MA,
     94305-2150. E-mail:
@@
 
+\change{We should add that researchers may vary with respect to which linking hypothesis (weak vs.
+strong) they consider more plausible.
+Many researchers would argue for the weak link.
+For them, judgments fall into three theoretically motivated categories: false, true but infelicitous, true and felicitous.
+Therefore, it is reasonable that false and true+felicitous responses occupy the ends of the scale while true-infelicitous responses occupy the mid-portion.
+In critical trials, participants judge underinformative statements that are true but infelicitous and therefore the mid portion of the scale can provide evidence for implicature computation.
+However, some other researchers argue that a strong link provides the best evidence for implicatures.
+They argue that if a participant computes an inference that results in an implicature-rich interpretation, their response in the task should show the commitment to the interpretation by judging the underinformative utterance as false or wrong.
+Any other response shows that they have not truly computed an implicature; i.e.
+they are not committed to the inference.
+So far these discussions have remained largely informal.
+In this paper we stay neutral with respect to the plausibility of each link and only aim to demonstrate the consequences of assuming them.}
+
 \section{Experiment}\label{experiment}

### 2018-12-19 manuscript.tex
updated manuscript

--- 2018-12-17 manuscript.tex
@@
 response options between participants and analyzed the results under
-different linking hypothesis.
+different linking hypothesis.\footnote{\change{Researchers may vary with respect to which linking hypothesis (Weak vs.~Strong, or others) they consider most plausible.
+Supporters of the Weak link may argue that there are three theoretically motivated categories of judgments: false, true but infelicitous, true and felicitous.
+Under such an account, it is plausible that false and true+felicitous responses occupy the ends of the false/true scale while true but infelicitous responses occupy the mid portion.
+On critical trials, participants judge underinformative statements that are true but infelicitous and therefore the mid portion of the scale can provide evidence for implicature computation.
+However, supporters of the Strong link may argue that if a participant computes an implicature, their response in the task should show the commitment to that interpretation by judging the underinformative utterance as false.
+Any other response shows that they have not truly computed an implicature.
+So far, these discussions have remained largely informal.
+In this paper we stay neutral with respect to the plausibility of each link and only aim to demonstrate the consequences of assuming them.}}
 

### 2018-12-19 manuscript.tex
second revisions

@@
 
-In addressing all of these questions, it has been \change{important} to obtain
+In addressing all of these questions, it has been important to obtain
 estimates of \emph{implicature rates}. For 1., implicature rates from
@@
 
-\change{Using the proportion of \enquote{FALSE} responses on true but underinformative trials as a proxy for implicature rate is  common in experimental pragmatics.
+Using the proportion of \enquote{FALSE} responses on true but underinformative trials as a proxy for implicature rate is  common in experimental pragmatics.
 For example, in one of the first studies to investigate scalar implicatures experimentally, Noveck (2001) tested adults' and children's interpretations of the scalar items \emph{might} and \emph{some}.
@@
 Based on these results, they concluded that children's ability to compute implicatures is affected by the type of scalar item as well as children's awareness of the task's goals.
-Since these early pioneering studies, the rate of ``FALSE'' (or ``No'', ``Wrong'', ``Disagree'') responses on underinformative trials in truth-value judgment tasks has become a commonplace dependent measure (Doran et al (2012),  Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), inter alia.)}
+Since these early pioneering studies, the rate of ``FALSE'' (or ``No'', ``Wrong'', ``Disagree'') responses on underinformative trials in truth-value judgment tasks has become a commonplace dependent measure (Doran et al (2012),  Geurts and Pouscoulous (2009), Potts, Lassiter, Levy, and Frank (2016), inter alia.)
 
@@
 tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
-Degen and Goodman (2014); Katsos and Bishop (2011); \change{Sikos et al (this issue)}). Indeed, the scalar
+Degen and Goodman (2014); Katsos and Bishop (2011); Sikos et al (this issue)). Indeed, the scalar
 implicature acquisition literature was shaken up when Katsos and Bishop
@@
 observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
-children to distribute \change{a small, a big, or a huge strawberry } to a puppet depending on
+children to distribute a small, a big, or a huge strawberry to a puppet depending on
 \enquote{how good the puppet said it}. The result was that children gave
-on average \change{smaller} strawberries to the puppet when he produced
+on average smaller strawberries to the puppet when he produced
 underinformative utterances compared to when he produced literally true
@@
 scalar implicature rates? Note that this way of asking the question
-\change{assumes} two things: first, that whatever participants are doing in a
+assumes two things: first, that whatever participants are doing in a
 truth value judgment task, the behavioral measure can be interpreted as
@@
   \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
-  vs. \enquote{disagree}--\enquote{agree}). \change{Studies vary in the labeling of scale points.}} In the binary case, this reproduces the standard
+  vs. \enquote{disagree}--\enquote{agree}). Studies vary in the labeling of scale points.} In the binary case, this reproduces the standard
 truth value judgment task. Figure \ref{fig:linkvisualization}
@@
 and Weak link. Figure \ref{fig:implicatureRatePlot} shows the resulting
-implicature rates by condition and link.
-\change{It is immediately apparent that there is variability in inferred implicature rate.
-In particular, the Weak link appears to result in greater estimates of
-implicature rates in tasks with four or five response options, compared to the Strong link. For the binary and ternary task, the assumed link appears to play a much smaller role.}
+implicature rates by condition and link. It is immediately apparent that there is variability in inferred implicature rate. In particular, the Weak link appears to result in greater estimates of
+implicature rates in tasks with four or five response options, compared to the Strong link. For the binary and ternary task, the assumed link appears to play a much smaller role.
 
@@
 Interval={[}10.64, 25.80{]}) resulted in greater
-implicature rates \change{with a weak link than with a strong link, but there was no evidence of a link-dependent difference in inferred implicature rate for the binary and ternary task}.
+implicature rates with a weak link than with a strong link, but there was no evidence of a link-dependent difference in inferred implicature rate for the binary and ternary task.
 Finally, there was a three-way interaction between
-link, trial type, and number of response options, \change{driven by the binary/quinary contrast} (Mean Estimate = -7.74,
+link, trial type, and number of response options, driven by the binary/quinary contrast (Mean Estimate = -7.74,
 95\% Credible Interval={[}-16.59, -0.16{]}).
-\change{Simple effects analysis on only the binary and and quinary trials, separately for the exhaustive and scalar subset of the data, revealed that the three-way interaction is driven by a different effect of number of response options under the Weak vs Strong link for the two inference types.
+Simple effects analysis on only the binary and and quinary trials, separately for the exhaustive and scalar subset of the data, revealed that the three-way interaction is driven by a different effect of number of response options under the Weak vs Strong link for the two inference types.
 Specifically, on exhaustive trials, number of response options (2 vs.~5) only resulted in greater implicature rates under the Weak ($\beta$ = .2, $p <$ .0001), but not the Strong link ($\beta$ = -.8, $p <$ .82).
-In contrast, on scalar trials, number of response options (2 vs.~5) resulted in greater implicature rates under the Weak ($\beta$ = 3.6, $p <$ .005) link, and in lower implicature rates under the Strong link ($\beta$ = -4.0, $p <$ .0007).}
-
-\change{In sum,} both number of response options and link
-affected the inferred implicature rate\change{, as did the type of inference (exhaustive vs.~scalar)}.
+In contrast, on scalar trials, number of response options (2 vs.~5) resulted in greater implicature rates under the Weak ($\beta$ = 3.6, $p <$ .005) link, and in lower implicature rates under the Strong link ($\beta$ = -4.0, $p <$ .0007).
+
+In sum, both number of response options and link
+affected the inferred implicature rate, as did the type of inference (exhaustive vs.~scalar).
 
@@
 as a function of an individual's mental representation of a cooperative
-\change{speaker} (\(S_1\) in the language of RSA) rather than of a pragmatic
-listener who interprets utterances (\(P_{L_1}\)).\footnote{\change{Degen and Goodman (2014) argue that sentence verification is more plausibly construed as a production task rather than as an interpretation task because participants, unlike in natural language comprehension, are provided with the ground truth about the state of the world that a speaker is describing.
+speaker (\(S_1\) in the language of RSA) rather than of a pragmatic
+listener who interprets utterances (\(P_{L_1}\)).\footnote{Degen and Goodman (2014) argue that sentence verification is more plausibly construed as a production task rather than as an interpretation task because participants, unlike in natural language comprehension, are provided with the ground truth about the state of the world that a speaker is describing.
 Thus, participants are in essence being asked to assess the quality of a speaker's utterance.
-In contrast, Degen and Goodman argue, true interpretation tasks are characterized by the listener inferring what the state of the world is that the speaker is describing, for instance by selecting from one of multiple interpretation options.}} In their paper, Degen
-\& Goodman \change{show} that sentence verification tasks are relatively more
-sensitive to contextual \change{features like} the
+In contrast, Degen and Goodman argue, true interpretation tasks are characterized by the listener inferring what the state of the world is that the speaker is describing, for instance by selecting from one of multiple interpretation options.} In their paper, Degen
+\& Goodman show that sentence verification tasks are relatively more
+sensitive to contextual features like the
 Question Under Discussion than are sentence interpretation tasks, and
@@
 one's interlocutors (Fine, Jaeger, Farmer, \& Qian, 2013; Kleinschmidt
-\& Jaeger, 2015; \change{Yildirim, Degen, Tanenhaus, \& Jaeger, 2016)}.
-
-However, if we should like to keep the above \change{simplifying} assumptions in place, then
+\& Jaeger, 2015; Yildirim, Degen, Tanenhaus, \& Jaeger, 2016).
+
+However, if we should like to keep the above simplifying assumptions in place, then
 this linking hypothesis commits us to explaining variation in the data in terms
@@
 threshold value is sampled from this distribution.
-\change{By  allowing values of \(\theta\) to vary stochastically in this way, we can capture that \(S_1\)(u \textbar{} s) can fall both above and below \(\theta\) for a given
-participant.}
-
-\change{The model in its present form already captures an interesting asymmetry in inferred implicature rates between exhaustive and scalar trials of the experiment: note specifically (c.f.
+By allowing values of \(\theta\) to vary stochastically in this way, we can capture that \(S_1\)(u \textbar{} s) can fall both above and below \(\theta\) for a given
+participant.
+
+The model in its present form already captures an interesting asymmetry in inferred implicature rates between exhaustive and scalar trials of the experiment: note specifically (c.f.
 Figure 8) that inferred implicature rates are greater in the binary and ternary conditions for scalar trials over exhaustive trials.
@@
 Assuming noisy  $\theta$ values centered around N, participants are expected to respond `Right' more frequently on exhaustive than on scalar trials, which is precisely what is observed.
-Recall that these probabilities were derived via the simplifying assumption of uniform cost on utterances; in fact, adding cost to relatively complex disjunctive sentences over simple declarative sentences only predicts a more pronounced asymmetry in the experimentally-observed direction.}
+Recall that these probabilities were derived via the simplifying assumption of uniform cost on utterances; in fact, adding cost to relatively complex disjunctive sentences over simple declarative sentences only predicts a more pronounced asymmetry in the experimentally-observed direction.
 
@@
 or pragmatic listener) probability distributions provided by an RSA
-model. We \change{leave this systematic, quantitative} investigation to future work. For now we
-emphasize that \change{explicit computational modeling of behavioral responses is a tool that is  available to researchers in experimental
+model. We leave this systematic, quantitative investigation to future work. For now we
+emphasize that explicit computational modeling of behavioral responses is a tool that is  available to researchers in experimental
 pragmatics. While using the RSA framework as the modeling tool requires revising traditional assumptions about the nature of scalar
@@
 One need not adopt the RSA framework as the tool for hypothesizing and testing the link between theoretical constructs and behavior in pragmatic experiments.
-However, the empirical findings we have reported here---that the inferences researchers draw about ``implicature rate'' are volatile and depend on various features of the paradigm and the linking hypothesis employed--- strongly suggest that experimental pragmatics  as a field must engage more seriously with the foundational questions of what we are measuring in the experiments we run.}
+However, the empirical findings we have reported here---that the inferences researchers draw about ``implicature rate'' are volatile and depend on various features of the paradigm and the linking hypothesis employed--- strongly suggest that experimental pragmatics  as a field must engage more seriously with the foundational questions of what we are measuring in the experiments we run.
 
@@
 
-\change{\hypertarget{ref-Sikos2019}{}
-Sikos, L., Kim, M., \& Grodner, D.J. (in press). Social context modulates tolerance for pragmatic violations in binary but not graded judgments. \emph{Frontiers in Psychology}.}
+\hypertarget{ref-Sikos2019}{}
+Sikos, L., Kim, M., \& Grodner, D.J. (in press). Social context modulates tolerance for pragmatic violations in binary but not graded judgments. \emph{Frontiers in Psychology}.
 
@@
 
-\change{\hypertarget{ref-Yildirim2016}{}
-Yildirim, I., Degen, J., Tanenhaus, M.K., \& Jaeger, T.F. (2016). Talker-specificity and adaptation in quantifier interpretation. \emph{Journal of Memory and Language}, \emph{87}, pp. 128-143.}
+\hypertarget{ref-Yildirim2016}{}
+Yildirim, I., Degen, J., Tanenhaus, M.K., \& Jaeger, T.F. (2016). Talker-specificity and adaptation in quantifier interpretation. \emph{Journal of Memory and Language}, \emph{87}, pp. 128-143.
 
